### 2024-02-15 tex/main.tex
Init

%3 May 2012
\documentclass[10pt,reqno]{amsart}

\setlength{\topmargin}{0cm}
\setlength{\textheight}{21cm}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{.25in}

\pagestyle{plain}
\usepackage{stmaryrd}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{showkeys}
\usepackage{enumerate}
\usepackage{subfig}
\usepackage{enumitem} 
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage[]{algorithm2e}
\usepackage[capitalize]{cleveref}
\usepackage{placeins}
\crefname{equation}{}{}
\usepackage{verbatim}

%\usepackage{graphicx}
%% expansion of width
\textwidth=15.7cm
\textheight=22.5cm
\parskip=3pt
\parindent=8mm
\oddsidemargin=2mm
\evensidemargin=0mm
\topmargin=-0.5cm
\marginparwidth=1cm
%% definition of theorem-type environments
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rmk}{Remark}
\newtheorem{exa}{Example}
\newtheorem{assum}{Assumption}
\numberwithin{equation}{section}
\newcommand{\bel}{\begin{equation} \label}
\newcommand{\ee}{\end{equation}}
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\newcommand{\jump}[1]{\llbracket#1\rrbracket}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\beas}{\begin{eqnarray*}}
\newcommand{\eeas}{\end{eqnarray*}}
\newcommand{\pd}{\partial}
\newcommand{\mdiv}[1]{\ensuremath{\mathrm{div} \left( #1 \right)}}
\newcommand{\dd}{\mbox{d}}

\newcommand{\ep}{\varepsilon}
\newcommand{\la}{\lambda}
\newcommand{\va}{\varphi}
\newcommand{\ppp}{\partial}
\newcommand{\chch}{\chi_{\eta}}
\newcommand{\walpha}{\widetilde{\alpha}}
\newcommand{\wbeta}{\widetilde{\beta}}

\newcommand{\re}{\mathfrak R}

\newcommand{\im}{\mathfrak I}
\newcommand{\pdif}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\ppdif}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}} 
\newcommand{\N}{\mathbb{N}} 
\newcommand{\ooo}{\overline}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\v}{\mathbf{v}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\RR}{\mathbf{R}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\G}{\mathbf{G}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\Hin}{\mathcal{H}_{\mathrm{in},T_0}}
\newcommand{\Gi}{S_{\mathrm{in}}}
\newcommand{\Go}{S_{\mathrm{out}}}
\newcommand{\dom}{\mathrm{Dom}}

\newcommand{\sdd}{\mathcal{E}}

\renewcommand{\baselinestretch}{1.5}
%
\renewcommand{\div}{\mathrm{div}\,}  %div
\newcommand{\grad}{\mathrm{grad}\,}  %grad
\newcommand{\rot}{\mathrm{rot}\,}  %rot

\newcommand{\supp}{\mathrm{supp}\,}  %supp
%\newcommand{\span}{\mathrm{span}\,} %span

\allowdisplaybreaks
%%  item
\renewcommand{\theenumi}{\arabic{enumi}}
\renewcommand{\labelenumi}{(\theenumi)}
\renewcommand{\theenumii}{\alph{enumii}}
\renewcommand{\labelenumii}{(\theenumii)}
\def\epsilon{\varepsilon}
%\def\phi {\varphi}
\def \la {{\lambda}}
\def \a {{\alpha}}
\def\t{\theta}
\def\fh{\frac{1}{h}}

\DeclareMathOperator{\dis}{dist}

\newcommand{\tnorm}[1]{\vert\hspace{-0.3mm}\Vert#1\Vert\hspace{-0.3mm}\vert}

\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
% pour les normes
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}

\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
% pour les normes
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\def\thefootnote{{}}

\newcommand{\HOX}[1]{\marginpar{\footnotesize #1}}

\newcommand{\gammaGLS}{\gamma_{\text{GLS}}}
\newcommand{\gammaCIP}{\gamma}

\newcommand{\dT}{\mathrm{d}t}
\newcommand{\dX}{\mathrm{d}x}
\newcommand{\dS}{\mathrm{d}S}

\newcommand{\STdom}{Q}

\newcommand{\STdata}{\omega_T}
\newcommand{\STdataDisc}{\underline{\omega}_T}
\newcommand{\SemiDiscSpace}{\mathcal{W}_h}
\newcommand{\FullyDiscSpace}{W}

%\newcommand{\FullyDiscrSpaceDisc}[2]{ W_{ {#1},{#2}}^{ \text{dc} } }
%\newcommand{\FullyDiscrSpaceCont}[2]{ W_{ {#1},{#2}}^{ \text{c}  } }
%\newcommand{\ProdFullyDiscrSpaceDisc}[2]{  \mathcal{W}_{ {#1},{#2} }^{ \text{dc} } }
%\newcommand{\ProdFullyDiscrSpaceCont}[1]{  \mathcal{W}_{ {#1} }^{ \text{c} } }

\newcommand{\SemiDiscrSpace}[1]{ W^{ {#1}}_{h} }
\newcommand{\ProdSemiDiscrSpace}[1]{ \mathcal{W}^{ {#1} }_{h} }
\newcommand{\FullyDiscrSpace}[2]{ W^{ {#1},{#2}}_{h, \Delta t  } }
\newcommand{\FullyDiscrSpaceHat}[2]{ \hat{W}^{ {#1},{#2}}_{h, \Delta t  } }
\newcommand{\ProdFullyDiscrSpace}[2]{ \mathcal{W}^{ {#1},{#2}}_{h, \Delta t  } }

\DeclarePairedDelimiterX{\inp}[2]{(}{)}{#1, #2}
\newcommand{\tangular}[1]{ \llbracket\kern-0.5ex|#1|\kern-0.5ex\rrbracket} 
%\newcommand{\jump}[1]{\llbracket#1\rrbracket}
\newcommand{\avg}[1]{ \{\!\!\{#1\}\!\!\}}

\newboolean{includeextras}
\ifdefined\withextras
\setboolean{includeextras}{true}
\else
\setboolean{includeextras}{false}
\fi

\newcommand{\putextra}[1]{\ifthenelse{\boolean{includeextras}}{#1}{}}

%%% TvB: Added for plots, some might be redundant ##

%------------------------- Added for Plots ----
% Tikz package
\usepackage{tikz}
\usepackage{pgfplots,pgfplotstable}
\usepgfplotslibrary{colorbrewer,groupplots}
\usepackage{caption}
\pgfplotsset{compat=1.18}

\pgfplotsset{
% initialize Set1-5:
cycle list/Set1-5,
% combine it with ’mark list*’:
cycle multiindex* list={
mark list*\nextlist
Set1-5\nextlist
},
}

\pgfplotsset{
    discard if not/.style 2 args={
        x filter/.append code={
            \edef\tempa{\thisrow{#1}}
            \edef\tempb{#2}
            \ifx\tempa\tempb
            \else
                \def\pgfmathresult{inf}
            \fi
        }
    }
}

%%%

\title{Data assimilation for the wave equation with discontinuous coefficients}
\author{Erik Burman, Janosch Preuss and Tim van Beeck}

\date{\today}
\begin{document}
\maketitle

\section{Introduction}

\section{Numerical experiments}

\end{document}

### 2024-02-15 tex/pgfplt.tex
Init

\usepackage{stmaryrd} %for double brackets
% plots
\usepackage{pgf,tikz}
\usetikzlibrary{spy,matrix, calc, arrows,shapes,decorations}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning,arrows,calc,decorations.markings,math,arrows.meta}
\usepackage{pgfplots} 
\usepgfplotslibrary{groupplots}
% tabels
\usepackage{csvsimple} 
%\usepackage{floatrow}
\usepackage{siunitx} %for scientific numbers \num
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}

%%%%% PGF Plot macros

\pgfplotscreateplotcyclelist{paulcolors}{%
violet,every mark/.append style={solid,fill=violet},mark=square*,very thick,mark size=3pt\\%
teal,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
violet,densely dashed,every mark/.append style={solid,fill=violet},mark=square*,very thick,mark size=3pt\\%
teal,densely dashed,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,densely dashed,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
violet,dash dot,every mark/.append style={solid,fill=violet},mark=square*,very thick,mark size=3pt\\%
teal,dash dot,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,dash dot,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
%cyan,every mark/.append style={fill=cyan},mark=star\\%
}
\pgfplotscreateplotcyclelist{paulcolors2}{%
teal,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
teal,densely dashed,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,densely dashed,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
teal,dash dot,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
orange,dash dot,every mark/.append style={solid,fill=orange},mark=diamond*,very thick,mark size=3pt\\%
}
\pgfplotscreateplotcyclelist{paulcolors1}{%
teal,every mark/.append style={solid,fill=teal},mark=*,very thick,mark size=3pt\\%
}
\pgfplotscreateplotcyclelist{paulcolorsfill}{%
teal,fill=teal,fill opacity=0.5,thick\\
orange,fill=orange,fill opacity=0.5,thick\\
violet,fill=violet,fill opacity=0.5,thick\\
}

\pgfplotscreateplotcyclelist{barcolors}{%
teal,fill=teal,fill opacity=0.5,thick\\
teal,fill=teal,fill opacity=0.5,thick,postaction={pattern=crosshatch dots,pattern color=teal}\\
orange,fill=orange,fill opacity=0.5,thick\\
orange,fill=orange,fill opacity=0.5,thick,postaction={pattern=crosshatch dots, pattern color=orange}\\
}

\pgfplotscreateplotcyclelist{barcolors2}{%
teal,fill=teal,fill opacity=0.5,thick\\
orange,fill=orange,fill opacity=0.5,thick\\
teal,fill=teal,fill opacity=0.5,thick,postaction={pattern=crosshatch dots,pattern color=teal}\\
orange,fill=orange,fill opacity=0.5,thick,postaction={pattern=crosshatch dots, pattern color=orange}\\
}

\pgfplotscreateplotcyclelist{barcolors3}{%
teal,fill=teal,fill opacity=0.7,thick,postaction={pattern=crosshatch dots,pattern color=teal}\\
orange,fill=orange,fill opacity=0.7,thick,postaction={pattern=crosshatch dots, pattern color=orange}\\
}

\pgfplotsset{
    discard if not/.style 2 args={
        x filter/.append code={
            \edef\tempa{\thisrow{#1}}
            \edef\tempb{#2}
            \ifx\tempa\tempb
            \else
                \def\pgfmathresult{inf}
            \fi
        }
    }
}
\pgfplotsset{compat=1.16}%1.16 %avoid warning

\pgfplotsset{tick label style={font=\small},label style={font=\small},legend style={font=\small},}
\pgfplotsset{ width=.49\linewidth}

%%% START MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.
\newcommand{\logLogSlopeTriangle}[5]
{
    % #1. Relative offset in x direction.
    % #2. Width in x direction, so xA-xB.
    % #3. Relative offset in y direction.
    % #4. Slope d(y)/d(log10(x)).
    % #5. Plot options.

    \pgfplotsextra
    {
        \pgfkeysgetvalue{/pgfplots/xmin}{\xmin}
        \pgfkeysgetvalue{/pgfplots/xmax}{\xmax}
        \pgfkeysgetvalue{/pgfplots/ymin}{\ymin}
        \pgfkeysgetvalue{/pgfplots/ymax}{\ymax}

        % Calculate auxilliary quantities, in relative sense.
        \pgfmathsetmacro{\xArel}{#1}
        \pgfmathsetmacro{\yArel}{#3}
        \pgfmathsetmacro{\xBrel}{#1-#2}
        \pgfmathsetmacro{\yBrel}{\yArel}
        \pgfmathsetmacro{\xCrel}{\xArel}
        %\pgfmathsetmacro{\yCrel}{ln(\yC/exp(\ymin))/ln(exp(\ymax)/exp(\ymin))} % REPLACE THIS EXPRESSION WITH AN EXPRESSION INDEPENDENT OF \yC TO PREVENT THE 'DIMENSION TOO LARGE' ERROR.

        \pgfmathsetmacro{\lnxB}{\xmin*(1-(#1-#2))+\xmax*(#1-#2)} % in [xmin,xmax].
        \pgfmathsetmacro{\lnxA}{\xmin*(1-#1)+\xmax*#1} % in [xmin,xmax].
        \pgfmathsetmacro{\lnyA}{\ymin*(1-#3)+\ymax*#3} % in [ymin,ymax].
        \pgfmathsetmacro{\lnyC}{\lnyA-#4*(\lnxA-\lnxB)}
        \pgfmathsetmacro{\yCrel}{\lnyC-\ymin)/(\ymax-\ymin)} % THE IMPROVED EXPRESSION WITHOUT 'DIMENSION TOO LARGE' ERROR.

        % Define coordinates for \draw. MIND THE 'rel axis cs' as opposed to the 'axis cs'.
        \coordinate (A) at (rel axis cs:\xArel,\yArel);
        \coordinate (B) at (rel axis cs:\xBrel,\yBrel);
        \coordinate (C) at (rel axis cs:\xCrel,\yCrel);

        % Draw slope triangle.
        \draw[#5]   (A)-- node[pos=0.5,anchor=north] {}
                    (B)-- 
                    (C)-- node[pos=0.5,anchor=west] {#4}
                    cycle;
    }
}
%%% END MACRO FOR ANNOTATION OF TRIANGLE WITH SLOPE %%%.

\usepackage{listings}
%\usepackage[lined,commentsnumbered]{algorithm2e}
\usepackage[plain]{algorithm}
%\usepackage{algpseudocodex}

\definecolor{maroon}{cmyk}{0, 0.87, 0.68, 0.32}
\definecolor{halfgray}{gray}{0.55}
\definecolor{ipython_frame}{RGB}{207, 207, 207}
\definecolor{ipython_bg}{RGB}{247, 247, 247}
\definecolor{ipython_red}{RGB}{186, 33, 33}
\definecolor{ipython_green}{RGB}{0, 128, 0}
\definecolor{ipython_cyan}{RGB}{64, 128, 128}
\definecolor{ipython_purple}{RGB}{170, 34, 255}

\lstset{
    breaklines=true,
    %
    extendedchars=true,
    literate=
    {á}{{\'a}}1 {é}{{\'e}}1 {í}{{\'i}}1 {ó}{{\'o}}1 {ú}{{\'u}}1
    {Á}{{\'A}}1 {É}{{\'E}}1 {Í}{{\'I}}1 {Ó}{{\'O}}1 {Ú}{{\'U}}1
    {à}{{\`a}}1 {è}{{\`e}}1 {ì}{{\`i}}1 {ò}{{\`o}}1 {ù}{{\`u}}1
    {À}{{\`A}}1 {È}{{\'E}}1 {Ì}{{\`I}}1 {Ò}{{\`O}}1 {Ù}{{\`U}}1
    {ä}{{\"a}}1 {ë}{{\"e}}1 {ï}{{\"i}}1 {ö}{{\"o}}1 {ü}{{\"u}}1
    {Ä}{{\"A}}1 {Ë}{{\"E}}1 {Ï}{{\"I}}1 {Ö}{{\"O}}1 {Ü}{{\"U}}1
    {â}{{\^a}}1 {ê}{{\^e}}1 {î}{{\^i}}1 {ô}{{\^o}}1 {û}{{\^u}}1
    {Â}{{\^A}}1 {Ê}{{\^E}}1 {Î}{{\^I}}1 {Ô}{{\^O}}1 {Û}{{\^U}}1
    {œ}{{\oe}}1 {Œ}{{\OE}}1 {æ}{{\ae}}1 {Æ}{{\AE}}1 {ß}{{\ss}}1
    {ç}{{\c c}}1 {Ç}{{\c C}}1 {ø}{{\o}}1 {å}{{\r a}}1 {Å}{{\r A}}1
    {€}{{\EUR}}1 {£}{{\pounds}}1
}

\lstdefinelanguage{iPython}{
    %morekeywords={access,and,break,class,continue,def,del,elif,else,except,exec,finally,for,from,global,if,import,in,is,lambda,not,or,pass,print,raise,return,try,while},%
    %
    % Built-ins
    morekeywords=[2]{abs,all,any,basestring,bin,bool,bytearray,callable,chr,classmethod,cmp,compile,complex,delattr,dict,dir,divmod,enumerate,eval,execfile,file,filter,float,format,frozenset,getattr,globals,hasattr,hash,help,hex,id,input,int,isinstance,issubclass,iter,len,list,locals,long,map,max,memoryview,min,next,object,oct,open,ord,pow,property,range,raw_input,reduce,reload,repr,reversed,round,set,setattr,slice,sorted,staticmethod,str,sum,super,tuple,type,unichr,unicode,vars,xrange,zip,apply,buffer,coerce,intern},%
    %
    sensitive=true,%
    morecomment=[l]\#,%
    morestring=[b]',%
    morestring=[b]",%
    %
    morestring=[s]{'''}{'''},% used for documentation text (mulitiline strings)
    morestring=[s]{"""}{"""},% added by Philipp Matthias Hahn
    %
    morestring=[s]{r'}{'},% `raw' strings
    morestring=[s]{r"}{"},%
    morestring=[s]{r'''}{'''},%
    morestring=[s]{r"""}{"""},%
    morestring=[s]{u'}{'},% unicode strings
    morestring=[s]{u"}{"},%
    morestring=[s]{u'''}{'''},%
    morestring=[s]{u"""}{"""},%
    %
    % {replace}{replacement}{lenght of replace}
    % *{-}{-}{1} will not replace in comments and so on
    literate=
    {á}{{\'a}}1 {é}{{\'e}}1 {í}{{\'i}}1 {ó}{{\'o}}1 {ú}{{\'u}}1
    {Á}{{\'A}}1 {É}{{\'E}}1 {Í}{{\'I}}1 {Ó}{{\'O}}1 {Ú}{{\'U}}1
    {à}{{\`a}}1 {è}{{\`e}}1 {ì}{{\`i}}1 {ò}{{\`o}}1 {ù}{{\`u}}1
    {À}{{\`A}}1 {È}{{\'E}}1 {Ì}{{\`I}}1 {Ò}{{\`O}}1 {Ù}{{\`U}}1
    {ä}{{\"a}}1 {ë}{{\"e}}1 {ï}{{\"i}}1 {ö}{{\"o}}1 {ü}{{\"u}}1
    {Ä}{{\"A}}1 {Ë}{{\"E}}1 {Ï}{{\"I}}1 {Ö}{{\"O}}1 {Ü}{{\"U}}1
    {â}{{\^a}}1 {ê}{{\^e}}1 {î}{{\^i}}1 {ô}{{\^o}}1 {û}{{\^u}}1
    {Â}{{\^A}}1 {Ê}{{\^E}}1 {Î}{{\^I}}1 {Ô}{{\^O}}1 {Û}{{\^U}}1
    {œ}{{\oe}}1 {Œ}{{\OE}}1 {æ}{{\ae}}1 {Æ}{{\AE}}1 {ß}{{\ss}}1
    {ç}{{\c c}}1 {Ç}{{\c C}}1 {ø}{{\o}}1 {å}{{\r a}}1 {Å}{{\r A}}1
    {€}{{\EUR}}1 {£}{{\pounds}}1
    %
    {^}{{{\color{ipython_purple}\^{}}}}1
    {=}{{{\color{ipython_purple}=}}}1
    %
    {+}{{{\color{ipython_purple}+}}}1
    {*}{{{\color{ipython_purple}$^\ast$}}}1
    {/}{{{\color{ipython_purple}/}}}1
    %
    {+=}{{{+=}}}1
    {-=}{{{-=}}}1
    {*=}{{{$^\ast$=}}}1
    {/=}{{{/=}}}1,
    literate=
    *{-}{{{\color{ipython_purple}-}}}1
     {?}{{{\color{ipython_purple}?}}}1,
    %
    identifierstyle=\color{black}\ttfamily,
    commentstyle=\color{ipython_cyan}\ttfamily,
    stringstyle=\color{ipython_red}\ttfamily,
    keepspaces=true,
    showspaces=false,
    showstringspaces=false,
    %
    rulecolor=\color{ipython_frame},
    %frame=single,
    %frameround={t}{t}{t}{t},
    framexleftmargin=0mm,
    numbers=left,
    numberstyle=\tiny\color{halfgray},
    numbersep=1mm,
    %
    %
    xleftmargin=1mm,
    %backgroundcolor=\color{ipython_bg},
    %   extendedchars=true,
    basicstyle=\scriptsize,
    keywordstyle=\color{ipython_green}\ttfamily,
}

\lstdefinestyle{trefftzy}{
    language=iPython,
    emptylines=1,
    breaklines=true,
    basicstyle=\footnotesize\ttfamily\color{black},    
    moredelim=**[is][\color{teal}]{<}{>},
    moredelim=**[is][\color{purple}]{'}{'},
}

### 2024-02-15 tex/main.tex
some notes

@@
 \usepackage{verbatim}
+\usepackage{bbm}
 
@@
 
+\newcommand{\wop}{\square_c}
+
 \newcommand{\tnorm}[1]{\vert\hspace{-0.3mm}\Vert#1\Vert\hspace{-0.3mm}\vert}
@@
 
+\newcommand{\Uh}{\underline{\mathbf{U}}_h}
+\newcommand{\Yh}{\underline{\mathbf{Y}}_h}
+\newcommand{\Zh}{\underline{\mathbf{Z}}_h}
+\newcommand{\Wh}{\underline{\mathbf{W}}_h}
+
+\newcommand{\ul}{\underline{u}}
+\newcommand{\yl}{\underline{y}}
+\newcommand{\zl}{\underline{z}}
+\newcommand{\wl}{\underline{w}}
+
+\newcommand{\Sud}{S^{\uparrow \downarrow}_{\Delta t}}
+
+\newcommand{\dt}{\partial_t}
+\newcommand{\dtt}{\partial_t^2}
+
 %%% TvB: Added for plots, some might be redundant ##
@@
 \section{Introduction}
+\noindent Let $\Omega \subset \mathbb{R}^d$ be a bounded domain such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
+We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma = \Omega \setminus (\Omega_1 \cup \Omega_2)$, but constant in time.
+\noindent In this article, we consider the following problem: find $u \in Q \rightarrow \mathbb{R}$ such that 
+\begin{subequations}
+    \begin{alignat}{2}
+        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \\
+        u &= u_{\omega} &&\text{ in } \omega_T,
+    \end{alignat}    
+\end{subequations}
+where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega}$ is the known data.
+
+\noindent The continuous problem has been studied in \cite{Filippas22}. In particular, the following result has been shown:
+\begin{thm}[Thm. 1.1 of \cite{Filippas22}]\label{thm:filippas}
+    For any nonempty subset $\omega \subset \Omega$ and $T > \text{dist}(\Omega,\omega)$, there exists $C,\kappa,\mu_0$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
+one has for any $\mu \ge \mu_0$ that
+    \begin{equation}
+        \Vert (u_0,u_1) \Vert_{L^2 \times H^{-1}} \le C e^{\kappa \mu} \Vert u \Vert_{L^2(\omega_T)} + \frac{C}{\mu} \Vert (u_0,u_1) \Vert_{H^1 \times L^2}. 
+    \end{equation}
+\end{thm}
+
+\section{Discretization (fully discrete \& dG in time)} 
+\noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
+We introduce the bilinear form 
+\begin{equation}
+    A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \left\{ (\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} - (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \right\}
+\end{equation} 
+and the Lagrangian 
+\begin{align*}
+    \cL_h (\Uh, \Zh) := \frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) - \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh).
+\end{align*}
+To define the stabilization terms $S_h$ and $S_h^\ast$, we introduce the following terms: 
+\begin{align*}
+    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c(x)^2 \nabla \ul_1}, \jump{c(x)^2 \nabla \wl_1})_F \ \dT, \\
+    I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \\
+    G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c(x)^2 \nabla \ul_1),\dt \wl_2 -\div( c(x)^2 \nabla \wl_1))_K \ \dT, \\
+    R(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
+\end{align*}
+Then, we define the primal stabilizer as 
+\begin{equation}
+    S_h(\Uh,\Wh) := J(\Uh,\Wh) + I_0(\Uh,\Wh) + G(\Uh,\Wh) + R(\Uh,\Wh), 
+\end{equation}
+and the dual stabilizer through 
+\begin{equation}
+    S_h^\ast(\Yh,\Zh) := \sum_{n = 0}^{N-1} \left\{ (\yl_1,\zl_1)_{Q^n} + a(\yl_1,\zl_1)_{Q^n} + (\yl_2,\zl_2)_{Q^n} + h^{-1} (\yl_1,\zl_1)_{\Sigma^n} \right\}.
+\end{equation}
+The stabilization term $\Sud$ imposes regularity on the discontinuities in time and is defined as 
+\begin{equation}
+    \Sud (\Uh,\Wh) := \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) + \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh),
+\end{equation}
+where 
+\begin{align*}
+    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c(x)^2 \jump{\nabla \ul_1^n},c(x)^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
+    \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
+\end{align*}
+
+\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in ...$ such that 
+\begin{alignat*}{2}
+    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in ... \\
+    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in ... 
+\end{alignat*}
+For convenience, we introduce
+\begin{equation}
+    \begin{aligned}
+        B[(\Uh,\Zh),(\Wh,\Yh)] := &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
+        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh),
+    \end{aligned}
+\end{equation}
+such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in ...$ such that
+\begin{equation}
+    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in ...
+\end{equation}
+
+\section{Analysis}
+\noindent We define the norms \textbf{has to be shown that they are indeed norms!} 
+\begin{equation}
+    \tnorm{ (\Uh,\Zh) }^2 := \gamma \vert \Uh \vert^2_{S_h} + \vert \Uh \vert^2_{\uparrow \downarrow} + \Vert \ul_1 \Vert^2_{\omega_T} + \gamma^{\ast} \Vert \Zh \Vert^2_{S_h^\ast},
+\end{equation}
+where $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ are the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
+\begin{equation}
+    \vert \Uh \vert^2_{S_h} := S_h(\Uh,\Uh), \quad \vert \Uh \vert^2_{\uparrow \downarrow} := \Sud(\Uh,\Uh), \quad \Vert \Zh \Vert^2_{S_h^{\ast}} := S_h^{\ast}(\Zh,\Zh).
+\end{equation}
+
+We modify the steps from \cite{BP24} to show that $\tnorm{(\cdot,\cdot)}$ is indeed a norm.
+
+\begin{lem}
+    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on ... 
+\end{lem}
+
+\begin{proof}
+    It suffices to show that $\tnorm{(\Uh,\Zh)} = 0$ implies that $\Uh=\Zh= 0$.
+We first note that $\vert \Uh \vert_{\uparrow \downarrow} = 0$ immediately implies that $(\ul_1,\ul_2) \in [H^1(Q)]^2$.
+Furthermore, by definition of $\tnorm{(\cdot,\cdot)}$ and definition the stabilization terms $S_h$ and $S_h^{\ast}$, we have that $\Zh = 0$, $\ul_1 \vert_{\Sigma} = 0$, $\ul_1 \vert_{\omega_T} = 0$ and $\dt \ul_1 = \ul_2$.
+Similar to \cite[Lem.
+2.1]{BP24}, we have with partial integration that
+    \begin{align*}
+        \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} &:= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c(x)^2 \nabla \ul_1 \nabla y \right\}  \\
+        &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c(x)^2 \nabla \ul_1),y)_{K} \ \dT \\
+        &\qquad + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c(x)^2 \nabla \ul_1}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\}.
+    \end{align*}
+    Thus it follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
+It directly follows from \ref{thm:filippas} that the initial data are zero.
+{\color{gray} Thats means that $\ul_1$ solves the wave equation with rhs zero, zero initial data, is zero on the boundary and zero on $\omega$...
+should enough to say that $\ul_1 = 0$ everywhere!?}
+\end{proof}
+
+\noindent Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, the inf-sup stability of $B$ on ...
+is a direct consequence of the previous lemma, i.e.
+there exists a constant $C>0$ such that
+\begin{equation}
+    \sup_{(\Wh,\Yh) \in ...} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C \tnorm{(\Uh,\Zh)}.
+\end{equation}
 
 \section{Numerical experiments}
+\subsection{Example in one space dimension}
+We consider the example from \cite{BDE22} with domain $\Omega = [0,1]$ that is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
+Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
+With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by
+\begin{equation}
+    u(x,t) = \begin{cases}
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) 0- u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
+      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), x \in \Omega_2.
+    \end{cases}
+\end{equation}
+
+\subsection{Example in two space dimensions}
+
+\bibliographystyle{alpha}
+\bibliography{references}
 

### 2024-02-19 tex/main.tex
Update draft

@@
     \begin{alignat}{2}
-        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \\
-        u &= u_{\omega} &&\text{ in } \omega_T,
+        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \label{eq:waveEquation} \\ 
+        u &= u_{\omega} &&\text{ in } \omega_T, \\ \label{eq:DataMatch}
     \end{alignat}    
@@
 \noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
+Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. We define the $H^1$-conforming finite element space 
+\begin{equation}
+    V_h^k := \{ v \in H^1(\Omega) : v \vert_{K} \in \mathcal{P}^k(K) \ \forall K \in \mathcal{T}_h \},
+\end{equation}
+where $\mathcal{P}^k(K)$ denotes the space of polynomials of degree at most $k \in \mathbb{N}$ on $K \in \mathcal{T}_h$.
+Furthermore, we partition the time axis into $N$ subinterals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$.
+We assume that the interavals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
+Consequently, we can define a corresponding partition of $Q$ and $\Sigma$ into time-slabs
+\begin{equation}
+    Q^n := I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, n = 0, \dots, N-1, \qquad Q = \bigcup_{n = 0}^{N-1} Q^n, \quad \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
+\end{equation}
+Then, we define the discontinuous in time finite element spaces 
+\begin{equation}
+    \FullyDiscrSpace{k}{q} := \otimes_{n = 0}^{N-1} \mathcal{P}^q(I_n) \otimes V_h^k, \quad \ProdFullyDiscrSpace{k}{q} :=  \FullyDiscrSpace{k}{q} \times \FullyDiscrSpace{k}{q}, q \in \mathbb{N}_0, k \in \mathbb{N}.
+\end{equation}
+
 We introduce the bilinear form 
@@
 such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in ...$ such that
-\begin{equation}
+\begin{equation}\label{eq:discreteProblem}
     B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in ...
@@
 \begin{lem}
-    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on ... 
+    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$.  
 \end{lem}
@@
 
+We recall the following interpolation results from \cite{BP24}:
+
+\begin{lem}[Lem. 2.4 of \cite{BP24}]\label{lem:interpolationOperator}
+    Assume that $\Delta t = Ch$ and set $(s,m) = (\min\{k,q\}, \max\{k,q\}+3)$.
+    Then, there exists an interpolation operator $\Pi_h$ into $\FullyDiscrSpace{k}{q}$ such that for $n = 0, \dots, N-1$ the following estimates hold
+    \begin{enumerate}
+        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert \nabla(u - \Pi_h u) \Vert_{L^2(Q^n)} \} \le C \Vert u \Vert_{H^1(Q)}$. 
+        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert u - \Pi_h u \Vert_{H^1(Q^n)} \} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}$.
+        \item $\left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert u - \Pi_h u \Vert^2_{H^2(K)} \ \dT \right)^{1/2} \le C h^{s} \Vert u \Vert_{H^{m}(Q)}$ for $u \in H^m(Q_n) \cap C^0(I_n,H^2(\Omega))$.
+    \end{enumerate}
+\end{lem}
+
+\begin{lem}[Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
+    In addition to the assumptions of Lem.
+\ref{lem:interpolationOperator}, let $u \in H^m(Q)$ solve \eqref{eq:waveEquation} and set $\mathbf{U} = (u,\partial_t u)$.
+Then, the following estimates hold true.
+    \begin{enumerate}
+        \item For $u \in H^m(Q) \cap C^0([0,2],H^2(\Omega))$ we have that 
+        \begin{equation}
+            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{S_h} = \vert \mathbf{\Pi}_h \mathbf{U} - \mathbf{U} \vert_{S_h} \le C h^{s} \Vert u \Vert_{H^m(Q)}.
+        \end{equation}
+        \item For $u \in H^m(Q)$ we have that
+        \begin{equation}
+            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{\uparrow \downarrow} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}.
+        \end{equation}
+        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ it holds that 
+        \begin{equation}
+            \Vert u - \ul_1 \Vert_{\Sigma} + \Vert u - \ul_1 \Vert_{\omega_T} \le C \left( h^{s+1/2} \Vert u \Vert_{H^m(Q)} + \tnorm{(\Uh - \mathbf{\Pi}_h \Uh,0)} \right).
+        \end{equation}
+        \item For $\mathbf{Y} = (y_1,y_2) \in [H^1(Q)]^2$, we have that
+        \begin{equation}
+            \Vert \mathbf{\Pi}^\ast_h \mathbf{Y} \Vert_{S_h^\ast} \le C \left( \Vert y_1 \Vert_{H^1(Q)} + \Vert y_2 \Vert_{H^2(Q)} \right). 
+        \end{equation}
+    \end{enumerate}
+\end{lem}
+
+\begin{thm}
+    Let $u$ be a sufficient regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be the solution to \eqref{eq:discreteProblem}.
+Set $\mathbf{U} := (u,\partial_t u)$.
+Then, there exists a constant $C>0$ such that
+    \begin{equation}
+        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C h^s \Vert u \Vert_{H^m(Q)}.
+    \end{equation}
+\end{thm}
+
 \section{Numerical experiments}
+\noindent We choose the domain $\Omega = [0,1]$ which is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
+Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
+
 \subsection{Example in one space dimension}
-We consider the example from \cite{BDE22} with domain $\Omega = [0,1]$ that is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
-Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
-With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by
+As a first example, we consider the exact solution
+\begin{equation}\label{eq:1D:exact:simple}
+    u(x,t) := \begin{cases}
+        \cos(w_1 c_1 t) \cos(w_1(x-0.5)), & x \in \Omega_1, \\
+        \cos(w_2 c_2 t) \cos(w_2(x-0.5)), & x \in \Omega_2,
+    \end{cases}
+\end{equation}
+where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. We compute until $T = 1.0$ to ensure that the GCC is fulfilled.
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{$L=1$, $L=2$, $L=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best, $k = 3$, best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$}
+    \label{fig:jumpCoefs:contrast:2.5}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{$L=1$, $L=2$, $L=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
+                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best, $k = 3$, best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 5.5$}
+    \label{fig:jumpCoefs:contrast:5.5}
+  \end{figure}
+
+\subsection{2nd one dimensional example}
+We consider the example from \cite{BDE22}. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
 \begin{equation}

### 2024-02-26 tex/main.tex
More figures

@@
 \end{equation}
-Then, we define the discontinuous in time finite element spaces 
+In the following, we denote the space-time integrals on the time slabs as 
+\begin{equation*}
+    (u,v)_{Q^n} := \int_{I_n} \int_{\Omega} uv \ \dX \dT, a(u,v)_{Q^n} := \int_{I_n} \int_{\Omega} c(x)^2 \nabla u \cdot \nabla v \ \dX \dT, \quad (u,v)_{\Sigma^n} := \int_{I_n} \int_{\Sigma} uv \ \dS \dT,
+\end{equation*}
+and define $\Vert v \Vert^2_{Q^n} := (v,v)_{Q^n}$ and $\Vert v \Vert^2_{\Sigma^n} := (v,v)_{\Sigma^n}$. Furthermore, we set 
+\begin{equation*}
+    \omega^n := I_n \times \omega, \quad (u,v)_{\omega^n} := \int_{I_n} \int_{\omega} uv \ \dX \dT, \quad \Vert v \Vert^2_{\omega_T} := \sum_{n = 0}^{N-1} (v,v)_{\omega^n}.
+\end{equation*}
+Finally, we define the time jump operator 
+\begin{equation*}
+    v^n_{\pm} (x) := \lim_{s \rightarrow 0^+} v(x,t_n \pm s), \quad \jump{v^n} := v^n_+ - v^n_-. 
+\end{equation*}
+
+\noindent We define the discontinuous in time finite element spaces 
 \begin{equation}
@@
 
-\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in ...$ such that 
+\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that 
 \begin{alignat*}{2}
-    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in ... \\
-    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in ... 
+    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
+    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
 \end{alignat*}
@@
 \end{equation}
-such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in ...$ such that
+such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that
 \begin{equation}\label{eq:discreteProblem}
-    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in ...
+    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}.
 \end{equation}
@@
 
-\noindent Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, the inf-sup stability of $B$ on ...
-is a direct consequence of the previous lemma, i.e.
+\noindent Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, the inf-sup stability of $B$ on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ is a direct consequence of the previous lemma, i.e.
 there exists a constant $C>0$ such that
 \begin{equation}
-    \sup_{(\Wh,\Yh) \in ...} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C \tnorm{(\Uh,\Zh)}.
+    \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C \tnorm{(\Uh,\Zh)}.
 \end{equation}
 
-We recall the following interpolation results from \cite{BP24}:
+\begin{lem}[Continuity of $A$]
+    \begin{enumerate}
+        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\mathbf{Y} \in ...$ we have that 
+        \begin{equation}
+            A[(\Uh,\mathbf{Y})] \le C ... 
+        \end{equation}
+        \item For $\mathbf{U} \vert_{Q^n} \in ...$ for all $n = 0, \dots, N-1$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ we have that
+        \begin{equation}
+            A[(\mathbf{U},\Yh)] \le C ...
+        \end{equation}
+    \end{enumerate}
+\end{lem}
+
+We recall the following interpolation result from \cite{BP24}:
 
@@
 
-\begin{lem}[Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
+\begin{lem}[Similar to Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
     In addition to the assumptions of Lem.
@@
 
+\begin{proof}
+    has to be adpated to the current setting.
+\end{proof}
+
+\begin{lem}\label{eq:lemma:stability}
+    Let $u$ be a solution of \eqref{eq:waveEquation} and $\mathbf{U} = (u,\partial_t u)$. For any $(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ it holds that
+    \begin{equation*}
+        (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
+    \end{equation*}
+\end{lem}
+
+\begin{proof}
+    We follow the proof of \cite[Lem. 2.6]{BP24}. 
+\end{proof}
+
 \begin{thm}
@@
     \begin{equation}
-        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C h^s \Vert u \Vert_{H^m(Q)}.
+        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C \inf_{...} ... 
     \end{equation}
 \end{thm}
+
+\begin{proof}
+    The inf-sup condition on $B$ implies that 
+    \begin{equation*}
+        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}}.
+    \end{equation*}
+    Furthermore, we have that 
+    \begin{equation*}
+        B[(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh),(\Wh,\Yh)] = (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh).
+    \end{equation*}
+    Hence the claim follows with Lemma \ref{eq:lemma:stability}. 
+\end{proof}
 
@@
                 \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
 
@@
 
-                \legend{$L=1$, $L=2$, $L=3$}
+                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
                 \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
@@
                 \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={contrast}{5.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
 
@@
 
+\subsubsection{Multiple jumps}
+We extend the above example to the case with multiple jumps 
+\begin{equation}\label{eq:1D:exact:simpleMult}
+    u(x,t) := \begin{cases}
+        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
+        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
+        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3,
+    \end{cases}
+\end{equation}
+We choose $w_1$, $c_1$, $w_2$, and $c_2$ as above, and set $c_3 = c_1$, $w_3 = w_1$. We have to choose $p_2$ in dependence of $p_1$ such that the function is continuous, where we use that 
+\begin{equation*}
+    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
+\end{equation*}
+Thus, we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$.
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \node [draw=none] at (axis description cs:0.38,0.15) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.6,0.15) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Multiple jumps}
+    \label{fig:jumpCoefs:multiple}
+  \end{figure}
+
 \subsection{2nd one dimensional example}
@@
 \subsection{Example in two space dimensions}
+\subsubsection{Simple example} We extend the function defined in \eqref{eq:1D:exact:simple} to the two dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
+we consider the one dimensional solution in the $x$-direction.
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {1.8*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.35*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=north east, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=north east, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=north east, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Convergence of the error for the simple example in two space dimensions}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
 

### 2024-03-07 tex/main.tex
Restructuring numexp

@@
 \newcommand{\Uh}{\underline{\mathbf{U}}_h}
+\newcommand{\Vh}{\underline{\mathbf{V}}_h}
 \newcommand{\Yh}{\underline{\mathbf{Y}}_h}
@@
 \noindent In this article, we consider the following problem: find $u \in Q \rightarrow \mathbb{R}$ such that 
-\begin{subequations}
+\begin{subequations}\label{eq:continuousProblem}
     \begin{alignat}{2}
         (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \label{eq:waveEquation} \\ 
-        u &= u_{\omega} &&\text{ in } \omega_T, \\ \label{eq:DataMatch}
+        u &= u_{\omega} &&\text{ in } \omega_T, \label{eq:DataMatch}
     \end{alignat}    
 \end{subequations}
-where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega}$ is the known data.
+where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega} \in L^2(\omega_T)$ is the known data.
 
-\noindent The continuous problem has been studied in \cite{Filippas22}. In particular, the following result has been shown:
+\noindent In the case that $c_1 = c_2 = 1$, the problem \eqref{eq:continuousProblem} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}, i.e.
+the following theorem holds cf.
+\cite[Rem.
+A.5]{BFMO21control}
+
+\begin{thm}
+    Assume that $c_1= c_2 = 1$. If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimate 
+    \begin{equation}
+        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right).
+    \end{equation}
+\end{thm}
+
+In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
+However, in the general case where $c_1 \not = c_2 \not = 1$, the above result is not applicable.
+Instead, we have the following result \cite[Thm.
+1.1]{Filippas22}:
 \begin{thm}[Thm. 1.1 of \cite{Filippas22}]\label{thm:filippas}
-    For any nonempty subset $\omega \subset \Omega$ and $T > \text{dist}(\Omega,\omega)$, there exists $C,\kappa,\mu_0$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
-one has for any $\mu \ge \mu_0$ that
+    For any nonempty subset $\omega \subset \Omega$ and $T > 2 \sup_{x \in \Omega} \text{dist}(x,\omega)$, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
+one has for any $\mu > 0$ that
     \begin{equation}
@@
 
+We note that the assumption that $T > 2 \sup_{x \in \Omega} \text{dist}(x,\omega)$ is in general weaker than the GCC.
+
 \section{Discretization (fully discrete \& dG in time)} 
 \noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
-Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. We define the $H^1$-conforming finite element space 
+Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
+Note that the triangulation can be constructed such that for $h$ small enough the following continuous trace inequality holds \cite[Sec. 4.2]{BFMO21control}:
+\begin{equation}\label{eq:traceInequality}
+    \Vert v \Vert_{[L^2(\partial K)]^d} \le C \left(h^{-1/2} \Vert v \Vert_{[L^2(K)]^d} + h^{1/2} \Vert \nabla v \Vert_{[L^2(K)]^d} \right), \quad \forall v \in [H^1(K)]^d \text{ and } K \in \mathcal{T}_h.
+\end{equation}
+
+We define the $H^1$-conforming finite element space 
 \begin{equation}
@@
 Furthermore, we partition the time axis into $N$ subinterals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$.
-We assume that the interavals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
+We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
 Consequently, we can define a corresponding partition of $Q$ and $\Sigma$ into time-slabs
@@
 \section{Analysis}
-\noindent We define the norms \textbf{has to be shown that they are indeed norms!} 
+\noindent Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
+\begin{equation}
+    \vert \Uh \vert^2_{S_h} := S_h(\Uh,\Uh), \quad \vert \Uh \vert^2_{\uparrow \downarrow} := \Sud(\Uh,\Uh), \quad \Vert \Zh \Vert^2_{S_h^{\ast}} := S_h^{\ast}(\Zh,\Zh).
+\end{equation}
+\noindent Then, we define the norms
 \begin{equation}
@@
 \end{equation}
-where $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ are the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
+and 
 \begin{equation}
-    \vert \Uh \vert^2_{S_h} := S_h(\Uh,\Uh), \quad \vert \Uh \vert^2_{\uparrow \downarrow} := \Sud(\Uh,\Uh), \quad \Vert \Zh \Vert^2_{S_h^{\ast}} := S_h^{\ast}(\Zh,\Zh).
+    \begin{aligned}
+        \tnorm{(\Uh, \Zh)}^2_{\wop} := \tnorm{(\Uh, \Zh)}^2 + \sum_{n = 0}^{N -1} \Big\{ &\Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \Vert \dt u_1 \Vert^2_{Q^n} \\
+        &+ \Vert u_2 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 u_1 \Vert^2_{H^2(K)} \dT \Big\}. 
+    \end{aligned}
 \end{equation}
-
-We modify the steps from \cite{BP24} to show that $\tnorm{(\cdot,\cdot)}$ is indeed a norm.
+Note that the $\tnorm{(\cdot,\cdot)}_{\wop}$ is stronger than the $\tnorm{(\cdot,\cdot)}$ and that is suffices to show that $\tnorm{(\cdot,\cdot)}$ is indeed a norm to conclude that $\tnorm{(\cdot,\cdot)}_{\wop}$ is a norm.
+We modify the steps from \cite{BP24} to show the following result.
 
@@
 It directly follows from \ref{thm:filippas} that the initial data are zero.
-{\color{gray} Thats means that $\ul_1$ solves the wave equation with rhs zero, zero initial data, is zero on the boundary and zero on $\omega$...
+{\color{gray} That means that $\ul_1$ solves the wave equation with rhs zero, zero initial data, is zero on the boundary and zero on $\omega$...
 should enough to say that $\ul_1 = 0$ everywhere!?}
@@
 
-\noindent Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, the inf-sup stability of $B$ on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ is a direct consequence of the previous lemma, i.e.
-there exists a constant $C>0$ such that
+\noindent A direct consequence of this result is that $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
+
+\begin{cor}
+    There exists a constant $C_B>0$ such that 
     \begin{equation}
-    \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C \tnorm{(\Uh,\Zh)}.
+        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C_B \tnorm{(\Uh,\Zh)}.
     \end{equation}
-
-\begin{lem}[Continuity of $A$]
-    \begin{enumerate}
-        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\mathbf{Y} \in ...$ we have that 
-        \begin{equation}
-            A[(\Uh,\mathbf{Y})] \le C ... 
-        \end{equation}
-        \item For $\mathbf{U} \vert_{Q^n} \in ...$ for all $n = 0, \dots, N-1$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ we have that
-        \begin{equation}
-            A[(\mathbf{U},\Yh)] \le C ...
-        \end{equation}
-    \end{enumerate}
-\end{lem}
-
-We recall the following interpolation result from \cite{BP24}:
-
-\begin{lem}[Lem. 2.4 of \cite{BP24}]\label{lem:interpolationOperator}
-    Assume that $\Delta t = Ch$ and set $(s,m) = (\min\{k,q\}, \max\{k,q\}+3)$.
-    Then, there exists an interpolation operator $\Pi_h$ into $\FullyDiscrSpace{k}{q}$ such that for $n = 0, \dots, N-1$ the following estimates hold
-    \begin{enumerate}
-        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert \nabla(u - \Pi_h u) \Vert_{L^2(Q^n)} \} \le C \Vert u \Vert_{H^1(Q)}$. 
-        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert u - \Pi_h u \Vert_{H^1(Q^n)} \} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}$.
-        \item $\left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert u - \Pi_h u \Vert^2_{H^2(K)} \ \dT \right)^{1/2} \le C h^{s} \Vert u \Vert_{H^{m}(Q)}$ for $u \in H^m(Q_n) \cap C^0(I_n,H^2(\Omega))$.
-    \end{enumerate}
-\end{lem}
-
-\begin{lem}[Similar to Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
-    In addition to the assumptions of Lem.
-\ref{lem:interpolationOperator}, let $u \in H^m(Q)$ solve \eqref{eq:waveEquation} and set $\mathbf{U} = (u,\partial_t u)$.
-Then, the following estimates hold true.
-    \begin{enumerate}
-        \item For $u \in H^m(Q) \cap C^0([0,2],H^2(\Omega))$ we have that 
-        \begin{equation}
-            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{S_h} = \vert \mathbf{\Pi}_h \mathbf{U} - \mathbf{U} \vert_{S_h} \le C h^{s} \Vert u \Vert_{H^m(Q)}.
-        \end{equation}
-        \item For $u \in H^m(Q)$ we have that
-        \begin{equation}
-            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{\uparrow \downarrow} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}.
-        \end{equation}
-        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ it holds that 
-        \begin{equation}
-            \Vert u - \ul_1 \Vert_{\Sigma} + \Vert u - \ul_1 \Vert_{\omega_T} \le C \left( h^{s+1/2} \Vert u \Vert_{H^m(Q)} + \tnorm{(\Uh - \mathbf{\Pi}_h \Uh,0)} \right).
-        \end{equation}
-        \item For $\mathbf{Y} = (y_1,y_2) \in [H^1(Q)]^2$, we have that
-        \begin{equation}
-            \Vert \mathbf{\Pi}^\ast_h \mathbf{Y} \Vert_{S_h^\ast} \le C \left( \Vert y_1 \Vert_{H^1(Q)} + \Vert y_2 \Vert_{H^2(Q)} \right). 
-        \end{equation}
-    \end{enumerate}
-\end{lem}
+\end{cor}
 
 \begin{proof}
-    has to be adpated to the current setting.
+    It holds that $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$ and thus
+    \begin{equation*}
+        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge \frac{B[(\Uh,\Zh),(\Uh,-\Zh)]}{\tnorm{(\Uh,-\Zh)}} = \tnorm{(\Uh,\Zh)}.
+    \end{equation*}
 \end{proof}
 
-\begin{lem}\label{eq:lemma:stability}
-    Let $u$ be a solution of \eqref{eq:waveEquation} and $\mathbf{U} = (u,\partial_t u)$. For any $(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ it holds that
+\begin{lem}[Continuity of $A$]\label{lem:continuityA}
+    For all $\mathbf{U} \in [H^1(Q_n) \cap L^2(0,T;H^2(\mathcal{T}_h))] \times H^1(Q_n)$ and all $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$, we have that 
     \begin{equation*}
-        (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
+        A[\mathbf{U},\Yh] \le C \tnorm{(\mathbf{U}, 0)}_{\wop} \tnorm{(0,\Yh)}. 
     \end{equation*} 
@@
 \begin{proof}
-    We follow the proof of \cite[Lem. 2.6]{BP24}. 
+    First, note that $\tnorm{(0,\Yh)} = \Vert \Yh \Vert_{S_h^\ast}$. Using the Cauchy-Schwarz inequality, we obtain
+    \begin{equation}
+        \sum_{n = 0}^{N-1} \left\{ (\dt u_2, \underline{y}_1)_{Q^n} + a(u_1,\underline{y}_1)_{Q^n} \right\} \le C \left( \sum_{n = 0}^{N-1} \Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} \right)^{1/2} \Vert \Yh \Vert_{S_h^{\ast}},
+    \end{equation}
+    and 
+    \begin{equation*}
+        \sum_{n = 0}^{N-1} (\dt u_1 - u_2,\underline{y}_2)_{Q^n} \le C \left( \sum_{n = 0}^{N-1} \Vert \dt u_1 \Vert^2_{Q^n} + \Vert u_2 \Vert^2_{Q^n} \right)^{1/2} \Vert \Yh \Vert_{S_h^{\ast}}.
+    \end{equation*}
+    Since the interface $\Gamma$ is fitted by the triangulation, we have that $c^2 \nabla u_1 \in H^1(K)$ for each $K \in \mathcal{T}_h$.
+Thus, we can apply the trace inequality \eqref{eq:traceInequality} to obtain
+    \begin{align*}
+        \sum_{n = 0}^{N-1} (c^2 \nabla u_1 \cdot n, \underline{y}_1)_{\Sigma^n} &\le \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h \Vert c^2 \nabla v \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^{-1} \Vert \underline{y}_1 \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \\
+        &\le C \left( \sum_{n = 0}^{N-1} \left\{ \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 u_1 \Vert_{H^2(K)} \dT \right\} \right)^{1/2} \Vert \Yh \Vert_{S_h^{\ast}}.
+    \end{align*}
+    Putting all estimates together, the claim follows. 
 \end{proof}
 
-\begin{thm}
+\begin{thm}\label{thm:bestapprox}
     Let $u$ be a sufficient regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be the solution to \eqref{eq:discreteProblem}.
@@
     \begin{equation}
-        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C \inf_{...} ... 
+        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \left( 1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\Uh - \Vh, 0)}_{\wop}.  
     \end{equation}
@@
 \begin{proof}
-    The inf-sup condition on $B$ implies that 
+    Let $\Vh \in \ProdFullyDiscrSpace{k}{q}$  and $(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be arbitrary. The triangle inequality yields 
     \begin{equation*}
-        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}}.
+        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \tnorm{(\mathbf{U} - \Vh,0)} + \tnorm{(\Vh - \Uh,\Zh)}.
     \end{equation*}
-    Furthermore, we have that 
+    For the second term, we consider
+    \begin{align*}
+        B[&(\Uh - \Vh, \Zh),( \Wh, \Yh)] \\
+        &= B[(\Uh,\Zh),( \Wh, \Yh)] - (\underline{v}_1, \underline{w}_1)_{\omega_T} - \gamma S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
+        &= (u_{\omega}, \underline{w}_1)_{\omega_T} - (\underline{v}_1, \underline{w}_1)_{\omega_T} - \gamma S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
+        &= (u - \underline{v}_1, \underline{w}_1)_{\omega_T}  + \gamma S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh],
+    \end{align*} 
+    where we use the fact that $\mathbf{U}$ is sufficiently smooth and $u = u_{\omega}$ on $\omega_T$. Then, we can apply Lem. \ref{lem:continuityA} to obtain 
+    \begin{align*}
+        (u - &\underline{v}_1, \underline{w}_1)_{\omega_T}  + \gamma S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh] \\
+        &\le C(\tnorm{(\mathbf{U} - \Vh,0)}_{\wop} \tnorm{(0,\Yh)}  + \tnorm{(\mathbf{U} - \Vh,0)} \tnorm{(\Wh,0)} ) \\
+        &\le C \tnorm{(\mathbf{U} - \Vh,0)}_{\wop} \tnorm{(\Wh,\Yh)}.
+    \end{align*}
+    Thus, the inf-sup condition on $B$ yields that 
     \begin{equation*}
-        B[(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh),(\Wh,\Yh)] = (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh).
+        \tnorm{(\Vh - \Uh,\Zh)} \le \frac{C}{C_B} \tnorm{(\Uh - \Vh, 0)}_{\wop},
     \end{equation*}
-    Hence the claim follows with Lemma \ref{eq:lemma:stability}. 
+    which gives the claim. 
 \end{proof}
 
+\begin{rmk}[The case $c_1 = c_2 = 1$]
+    Theorem \ref{thm:bestapprox} allows us to recover the results obtained in \cite{BP24}.
+To this end, let $\Pi_h$ be the interpolation operator into $\ProdFullyDiscrSpace{k}{q}$ as defined in \cite[Lem.
+2.4]{BP24}.
+Then, for $u \in H^{k+2}(Q)$ it holds that
+    \begin{equation}
+        \tnorm{(\mathbf{U} - \Pi_h \mathbf{U}, 0)}_{\wop} \le C h^k \Vert u \Vert_{H^{k+2}(Q)},
+    \end{equation} 
+    and consequently theorem \ref{thm:bestapprox} gives 
+    \begin{equation}
+        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \left(1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop} \le \left(1 + \frac{C}{C_B}\right) C h^k \Vert u \Vert_{H^{k+2}(Q)}.
+    \end{equation}
+\end{rmk}
+
 \section{Numerical experiments}
+\noindent In this section, we present numerical experiments carried out with the proposed method.
+The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
+Reproduction material is available at \textbf{insert reproduction files...}
+
+\subsection{Examples in one space dimension}
 \noindent We choose the domain $\Omega = [0,1]$ which is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
 Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
-
-\subsection{Example in one space dimension}
-As a first example, we consider the exact solution
+As a first example, we consider the following exact solution considered in \cite{MHI08}
 \begin{equation}\label{eq:1D:exact:simple}
@@
 where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. We compute until $T = 1.0$ to ensure that the GCC is fulfilled. 
+We consider $h = 1/2^{1+L}$ and $\Delta t = h/2$ for refinement level $L \in \{1,2,3,4\}$.
 
@@
                 \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=, 
                 legend pos=south west, %yticklabels={,,},
                 ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                %L2-L2-u_t (k = 2)
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+                %L-infty-L2-u (k = 2)
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+                %L2-L2-u_t (k = 3)
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                %L-infty-L2-u (k = 3)
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
                 \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
                 \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best, $k = 3$, best}
+                \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2 (e_{L^2-L^2})$,, $k = 2 (e_{L^\infty-L^2})$,,$k = 3 (e_{L^2-L^2})$,,$k=3 (e_{L^\infty-L^2})$}
             \end{groupplot}
@@
     \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.7]
+            \begin{groupplot}[%
+                group style={%
+                group size=3 by 1,
+                horizontal sep=1.0cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            %L-infty-L2-u (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.80,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$k = 3$, $L = 3$}, %cycle list name=, 
+            legend pos=south east, %yticklabels={,,},
+            ymin=1e-7,
+            ]
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
+
+            \addplot+[line width=1.1pt,dashed,color=black] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+            \legend{$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$,,$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$ (new)}
     \label{fig:jumpCoefs:contrast:2.5}
@@
 
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 2.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 5.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={contrast}{5.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-3) -- (0.5,3);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{$L=1$, $L=2$, $L=3$}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution and approximations with $k = 3$ on different refinement levels for $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).}
+    \label{fig:jumpCoefs:quality}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=3 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestnoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                %\addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.0001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestRestricted_NoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Filippas lambda...}
+  \end{figure}
+
+\textbf{note: the example without GCC violates the assumptions of Filippas..., it seems that in 1D the GCC is always fulfilled if $T > 2 \sup \dots$.}
+
 \subsubsection{Multiple jumps}
@@
 \end{equation*}
-Thus, we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$.
+Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function is continuous.
+In the following, we choose $n = 3$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
+Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$.
 
@@
 
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
                 \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3.csv};
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
 
@@
                 \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                \node [draw=none] at (axis description cs:0.38,0.15) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.6,0.15) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
                 \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
@@
     \end{center}
-    \caption{Multiple jumps}
-    \label{fig:jumpCoefs:multiple}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 7.5$ and $c_2 = 1.0$.}
+    \label{fig:jumpCoefs:multipleJumps}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                %\node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                %\node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = T/2 = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (upper) and $c_1 = c_3 = 7.5$, $n = 3$ (lower) and $c_2 = 1.0$.
+We only prescribe data on $\omega = [0.0,0.3]$ and choose $\Delta t = 1/32$ (upper) and $\Delta t = 1/64$ (lower), $h = 1/64$.}
+    \label{fig:jumpCoefs:multipleJumps:noGCC}
+  \end{figure}
+
+  \begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ - with bug in the code....}
+    \label{fig:jumpCoefs:multipleJumps2}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ (uniform mesh), computed with $64$ points in space, $32$ in time and $T = 0.5$.}
+    \label{fig:jumpCoefs:multipleJumps3}
   \end{figure}
@@
 \end{equation}
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,best,$k = 3$,best}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{...}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
 
@@
 
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.000000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \legend{$k=2$,$k=3$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Convergence of the error for the simple example in two space dimensions}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=1 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u - u_h) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
+                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
+
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Filippas lambda... (2D), noGCC}
+  \end{figure}
+
+\appendix
+\section*{Outtakes}
+{\color{gray}
+\begin{lem}[Continuity of $A$]
+    \begin{enumerate}
+        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\mathbf{Y} \in ...$ we have that 
+        \begin{equation}
+            A[(\Uh,\mathbf{Y})] \le C ... 
+        \end{equation}
+        \item For $\mathbf{U} \vert_{Q^n} \in ...$ for all $n = 0, \dots, N-1$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ we have that
+        \begin{equation}
+            A[(\mathbf{U},\Yh)] \le C ...
+        \end{equation}
+    \end{enumerate}
+\end{lem}
+
+We recall the following interpolation result from \cite{BP24}:
+
+\begin{lem}[Lem. 2.4 of \cite{BP24}]\label{lem:interpolationOperator}
+    Assume that $\Delta t = Ch$ and set $(s,m) = (\min\{k,q\}, \max\{k,q\}+3)$.
+    Then, there exists an interpolation operator $\Pi_h$ into $\FullyDiscrSpace{k}{q}$ such that for $n = 0, \dots, N-1$ the following estimates hold
+    \begin{enumerate}
+        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert \nabla(u - \Pi_h u) \Vert_{L^2(Q^n)} \} \le C \Vert u \Vert_{H^1(Q)}$. 
+        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert u - \Pi_h u \Vert_{H^1(Q^n)} \} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}$.
+        \item $\left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert u - \Pi_h u \Vert^2_{H^2(K)} \ \dT \right)^{1/2} \le C h^{s} \Vert u \Vert_{H^{m}(Q)}$ for $u \in H^m(Q_n) \cap C^0(I_n,H^2(\Omega))$.
+    \end{enumerate}
+\end{lem}
+
+\begin{lem}[Similar to Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
+    In addition to the assumptions of Lem.
+\ref{lem:interpolationOperator}, let $u \in H^m(Q)$ solve \eqref{eq:waveEquation} and set $\mathbf{U} = (u,\partial_t u)$.
+Then, the following estimates hold true.
+    \begin{enumerate}
+        \item For $u \in H^m(Q) \cap C^0([0,2],H^2(\Omega))$ we have that 
+        \begin{equation}
+            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{S_h} = \vert \mathbf{\Pi}_h \mathbf{U} - \mathbf{U} \vert_{S_h} \le C h^{s} \Vert u \Vert_{H^m(Q)}.
+        \end{equation}
+        \item For $u \in H^m(Q)$ we have that
+        \begin{equation}
+            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{\uparrow \downarrow} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}.
+        \end{equation}
+        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ it holds that 
+        \begin{equation}
+            \Vert u - \ul_1 \Vert_{\Sigma} + \Vert u - \ul_1 \Vert_{\omega_T} \le C \left( h^{s+1/2} \Vert u \Vert_{H^m(Q)} + \tnorm{(\Uh - \mathbf{\Pi}_h \Uh,0)} \right).
+        \end{equation}
+        \item For $\mathbf{Y} = (y_1,y_2) \in [H^1(Q)]^2$, we have that
+        \begin{equation}
+            \Vert \mathbf{\Pi}^\ast_h \mathbf{Y} \Vert_{S_h^\ast} \le C \left( \Vert y_1 \Vert_{H^1(Q)} + \Vert y_2 \Vert_{H^2(Q)} \right). 
+        \end{equation}
+    \end{enumerate}
+\end{lem}
+
+\begin{proof}
+    has to be adapted to the current setting.
+\end{proof}}
+
+{\color{red} do we need this one? 
+\begin{lem}\label{eq:lemma:stability}
+    Let $u$ be a solution of \eqref{eq:waveEquation} and $\mathbf{U} = (u,\partial_t u)$. For any $(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ it holds that
+    \begin{equation*}
+        (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
+    \end{equation*}
+\end{lem}
+
+\begin{proof}
+    We follow the proof of \cite[Lem. 2.6]{BP24}. 
+\end{proof}}
+
 \bibliographystyle{alpha}

### 2024-03-19 tex/main.tex
Update notes

@@
 %3 May 2012
-\documentclass[10pt,reqno]{amsart}
-
-\setlength{\topmargin}{0cm}
-\setlength{\textheight}{21cm}
-\setlength{\oddsidemargin}{0in}
-\setlength{\evensidemargin}{0in}
-\setlength{\textwidth}{6.5in}
-\setlength{\parindent}{.25in}
-
-\pagestyle{plain}
+%\documentclass[10pt,reqno]{amsart}
+\documentclass[sn-mathphys-num]{sn-jnl}
+
+%\setlength{\topmargin}{0cm}
+%\setlength{\textheight}{21cm}
+%\setlength{\oddsidemargin}{0in}
+%\setlength{\evensidemargin}{0in}
+%\setlength{\textwidth}{6.5in}
+%\setlength{\parindent}{.25in}
+
+%\pagestyle{plain}
 \usepackage{stmaryrd}
@@
 %% expansion of width
-\textwidth=15.7cm
-\textheight=22.5cm
-\parskip=3pt
-\parindent=8mm
-\oddsidemargin=2mm
-\evensidemargin=0mm
-\topmargin=-0.5cm
-\marginparwidth=1cm
+%\textwidth=15.7cm
+%\textheight=22.5cm
+%\parskip=3pt
+%\parindent=8mm
+%\oddsidemargin=2mm
+%\evensidemargin=0mm
+%\topmargin=-0.5cm
+%\marginparwidth=1cm
+
 %% definition of theorem-type environments
@@
 
-\title{Data assimilation for the wave equation with discontinuous coefficients}
-\author{Erik Burman, Janosch Preuss and Tim van Beeck}
-
 \date{\today}
 \begin{document}
+
+\title{Data assimilation for the wave equation with discontinuous coefficients}
+
+\author[1]{\fnm{Erik} \sur{Burman}}\email{e.burman@ucl.ac.uk}
+\author[1]{\fnm{Janosch} \sur{Preuss}}\email{j.preuss@ucl.ac.uk}
+\author[2]{\fnm{Tim} \sur{van Beeck}}\email{t.beeck@math.uni-goettingen.de}
+
+\affil[1]{\orgdiv{Department of Mathematics}, \orgname{University College London}, \orgaddress{\street{Gower Street}, \city{London}, \postcode{WC1E 6BT}, \country{United Kingdom}}}
+
+\affil[2]{\orgdiv{Institute for Numerical and Applied Mathematics}, \orgname{University of G\"{o}ttingen}, \orgaddress{\street{Lotzenstr.}, \city{G\"{o}ttingen}, \postcode{37083}, \country{Germany}}}
+
+\abstract{Todo...}
+
+\keywords{Data assimilation, wave equation, discontinuous coefficients}
+
 \maketitle
@@
 \section{Introduction}
-\noindent Let $\Omega \subset \mathbb{R}^d$ be a bounded domain such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
+\noindent In this article, we consider the discretization of a unique continuation problem for the wave equation with discontinuous coefficients.
+In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$ such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
 We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma = \Omega \setminus (\Omega_1 \cup \Omega_2)$, but constant in time.
-\noindent In this article, we consider the following problem: find $u \in Q \rightarrow \mathbb{R}$ such that 
+For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$.
+For a subset $\omega \subset \Omega$, we define the data domain $\omega_T \coloneqq (0,T) \times \omega$.
+Then, we consider the problem: find $u : Q \rightarrow \mathbb{R}$ such that
 \begin{subequations}\label{eq:continuousProblem}
@@
 
-\noindent In the case that $c_1 = c_2 = 1$, the problem \eqref{eq:continuousProblem} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}, i.e.
-the following theorem holds cf.
+\noindent If $\partial \Omega$ is stricly convex and $c_1 = c_2 = 1$, the problem \eqref{eq:continuousProblem} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}.
+More precisely, we have the following theorem, cf.
 \cite[Rem.
-A.5]{BFMO21control}
+A.5]{BFMO21control}.
 
 \begin{thm}
-    Assume that $c_1= c_2 = 1$. If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimate 
-    \begin{equation}
+    Assume that $c_1= c_2 = 1$ and that $\partial \Omega$ is stricly convex.
+If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimate
+    \begin{equation*}
         \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right).
-    \end{equation}
+    \end{equation*}
 \end{thm}
@@
 However, in the general case where $c_1 \not = c_2 \not = 1$, the above result is not applicable.
-Instead, we have the following result \cite[Thm.
+Let $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$, where $d_c$ is the metric induced by the wave speed $c$.
+Then, we have the following result \cite[Thm.
 1.1]{Filippas22}:
 \begin{thm}[Thm. 1.1 of \cite{Filippas22}]\label{thm:filippas}
-    For any nonempty subset $\omega \subset \Omega$ and $T > 2 \sup_{x \in \Omega} \text{dist}(x,\omega)$, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
+    For any nonempty subset $\omega_T \subset \Omega$ and $T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T)$, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
 one has for any $\mu > 0$ that
@@
 \section{Discretization (fully discrete \& dG in time)} 
-\noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
+\noindent In \cite{BP24} a fully discrete FEM using dG in time was introduced for the wave equation. Here, we consider a similar scheme that incoporates the discontinuous wave speed $c$.
 Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
-Note that the triangulation can be constructed such that for $h$ small enough the following continuous trace inequality holds \cite[Sec. 4.2]{BFMO21control}:
+Note that the triangulation can be constructed such that for $h$ small enough the following continuous trace inequality holds \cite[Sec.
+4.2]{BFMO21control}: For all $v \in [H^1(K)]^d$ and $K \in \mathcal{T}_h$, we have
 \begin{equation}\label{eq:traceInequality}
-    \Vert v \Vert_{[L^2(\partial K)]^d} \le C \left(h^{-1/2} \Vert v \Vert_{[L^2(K)]^d} + h^{1/2} \Vert \nabla v \Vert_{[L^2(K)]^d} \right), \quad \forall v \in [H^1(K)]^d \text{ and } K \in \mathcal{T}_h.
-\end{equation}
-
-We define the $H^1$-conforming finite element space 
+    \Vert v \Vert_{[L^2(\partial K)]^d} \le C \left(h^{-1/2} \Vert v \Vert_{[L^2(K)]^d} + h^{1/2} \Vert \nabla v \Vert_{[L^2(K)]^d} \right).  
+\end{equation}
+
+\noindent For $k \ge 1$, we define the $H^1$-conforming finite element space 
 \begin{equation}
@@
 \begin{equation}
-    Q^n := I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, n = 0, \dots, N-1, \qquad Q = \bigcup_{n = 0}^{N-1} Q^n, \quad \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
+    \begin{aligned}
+        Q^n := &I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, \quad n = 0, \dots, N-1, \\
+        Q = &\bigcup_{n = 0}^{N-1} Q^n, \quad \phantom{:} \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
+    \end{aligned}
 \end{equation}
@@
 \begin{equation*}
-    (u,v)_{Q^n} := \int_{I_n} \int_{\Omega} uv \ \dX \dT, a(u,v)_{Q^n} := \int_{I_n} \int_{\Omega} c(x)^2 \nabla u \cdot \nabla v \ \dX \dT, \quad (u,v)_{\Sigma^n} := \int_{I_n} \int_{\Sigma} uv \ \dS \dT,
+    (u,v)_{Q^n} := \int_{I_n} \int_{\Omega} uv \ \dX \dT, \quad (u,v)_{\Sigma^n} := \int_{I_n} \int_{\Sigma} uv \ \dS \dT,
 \end{equation*}
-and define $\Vert v \Vert^2_{Q^n} := (v,v)_{Q^n}$ and $\Vert v \Vert^2_{\Sigma^n} := (v,v)_{\Sigma^n}$. Furthermore, we set 
+and define $\Vert v \Vert^2_{Q^n} := (v,v)_{Q^n}$ and $\Vert v \Vert^2_{\Sigma^n} := (v,v)_{\Sigma^n}$. 
+Furthermore, we set 
 \begin{equation*}
@@
 \begin{equation}
-    \FullyDiscrSpace{k}{q} := \otimes_{n = 0}^{N-1} \mathcal{P}^q(I_n) \otimes V_h^k, \quad \ProdFullyDiscrSpace{k}{q} :=  \FullyDiscrSpace{k}{q} \times \FullyDiscrSpace{k}{q}, q \in \mathbb{N}_0, k \in \mathbb{N}.
-\end{equation}
-
-We introduce the bilinear form 
-\begin{equation}
-    A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \left\{ (\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} - (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \right\}
-\end{equation} 
-and the Lagrangian 
+    \FullyDiscrSpace{k}{q} := \otimes_{n = 0}^{N-1} \mathcal{P}^q(I_n) \otimes V_h^k, \quad \ProdFullyDiscrSpace{k}{q} :=  \FullyDiscrSpace{k}{q} \times \FullyDiscrSpace{k}{q}, \quad q \in \mathbb{N}_0, k \in \mathbb{N}.
+\end{equation}
+
+\noindent In the following, we denote
+\begin{equation*}
+    a(u,v)_{Q^n} := \int_{I_n} \int_{\Omega} c(x)^2 \nabla u \cdot \nabla v \ \dX \dT,
+\end{equation*}
+and introduce a bilinear form $A$ that represents the wave-equation \eqref{eq:waveEquation} in mixed formulation:  
+\begin{equation}
+    \begin{aligned}
+        A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \Big\{ &(\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} \\
+        &- (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \Big\},
+    \end{aligned}
+\end{equation} 
+where $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with $k, k^\ast, q \in \mathbb{N}$ and $q^\ast \in \mathbb{N}_0$. 
+To approximate solutions of \eqref{eq:continuousProblem}, we search for stationary points of the Lagrangian 
 \begin{align*}
-    \cL_h (\Uh, \Zh) := \frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) - \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh).
+    \cL_h (\Uh, \Zh) := &\frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) \\
+    &- \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh),
 \end{align*}
+where $S_h$, $S_h^\ast$, and $\Sud$ are stabilization terms yet to be defined.
+Note that the first and the second terms of $\cL_h$ incorporate the data and the PDE constraints, respectively.
 To define the stabilization terms $S_h$ and $S_h^\ast$, we introduce the following terms:
@@
     J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c(x)^2 \nabla \ul_1}, \jump{c(x)^2 \nabla \wl_1})_F \ \dT, \\
-    I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \\
     G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c(x)^2 \nabla \ul_1),\dt \wl_2 -\div( c(x)^2 \nabla \wl_1))_K \ \dT, \\
-    R(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
+    I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \qquad 
+    R(\Uh,\Wh) := \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
 \end{align*}
-Then, we define the primal stabilizer as 
+$J(\cdot,\cdot)$ is a continuous interior penalty term in space, $G(\cdot,\cdot)$ is a Galerkin least squares term enforcing the PDE locally on each element, $I_0(\cdot,\cdot)$ enforces that $\ul_2 = \dt \ul_1$, and $R(\cdot,\cdot)$ ensures boundary stability.
+With those terms, we define the primal stabilizer $S_h$ as 
 \begin{equation}
@@
 \end{equation}
-and the dual stabilizer through 
+and the dual stabilizer $S_h^\ast$ through 
 \begin{equation}
@@
 
-\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that 
+\noindent With the definition of $\cL_h$, the first order optimality conditions take the form: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that 
 \begin{alignat*}{2}
-    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
-    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
+    (\ul_1,\wl_1)_{\omega_T} \! + \! A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \ &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
+    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \ &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
 \end{alignat*}
-For convenience, we introduce
+In a more compact form, we can write theses conditions as: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that
+\begin{equation}\label{eq:discreteProblem}
+    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast},
+\end{equation}
+where 
 \begin{equation}
     \begin{aligned}
-        B[(\Uh,\Zh),(\Wh,\Yh)] := &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
-        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh),
+        B[(\Uh,\Zh),(\Wh,\Yh)] \coloneqq \ &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
+        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh).
     \end{aligned}
 \end{equation}
-such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that
-\begin{equation}\label{eq:discreteProblem}
-    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}.
-\end{equation}
 
 \section{Analysis}
-\noindent Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
+\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:continuousProblem} through stationary points of the Laplacian $\cL_h$.
+In particular, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in suitable discrete norms defined below.
+Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
 \begin{equation}
@@
 \end{equation}
-\noindent Then, we define the norms
+\noindent Then, we define the discrete norm 
 \begin{equation}
@@
 \end{equation}
-and 
+and its strenghend version
 \begin{equation}
     \begin{aligned}
-        \tnorm{(\Uh, \Zh)}^2_{\wop} := \tnorm{(\Uh, \Zh)}^2 + \sum_{n = 0}^{N -1} \Big\{ &\Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \Vert \dt u_1 \Vert^2_{Q^n} \\
+        \tnorm{(\Uh, \Zh)}^2_{\wop} := \tnorm{(\Uh, \Zh)}^2 &+ \sum_{n = 0}^{N -1} \Big\{ \Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \Vert \dt u_1 \Vert^2_{Q^n} \\
         &+ \Vert u_2 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 u_1 \Vert^2_{H^2(K)} \dT \Big\}. 
@@
 \end{equation}
-Note that the $\tnorm{(\cdot,\cdot)}_{\wop}$ is stronger than the $\tnorm{(\cdot,\cdot)}$ and that is suffices to show that $\tnorm{(\cdot,\cdot)}$ is indeed a norm to conclude that $\tnorm{(\cdot,\cdot)}_{\wop}$ is a norm.
-We modify the steps from \cite{BP24} to show the following result.
+Note it suffices to show that $\tnorm{(\cdot,\cdot)}$ is a norm. We modify the steps from \cite{BP24} to show the following result.
 
@@
         \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} &:= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c(x)^2 \nabla \ul_1 \nabla y \right\}  \\
-        &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c(x)^2 \nabla \ul_1),y)_{K} \ \dT \\
+        &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} \\
+        &\qquad+ \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c(x)^2 \nabla \ul_1),y)_{K} \ \dT \\
         &\qquad + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c(x)^2 \nabla \ul_1}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\}.
@@
     Thus it follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
-It directly follows from \ref{thm:filippas} that the initial data are zero.
+It directly follows from Thm.
+\ref{thm:filippas} that the initial data is zero.
 {\color{gray} That means that $\ul_1$ solves the wave equation with rhs zero, zero initial data, is zero on the boundary and zero on $\omega$...
@@
 
-\noindent A direct consequence of this result is that $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
+\noindent A direct consequence of this result is that the bilinear form $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
 
@@
 \begin{proof}
-    It holds that $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$ and thus
+    First of all, we note that 
     \begin{equation*}
-        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge \frac{B[(\Uh,\Zh),(\Uh,-\Zh)]}{\tnorm{(\Uh,-\Zh)}} = \tnorm{(\Uh,\Zh)}.
+        B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}.
     \end{equation*} 
+    As a direct consequence, we have that 
+    \begin{align*}
+        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} &\frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \\
+        &\quad \ge \frac{B[(\Uh,\Zh),(\Uh,-\Zh)]}{\tnorm{(\Uh,-\Zh)}} = \tnorm{(\Uh,\Zh)}.
+    \end{align*}
 \end{proof}
@@
     First, note that $\tnorm{(0,\Yh)} = \Vert \Yh \Vert_{S_h^\ast}$. Using the Cauchy-Schwarz inequality, we obtain
-    \begin{equation}
-        \sum_{n = 0}^{N-1} \left\{ (\dt u_2, \underline{y}_1)_{Q^n} + a(u_1,\underline{y}_1)_{Q^n} \right\} \le C \left( \sum_{n = 0}^{N-1} \Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} \right)^{1/2} \Vert \Yh \Vert_{S_h^{\ast}},
-    \end{equation}
+    \begin{equation*}
+        \sum_{n = 0}^{N-1} \left\{ (\dt u_2, \underline{y}_1)_{Q^n} + a(u_1,\underline{y}_1)_{Q^n} \right\} \le C \left( \sum_{n = 0}^{N-1} \Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} \right)^{1/2} \!
+\!
+\!
+\Vert \Yh \Vert_{S_h^{\ast}},
+    \end{equation*}
     and 
@@
     \begin{align*}
-        \sum_{n = 0}^{N-1} (c^2 \nabla u_1 \cdot n, \underline{y}_1)_{\Sigma^n} &\le \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h \Vert c^2 \nabla v \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^{-1} \Vert \underline{y}_1 \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \\
+        \sum_{n = 0}^{N-1} (c^2 \nabla &u_1 \cdot n, \underline{y}_1)_{\Sigma^n} \\
+        &\le \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h \Vert c^2 \nabla v \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^{-1} \Vert \underline{y}_1 \Vert_{\partial \Omega \cap \partial K}^2 \dT \right)^{1/2} \\
         &\le C \left( \sum_{n = 0}^{N-1} \left\{ \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 u_1 \Vert_{H^2(K)} \dT \right\} \right)^{1/2} \Vert \Yh \Vert_{S_h^{\ast}}.
@@
 \end{proof}
+
+\noindent Using the inf-sup stability of $B$ and the continuity of $A$, we can show that the approximation error in the $\tnorm{(\cdot,\cdot)}$-norm scales like the best approximation error.
 
@@
     \end{equation} 
-    and consequently theorem \ref{thm:bestapprox} gives 
-    \begin{equation}
-        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \left(1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop} \le \left(1 + \frac{C}{C_B}\right) C h^k \Vert u \Vert_{H^{k+2}(Q)}.
+    and consequently Thm. \ref{thm:bestapprox} gives 
+    \begin{equation}
+        \begin{aligned}
+            \tnorm{(\mathbf{U} - \Uh,\Zh)} &\le \left(1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop} \\
+            &\le \left(1 + \frac{C}{C_B}\right) C h^k \Vert u \Vert_{H^{k+2}(Q)}. 
+        \end{aligned}
     \end{equation}
@@
 \end{equation}
-where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. We compute until $T = 1.0$ to ensure that the GCC is fulfilled. 
-We consider $h = 1/2^{1+L}$ and $\Delta t = h/2$ for refinement level $L \in \{1,2,3,4\}$.
+where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$.
+Furthermore, we consider the data domain $\omega = [0.0,0.25] \cup [0.75,1.0]$ and set $\Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75]$.
+We note that in one space dimension, the requirement that the domain $\omega_T$ fulfills the GCC is equivalent to the requirement $T > 2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$ from Thm.
+\ref{thm:filippas}.
+In the following, we denote by $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, the Euclidean metric and set
+\begin{equation}
+    d_c(x,y) \coloneqq \mathbbm{1}_{\Omega_1} c_1(x)^{-1} d(x,y) + \mathbbm{1}_{\Omega_2} c_2(x)^{-1} d(x,y), \quad x,y \in \Omega.
+\end{equation} 
+Thus, in the case where $c_2 = 1$ is fixed, we require $T > 0.25(1+c_1^{-1})$.
+
+and \textbf{compute until $T = 1.0$, correct...} to ensure that the GCC is fulfilled.
+Furthermore, we set $h = 1/2^{1+L}$ and $\Delta t = h/2$ for different refinement levels $L \in \{1,2,3,4\}$.
+The results of the experiments can be found in Fig.
+\ref{fig:jumpCoefs:contrast:2.5} and Fig.
+\ref{fig:jumpCoefs:quality}.
+...
+\\
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.25cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %L-infty-L2-u (k = 3)
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.3*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %L-infty-L2-u (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.001*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.02*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{We consider the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ for contrast $c_1 = 2.5$ (left \& middle).
+Both, the $L^\infty(0,T;L^2(\Omega_R))$-error of $u-u_h$ (left) and the $L^2(0,T;L^2(\Omega_R))$-error of $\dt (u-u_h)$ (middle) converge with order $\mathcal{O}(h^k)$ and are close to the respective error of the $L^2$-bestapproximation (dashed lines).
+For increasing contrast $c_1$, both errors increase with the same order of magnitude as the respective best approximation error (right).
+\textbf{left is with $T = 0.5$, the increasing contrast is still with $T = 1.0$ and not on $\Omega_R$..., also adjust the time step...}, rewrite...}
+    \label{fig:jumpCoefs:contrast:2.5}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.85]
+            \begin{groupplot}[%
+                group style={%
+                group size=1 by 1,
+                horizontal sep=1.0cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$k = 3$, $L = 3$}, %cycle list name=, 
+            legend pos=south east, %yticklabels={,,},
+            ymin=1e-7,
+            ]
+            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            %\addplot+[line width=1.1pt,dashed,color=black] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+            \legend{$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$,,$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{We consider $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ for polynomial degree $k = 3$ on the refinement level $L = 3$ for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
+Both errors increase with the same order of magnitude as the respective best approximation error (dashed lines).}
+    \label{fig:jumpCoefs:increasingcontrast}
+  \end{figure}
 
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 2.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
@@
                 \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
-                \nextgroupplot[width=9cm,height=7cm,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=, 
-                legend pos=south west, %yticklabels={,,},
-                ]
-                %L2-L2-u_t (k = 2)
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-                %L-infty-L2-u (k = 2)
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-                %L2-L2-u_t (k = 3)
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-                %L-infty-L2-u (k = 3)
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2 (e_{L^2-L^2})$,, $k = 2 (e_{L^\infty-L^2})$,,$k = 3 (e_{L^2-L^2})$,,$k=3 (e_{L^\infty-L^2})$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.7]
-            \begin{groupplot}[%
-                group style={%
-                group size=3 by 1,
-                horizontal sep=1.0cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L-infty-L2-u (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            %L-infty-L2-u (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.80,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-            %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
-
-            %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$k = 3$, $L = 3$}, %cycle list name=, 
-            legend pos=south east, %yticklabels={,,},
-            ymin=1e-7,
-            ]
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
-
-            \addplot+[line width=1.1pt,dashed,color=black] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-            \legend{$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$,,$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$ (new)}
-    \label{fig:jumpCoefs:contrast:2.5}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 5.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
@@
                 \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={contrast}{5.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \legend{$L=1$, $L=2$, $L=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
-                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
-                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
-                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best, $k = 3$, best}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 5.5$}
-    \label{fig:jumpCoefs:contrast:5.5}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 2.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 5.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
                 \addplot+[discard if not={contrast}{5.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
@@
 
-                \legend{$L=1$, $L=2$, $L=3$}
+                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
 
@@
 
+  \begin{comment}
   \begin{figure}[!htbp]
@@
   \end{figure}
-
-\textbf{note: the example without GCC violates the assumptions of Filippas..., it seems that in 1D the GCC is always fulfilled if $T > 2 \sup \dots$.}
+\end{comment}
 
 \subsubsection{Multiple jumps}
-We extend the above example to the case with multiple jumps 
+\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
+For points $p_1,p_2 \in (0,1)$, we decompose the interval $\Omega = [0,1]$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
+$\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$.
+Then, we consider the following Ansatz for the exact solution:
 \begin{equation}\label{eq:1D:exact:simpleMult}
@@
         \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
-        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3,
+        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
     \end{cases}
 \end{equation}
-We choose $w_1$, $c_1$, $w_2$, and $c_2$ as above, and set $c_3 = c_1$, $w_3 = w_1$. We have to choose $p_2$ in dependence of $p_1$ such that the function is continuous, where we use that 
+To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
 \begin{equation*}
@@
 \end{equation*}
-Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function is continuous.
-In the following, we choose $n = 3$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
-Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$.
+Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
+In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
+As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
+Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ and $c_1 = 7.5$.
 
@@
             grid style=dashed,
-            ymin = -1.1e0, ymax = 1.1e0,
+            ymin = -0.6e0, ymax = 0.6e0,
             ]    
@@
                 ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
+                \addplot+[line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                \addplot+[line width=1.0pt,mark=None,color=teal!55!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
 
@@
                 \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
+                \node [draw=none] at (axis description cs:0.7,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+                \legend{exact, $L = 4$, $L = 3$}
                 \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
+
+                \addplot+[line width=2.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=teal!55!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
 
                 \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
                 \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
@@
 
-\subsection{2nd one dimensional example}
+\subsubsection{2nd one dimensional example}
 We consider the example from \cite{BDE22}. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
@@
     u(x,t) = \begin{cases}
-      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) 0- u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
       \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), x \in \Omega_2.
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
                 legend pos=north east, %yticklabels={,,},
@@
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+
                 %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
                 %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
 
-                \addplot[gray, dashed, domain=1:4] {1.8*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.35*(1/2^(3))^(x-0.9)};
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
                 \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
@@
                 \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
                 legend pos=north east, %yticklabels={,,},
                 ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+
+                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
                 \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
@@
 
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
                 legend pos=north east, %yticklabels={,,},
                 ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+
+                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
                 \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
@@
 
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
                 legend pos=north east, %yticklabels={,,},
                 ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
                 \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
@@
     \end{center}
-    \caption{Convergence of the error for the simple example in two space dimensions}
+    \caption{Convergence of $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
     \label{fig:2DjumpCoefs}
@@
 
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.000000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \legend{$k=2$,$k=3$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Convergence of the error for the simple example in two space dimensions}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-
+\begin{comment}
   \begin{figure}[!htbp]
@@
   \end{figure}
-
+\end{comment}
+
+\subsubsection{Snell's law... }
+
+\begin{comment}
 \appendix
@@
 \end{proof}}
-
-\bibliographystyle{alpha}
+\end{comment}
+
+%\bibliographystyle{alpha}
 \bibliography{references}

### 2024-03-21 tex/main.tex
Update notes

@@
 For a subset $\omega \subset \Omega$, we define the data domain $\omega_T \coloneqq (0,T) \times \omega$.
+In the following, let $\wop$ be the wave operator defined as
+\begin{equation*}
+    \wop u := \partial_t^2 - \div(c(x)^2 \nabla u).
+\end{equation*}
+In particular, we write $\square_1$ if $c_i = 1$, $i = 1,2$, i.e. if we are considering the case of homogeneous media. 
 Then, we consider the problem: find $u : Q \rightarrow \mathbb{R}$ such that 
-\begin{subequations}\label{eq:continuousProblem}
-    \begin{alignat}{2}
-        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \label{eq:waveEquation} \\ 
-        u &= u_{\omega} &&\text{ in } \omega_T, \label{eq:DataMatch}
-    \end{alignat}    
-\end{subequations}
-where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega} \in L^2(\omega_T)$ is the known data.
-
-\noindent If $\partial \Omega$ is stricly convex and $c_1 = c_2 = 1$, the problem \eqref{eq:continuousProblem} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}.
+\begin{equation}\label{eq:waveEquation}
+        (\wop u, u) = (0,0) \quad \text{ in } Q \times \Sigma.  
+\end{equation}
+To ensure that the problem is well-posed, one usually prescribes initial data 
+\begin{equation}\label{eq:initialData}
+    (u,\dt u) \vert_{t = 0} = (u_0,u_1) \text{ in } \Omega. \tag{IVP} 
+\end{equation}
+Here we will consider a data assimilation problem instead, i.e.
+we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in $\omega_T$:
+\begin{equation}\label{eq:dataMatch}
+    u = u_{\omega} \text{ in } \omega_T. \tag{DA}
+\end{equation}
+
+\noindent If $\partial \Omega$ is stricly convex and $c_i = 1$, $i = 1,2$, the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}.
 More precisely, we have the following theorem, cf.
-\cite[Rem.
+\cite[Thm.
+A.4 \& Rem.
 A.5]{BFMO21control}.
 
-\begin{thm}
-    Assume that $c_1= c_2 = 1$ and that $\partial \Omega$ is stricly convex.
-If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimate
-    \begin{equation*}
-        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right).
-    \end{equation*}
+\begin{thm}\label{thm:Lipschitz}
+    Assume that $c_i = 1$, $i = 1,2$, and that $\partial \Omega$ is stricly convex.
+If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimates
+    \begin{align*}
+        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} &\le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right), \\
+        \Vert \phi \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert \dt \phi \vert_{t = 0} \Vert_{H^{-1}(\Omega)} &\le C \left(\Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right).
+    \end{align*}
 \end{thm}
 
-In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
+\noindent In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
 However, in the general case where $c_1 \not = c_2 \not = 1$, the above result is not applicable.
@@
 Then, we have the following result \cite[Thm.
-1.1]{Filippas22}:
-\begin{thm}[Thm. 1.1 of \cite{Filippas22}]\label{thm:filippas}
-    For any nonempty subset $\omega_T \subset \Omega$ and $T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T)$, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving...
-one has for any $\mu > 0$ that
-    \begin{equation}
-        \Vert (u_0,u_1) \Vert_{L^2 \times H^{-1}} \le C e^{\kappa \mu} \Vert u \Vert_{L^2(\omega_T)} + \frac{C}{\mu} \Vert (u_0,u_1) \Vert_{H^1 \times L^2}. 
+5.17]{Filippas22}:
+\begin{thm}[Thm. 5.17 of \cite{Filippas22}]\label{thm:filippas}
+    Let $\omega_T \subset \Omega$ be nonempty and $T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T)$.
+Then, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving \eqref{eq:waveEquation}-\eqref{eq:initialData} one has for any $\mu > 0$ that
+    \begin{equation}\label{eq:FilippasEstimate}
+        \Vert (u_0,u_1) \Vert_{L^2 \times H^{-1}} \le C e^{\kappa \mu} \left( \Vert u \Vert_{L^2(\omega_T)} + \Vert \wop u \Vert_{L^2(Q)} \right) + \frac{C}{\mu} \Vert (u_0,u_1) \Vert_{H^1 \times L^2}.
+    \end{equation}
+    In particular, if $(u_0,u_1) \not = (0,0)$ we have that 
+    \begin{equation}\label{eq:FilippasEstimateLog}
+        \Vert (u_0,u_1) \Vert_{L^2 \times H^{-1}} \le C \frac{\Vert (u_0,u_1) \Vert_{H^1 \times L^2}}{\log \left( 1 + \frac{\Vert (u_0,u_1) \Vert_{H^1 \times L^2}}{ \Vert u \Vert_{L^2(\omega_T)} + \Vert \wop u \Vert_{L^2(Q)}} \right)}.
     \end{equation} 
@@
 and its strenghend version
-\begin{equation}
+\begin{equation}\label{eq:tnormwop}
     \begin{aligned}
@@
     Thus it follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
-It directly follows from Thm.
-\ref{thm:filippas} that the initial data is zero.
-{\color{gray} That means that $\ul_1$ solves the wave equation with rhs zero, zero initial data, is zero on the boundary and zero on $\omega$...
-should enough to say that $\ul_1 = 0$ everywhere!?}
+Thus, $\ul_1$ solves \eqref{eq:waveEquation} and by taking $\mu \rightarrow \infty$ in Thm.
+\ref{thm:filippas}, it follows that the initial data is zero.
+As solutions to \eqref{eq:waveEquation} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
 \end{proof}
@@
 
-\begin{rmk}[The case $c_1 = c_2 = 1$]
-    Theorem \ref{thm:bestapprox} allows us to recover the results obtained in \cite{BP24}.
-To this end, let $\Pi_h$ be the interpolation operator into $\ProdFullyDiscrSpace{k}{q}$ as defined in \cite[Lem.
-2.4]{BP24}.
-Then, for $u \in H^{k+2}(Q)$ it holds that
-    \begin{equation}
-        \tnorm{(\mathbf{U} - \Pi_h \mathbf{U}, 0)}_{\wop} \le C h^k \Vert u \Vert_{H^{k+2}(Q)},
-    \end{equation} 
-    and consequently Thm. \ref{thm:bestapprox} gives 
-    \begin{equation}
-        \begin{aligned}
-            \tnorm{(\mathbf{U} - \Uh,\Zh)} &\le \left(1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop} \\
-            &\le \left(1 + \frac{C}{C_B}\right) C h^k \Vert u \Vert_{H^{k+2}(Q)}. 
-        \end{aligned}
+\begin{cor}\label{cor:tnormConvRates}
+    Under the assumption of Thm. \ref{thm:bestapprox}, we have that
+    \begin{equation*}
+        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le C h^s \Vert u \Vert_{H^m(Q)},
+    \end{equation*}
+    where $(s,m) := (\min\{ k,q \}, \max\{k,q\}+3)$. 
+\end{cor}
+
+\begin{proof}
+    Due to the assumption that $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, we have that 
+    \begin{equation*}
+        \tnorm{(\Uh - \Vh, 0)}_{\wop} \le C \tnorm{(\Uh - \Vh, 0)}_{\square_1},
+    \end{equation*}
+    where $\tnorm{(\cdot, \cdot)}_{\square_1}$ is defined by \eqref{eq:tnormwop} with $c_i = 1$, $i = 1,2$.
+Thus, we can apply the interpolation results derived in \cite[Lem.
+2.4]{BP24} to obtain the claim.
+\end{proof}
+
+\begin{rmk}[Homogenous media]\label{rem:homMedia}
+    Assume that the set $\omega_T \subset \Omega$ fulfills the GCC.
+In the case where $c_i = 1$, $i = 1,2$, we can apply the Lipschitz stability result from Thm.
+\ref{thm:Lipschitz} to proof convergence in a physically relevant norm, see \cite[Thm.
+4.4]{BP24}.
+As discussed in \cite[Sec.
+4]{BP24}, there exists a suitable lifting operator $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ such that $L_{\Delta t} \ul_1 \in H^1(Q)$.
+Thus, applying Thm.
+\ref{thm:Lipschitz} and Cor.
+\ref{cor:tnormConvRates} to the residual $u - L_{\Delta t} \ul_1$ yields that
+    \begin{equation}\label{eq:homMedia:estimate}
+        \Vert u - L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}  + \Vert \dt (u - L_{\Delta t} \ul_1) \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C h^s \Vert u \Vert_{H^m(Q)}. 
     \end{equation}
 \end{rmk}
+
+\textbf{discuss what we expect in the heterogenous case...}
+
+\noindent \textbf{Assume for now} that we can rewrite the estimates from Thm.
+\ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
+As discussed in Rem.
+\ref{rem:homMedia}, we can then apply this continuum estimate to the residual $\tilde{e}_h := u - L_{\Delta t} \ul_1$, where the lifting operator $L_{\Delta t}$ ensures that $\tilde{e}_h \in H^1$.
+Following the argumentation from \cite[Thm.
+4.4]{BP24}, it follows that
+\begin{equation}
+    \Vert \ul_1 - L_{\Delta t} \ul_1 \Vert_{L^2(\omega_T)} \le C h^s \Vert u \Vert_{H^m(Q)}, 
+\end{equation}
+and $\Vert u - \ul_1 \Vert_{L^2(\omega_T)} \le \tnorm{(\mathbf{U}-\Uh,\Zh)}$ by definition of the triple-norm, it follows from Cor.
+\ref{cor:tnormConvRates} that $\Vert \tilde{e}_h \Vert_{L^2(\omega_T)} \le C h^s \Vert u \Vert_{H^m(Q)}$.
+Furthermore, \textbf{with similar arguments as in} \cite[Thm.
+4.4]{BP24}, we obtain that
+\begin{equation}
+    \Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)} \le C h^s \Vert u \Vert_{H^m(Q)}. 
+\end{equation}
+Thus, \eqref{eq:FilippasEstimateLog} yields 
+\begin{equation}
+    \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1}),
+\end{equation} 
+where $C_{0,1} := \Vert (u_0,u_1) \Vert_{H^1 \times L^2}$.
+While this estimates holds under the general condition $T > 2 \sup_{x \in \Omega} d_c(x,\omega_T)$, we suspect that under the assumption of the geometric control condition, the estimate can be improved considerably.
+In particular, the numerical experiments considered in the following section suggest that a similar estimate to \eqref{eq:homMedia:estimate} holds in the heterogenous case.
 
@@
                 vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u - u_h) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
+                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u - u_h) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
                 legend pos=south east, %ymax = 1e2, %yticklabels={,,},
@@
                 \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
-
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
 
@@
 \subsubsection{Snell's law... }
+\noindent Finally, we consider a more elaborate example.
+We divide the unit-square $\Omega = [0,1]^2$ into $\Omega_1 = (0,0.5)^2$ and $\Omega_2 = (0.5,1)^2$ and fix the wave-speed $c_1 = 1$ in $\Omega_1$.
+Then, we consider the initial conditions
+\begin{align*}
+    u_0 (x,y) &= \frac{1}{100} \exp(-(80(x+y-t-1/5))^2) \vert_{t=0}, \\
+    u_1(x,y) &= 128(x+y-t-1/5) \exp(-(80(x+y-t-1/5))^2) \vert_{t = 0}
+\end{align*}
+and compute a reference solution $u_{\text{ref}}$ numerically. We consider the data domain $\omega_T$ as described in Fig. \ref{fig:2d:SnellsLaw} and presribe $u = \Pi_h u_{\text{ref}}$ on $\omega_T$.
+
+\newcommand{\hpoint}{0.85}
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[scale=4]
+        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
+        \draw[fill=gray!40,draw=none,opacity=0.5] (0,1) -- (0,\hpoint) -- (0.65,\hpoint) -- (0.65,1-\hpoint) -- (0,1-\hpoint) -- (0,0) -- (1,0) -- (1,1) -- cycle;
+        \node[draw=none] at (0.85,0.25) {\color{gray} $\omega$};
+        \draw[stealth-stealth] (0.7,1-\hpoint) -- (0.7,\hpoint); 
+        \node[draw=none] at (0.8,0.5) {\color{black} $h_\omega$};
+        \draw[dashed] (0.5,0.5) -- (0,0.5); 
+        \draw[-stealth,red,very thick] (0,0.2) -- (0.49,0.5) -- (0,0.8);
+        \draw[black,very thick] (0.5,0) -- (0.5,1); 
+        \node[draw=none] at (0.55,0.5) {\color{black} $\Gamma$};
+        \draw (0.25,0.5) to [bend right=45] (0.25,0.35);
+        \node[draw=none] at (0.28,0.44) {\color{black} $\theta_c$};
+        \node[draw=none] at (0.5,1.1) {GCC not fulfilled};
+        \begin{scope}[xshift=1.25cm]
+            \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
+            \draw[fill=gray!40,draw=none,opacity=0.5] (0,1) -- (0,0.85*\hpoint) -- (0.65,0.85*\hpoint) -- (0.65,1-0.85*\hpoint) -- (0,1-0.85*\hpoint) -- (0,0) -- (1,0) -- (1,1) -- cycle;
+            \draw[stealth-stealth] (0.7,1-0.85*\hpoint) -- (0.7,0.85*\hpoint); 
+            \node[draw=none] at (0.8,0.5) {\color{black} $h_\omega$};
+            \node[draw=none] at (0.85,0.25) {\color{gray} $\omega$};
+            \draw[dashed] (0.5,0.5) -- (0,0.5); 
+            \draw[-stealth,red,very thick] (0,0.2) -- (0.49,0.5) -- (0,0.8);
+            \draw[black,very thick] (0.5,0) -- (0.5,1); 
+            \node[draw=none] at (0.55,0.5) {\color{black} $\Gamma$};
+            \draw (0.25,0.5) to [bend right=45] (0.25,0.35);
+            \node[draw=none] at (0.28,0.44) {\color{black} $\theta_c$};
+            \node[draw=none] at (0.5,1.1) {GCC fulfilled};
+        \end{scope}
+    \end{tikzpicture}
+    \caption{According to Snell's law, rays hitting the interface with an angle greater than the critical angle $\theta_c := \arcsin(\frac{c_1}{c_2})$ are reflected back into the domain $\Omega_1$.
+To ensure that the GCC is fulfilled, the height $h_{\omega}$ has to chosen smaller than $\tan(\theta_c)$.}
+    \label{fig:2d:SnellsLaw}
+\end{figure}
 

### 2024-03-26 tex/main.tex
Notes update

@@
 
+%find colors at https://colorbrewer2.org/#type=qualitative&scheme=Set1&n=5
 \pgfplotsset{
@@
 For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$.
-For a subset $\omega \subset \Omega$, we define the data domain $\omega_T \coloneqq (0,T) \times \omega$.
+For any nonempty subset $\omega \subset \Omega$, we set $\omega_T \coloneqq (0,T) \times \omega$.
 In the following, let $\wop$ be the wave operator defined as
@@
 \noindent If $\partial \Omega$ is stricly convex and $c_i = 1$, $i = 1,2$, the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}.
-More precisely, we have the following theorem, cf.
-\cite[Thm.
-A.4 \& Rem.
-A.5]{BFMO21control}.
+More precisely, we have the following theorem.
 
@@
     \begin{align*}
-        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} &\le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right), \\
-        \Vert \phi \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert \dt \phi \vert_{t = 0} \Vert_{H^{-1}(\Omega)} &\le C \left(\Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \wop \phi \Vert_{H^{-1}(Q)} \right).
+        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} &\le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \square_1 \phi \Vert_{H^{-1}(Q)} \right), \\
+        \Vert \phi \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert \dt \phi \vert_{t = 0} \Vert_{H^{-1}(\Omega)} &\le C \left(\Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \square_1 \phi \Vert_{H^{-1}(Q)} \right).
     \end{align*}
 \end{thm}
+
+\begin{proof}
+    See \cite[Thm. A.4]{BFMO21control} and \cite[Rem. A.5]{BFMO21control}.
+\end{proof}
 
@@
 We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
-Consequently, we can define a corresponding partition of $Q$ and $\Sigma$ into time-slabs
+Then, we partition of $Q$ and $\Sigma$ into time-slabs
 \begin{equation}
@@
 where $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with $k, k^\ast, q \in \mathbb{N}$ and $q^\ast \in \mathbb{N}_0$. 
-To approximate solutions of \eqref{eq:continuousProblem}, we search for stationary points of the Lagrangian 
+To approximate solutions of \eqref{eq:waveEquation}-\eqref{eq:dataMatch}, we search for stationary points of the Lagrangian 
 \begin{align*}
@@
 $J(\cdot,\cdot)$ is a continuous interior penalty term in space, $G(\cdot,\cdot)$ is a Galerkin least squares term enforcing the PDE locally on each element, $I_0(\cdot,\cdot)$ enforces that $\ul_2 = \dt \ul_1$, and $R(\cdot,\cdot)$ ensures boundary stability.
-With those terms, we define the primal stabilizer $S_h$ as 
+Then we define the primal stabilizer $S_h$ as 
 \begin{equation}
@@
 \end{equation}
-The stabilization term $\Sud$ imposes regularity on the discontinuities in time and is defined as 
+The remaining stabilization term $\Sud$ imposes regularity on the discontinuities in time and is defined as 
 \begin{equation}
@@
 \section{Analysis}
-\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:continuousProblem} through stationary points of the Laplacian $\cL_h$.
+\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
 In particular, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in suitable discrete norms defined below.
@@
 \end{equation}
-Note it suffices to show that $\tnorm{(\cdot,\cdot)}$ is a norm. We modify the steps from \cite{BP24} to show the following result.
+%Note it suffices to show that $\tnorm{(\cdot,\cdot)}$ is a norm. We modify the steps from \cite{BP24} to show the following result.
 
 \begin{lem}
-    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$.  
+    The expressions $\tnorm{(\cdot,\cdot)}$ and $\tnorm{(\cdot,\cdot)}_{\wop}$ are norms on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$.  
 \end{lem}
@@
 \begin{equation}
-    \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1}),
+    \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1},
 \end{equation} 
@@
 \subsection{Examples in one space dimension}
-\noindent We choose the domain $\Omega = [0,1]$ which is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
+\noindent We set $\Omega \coloneqq [0,1]$ and define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
 Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
@@
 \end{equation}
-where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$.
-Furthermore, we consider the data domain $\omega = [0.0,0.25] \cup [0.75,1.0]$ and set $\Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75]$.
-We note that in one space dimension, the requirement that the domain $\omega_T$ fulfills the GCC is equivalent to the requirement $T > 2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$ from Thm.
-\ref{thm:filippas}.
-In the following, we denote by $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, the Euclidean metric and set
+where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. Furthermore, we define
+\begin{equation}
+    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq [0.25,0.75].
+\end{equation}
+In one space dimension, the domain $\omega_T$ fulfills the GCC if and only if $T > 2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, where $\operatorname{dist}_c(x,\omega_T)$ denotes the distance of $x$ to $\omega_T$ with respect to the rescaled metric $d_c$.
+Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric.
+Then, we have that
 \begin{equation}
@@
 \end{equation} 
-Thus, in the case where $c_2 = 1$ is fixed, we require $T > 0.25(1+c_1^{-1})$.
+Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, we require that $T > 0.25(1+c_1^{-1})$.
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=teal,mark=*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal,mark=*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=red,mark=star] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=red,mark=star] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
@@
 For increasing contrast $c_1$, both errors increase with the same order of magnitude as the respective best approximation error (right).
-\textbf{left is with $T = 0.5$, the increasing contrast is still with $T = 1.0$ and not on $\Omega_R$..., also adjust the time step...}, rewrite...}
+\textbf{left is with $T = 0.5$, the increasing contrast is still with $T = 1.0$ and not on $\Omega_R$..., also adjust the time step...}, rewrite..., plot $\mathcal{O}(\log(h))$ ...
+}
     \label{fig:jumpCoefs:contrast:2.5}
@@
                 group style={%
-                group size=1 by 1,
+                group size=2 by 1,
                 horizontal sep=1.0cm,
@@
             ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$k = 3$, $L = 3$}, %cycle list name=, 
-            legend pos=south east, %yticklabels={,,},
-            ymin=1e-7,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
+            legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+            %ymin=1e-7,ymax=1e1,
             ]
@@
             \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            %\addplot+[line width=1.1pt,dashed,color=black] table [x=contrast, y expr=\thisrow{exp_Lambda}*1, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-            \legend{$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$,,$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-3))^(x-0.9)};
+
+            \node [draw=none] at (axis description cs:0.70,0.37) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
+            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
+
+            \legend{$T = 0.5$, $L^2$-best approx. ($T = 0.5$), $T$ variable, $L^2$-best approx. ($T$ variable)}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
+            legend pos=south east, %yticklabels={,,},
+            %ymin=1e-7,ymax=1e1,
+            ]
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4.5] {0.00001*(1/2^(-2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4.5] {0.0003*(1/2^(-3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.70,0.27) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
+            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
+
             \end{groupplot}
         \end{tikzpicture}
+        \pgfplotslegendfromname{named}
     \end{center}
-    \caption{We consider $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ for polynomial degree $k = 3$ on the refinement level $L = 3$ for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
-Both errors increase with the same order of magnitude as the respective best approximation error (dashed lines).}
+    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
+We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ decreases with the constrast $c_1$ while keeping the GCC fulfilled.}
     \label{fig:jumpCoefs:increasingcontrast}
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 2.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=5, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+                ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
                 \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
@@
                 \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
 
@@
 
-                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$c_1 = 5.5$, $u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \legend{exact,$L=1$, $L=2$, $L=3$, $L=4$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 5.5$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
                 ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
                 \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
@@
                 \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={contrast}{5.5},line width=1.1pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
 
@@
 
-                \legend{$L=1$, $L=2$, $L=3$, $L=4$, exact}
+                %Colors
+                \definecolor{L1Color}{RGB}{55,126,184}
+                \definecolor{L2Color}{RGB}{77,175,74}
+                \definecolor{L3Color}{RGB}{152,78,163}
+                \definecolor{L4Color}{RGB}{255,127,0}
+
+                %L = 1
+                \draw[color=L1Color,thick] (0.75,-2) -- (1,-2);
+                \draw[color=L1Color,thick] (0.75,-2.05) -- (0.75,-1.95);
+                \draw[color=L1Color,thick] (1.0,-2.05) -- (1.0,-1.95);
+
+                %L = 2
+                \draw[color=L2Color,thick] (0.75,-1.75) -- (1,-1.75);
+                \draw[color=L2Color,thick] (0.75,-1.70) -- (0.75,-1.8);
+                \draw[color=L2Color,thick] (0.875,-1.70) -- (0.875,-1.8);
+                \draw[color=L2Color,thick] (1.0,-1.70) -- (1.0,-1.8);
+
+                %L = 3
+                \draw[color=L3Color,thick] (0.75,-1.5) -- (1,-1.5);
+                \draw[color=L3Color,thick] (0.75,-1.45) -- (0.75,-1.55);
+                \draw[color=L3Color,thick] (0.8125,-1.45) -- (0.8125,-1.55);
+                \draw[color=L3Color,thick] (0.875,-1.45) -- (0.875,-1.55);
+                \draw[color=L3Color,thick] (0.9375,-1.45) -- (0.9375,-1.55);
+                \draw[color=L3Color,thick] (1.0,-1.45) -- (1.0,-1.55);
+
+                %L = 4
+                \draw[color=L4Color,thick] (0.75,-1.25) -- (1,-1.25);
+                \draw[color=L4Color,thick] (0.75,-1.20) -- (0.75,-1.30);
+                \draw[color=L4Color,thick] (0.78125,-1.20) -- (0.78125,-1.30);
+                \draw[color=L4Color,thick] (0.8125,-1.20) -- (0.8125,-1.30);
+                \draw[color=L4Color,thick] (0.84375,-1.20) -- (0.84375,-1.30);
+                \draw[color=L4Color,thick] (0.875,-1.20) -- (0.875,-1.30);
+                \draw[color=L4Color,thick] (0.90625,-1.20) -- (0.90625,-1.30);
+                \draw[color=L4Color,thick] (0.9375,-1.20) -- (0.9375,-1.30);
+                \draw[color=L4Color,thick] (0.96875,-1.20) -- (0.96875,-1.30);
+                \draw[color=L4Color,thick] (1.0,-1.20) -- (1.0,-1.30);
+
+                %\legend{exact, $L=1$, $L=2$, $L=3$, $L=4$}
 
@@
         \end{tikzpicture}
+        \pgfplotslegendfromname{named}
     \end{center}
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1= 7.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
                 ]
@@
                 %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
-                \addplot+[line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
                 %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                \addplot+[line width=1.0pt,mark=None,color=teal!55!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
                 \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
@@
 
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.7,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.7,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
+
+                 %L = 3
+                %\draw[color=orange,thick] (0.4,-0.5) -- (2/3,-0.5);
+                %\draw[color=orange,thick] (0.4,-0.48) -- (0.4,-0.52);
+                %\draw[color=orange,thick] (0.4375,-0.48) -- (0.4375,-0.52);
+                %\draw[color=orange,thick] (0.5,-0.48) -- (0.5,-0.52);
+                %\draw[color=orange,thick] (0.5625,-0.48) -- (0.5625,-0.52);
+                %\draw[color=orange,thick] (0.625,-0.48) -- (0.625,-0.52);
+                %\draw[color=orange,thick] (0.6666,-0.48) -- (0.6666,-0.52);
 
                 \legend{exact, $L = 4$, $L = 3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
@@
 
-                \addplot+[line width=2.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=teal!55!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
                 \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
@@
                 \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
 
@@
   \end{figure}
+
+\noindent As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
+\begin{equation}
+    T > 2 \left[ (p_2 - p_1) + \frac{p_1 - 0.3 + 1 - p_2}{c_1} \right]. 
+\end{equation}
+Figure \ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
 
@@
                 group style={%
-                group size=2 by 2,
+                group size=2 by 1,
                 horizontal sep=1.5cm,
@@
             grid style=dashed,
-            ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
+            %ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
 
@@
 
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \legend{exact,$T=1.0$,$T=0.5$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
 
@@
                 \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                %\node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                %\node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
 
@@
         \end{tikzpicture}
+         \pgfplotslegendfromname{named}
     \end{center}
@@
   \end{figure}
-\end{comment}
 
@@
   \end{figure}
+\end{comment}
 
@@
 We consider the example from \cite{BDE22}. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
-\begin{equation}
+\begin{equation}\label{eq:1D:complicatedSol}
     u(x,t) = \begin{cases}
@@
 
+\begin{comment}
 \begin{figure}[!htbp]
@@
     \caption{...}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
+                legend pos=south west, 
+                %yticklabels={,,}, 
+                xlabel={$L$}, ylabel={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
+
+                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_complexSol.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
+                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
+
+                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
+                \legend{exact,$L=4$, $L=5$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{We consider the approximation of \eqref{eq:1D:complicatedSol} with $h = 1/2^{(L+1)}$ and $\Delta t = 1/2^L$.}
     %\label{fig:2DjumpCoefs}

### 2024-03-26 tex/main.tex
Update numex

@@
 \subsection{Examples in one space dimension}
+
+\subsubsection{Simple Example}\label{sec:numex:1D:simple}
 \noindent We set $\Omega \coloneqq [0,1]$ and define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
@@
 \begin{equation}
-    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq [0.25,0.75].
+    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75].
 \end{equation}
@@
             \addplot[gray, dashed, domain=1:4] {0.001*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.009999968541169805
+                2 0.006666645694113204
+                3 0.004999984270584902
+                4 0.003999987416467922
+
+            };
             \node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
             \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
             \legend{$k=2 $,, $k = 3$,}
@@
             %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.09999968541169805
+                2 0.06666645694113204
+                3 0.04999984270584902
+                4 0.03999987416467922
+
+            };
             \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
             \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
             \legend{$k=2 $,, $k = 3$,}
@@
 \subsubsection{2nd one dimensional example}
-We consider the example from \cite{BDE22}. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
+We consider the same geometrical setup as in Sec.
+\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
+With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
 \begin{equation}\label{eq:1D:complicatedSol}
     u(x,t) = \begin{cases}
-      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
-      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), x \in \Omega_2.
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
+      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
     \end{cases}
 \end{equation}
+This solution describes a wave traveling towards the interface $\Gamma$.
+Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+\begin{comment}
+\begin{figure}[!htbp]
+    \begin{center}with 
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,best,$k = 3$,best}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{...}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
+                legend pos=south west, 
+                %yticklabels={,,}, 
+                xlabel={$L$}, ylabel={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
+
+                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_complexSol.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
+                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
+
+                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
+
+                %L = 2
+                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
+                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
+                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
+                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
+
+                %L = 3
+                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
+                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
+                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
+                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
+                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
+                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
+                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
+
+                \legend{exact,$L=4$, $L=5$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{We consider the approximation of \eqref{eq:1D:complicatedSol} with $h = 1/2^{(L+1)}$ and $\Delta t = 1/2^L$, \textbf{now $\Delta t = 1/2^{L+1}$ on the right}.}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+
+\subsection{Example in two space dimensions}
+\noindent In this section, we present numerical examples in two space dimensions.
+We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
+
+\subsubsection{Simple example} 
+As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
+we consider the original solution in the $x$-direction.
+We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
+To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
+We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
+As before, we fix $c_2 = 1$ and consider different values for $c_1$.
+The results of the experiment are presented in Fig.
+\ref{fig:2DjumpCoefs}.
 
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,best,$k = 3$,best}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+
+                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+
+                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
             \end{groupplot}
@@
     \end{center}
-    \caption{...}
-    %\label{fig:2DjumpCoefs}
+    \caption{Convergence of $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
+    \label{fig:2DjumpCoefs}
   \end{figure}
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
-                legend pos=south west, 
-                %yticklabels={,,}, 
-                xlabel={$L$}, ylabel={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
-
-                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u errorreduced
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {9*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.65*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.15*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.50,0.52) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \node [draw=none] at (axis description cs:0.60,0.82) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.6,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
                 ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-
-                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_complexSol.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
-                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
-
-                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
-                \legend{exact,$L=4$, $L=5$}
+
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:2.5] {2*(1/2^(-3/2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:2.5] {1.35*(1/2^(-1/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.70,0.7) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3/2})$};
+                \node [draw=none] at (axis description cs:0.7,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{1/2})$};
+
+                \legend{$k=2$,$k=3$}
+
             \end{groupplot}
@@
     \end{center}
-    \caption{We consider the approximation of \eqref{eq:1D:complicatedSol} with $h = 1/2^{(L+1)}$ and $\Delta t = 1/2^L$.}
-    %\label{fig:2DjumpCoefs}
-  \end{figure}
-
-\subsection{Example in two space dimensions}
-\subsubsection{Simple example} We extend the function defined in \eqref{eq:1D:exact:simple} to the two dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
-we consider the one dimensional solution in the $x$-direction.
-
-\begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-
-                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-
-                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Convergence of $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
+    \caption{For $c_1 = 2.5$, $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left).}
     \label{fig:2DjumpCoefs}
@@
 \subsubsection{Snell's law... }
-\noindent Finally, we consider a more elaborate example.
-We divide the unit-square $\Omega = [0,1]^2$ into $\Omega_1 = (0,0.5)^2$ and $\Omega_2 = (0.5,1)^2$ and fix the wave-speed $c_1 = 1$ in $\Omega_1$.
-Then, we consider the initial conditions
+\noindent Finally, we consider a more elaborate example. We consider the initial conditions 
 \begin{align*}

### 2024-03-28 tex/main.tex
Data transfer

@@
 
-\title{Data assimilation for the wave equation with discontinuous coefficients}
+\title{A numerical study of variational data assimilation for the wave equation in heterogeneous media}
 
@@
 \section{Introduction}
-\noindent In this article, we consider the discretization of a unique continuation problem for the wave equation with discontinuous coefficients.
+\noindent In this article, we consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
 In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$ such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
@@
 \begin{equation*}
-    \wop u := \partial_t^2 - \div(c(x)^2 \nabla u).
+    \wop u := \partial_t^2 - \div(c^2 \nabla u).
 \end{equation*}
@@
 \end{equation}
-To ensure that the problem is well-posed, one usually prescribes initial data 
+To ensure that the problem is well posed, one usually prescribes initial data
 \begin{equation}\label{eq:initialData}
-    (u,\dt u) \vert_{t = 0} = (u_0,u_1) \text{ in } \Omega. \tag{IVP} 
-\end{equation}
+    (u,\dt u) \vert_{t = 0} = (u_0,u_1) \text{ in } \Omega, \tag{IVP} 
+\end{equation}
+where $u_0 \in H^1(Q)$ and $u_1 \in L^2(Q)$ are given.
+For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:initialData} in heterogeneous media we refer to \cite{StolkPhD}.
 Here we will consider a data assimilation problem instead, i.e.
-we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in $\omega_T$:
+we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in the data domain $\omega_T$:
 \begin{equation}\label{eq:dataMatch}
@@
 
-\noindent If $\partial \Omega$ is stricly convex and $c_i = 1$, $i = 1,2$, the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is Lipschitz stable if the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}.
-More precisely, we have the following theorem.
+\noindent In a homogeneous medium, where $c_i = 1$, $i = 1,2$, the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-studied \cite{BFO20,BFMO21,DMS23}.
+In particular, it is known that if the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92} then the problem is Lipschitz stable.
+To be more precise, we have the following result.
 
@@
 \end{proof}
-
-\noindent In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
-However, in the general case where $c_1 \not = c_2 \not = 1$, the above result is not applicable.
-Let $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$, where $d_c$ is the metric induced by the wave speed $c$.
-Then, we have the following result \cite[Thm.
-5.17]{Filippas22}:
+In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
+
+\noindent For the heterogeneous case where $c_1 \not =  c_2$, the problem is less studied.
+In the absence of the GCC, we have to assume that the final time $T$ is large enough to ensure that problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-posed.
+To be precise, Holmgren's unique continuation theorem guarantees that \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is uniquely solvable if
+\begin{equation}\label{eq:Tcondition}
+    T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T),
+\end{equation}
+where $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$ with $d_c$ being the distance function defined as the length of the shortest continuous path in $\Omega$ connecting $x$ and $y$ with respect to the metric adapted to the discontinuous wave speed $c$.
+While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} can be poor.
+In fact, it has been shown \cite[Thm.
+5.17]{Filippas22} that the assumption \eqref{eq:Tcondition} only guarantees the following result:
 \begin{thm}[Thm. 5.17 of \cite{Filippas22}]\label{thm:filippas}
-    Let $\omega_T \subset \Omega$ be nonempty and $T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T)$.
+    Let $\omega_T \subset \Omega$ be nonempty and let $T$ be s.t.
+\eqref{eq:Tcondition} holds.
 Then, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving \eqref{eq:waveEquation}-\eqref{eq:initialData} one has for any $\mu > 0$ that
@@
 
-We note that the assumption that $T > 2 \sup_{x \in \Omega} \text{dist}(x,\omega)$ is in general weaker than the GCC.
+\noindent In this article, we introduce a discontinuous in time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} in the heterogeneous case.
+In particular, we want to investigate numerically if the following assumption is justified.
+
+\begin{assum}\label{assum:LipschitzStability}
+    If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimates
+    \begin{align*}
+        \Vert \phi \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt \phi \Vert_{L^2(0,T;H^{-1}(\Omega))} &\le C \left(  \Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \square_c \phi \Vert_{H^{-1}(Q)} \right), \\
+        \Vert \phi \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert \dt \phi \vert_{t = 0} \Vert_{H^{-1}(\Omega)} &\le C \left(\Vert \phi \Vert_{L^2(\omega_T)} + \Vert \phi \Vert_{L^2(\Sigma)} + \Vert \square_c \phi \Vert_{H^{-1}(Q)} \right).
+    \end{align*}
+\end{assum}
 
 \section{Discretization (fully discrete \& dG in time)} 
-\noindent In \cite{BP24} a fully discrete FEM using dG in time was introduced for the wave equation. Here, we consider a similar scheme that incoporates the discontinuous wave speed $c$.
+\noindent In this section, we introduce a fully discrete discontinuous in time finite element method to discretize the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} for the wave equation in heterogeneous media.
+The discretization is based on the scheme introduced in \cite{BP24} for the homogeneous case.
+Before introducing the method in Section \ref{sec:method}, we introduce a geometric partition of the space-time domain $Q$ into time slabs in Section \ref{sec:spaceTimeDiscretization}.
+
+\subsection{Discretization of the space-time domain}\label{sec:spaceTimeDiscretization}
 Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
@@
 
+\subsection{A discontinuous in time FEM for the data assimilation problem}\label{sec:method}
 \noindent We define the discontinuous in time finite element spaces 
@@
 \end{equation}
-
-\noindent In the following, we denote
+For elements of $\ProdFullyDiscrSpace{k}{q}$, we use the notation $\Uh = (\ul_1,\ul_2) \in \ProdFullyDiscrSpace{k}{q}$. In the following, we denote
 \begin{equation*}
-    a(u,v)_{Q^n} := \int_{I_n} \int_{\Omega} c(x)^2 \nabla u \cdot \nabla v \ \dX \dT,
+    a(u,v)_{Q^n} := \int_{I_n} \int_{\Omega} c^2 \nabla u \cdot \nabla v \ \dX \dT,
 \end{equation*}
@@
         A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \Big\{ &(\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} \\
-        &- (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \Big\},
+        &- (c^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \Big\},
     \end{aligned}
@@
 \begin{align*}
-    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c(x)^2 \nabla \ul_1}, \jump{c(x)^2 \nabla \wl_1})_F \ \dT, \\
-    G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c(x)^2 \nabla \ul_1),\dt \wl_2 -\div( c(x)^2 \nabla \wl_1))_K \ \dT, \\
+    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c^2 \nabla \ul_1}, \jump{c^2 \nabla \wl_1})_F \ \dT, \\
+    G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c^2 \nabla \ul_1),\dt \wl_2 -\div( c^2 \nabla \wl_1))_K \ \dT, \\
     I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \qquad 
@@
 \begin{align*}
-    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c(x)^2 \jump{\nabla \ul_1^n},c(x)^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
+    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c^2 \jump{\nabla \ul_1^n},c^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
     \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
@@
 \end{alignat*}
-In a more compact form, we can write theses conditions as: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that
+In a more compact form, we can write these conditions as: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that
 \begin{equation}\label{eq:discreteProblem}
@@
 
-\section{Analysis}
+\section{Error analysis}
 \noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
 In particular, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in suitable discrete norms defined below.
+Then, we show that under Assumption \ref{assum:LipschitzStability}, we can recover convergence rates in a physically relevant norm.
 Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
@@
 \end{equation}
-and its strenghend version
+and its strengthened version
 \begin{equation}\label{eq:tnormwop}
@@
 \begin{proof}
-    It suffices to show that $\tnorm{(\Uh,\Zh)} = 0$ implies that $\Uh=\Zh= 0$.
-We first note that $\vert \Uh \vert_{\uparrow \downarrow} = 0$ immediately implies that $(\ul_1,\ul_2) \in [H^1(Q)]^2$.
-Furthermore, by definition of $\tnorm{(\cdot,\cdot)}$ and definition the stabilization terms $S_h$ and $S_h^{\ast}$, we have that $\Zh = 0$, $\ul_1 \vert_{\Sigma} = 0$, $\ul_1 \vert_{\omega_T} = 0$ and $\dt \ul_1 = \ul_2$.
+    It suffices to show that $\tnorm{(\cdot,\cdot)}$ is a norm.
+Since $\tnorm{(\cdot,\cdot)}$ is a semi-norm by definition, we only require that $\tnorm{(\Uh,\Zh)} = 0$ implies $\Uh=\Zh= 0$.
+Assume that $\tnorm{(\Uh,\Zh)} = 0$.
+Then, in particular, $\vert \Uh \vert_{\uparrow \downarrow} = 0$ and therefore $(\ul_1,\ul_2) \in [H^1(Q)]^2$.
+Furthermore, by definition of the stabilization terms $S_h$ and $S_h^{\ast}$, we have that $\Zh = 0$, $\ul_1 \vert_{\Sigma} = 0$, $\ul_1 \vert_{\omega_T} = 0$ and $\dt \ul_1 = \ul_2$.
 Similar to \cite[Lem.
-2.1]{BP24}, we have with partial integration that
+2.1]{BP24}, partial integration yields
     \begin{align*}
-        \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} &:= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c(x)^2 \nabla \ul_1 \nabla y \right\}  \\
+        \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} &:= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c^2 \nabla \ul_1 \nabla y \right\}  \\
         &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} \\
-        &\qquad+ \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c(x)^2 \nabla \ul_1),y)_{K} \ \dT \\
-        &\qquad + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c(x)^2 \nabla \ul_1}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\}.
+        &\qquad+ \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c^2 \nabla \ul_1),y)_{K} \ \dT \\
+        &\qquad + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c^2 \nabla \ul_1}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\}.
     \end{align*}
-    Thus it follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
+    It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
 Thus, $\ul_1$ solves \eqref{eq:waveEquation} and by taking $\mu \rightarrow \infty$ in Thm.
-\ref{thm:filippas}, it follows that the initial data is zero.
-As solutions to \eqref{eq:waveEquation} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
+\ref{thm:filippas}, we conclude that $u_0 = u_1 = 0$.
+As solutions to \eqref{eq:waveEquation}-\eqref{eq:initialData} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
 \end{proof}
 
-\noindent A direct consequence of this result is that the bilinear form $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
+\noindent From this result it directly follows that the bilinear form $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
 
@@
 \begin{proof}
-    First of all, we note that 
-    \begin{equation*}
-        B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}.
-    \end{equation*} 
-    As a direct consequence, we have that 
+    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, it directly follows that  
     \begin{align*}
@@
 
-\noindent Using the inf-sup stability of $B$ and the continuity of $A$, we can show that the approximation error in the $\tnorm{(\cdot,\cdot)}$-norm scales like the best approximation error.
+\noindent Using the inf-sup stability of $B$ and the continuity of $A$, we can show that the approximation error in the $\tnorm{(\cdot,\cdot)}$-norm is bounded by the best approximation error in the $\tnorm{(\cdot,\cdot)}_{\wop}$-norm.
 
@@
 
+\noindent In the following, we want to show how the assumption of Lipschitz stability, cf.
+Assumption \ref{assum:LipschitzStability} or Thm.
+\ref{thm:Lipschitz} in the homogeneous case, can be used to show convergence in a physically relevant norm.
+To apply these results, we deal with the fact that the discrete solution is discontinuous in time by introducing a suitable lifting operator $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as discussed in \cite[Sec.
+4]{BP24}.
+
+\begin{thm}
+    Let Assumption \ref{assum:LipschitzStability} be satisfied.
+For $u$ being a sufficiently regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ being the solution to \eqref{eq:discreteProblem}, there exists a constant $C>0$ such that
+    \begin{equation}
+        \Vert u - L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt (u - L_{\Delta t} \ul_1) \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C h^s \Vert u \Vert_{H^m(Q)}. 
+    \end{equation}
+    In particular, we have that 
+    \begin{equation}
+        \Vert u_0 - \ul_1 \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert u_1 - (\dt \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C h^s \Vert u \Vert_{H^m(Q)}.
+    \end{equation}
+\end{thm}
+
+\begin{proof}
+    The proof follows from the same argumentation as the proof of \cite[Thm. 4.4]{BP24}.
+\end{proof}
+
 \begin{rmk}[Homogenous media]\label{rem:homMedia}
-    Assume that the set $\omega_T \subset \Omega$ fulfills the GCC.
-In the case where $c_i = 1$, $i = 1,2$, we can apply the Lipschitz stability result from Thm.
-\ref{thm:Lipschitz} to proof convergence in a physically relevant norm, see \cite[Thm.
+    In the homogenous case where $c_i = 1$, $i = 1,2$, we know that assumption \ref{assum:LipschitzStability} is satisfied, cf.
+Thm.
+\ref{thm:Lipschitz}.
+Thus, we recover the result from \cite[Thm.
 4.4]{BP24}.
-As discussed in \cite[Sec.
-4]{BP24}, there exists a suitable lifting operator $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ such that $L_{\Delta t} \ul_1 \in H^1(Q)$.
-Thus, applying Thm.
-\ref{thm:Lipschitz} and Cor.
-\ref{cor:tnormConvRates} to the residual $u - L_{\Delta t} \ul_1$ yields that
-    \begin{equation}\label{eq:homMedia:estimate}
-        \Vert u - L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}  + \Vert \dt (u - L_{\Delta t} \ul_1) \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C h^s \Vert u \Vert_{H^m(Q)}. 
-    \end{equation}
 \end{rmk}
 
-\textbf{discuss what we expect in the heterogenous case...}
-
-\noindent \textbf{Assume for now} that we can rewrite the estimates from Thm.
-\ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
-As discussed in Rem.
-\ref{rem:homMedia}, we can then apply this continuum estimate to the residual $\tilde{e}_h := u - L_{\Delta t} \ul_1$, where the lifting operator $L_{\Delta t}$ ensures that $\tilde{e}_h \in H^1$.
-Following the argumentation from \cite[Thm.
-4.4]{BP24}, it follows that
-\begin{equation}
-    \Vert \ul_1 - L_{\Delta t} \ul_1 \Vert_{L^2(\omega_T)} \le C h^s \Vert u \Vert_{H^m(Q)}, 
-\end{equation}
-and $\Vert u - \ul_1 \Vert_{L^2(\omega_T)} \le \tnorm{(\mathbf{U}-\Uh,\Zh)}$ by definition of the triple-norm, it follows from Cor.
-\ref{cor:tnormConvRates} that $\Vert \tilde{e}_h \Vert_{L^2(\omega_T)} \le C h^s \Vert u \Vert_{H^m(Q)}$.
-Furthermore, \textbf{with similar arguments as in} \cite[Thm.
-4.4]{BP24}, we obtain that
-\begin{equation}
-    \Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)} \le C h^s \Vert u \Vert_{H^m(Q)}. 
-\end{equation}
-Thus, \eqref{eq:FilippasEstimateLog} yields 
+\begin{rmk}
+    If assumption \ref{assum:LipschitzStability} is not satisfied, e.g.
+if the GCC is not fulfilled, we can still apply the results from Thm.
+\ref{thm:filippas} if $T > 2 \sup_{x \in \Omega} \text{dist}_c(x,\omega)$.
+\textbf{For this we require:}
+    \begin{itemize}
+        \item control of $\Vert (u_0,u_1) \Vert_{H^1 \times L^2}$ (discrete), e.g. through Tikhonov regularization,
+        \item being able to rewrite the estimates from Thm. \ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$,
+    \end{itemize}
+    Then, we obtain 
     \begin{equation}
@@
     where $C_{0,1} := \Vert (u_0,u_1) \Vert_{H^1 \times L^2}$.
-While this estimates holds under the general condition $T > 2 \sup_{x \in \Omega} d_c(x,\omega_T)$, we suspect that under the assumption of the geometric control condition, the estimate can be improved considerably.
-In particular, the numerical experiments considered in the following section suggest that a similar estimate to \eqref{eq:homMedia:estimate} holds in the heterogenous case.
+\end{rmk}
 
@@
             %L-infty-L2-u (k = 2)
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
             %L-infty-L2-u (k = 3)
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
 
@@
             %L-infty-L2-u (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
             %L-infty-L2-u (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
 
@@
             ]
-            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
 
@@
             ]
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../../wave_data_assimilation/data/jumpCoefs/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
 
@@
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
 
@@
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
 
@@
                 %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
 
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
-
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
+
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
 
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
 
@@
                 \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
 
@@
                 ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
 
@@
 
-                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_complexSol.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
 
@@
 \subsubsection{Simple example} 
-As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
+As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
 we consider the original solution in the $x$-direction.
@@
                 ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
 
                 %L-infty-L2-u errorreduced
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
 
@@
 
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
 
                 %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
 

### 2024-03-28 tex/main.tex
Updates from Overleaf
GCC figure & Plot update

@@
 \subsection{Examples in one space dimension}
+\noindent We consider the unit interval $\Omega \coloneqq [0,1] \subset \mathbb{R}$.
+For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$.
+The time step is chosen as $\Delta t = h$.
 
 \subsubsection{Simple Example}\label{sec:numex:1D:simple}
-\noindent We set $\Omega \coloneqq [0,1]$ and define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
+\noindent We define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
 Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
-As a first example, we consider the following exact solution considered in \cite{MHI08}
+As a first example, we consider the following exact solution \cite{MHI08}
 \begin{equation}\label{eq:1D:exact:simple}
@@
 \end{equation}
-In one space dimension, the domain $\omega_T$ fulfills the GCC if and only if $T > 2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, where $\operatorname{dist}_c(x,\omega_T)$ denotes the distance of $x$ to $\omega_T$ with respect to the rescaled metric $d_c$.
+Note that in one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC.
 Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric.
-Then, we have that
-\begin{equation}
-    d_c(x,y) \coloneqq \mathbbm{1}_{\Omega_1} c_1(x)^{-1} d(x,y) + \mathbbm{1}_{\Omega_2} c_2(x)^{-1} d(x,y), \quad x,y \in \Omega.
-\end{equation} 
-Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, we require that $T > 0.25(1+c_1^{-1})$.
-
-and \textbf{compute until $T = 1.0$, correct...} to ensure that the GCC is fulfilled.
-Furthermore, we set $h = 1/2^{1+L}$ and $\Delta t = h/2$ for different refinement levels $L \in \{1,2,3,4\}$.
-The results of the experiments can be found in Fig.
-\ref{fig:jumpCoefs:contrast:2.5} and Fig.
-\ref{fig:jumpCoefs:quality}.
-...
-\\
+Then, we set
+\begin{equation}
+    d_c(x,y) \coloneqq \mathbbm{1}_{\Omega_1} c_1(x)^{-1} d(x,y) + \mathbbm{1}_{\Omega_2} d(x,y), \quad x,y \in \Omega.
+\end{equation} 
+Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[scale=3]
+        \draw[-stealth] (-0.15,0) -- (1.15,0); 
+        \draw[-stealth] (0,-0.15) -- (0,1.15);
+        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
+        \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.5,0) -- (0.5,1) -- (0,1) -- cycle;
+        \draw[-stealth] (0.5,0) -- (1,0.5) -- (0.5,1);
+        \node at (-0.15,1) {\footnotesize $T$}; 
+        \node at (0.75,-0.15) {\footnotesize $\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
+        \node at (1.15,0.5) {\footnotesize $t_0$};
+        \draw (0.7,0) to[bend right=45] (0.65,0.15); 
+        \node at (0.6,0.05) {\footnotesize $\alpha$};
+        \node at (0.25,0.5) {\footnotesize $\omega_T$};
+        \begin{scope}[xshift=2cm]
+            \draw[-stealth] (-0.15,0) -- (1.15,0); 
+            \draw[-stealth] (0,-0.15) -- (0,1.15);
+            \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
+            \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.25,0) -- (0.25,1) -- (0,1) -- cycle;
+            \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,0) -- (1,0) -- (1,1) -- (0.75,1) -- cycle;
+            \draw[-stealth] (0.25,0) -- (0.75,0.5);
+            \node at (-0.15,1) {\footnotesize $T$}; 
+            \node at (0.5,-0.15) {\footnotesize $2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
+            \node at (0.67,0.5) {\footnotesize $t_0$};
+            \draw (0.45,0) to[bend right=45] (0.4,0.15); 
+            \node at (0.35,0.05) {\footnotesize $\alpha$};
+            \node at (0.125,0.5) {\footnotesize $\omega_T$};
+            \node at (0.875,0.5) {\footnotesize $\omega_T$};
+        \end{scope}
+    \end{tikzpicture}
+    \caption{(\textbf{Can be deleted lateron, only for our own understanding:}) Illustration of the GCC and condition \eqref{eq:Tcondition} in one space dimension.
+The geometrical setup where the data is given only in one half of the domain is the worst case, because the ray can be reflected at the boundary.
+We still calculate that $1 = \tan(\alpha) = t_0 / \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, i.e.
+$T > 2 t_0 = 2\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$ is required for the GCC.
+Note we can also assume that $c_1 = c_2 = 1$, because the metric is rescaled wrt to the wavespeed.
+Could probably show that the GCC and the condition on $T$ are in fact equivalent in one dimension.}
+\end{figure}
+
+\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
+In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
+Figures \ref{fig:jumpCoefs:quality} and \ref{fig:jumpCoefs:increasingcontrast} show that ...
 
@@
             ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
 
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
             ]
+
             %L2-L2-u_t (k = 2)
@@
             \legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
 
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
     \end{center}
-    \caption{We consider the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ for contrast $c_1 = 2.5$ (left \& middle).
-Both, the $L^\infty(0,T;L^2(\Omega_R))$-error of $u-u_h$ (left) and the $L^2(0,T;L^2(\Omega_R))$-error of $\dt (u-u_h)$ (middle) converge with order $\mathcal{O}(h^k)$ and are close to the respective error of the $L^2$-bestapproximation (dashed lines).
-For increasing contrast $c_1$, both errors increase with the same order of magnitude as the respective best approximation error (right).
-\textbf{left is with $T = 0.5$, the increasing contrast is still with $T = 1.0$ and not on $\Omega_R$..., also adjust the time step...}, rewrite..., plot $\mathcal{O}(\log(h))$ ...
-}
+    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
+We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
+The gray dashed lines indicate the observed convergence rates.}
     \label{fig:jumpCoefs:contrast:2.5}
@@
     \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
-We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ decreases with the constrast $c_1$ while keeping the GCC fulfilled.}
+We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
     \label{fig:jumpCoefs:increasingcontrast}
@@
     \end{center}
-    \caption{Exact solution and approximations with $k = 3$ on different refinement levels for $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).}
+    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
     \label{fig:jumpCoefs:quality}
@@
 \noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
-For points $p_1,p_2 \in (0,1)$, we decompose the interval $\Omega = [0,1]$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
+For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
 $\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$.

### 2024-03-29 tex/main.tex
GCC Remarks, Minor

@@
 In particular, it is known that if the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92} then the problem is Lipschitz stable.
-To be more precise, we have the following result.
+Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
+For a precise definition, we refer to \cite{BLR88,BLR92}.
+Assuming that the GCC is satisfied, we have the following result.
 
@@
 \end{proof}
-In that case, this estimate can be applied to $\phi = u-u_h$ to recover convergence rates in terms of the norm on the left-hand side.
 
@@
 Then we define the primal stabilizer $S_h$ as 
-\begin{equation}
+\begin{equation}\label{eq:primalStab}
     S_h(\Uh,\Wh) := J(\Uh,\Wh) + I_0(\Uh,\Wh) + G(\Uh,\Wh) + R(\Uh,\Wh), 
@@
 \ref{thm:Lipschitz} in the homogeneous case, can be used to show convergence in a physically relevant norm.
-To apply these results, we deal with the fact that the discrete solution is discontinuous in time by introducing a suitable lifting operator $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as discussed in \cite[Sec.
+To utilize these results, we need to deal with the fact that the discrete solution is discontinuous in time.
+To this end, let $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ be a suitable lifting operator such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as discussed in \cite[Sec.
 4]{BP24}.
-
-\begin{thm}
+Then, we formulate the following result.
+
+\begin{thm}\label{thm:convergence}
     Let Assumption \ref{assum:LipschitzStability} be satisfied.
@@
 \begin{rmk}[Homogenous media]\label{rem:homMedia}
-    In the homogenous case where $c_i = 1$, $i = 1,2$, we know that assumption \ref{assum:LipschitzStability} is satisfied, cf.
+    In the homogenous case where $c_i = 1$, $i = 1,2$, we know that Assumption \ref{assum:LipschitzStability} is satisfied, cf.
 Thm.
@@
 \begin{rmk}
-    If assumption \ref{assum:LipschitzStability} is not satisfied, e.g.
-if the GCC is not fulfilled, we can still apply the results from Thm.
-\ref{thm:filippas} if $T > 2 \sup_{x \in \Omega} \text{dist}_c(x,\omega)$.
-\textbf{For this we require:}
-    \begin{itemize}
-        \item control of $\Vert (u_0,u_1) \Vert_{H^1 \times L^2}$ (discrete), e.g. through Tikhonov regularization,
-        \item being able to rewrite the estimates from Thm. \ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$,
-    \end{itemize}
-    Then, we obtain 
-    \begin{equation}
-        \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1},
-    \end{equation} 
-    where $C_{0,1} := \Vert (u_0,u_1) \Vert_{H^1 \times L^2}$.
+    Suppose that Assumption \ref{assum:LipschitzStability} is not satisfied, e.g.
+if the GCC is not fulfilled.
+If $T$ is large enough such that \eqref{eq:Tcondition} holds, we can still apply the results from Thm.
+\ref{thm:filippas}.
+To utilize this result similarly to Assumption \ref{assum:LipschitzStability}, we would have to deal with the following technicalities:
+    \begin{enumerate}
+        \item The results from Thm.
+\ref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$.
+However, we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$.
+Thus, we would have to rewrite the estimates from Thm.
+\ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
+To this end, one might be able to shift the regularity suitably, cf.
+\cite[Sec.
+2.6]{StolkPhD}, or use similar arguments as in \cite[Thm.
+A.1]{BFMO21}.
+        \item We have to ensure that the constants in the estimates from Thm.
+\ref{thm:filippas} remain bounded when we consider the residual $\tilde{e}_h$.
+In particular, we have to control $C_{0,1} := \Vert (\tilde{e}_h \vert_{t = 0}, \dt \tilde{e}_h \vert_{t = 0}) \Vert_{H^1 \times L^2}$.
+We note that we can always ensure that $C_{0,1}$ is bounded by adding a suitable Tikhonov regularization term to \eqref{eq:primalStab}.
+    \end{enumerate}
+    Then, we can use the arguments of \cite[Thm. 4.4]{BP24} to show that 
+    \begin{equation}
+        \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1}. 
+    \end{equation}
 \end{rmk}
@@
 
-\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
+\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
 In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
@@
             ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
 
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
             \legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
 
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
             legend pos=south west, %yticklabels={,,},
@@
     \end{center}
-    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
+    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
 We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
@@
             ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
@@
             \legend{$T = 0.5$, $L^2$-best approx. ($T = 0.5$), $T$ variable, $L^2$-best approx. ($T$ variable)}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             legend pos=south east, %yticklabels={,,},
@@
     \end{center}
-    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
+    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
 We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
@@
 As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
-Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ and $c_1 = 7.5$.
+For contrast $c_1 \in \{ 7.5,11.5 \}$, Fig.
+\ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
 
@@
     \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 7.5$ and $c_2 = 1.0$.}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
+We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
     \label{fig:jumpCoefs:multipleJumps}
@@
     \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = T/2 = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (upper) and $c_1 = c_3 = 7.5$, $n = 3$ (lower) and $c_2 = 1.0$.
-We only prescribe data on $\omega = [0.0,0.3]$ and choose $\Delta t = 1/32$ (upper) and $\Delta t = 1/64$ (lower), $h = 1/64$.}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
+We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
     \label{fig:jumpCoefs:multipleJumps:noGCC}
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
                 legend pos=south west, %yticklabels={,,},
@@
                 \legend{$k=2$,best,$k = 3$,best}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
                 legend pos=south west, %yticklabels={,,},
@@
 
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
                 legend pos=south west, %yticklabels={,,},
@@
 
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
                 legend pos=south west, %yticklabels={,,},
@@
                 %yticklabels={,,}, 
-                xlabel={$L$}, ylabel={$\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                xlabel={$L$}, ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
                 ]
@@
     \end{center}
-    \caption{We consider the approximation of \eqref{eq:1D:complicatedSol} with $h = 1/2^{(L+1)}$ and $\Delta t = 1/2^L$, \textbf{now $\Delta t = 1/2^{L+1}$ on the right}.}
+    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
     %\label{fig:2DjumpCoefs}
@@
     \end{center}
-    \caption{Convergence of $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
+    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
     \label{fig:2DjumpCoefs}
@@
     \end{center}
-    \caption{For $c_1 = 2.5$, $\Vert \dt(u-u_h) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left).}
+    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
     \label{fig:2DjumpCoefs}
@@
                 vertical sep=2cm,
-                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u - u_h) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
+                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
                 legend pos=south east, %ymax = 1e2, %yticklabels={,,},

### 2024-05-14 tex/main.tex
Updates from Overleaf
Minor

@@
 
-\affil[2]{\orgdiv{Institute for Numerical and Applied Mathematics}, \orgname{University of G\"{o}ttingen}, \orgaddress{\street{Lotzenstr.}, \city{G\"{o}ttingen}, \postcode{37083}, \country{Germany}}}
+\affil[2]{\orgdiv{Institute for Numerical and Applied Mathematics}, \orgname{University of G\"{o}ttingen}, \orgaddress{\street{Lotzestr.
+16-18}, \city{G\"{o}ttingen}, \postcode{37083}, \country{Germany}}}
 
@@
 For any nonempty subset $\omega \subset \Omega$, we set $\omega_T \coloneqq (0,T) \times \omega$.
-In the following, let $\wop$ be the wave operator defined as
+In the following, let $\wop$ be the wave operator with discontinuous wave-speed defined as
 \begin{equation*}
@@
 For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:initialData} in heterogeneous media we refer to \cite{StolkPhD}.
-Here we will consider a data assimilation problem instead, i.e.
-we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in the data domain $\omega_T$:
+Here we consider a data assimilation problem instead, i.e.
+we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in a data domain $\omega_T$, $\omega \subset \Omega$, $\omega \not = \emptyset$:
 \begin{equation}\label{eq:dataMatch}
@@
 While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} can be poor.
-In fact, it has been shown \cite[Thm.
-5.17]{Filippas22} that the assumption \eqref{eq:Tcondition} only guarantees the following result:
+It has been shown \cite[Thm.
+5.17]{Filippas22} under the assumption \eqref{eq:Tcondition} the following stability result holds:
 \begin{thm}[Thm. 5.17 of \cite{Filippas22}]\label{thm:filippas}
@@
 The discretization is based on the scheme introduced in \cite{BP24} for the homogeneous case.
-Before introducing the method in Section \ref{sec:method}, we introduce a geometric partition of the space-time domain $Q$ into time slabs in Section \ref{sec:spaceTimeDiscretization}.
+Before introducing the method in Section \ref{sec:method}, we describe the geometric partition of the space-time domain $Q$ into time slabs in Section \ref{sec:spaceTimeDiscretization}.
 
 \subsection{Discretization of the space-time domain}\label{sec:spaceTimeDiscretization}
-Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
+Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ with mesh size $h$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
 Note that the triangulation can be constructed such that for $h$ small enough the following continuous trace inequality holds \cite[Sec.
@@
     \begin{aligned}
-        \tnorm{(\Uh, \Zh)}^2_{\wop} := \tnorm{(\Uh, \Zh)}^2 &+ \sum_{n = 0}^{N -1} \Big\{ \Vert \dt u_2 \Vert^2_{Q^n} + \Vert c^2 \nabla u_1 \Vert^2_{Q^n} + \Vert \dt u_1 \Vert^2_{Q^n} \\
-        &+ \Vert u_2 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 u_1 \Vert^2_{H^2(K)} \dT \Big\}. 
+        \tnorm{(\Uh, \Zh)}^2_{\wop} := \tnorm{(\Uh, \Zh)}^2 &+ \sum_{n = 0}^{N -1} \Big\{ \Vert \dt \ul_2 \Vert^2_{Q^n} + \Vert c^2 \nabla \ul_1 \Vert^2_{Q^n} + \Vert \dt \ul_1 \Vert^2_{Q^n} \\
+        &+ \Vert \ul_2 \Vert^2_{Q^n} + \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert c^2 \ul_1 \Vert^2_{H^2(K)} \dT \Big\}. 
     \end{aligned}
@@
 \begin{proof}
-    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, it directly follows that  
+    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, we conclude that  
     \begin{align*}
@@
 \begin{proof}
-    Due to the assumption that $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, we have that 
+    Due to the assumption that $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, there exists $C > 0$ s.t.  
     \begin{equation*}
@@
 
-\noindent In the following, we want to show how the assumption of Lipschitz stability, cf.
+\noindent In the following, we want to note that the assumption of Lipschitz stability, cf.
 Assumption \ref{assum:LipschitzStability} or Thm.
@@
 To utilize these results, we need to deal with the fact that the discrete solution is discontinuous in time.
-To this end, let $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ be a suitable lifting operator such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as discussed in \cite[Sec.
+To this end, let $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ be a suitable lifting operator such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as introduced in \cite[Sec.
 4]{BP24}.

### 2024-12-06 tex/main.tex
elaborate on mesh

@@
 \subsection{Discretization of the space-time domain}\label{sec:spaceTimeDiscretization}
-Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ with mesh size $h$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. 
-Note that the triangulation can be constructed such that for $h$ small enough the following continuous trace inequality holds \cite[Sec.
-4.2]{BFMO21control}: For all $v \in [H^1(K)]^d$ and $K \in \mathcal{T}_h$, we have
+\todo[inline]{ $\mathcal{T}_h$ is not quasi-uniform. Introduce $ \hat{\mathcal{T}}_h$   }
+Let $\hat{\mathcal{T}}_h$ be a quasi-uniform triangulation with mesh size $h$ such that $\hat{\Omega}:= \cup_{K \in \hat{\mathcal{T}}_h} K $ contains $\Omega$, i.e.\ $\Omega \subset \hat{\Omega}$.
+Setting $\mathcal{T}_h := \{ K \cap \Omega \mid K \in  \hat{\mathcal{T}}_h \}$ then ensures that $\Omega = \cup_{K \in \mathcal{T}_h} K$ holds true.
+We recall from  \cite[Sec.
+4.2]{BFMO21control} that the triangulation $\{ \hat{\mathcal{T}}_h \mid h > 0 \}$ can be constructed such that for $h$ small enough the following continuous trace inequality holds:  For all $v \in [H^1(K)]^d$ and $K \in \mathcal{T}_h$, we have
 \begin{equation}\label{eq:traceInequality}
@@
 \end{equation}
+We assume in what follows additionally that the triangulation $\mathcal{T}_h$ fits the interface $\Gamma$ and the data domain $\omega$.
+An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP23arxiv} but is certainly beyond the scope of this article.
 

### 2024-12-06 tex/main.tex
restructuring

@@
-%3 May 2012
 %\documentclass[10pt,reqno]{amsart}
@@
 
+\providecommand{\jp}[1]{\newline {\color{cyan} \hspace*{-0.5cm} $\rightsquigarrow$ \underline{\textbf{JP:}} \textit{#1} \newline}}
+
 \date{\today}
@@
 \subsection{Discretization of the space-time domain}\label{sec:spaceTimeDiscretization}
-\todo[inline]{ $\mathcal{T}_h$ is not quasi-uniform. Introduce $ \hat{\mathcal{T}}_h$   }
 Let $\hat{\mathcal{T}}_h$ be a quasi-uniform triangulation with mesh size $h$ such that $\hat{\Omega}:= \cup_{K \in \hat{\mathcal{T}}_h} K $ contains $\Omega$, i.e.\ $\Omega \subset \hat{\Omega}$.
@@
 
+\subsection{Example in two space dimensions}
+\noindent In this section, we present numerical examples in two space dimensions.
+We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
+
+\subsubsection{Simple example} 
+As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
+we consider the original solution in the $x$-direction.
+We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
+To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
+We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
+As before, we fix $c_2 = 1$ and consider different values for $c_1$.
+The results of the experiment are presented in Fig.
+\ref{fig:2DjumpCoefs}.
+
+\begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+
+                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+
+                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u errorreduced
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {9*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.65*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.15*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.50,0.52) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \node [draw=none] at (axis description cs:0.60,0.82) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.6,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:2.5] {2*(1/2^(-3/2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:2.5] {1.35*(1/2^(-1/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.70,0.7) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3/2})$};
+                \node [draw=none] at (axis description cs:0.7,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{1/2})$};
+
+                \legend{$k=2$,$k=3$}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
+
+\begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=1 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
+                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
+
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Filippas lambda... (2D), noGCC}
+  \end{figure}
+\end{comment}
+
 \subsubsection{2nd one dimensional example}
+
+~\jp{I am not sure whether this section really fits into the narrative ... Shall we just remove it?}
 We consider the same geometrical setup as in Sec.
@@
 
-\subsection{Example in two space dimensions}
-\noindent In this section, we present numerical examples in two space dimensions.
-We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
-
-\subsubsection{Simple example} 
-As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
-we consider the original solution in the $x$-direction.
-We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
-To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
-We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
-As before, we fix $c_2 = 1$ and consider different values for $c_1$.
-The results of the experiment are presented in Fig.
-\ref{fig:2DjumpCoefs}.
+ \section{Conclusion}
+Lalala
+
+\appendix
 
 \begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-
-                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-
-                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u errorreduced
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {9*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.65*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.15*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.50,0.52) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \node [draw=none] at (axis description cs:0.60,0.82) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.6,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:2.5] {2*(1/2^(-3/2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:2.5] {1.35*(1/2^(-1/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.70,0.7) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3/2})$};
-                \node [draw=none] at (axis description cs:0.7,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{1/2})$};
-
-                \legend{$k=2$,$k=3$}
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-
-\begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=1 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
-                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
-
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Filippas lambda... (2D), noGCC}
-  \end{figure}
-\end{comment}
-
 \subsubsection{Snell's law... }
@@
 \end{figure}
+\end{comment}
 
 \begin{comment}
-\appendix
 \section*{Outtakes}

### 2024-12-06 tex/main.tex
more refs for homogeneous problem

@@
 
-\noindent In a homogeneous medium, where $c_i = 1$, $i = 1,2$, the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-studied \cite{BFO20,BFMO21,DMS23}.
-In particular, it is known that if the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92} then the problem is Lipschitz stable.
+%\noindent In a homogeneous medium, where $c_i = 1$, $i = 1,2$,
+\noindent In a medium without an interface the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-studied, see e.g.~References \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
+In particular, it is known that if $c_i = 1$, $i = 1,2$, the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}, then the problem is Lipschitz stable.
 Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.

### 2024-12-06 tex/main.tex
fix references

@@
 \noindent In a medium without an interface the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-studied, see e.g.~References \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
-In particular, it is known that if $c_i = 1$, $i = 1,2$, the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR88,BLR92}, then the problem is Lipschitz stable.
+In particular, it is known that if $c_i = 1$, $i = 1,2$, the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR92}, then the problem is Lipschitz stable.
 Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
-For a precise definition, we refer to \cite{BLR88,BLR92}.
+For a precise definition, we refer to \cite{BLR92}.
 Assuming that the GCC is satisfied, we have the following result.
@@
 5.17]{Filippas22} under the assumption \eqref{eq:Tcondition} the following stability result holds:
-\begin{thm}[Thm. 5.17 of \cite{Filippas22}]\label{thm:filippas}
+\begin{thm}[Thm. 5.19 of \cite{Filippas22}]\label{thm:filippas}
     Let $\omega_T \subset \Omega$ be nonempty and let $T$ be s.t.

### 2024-12-06 tex/main.tex
some small fixes

@@
 \noindent In this article, we consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
-In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$ such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
-We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma = \Omega \setminus (\Omega_1 \cup \Omega_2)$, but constant in time.
+In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$.
+We assume that $\Omega$ is split by a smooth $(d-1)$-dimensional
+interface $\Gamma$ into two disjoint components, i.e.\ $\Omega \setminus \Gamma = \Omega_1 \cup 
+\Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
+ We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma$, but constant in time.
 For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$.
@@
     \begin{align*}
-        \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} &:= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c^2 \nabla \ul_1 \nabla y \right\}  \\
-        &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} \\
-        &\qquad+ \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c^2 \nabla \ul_1),y)_{K} \ \dT \\
-        &\qquad + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c^2 \nabla \ul_1}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\}.
+	   & \Vert \wop \ul_1 \Vert^2_{H^{-1}(Q)} := \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \int_{Q} \left\{ -(\dt \ul_1) \dt y + c^2 \nabla \ul_1 \nabla y \right\}  \\
+        &= \sup_{\substack{  y \in H^1_0(Q), \\ \norm{y}_{H^1(Q) } = 1  }} \Big\{ \sum_{n = 0}^{N-1} (\ul_2 - \dt \ul_1, \dt y)_{Q_n} 
+        + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c^2 \nabla \ul_1),y)_{K} \ \dT \\
+	    & \hspace{6em} + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c^2 \nabla \ul_1 \cdot \mathbf{n}}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\},
     \end{align*}
+where $ \jump{c^2 \nabla \ul_1 \cdot \mathbf{n}}$  denotes the jump of the normal derivative over interior facets.
 It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
@@
 
-\noindent From this result it directly follows that the bilinear form $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
+\noindent From this result and the identity
+\[
+B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}
+\]
+it directly follows that the bilinear form $B$ enjoys inf-sup stability on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with respect to the $\tnorm{(\cdot,\cdot)}$-norm.
 
@@
 
-\begin{proof}
-    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, we conclude that  
-    \begin{align*}
-        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} &\frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \\
-        &\quad \ge \frac{B[(\Uh,\Zh),(\Uh,-\Zh)]}{\tnorm{(\Uh,-\Zh)}} = \tnorm{(\Uh,\Zh)}.
-    \end{align*}
-\end{proof}
-
+%\begin{proof}
+%    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, we conclude that  
+%    \begin{align*}
+%        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} &\frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \\
+%        &\quad \ge \frac{B[(\Uh,\Zh),(\Uh,-\Zh)]}{\tnorm{(\Uh,-\Zh)}} = \tnorm{(\Uh,\Zh)}.
+%    \end{align*}
+%\end{proof}
+
+We report a continuity result for the bilinear form $A$ which follows from the Cauchy-Schwarz and the trace inequality \eqref{eq:traceInequality}. 
 \begin{lem}[Continuity of $A$]\label{lem:continuityA}
-    For all $\mathbf{U} \in [H^1(Q_n) \cap L^2(0,T;H^2(\mathcal{T}_h))] \times H^1(Q_n)$ and all $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$, we have that 
+If $\mathbf{U}|_{Q^n} \in [H^1(Q^n) \cap L^2(0,T;H^2(\mathcal{T}_h))] \times H^1(Q^n)$ for $n=0,\ldots,N-1$ and for all $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$, we have that 
     \begin{equation*}
@@
 \end{lem}
-
+\begin{comment}
 \begin{proof}
@@
 \end{proof}
+\end{comment}
 
@@
     \begin{equation}
-        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \left( 1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\Uh - \Vh, 0)}_{\wop}.  
+   \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \left( 1 + \frac{C}{C_B} \right) \inf_{\Vh \in \ProdFullyDiscrSpace{k}{q}} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop}.  
     \end{equation}
@@
     \begin{equation*}
-        \tnorm{(\Vh - \Uh,\Zh)} \le \frac{C}{C_B} \tnorm{(\Uh - \Vh, 0)}_{\wop},
+    \tnorm{(\mathbf{U} - \Uh,\Zh)} \le \frac{C}{C_B} \tnorm{(\mathbf{U} - \Vh, 0)}_{\wop},
     \end{equation*}
@@
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
-Reproduction material is available at \textbf{insert reproduction files...}
+%Reproduction material is available at \textbf{insert reproduction files...}
 

### 2024-12-07 tex/main.tex
remove gamma
interface conditions

@@
 \begin{equation}\label{eq:waveEquation}
-        (\wop u, u) = (0,0) \quad \text{ in } Q \times \Sigma.  
-\end{equation}
-To ensure that the problem is well posed, one usually prescribes initial data
+        (\wop u, u) = (0,0) \quad \text{ in } Q \times \Sigma,
+\end{equation}
+along with the natural interface conditions 
+\begin{equation}\label{eq:IF-conditions}
+	\jump{u}_{\Gamma} = 0 \text{ on } \Sigma, \qquad 
+	\quad \jump{c^2 \nabla u}_{\Gamma} \cdot \mathbf{n}_{\Gamma} = 0 \text{ on } \Sigma, 
+\end{equation}
+where $\mathbf{n}_{\Gamma}$ is the normal vector on $\Gamma$ pointing into $\Omega_+$ 
+and the jump is defined\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}And anologously for vector-valued functions.} as $\jump{u}_{\Gamma} = u_{+}-u_{-}$ with $u_{\pm}$ being the traces
+of $u|_{\Omega_{\pm}}$ on $\Gamma$. \par 
+\noindent To ensure that the problem is well posed, one usually prescribes initial data
 \begin{equation}\label{eq:initialData}
@@
 where $u_0 \in H^1(Q)$ and $u_1 \in L^2(Q)$ are given.
-For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:initialData} in heterogeneous media we refer to \cite{StolkPhD}.
+For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:initialData} in heterogeneous media we refer to \cite{StolkPhD}.
 Here we consider a data assimilation problem instead, i.e.
@@
 %\noindent In a homogeneous medium, where $c_i = 1$, $i = 1,2$,
-\noindent In a medium without an interface the problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-studied, see e.g.~References \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
+\noindent In a medium without an interface the problem \eqref{eq:waveEquation}+\eqref{eq:dataMatch} is well-studied, see e.g.~References \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
 In particular, it is known that if $c_i = 1$, $i = 1,2$, the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR92}, then the problem is Lipschitz stable.
-Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
+Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{2}\footnotemark \footnotetext{\textsuperscript{2}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
 For a precise definition, we refer to \cite{BLR92}.
@@
 \noindent For the heterogeneous case where $c_1 \not =  c_2$, the problem is less studied.
-In the absence of the GCC, we have to assume that the final time $T$ is large enough to ensure that problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is well-posed.
-To be precise, Holmgren's unique continuation theorem guarantees that \eqref{eq:waveEquation}-\eqref{eq:dataMatch} is uniquely solvable if
+In the absence of the GCC, we have to assume that the final time $T$ is large enough to ensure that problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} is well-posed.
+To be precise, Holmgren's unique continuation theorem guarantees that \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} is uniquely solvable if
 \begin{equation}\label{eq:Tcondition}
@@
 where $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$ with $d_c$ being the distance function defined as the length of the shortest continuous path in $\Omega$ connecting $x$ and $y$ with respect to the metric adapted to the discontinuous wave speed $c$.
-While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} can be poor.
+While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} can be poor.
 It has been shown \cite[Thm.
-5.17]{Filippas22} under the assumption \eqref{eq:Tcondition} the following stability result holds:
+5.19]{Filippas22} under the assumption \eqref{eq:Tcondition} the following stability result holds:
 \begin{thm}[Thm. 5.19 of \cite{Filippas22}]\label{thm:filippas}
@@
 \eqref{eq:Tcondition} holds.
-Then, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving \eqref{eq:waveEquation}-\eqref{eq:initialData} one has for any $\mu > 0$ that
+Then, there exists $C,\kappa$ such that for any initial data $(u_0,u_1) \in H^1_0(\Omega) \times L^2(\Omega)$ and $u$ solving \eqref{eq:IF-conditions}+\eqref{eq:initialData} and
+\[
+\wop u \in L^2(Q), \quad u = 0 \text{ on } \Sigma,
+\]
+one has for any $\mu > 0$ that 
     \begin{equation}\label{eq:FilippasEstimate}
@@
 
-\noindent In this article, we introduce a discontinuous in time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} in the heterogeneous case.
+\noindent In this article, we introduce a discontinuous in time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} in the heterogeneous case.
 In particular, we want to investigate numerically if the following assumption is justified.
@@
 \begin{align*}
-    \cL_h (\Uh, \Zh) := &\frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) \\
-    &- \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh),
+    \cL_h (\Uh, \Zh) := &\frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2}  S_h(\Uh,\Uh) \\
+    &- \frac{1}{2}  S_h^\ast(\Zh,\Zh) + \frac{1}{2} \Sud(\Uh,\Uh),
 \end{align*}
@@
 \end{align*}
+~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only.
+Indeed, it follows from the first conditon in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
+So stabbilizing the full gradient is not consistent, which becomes an issue in Cor.~\ref{cor:tnormConvRates}.
+}
 $J(\cdot,\cdot)$ is a continuous interior penalty term in space, $G(\cdot,\cdot)$ is a Galerkin least squares term enforcing the PDE locally on each element, $I_0(\cdot,\cdot)$ enforces that $\ul_2 = \dt \ul_1$, and $R(\cdot,\cdot)$ ensures boundary stability.
@@
 \begin{alignat*}{2}
-    (\ul_1,\wl_1)_{\omega_T} \! + \! A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \ &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
-    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \ &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
+    (\ul_1,\wl_1)_{\omega_T} \! + \! A[\Wh,\Zh] + S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \ &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
+    A[\Uh,\Yh] -  S_h^\ast(\Yh,\Zh) &= 0 \ &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
 \end{alignat*}
@@
     \begin{aligned}
-        B[(\Uh,\Zh),(\Wh,\Yh)] \coloneqq \ &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
-        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh).
+        B[(\Uh,\Zh),(\Wh,\Yh)] \coloneqq \ &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ S_h(\Uh,\Wh) \\
+        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - S_h^\ast(\Yh,\Zh).
     \end{aligned}
@@
 \begin{equation}
-    \tnorm{ (\Uh,\Zh) }^2 := \gamma \vert \Uh \vert^2_{S_h} + \vert \Uh \vert^2_{\uparrow \downarrow} + \Vert \ul_1 \Vert^2_{\omega_T} + \gamma^{\ast} \Vert \Zh \Vert^2_{S_h^\ast},
+    \tnorm{ (\Uh,\Zh) }^2 :=  \vert \Uh \vert^2_{S_h} + \vert \Uh \vert^2_{\uparrow \downarrow} + \Vert \ul_1 \Vert^2_{\omega_T} + \Vert \Zh \Vert^2_{S_h^\ast},
 \end{equation}
@@
         + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} (\dt \ul_2 - \div(c^2 \nabla \ul_1),y)_{K} \ \dT \\
-	    & \hspace{6em} + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c^2 \nabla \ul_1 \cdot \mathbf{n}}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\},
+	    & \hspace{6em} + \sum_{n = 0}^{N-1} \int_{I_n} \sum_{F \in \mathcal{F}_i} (\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}, y)_F \ \dT + \sum_{n = 0}^{N-1} (\jump{\ul_1^n},y)_{\Sigma^n} \Big\},
     \end{align*}
-where $ \jump{c^2 \nabla \ul_1 \cdot \mathbf{n}}$  denotes the jump of the normal derivative over interior facets.
-It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$.
-Thus, $\ul_1$ solves \eqref{eq:waveEquation} and by taking $\mu \rightarrow \infty$ in Thm.
+where $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$  denotes the jump of the normal derivative over interior facets.
+It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$ and that the interface conditions \eqref{eq:IF-conditions} are fulfilled.
+Thus, by taking $\mu \rightarrow \infty$ in Thm.
 \ref{thm:filippas}, we conclude that $u_0 = u_1 = 0$.
-As solutions to \eqref{eq:waveEquation}-\eqref{eq:initialData} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
+As solutions to \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:initialData} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
 \end{proof}
@@
         B[&(\Uh - \Vh, \Zh),( \Wh, \Yh)] \\
-        &= B[(\Uh,\Zh),( \Wh, \Yh)] - (\underline{v}_1, \underline{w}_1)_{\omega_T} - \gamma S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
-        &= (u_{\omega}, \underline{w}_1)_{\omega_T} - (\underline{v}_1, \underline{w}_1)_{\omega_T} - \gamma S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
-        &= (u - \underline{v}_1, \underline{w}_1)_{\omega_T}  + \gamma S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh],
+        &= B[(\Uh,\Zh),( \Wh, \Yh)] - (\underline{v}_1, \underline{w}_1)_{\omega_T} - S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
+        &= (u_{\omega}, \underline{w}_1)_{\omega_T} - (\underline{v}_1, \underline{w}_1)_{\omega_T} - S_h(\Vh,\Wh) - \Sud(\Vh,\Wh) - A[\Vh,\Yh] \\
+        &= (u - \underline{v}_1, \underline{w}_1)_{\omega_T}  +  S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh],
     \end{align*} 
@@
     \begin{align*}
-        (u - &\underline{v}_1, \underline{w}_1)_{\omega_T}  + \gamma S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh] \\
+        (u - &\underline{v}_1, \underline{w}_1)_{\omega_T}  +  S_h(\mathbf{U} - \Vh,\Wh) + \Sud(\mathbf{U} - \Vh,\Wh) + A[\mathbf{U} - \Vh,\Yh] \\
         &\le C(\tnorm{(\mathbf{U} - \Vh,0)}_{\wop} \tnorm{(0,\Yh)}  + \tnorm{(\mathbf{U} - \Vh,0)} \tnorm{(\Wh,0)} ) \\
@@
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
-%Reproduction material is available at \textbf{insert reproduction files...}
+~\jp{We need to setup some reproduction material.}
 
@@
     \begin{equation*}
-        (u - \Pi_h u, \wl_1)_{\omega_T} - \gamma S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
+        (u - \Pi_h u, \wl_1)_{\omega_T} -  S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
     \end{equation*}

### 2024-12-07 tex/main.tex
minors

@@
     where $\tnorm{(\cdot, \cdot)}_{\square_1}$ is defined by \eqref{eq:tnormwop} with $c_i = 1$, $i = 1,2$.
-Thus, we can apply the interpolation results derived in \cite[Lem.
-2.4]{BP24} to obtain the claim.
+Thus, we can apply the interpolation results derived in \cite[Lemma 5]{BP24} to obtain the claim.
 \end{proof}
@@
 \begin{proof}
-    The proof follows from the same argumentation as the proof of \cite[Thm. 4.4]{BP24}.
+    The proof follows from the same argumentation as the proof of \cite[Theorem 10]{BP24}.
 \end{proof}
@@
     \end{enumerate}
-    Then, we can use the arguments of \cite[Thm. 4.4]{BP24} to show that 
+    Then, we can use the arguments of \cite[Theorem 10]{BP24} to show that 
     \begin{equation}
@@
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
-~\jp{We need to setup some reproduction material.}
-
+~\jp{We need to prepare some reproduction material.}
 \subsection{Examples in one space dimension}
@@
 Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.
+
+\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
+In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
+Figures \ref{fig:jumpCoefs:quality} and \ref{fig:jumpCoefs:increasingcontrast} show that ...
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.25cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %L-infty-L2-u (k = 3)
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.3*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \legend{$k=2 $,, $k = 3$,}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %L-infty-L2-u (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.001*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.009999968541169805
+                2 0.006666645694113204
+                3 0.004999984270584902
+                4 0.003999987416467922
+
+            };
+            \node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+            \legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.02*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.09999968541169805
+                2 0.06666645694113204
+                3 0.04999984270584902
+                4 0.03999987416467922
+
+            };
+            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+            \legend{$k=2 $,, $k = 3$,}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
+We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
+The gray dashed lines indicate the observed convergence rates.}
+    \label{fig:jumpCoefs:contrast:2.5}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.85]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.0cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+            %ymin=1e-7,ymax=1e1,
+            ]
+            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-3))^(x-0.9)};
+
+            \node [draw=none] at (axis description cs:0.70,0.37) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
+            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
+
+            \legend{$T = 0.5$, $L^2$-best approx. ($T = 0.5$), $T$ variable, $L^2$-best approx. ($T$ variable)}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south east, %yticklabels={,,},
+            %ymin=1e-7,ymax=1e1,
+            ]
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+
+            \addplot[gray, dashed, domain=1:4.5] {0.00001*(1/2^(-2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4.5] {0.0003*(1/2^(-3))^(x-0.9)};
+            \node [draw=none] at (axis description cs:0.70,0.27) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
+            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
+We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
+    \label{fig:jumpCoefs:increasingcontrast}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=5, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+                ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{exact,$L=1$, $L=2$, $L=3$, $L=4$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 5.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-3) -- (0.5,3);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                %Colors
+                \definecolor{L1Color}{RGB}{55,126,184}
+                \definecolor{L2Color}{RGB}{77,175,74}
+                \definecolor{L3Color}{RGB}{152,78,163}
+                \definecolor{L4Color}{RGB}{255,127,0}
+
+                %L = 1
+                \draw[color=L1Color,thick] (0.75,-2) -- (1,-2);
+                \draw[color=L1Color,thick] (0.75,-2.05) -- (0.75,-1.95);
+                \draw[color=L1Color,thick] (1.0,-2.05) -- (1.0,-1.95);
+
+                %L = 2
+                \draw[color=L2Color,thick] (0.75,-1.75) -- (1,-1.75);
+                \draw[color=L2Color,thick] (0.75,-1.70) -- (0.75,-1.8);
+                \draw[color=L2Color,thick] (0.875,-1.70) -- (0.875,-1.8);
+                \draw[color=L2Color,thick] (1.0,-1.70) -- (1.0,-1.8);
+
+                %L = 3
+                \draw[color=L3Color,thick] (0.75,-1.5) -- (1,-1.5);
+                \draw[color=L3Color,thick] (0.75,-1.45) -- (0.75,-1.55);
+                \draw[color=L3Color,thick] (0.8125,-1.45) -- (0.8125,-1.55);
+                \draw[color=L3Color,thick] (0.875,-1.45) -- (0.875,-1.55);
+                \draw[color=L3Color,thick] (0.9375,-1.45) -- (0.9375,-1.55);
+                \draw[color=L3Color,thick] (1.0,-1.45) -- (1.0,-1.55);
+
+                %L = 4
+                \draw[color=L4Color,thick] (0.75,-1.25) -- (1,-1.25);
+                \draw[color=L4Color,thick] (0.75,-1.20) -- (0.75,-1.30);
+                \draw[color=L4Color,thick] (0.78125,-1.20) -- (0.78125,-1.30);
+                \draw[color=L4Color,thick] (0.8125,-1.20) -- (0.8125,-1.30);
+                \draw[color=L4Color,thick] (0.84375,-1.20) -- (0.84375,-1.30);
+                \draw[color=L4Color,thick] (0.875,-1.20) -- (0.875,-1.30);
+                \draw[color=L4Color,thick] (0.90625,-1.20) -- (0.90625,-1.30);
+                \draw[color=L4Color,thick] (0.9375,-1.20) -- (0.9375,-1.30);
+                \draw[color=L4Color,thick] (0.96875,-1.20) -- (0.96875,-1.30);
+                \draw[color=L4Color,thick] (1.0,-1.20) -- (1.0,-1.30);
+
+                %\legend{exact, $L=1$, $L=2$, $L=3$, $L=4$}
+
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
+    \label{fig:jumpCoefs:quality}
+  \end{figure}
+
+  \begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=3 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestnoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+                %\addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.0001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
+                legend pos=south east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestRestricted_NoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
+
+                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Filippas lambda...}
+  \end{figure}
+\end{comment}
+
+\subsubsection{Multiple jumps}
+\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
+For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
+$\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$.
+Then, we consider the following Ansatz for the exact solution:
+\begin{equation}\label{eq:1D:exact:simpleMult}
+    u(x,t) := \begin{cases}
+        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
+        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
+        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
+    \end{cases}
+\end{equation}
+To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
+\begin{equation*}
+    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
+\end{equation*}
+Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
+In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
+As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
+For contrast $c_1 \in \{ 7.5,11.5 \}$, Fig.
+\ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -0.6e0, ymax = 0.6e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1= 7.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.7,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
+
+                 %L = 3
+                %\draw[color=orange,thick] (0.4,-0.5) -- (2/3,-0.5);
+                %\draw[color=orange,thick] (0.4,-0.48) -- (0.4,-0.52);
+                %\draw[color=orange,thick] (0.4375,-0.48) -- (0.4375,-0.52);
+                %\draw[color=orange,thick] (0.5,-0.48) -- (0.5,-0.52);
+                %\draw[color=orange,thick] (0.5625,-0.48) -- (0.5625,-0.52);
+                %\draw[color=orange,thick] (0.625,-0.48) -- (0.625,-0.52);
+                %\draw[color=orange,thick] (0.6666,-0.48) -- (0.6666,-0.52);
+
+                \legend{exact, $L = 4$, $L = 3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
+                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
+
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
+We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
+    \label{fig:jumpCoefs:multipleJumps}
+  \end{figure}
+
+\noindent As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
+\begin{equation}
+    T > 2 \left[ (p_2 - p_1) + \frac{p_1 - 0.3 + 1 - p_2}{c_1} \right]. 
+\end{equation}
+Figure \ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \legend{exact,$T=1.0$,$T=0.5$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+         \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
+We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
+    \label{fig:jumpCoefs:multipleJumps:noGCC}
+  \end{figure}
+
+  \begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ - with bug in the code....}
+    \label{fig:jumpCoefs:multipleJumps2}
+  \end{figure}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ (uniform mesh), computed with $64$ points in space, $32$ in time and $T = 0.5$.}
+    \label{fig:jumpCoefs:multipleJumps3}
+  \end{figure}
+\end{comment}
+
+\subsection{Example in two space dimensions}
+\noindent In this section, we present numerical examples in two space dimensions.
+We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
+
+\subsubsection{Simple example} 
+As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
+we consider the original solution in the $x$-direction.
+We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
+To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
+We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
+As before, we fix $c_2 = 1$ and consider different values for $c_1$.
+The results of the experiment are presented in Fig.
+\ref{fig:2DjumpCoefs}.
+
+\begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
+
+                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
+
+                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,$k = 3$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
+                legend pos=north east, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u errorreduced
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
+                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:4] {9*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.65*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.15*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(3))^(x-0.9)};
+                \node [draw=none] at (axis description cs:0.50,0.52) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \node [draw=none] at (axis description cs:0.60,0.82) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.6,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,$k=3$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+
+                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                %L-infty-L2-u error
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+
+                \addplot[gray, dashed, domain=1:2.5] {2*(1/2^(-3/2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:2.5] {1.35*(1/2^(-1/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.70,0.7) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3/2})$};
+                \node [draw=none] at (axis description cs:0.7,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{1/2})$};
+
+                \legend{$k=2$,$k=3$}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
+    \label{fig:2DjumpCoefs}
+  \end{figure}
+
+\begin{comment}
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=1 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
+                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
+                ]
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
+
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
+
+                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
+
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{Filippas lambda... (2D), noGCC}
+  \end{figure}
+\end{comment}
+
+\subsubsection{2nd one dimensional example}
+
+~\jp{I am not sure whether this section really fits into the narrative ... Shall we just remove it?}
+We consider the same geometrical setup as in Sec.
+\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
+With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
+\begin{equation}\label{eq:1D:complicatedSol}
+    u(x,t) = \begin{cases}
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
+      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
+    \end{cases}
+\end{equation}
+This solution describes a wave traveling towards the interface $\Gamma$.
+Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+\begin{comment}
+\begin{figure}[!htbp]
+    \begin{center}with 
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,best,$k = 3$,best}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{...}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
+                legend pos=south west, 
+                %yticklabels={,,}, 
+                xlabel={$L$}, ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
+
+                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
+                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
+
+                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
+
+                %L = 2
+                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
+                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
+                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
+                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
+
+                %L = 3
+                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
+                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
+                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
+                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
+                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
+                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
+                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
+
+                \legend{exact,$L=4$, $L=5$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+
+ \section{Conclusion}
+Lalala
+
+\appendix
+
+\section{More material}
 
@@
 
-\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
-In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
-Figures \ref{fig:jumpCoefs:quality} and \ref{fig:jumpCoefs:increasingcontrast} show that ...
-
-\begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.25cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L-infty-L2-u (k = 2)
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            %L-infty-L2-u (k = 3)
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.3*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L-infty-L2-u (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %L-infty-L2-u (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.001*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.009999968541169805
-                2 0.006666645694113204
-                3 0.004999984270584902
-                4 0.003999987416467922
-
-            };
-            \node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
-            \legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-            %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.02*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.09999968541169805
-                2 0.06666645694113204
-                3 0.04999984270584902
-                4 0.03999987416467922
-
-            };
-            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
-            \legend{$k=2 $,, $k = 3$,}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
-We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
-The gray dashed lines indicate the observed convergence rates.}
-    \label{fig:jumpCoefs:contrast:2.5}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.85]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.0cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
-            %ymin=1e-7,ymax=1e1,
-            ]
-            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4.5] {0.001*(1/2^(-3))^(x-0.9)};
-
-            \node [draw=none] at (axis description cs:0.70,0.37) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
-            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
-
-            \legend{$T = 0.5$, $L^2$-best approx. ($T = 0.5$), $T$ variable, $L^2$-best approx. ($T$ variable)}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:5,xmode=linear,ymode=log, ylabel={}, xlabel={$c_1$}, title={$\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend pos=south east, %yticklabels={,,},
-            %ymin=1e-7,ymax=1e1,
-            ]
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4.5] {0.00001*(1/2^(-2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4.5] {0.0003*(1/2^(-3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.70,0.27) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{2})$};
-            \node [draw=none] at (axis description cs:0.50,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3})$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-        \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
-We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
-    \label{fig:jumpCoefs:increasingcontrast}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=5, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
-                ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \legend{exact,$L=1$, $L=2$, $L=3$, $L=4$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 5.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-3) -- (0.5,3);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                %Colors
-                \definecolor{L1Color}{RGB}{55,126,184}
-                \definecolor{L2Color}{RGB}{77,175,74}
-                \definecolor{L3Color}{RGB}{152,78,163}
-                \definecolor{L4Color}{RGB}{255,127,0}
-
-                %L = 1
-                \draw[color=L1Color,thick] (0.75,-2) -- (1,-2);
-                \draw[color=L1Color,thick] (0.75,-2.05) -- (0.75,-1.95);
-                \draw[color=L1Color,thick] (1.0,-2.05) -- (1.0,-1.95);
-
-                %L = 2
-                \draw[color=L2Color,thick] (0.75,-1.75) -- (1,-1.75);
-                \draw[color=L2Color,thick] (0.75,-1.70) -- (0.75,-1.8);
-                \draw[color=L2Color,thick] (0.875,-1.70) -- (0.875,-1.8);
-                \draw[color=L2Color,thick] (1.0,-1.70) -- (1.0,-1.8);
-
-                %L = 3
-                \draw[color=L3Color,thick] (0.75,-1.5) -- (1,-1.5);
-                \draw[color=L3Color,thick] (0.75,-1.45) -- (0.75,-1.55);
-                \draw[color=L3Color,thick] (0.8125,-1.45) -- (0.8125,-1.55);
-                \draw[color=L3Color,thick] (0.875,-1.45) -- (0.875,-1.55);
-                \draw[color=L3Color,thick] (0.9375,-1.45) -- (0.9375,-1.55);
-                \draw[color=L3Color,thick] (1.0,-1.45) -- (1.0,-1.55);
-
-                %L = 4
-                \draw[color=L4Color,thick] (0.75,-1.25) -- (1,-1.25);
-                \draw[color=L4Color,thick] (0.75,-1.20) -- (0.75,-1.30);
-                \draw[color=L4Color,thick] (0.78125,-1.20) -- (0.78125,-1.30);
-                \draw[color=L4Color,thick] (0.8125,-1.20) -- (0.8125,-1.30);
-                \draw[color=L4Color,thick] (0.84375,-1.20) -- (0.84375,-1.30);
-                \draw[color=L4Color,thick] (0.875,-1.20) -- (0.875,-1.30);
-                \draw[color=L4Color,thick] (0.90625,-1.20) -- (0.90625,-1.30);
-                \draw[color=L4Color,thick] (0.9375,-1.20) -- (0.9375,-1.30);
-                \draw[color=L4Color,thick] (0.96875,-1.20) -- (0.96875,-1.30);
-                \draw[color=L4Color,thick] (1.0,-1.20) -- (1.0,-1.30);
-
-                %\legend{exact, $L=1$, $L=2$, $L=3$, $L=4$}
-
-            \end{groupplot}
-        \end{tikzpicture}
-        \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
-The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
-    \label{fig:jumpCoefs:quality}
-  \end{figure}
-
-  \begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=3 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestnoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                %\addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.0001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestRestricted_NoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Filippas lambda...}
-  \end{figure}
-\end{comment}
-
-\subsubsection{Multiple jumps}
-\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
-For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
-$\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$.
-Then, we consider the following Ansatz for the exact solution:
-\begin{equation}\label{eq:1D:exact:simpleMult}
-    u(x,t) := \begin{cases}
-        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
-        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
-        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
-    \end{cases}
-\end{equation}
-To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
-\begin{equation*}
-    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
-\end{equation*}
-Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
-In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
-As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
-For contrast $c_1 \in \{ 7.5,11.5 \}$, Fig.
-\ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
-
-\begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            ymin = -0.6e0, ymax = 0.6e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1= 7.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.7,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
-
-                 %L = 3
-                %\draw[color=orange,thick] (0.4,-0.5) -- (2/3,-0.5);
-                %\draw[color=orange,thick] (0.4,-0.48) -- (0.4,-0.52);
-                %\draw[color=orange,thick] (0.4375,-0.48) -- (0.4375,-0.52);
-                %\draw[color=orange,thick] (0.5,-0.48) -- (0.5,-0.52);
-                %\draw[color=orange,thick] (0.5625,-0.48) -- (0.5625,-0.52);
-                %\draw[color=orange,thick] (0.625,-0.48) -- (0.625,-0.52);
-                %\draw[color=orange,thick] (0.6666,-0.48) -- (0.6666,-0.52);
-
-                \legend{exact, $L = 4$, $L = 3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
-
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-        \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
-We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
-    \label{fig:jumpCoefs:multipleJumps}
-  \end{figure}
-
-\noindent As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
-\begin{equation}
-    T > 2 \left[ (p_2 - p_1) + \frac{p_1 - 0.3 + 1 - p_2}{c_1} \right]. 
-\end{equation}
-Figure \ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \legend{exact,$T=1.0$,$T=0.5$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-         \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
-We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
-    \label{fig:jumpCoefs:multipleJumps:noGCC}
-  \end{figure}
-
-  \begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ - with bug in the code....}
-    \label{fig:jumpCoefs:multipleJumps2}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ (uniform mesh), computed with $64$ points in space, $32$ in time and $T = 0.5$.}
-    \label{fig:jumpCoefs:multipleJumps3}
-  \end{figure}
-\end{comment}
-
-\subsection{Example in two space dimensions}
-\noindent In this section, we present numerical examples in two space dimensions.
-We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
-
-\subsubsection{Simple example} 
-As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
-we consider the original solution in the $x$-direction.
-We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
-To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
-We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
-As before, we fix $c_2 = 1$ and consider different values for $c_1$.
-The results of the experiment are presented in Fig.
-\ref{fig:2DjumpCoefs}.
-
-\begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-
-                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-
-                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u errorreduced
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {9*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.65*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.15*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.50,0.52) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \node [draw=none] at (axis description cs:0.60,0.82) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.6,0.65) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:2.5] {2*(1/2^(-3/2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:2.5] {1.35*(1/2^(-1/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.70,0.7) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{3/2})$};
-                \node [draw=none] at (axis description cs:0.7,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(c_1^{1/2})$};
-
-                \legend{$k=2$,$k=3$}
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-
-\begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=1 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
-                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
-
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Filippas lambda... (2D), noGCC}
-  \end{figure}
-\end{comment}
-
-\subsubsection{2nd one dimensional example}
-
-~\jp{I am not sure whether this section really fits into the narrative ... Shall we just remove it?}
-We consider the same geometrical setup as in Sec.
-\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
-With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
-\begin{equation}\label{eq:1D:complicatedSol}
-    u(x,t) = \begin{cases}
-      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
-      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
-    \end{cases}
-\end{equation}
-This solution describes a wave traveling towards the interface $\Gamma$.
-Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
-
-\begin{comment}
-\begin{figure}[!htbp]
-    \begin{center}with 
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,best,$k = 3$,best}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{...}
-    %\label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
-                legend pos=south west, 
-                %yticklabels={,,}, 
-                xlabel={$L$}, ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
-
-                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-
-                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
-                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
-
-                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
-
-                %L = 2
-                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
-                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
-                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
-                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
-
-                %L = 3
-                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
-                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
-                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
-                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
-                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
-                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
-                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
-
-                \legend{exact,$L=4$, $L=5$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
-    %\label{fig:2DjumpCoefs}
-  \end{figure}
-
- \section{Conclusion}
-Lalala
-
-\appendix
-
 \begin{comment}

### 2024-12-09 tex/main.tex
add paragraph in intro and expand description of numexp

@@
 \noindent In this article, we introduce a discontinuous in time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} in the heterogeneous case.
-In particular, we want to investigate numerically if the following assumption is justified.
+In particular, we want to investigate numerically if the following assumption, motivated by Thm.
+\ref{thm:Lipschitz} for the homogeneous case, is justified.
 
@@
 \end{assum}
+
+That is, we would like to understand whether the Lipschitz stability property is preserved in presence of strong heterogeneity in the medium if the GCC holds.
+This question is of high practical importance since discontinuous media appear in many applications, e.g.\ in seismology.
+If the corresponding data assimilation problems were indeed subject to the poor logarithmic stability property ensured by \eqref{eq:FilippasEstimateLog}, this would pose an enormous challenge for the design of accurate and realiable numerical methods for their resolution.
 
@@
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
-~\jp{We need to prepare some reproduction material.}
+~\jp{We need to prepare some reproduction material ...}
 \subsection{Examples in one space dimension}
-\noindent We consider the unit interval $\Omega \coloneqq [0,1] \subset \mathbb{R}$.
+\noindent We consider the unit interval $\Omega \coloneqq (0,1) \subset \mathbb{R}$.
 For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$.
@@
 \subsubsection{Simple Example}\label{sec:numex:1D:simple}
-\noindent We define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
+\noindent We define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
 Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
@@
 \begin{equation}
-    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75].
+	\omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq \bar{\Omega} \setminus \omega = [0.25,0.75].
 \end{equation}
@@
 In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
-Figures \ref{fig:jumpCoefs:quality} and \ref{fig:jumpCoefs:increasingcontrast} show that ...
+
+In Fig.~\ref{fig:jumpCoefs:increasingcontrast} the dependence of the errors for increasing $c_1$ and 
+leaving $c_2 = 1$ fixed (i.e.\ increasing the contrast value) is investigated.
+When $T$ is chosen such that the GCC is barely fulfilled we observe that the errors grow polynomially in the contrast, more precisely like $\mathcal{O}(c_1^3)$.
+This is an important observation, since an exponential growth in the contrast would have rendered the corresponding problems nearly impossible to resolve numerically.
+Still, compared to the best approximation error which grows quadratically we 
+loose a factor of $c_1$.
+This entails that a strong refinement of the discretization is required to maintain the accuracy of the numerical solution as the contrast increases.
+We illustrate this problem in Fig.~\ref{fig:jumpCoefs:quality}.
+For $c_1 = 2.5$ the exact solution is already well-captured by the numerical solution on refinement level $L=2$.
+However, for $c_1 = 5.5$ this refinement level is clearly insufficient.
 
@@
 \end{equation}
-Figure \ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
+Fig.~\ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
 
@@
 \ref{fig:2DjumpCoefs}.
+For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$.
+Similar as already observed in the one-dimensional case the right plot in Fig.~\ref{fig:2DjumpCoefs} shows that these errors are more sensitive to inreasing $c_1$ than the corresponding best approximation errors.
+In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$ which renders it very demanding to maintain a resonable accuracy as the contrast increases.
 
@@
     \end{center}
-    \caption{For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ (left) and the ratio between the approximation error and the $L^2$-bestapproximation error (right).}
+    \caption{Left: Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for $c_1 = 2.5$.
+Right: Ratio between these errors and the $L^2$-bestapproximation error for increasing $c_1$.}
     \label{fig:2DjumpCoefs}
@@
 
-~\jp{I am not sure whether this section really fits into the narrative ... Shall we just remove it?}
+Let us consider a final two-dimensional example to illustrate the high computational demand 
+required to simulate wave propagation in heterogeneous media. 
 We consider the same geometrical setup as in Sec.
@@
 Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+In Fig.~\ref{fig:2D-complicated-sol} we consider the approximation of this function by the $L^2$-interpolation.
+The plot on the right shows that for $c_1 = 2.5$ the velocity is not captured well yet even for $k=3$ on the finest refinement level we considered.
+In terms of convergence rates, we merely observe $\mathcal{O}(h^2)$ for $k=2$.
+In view of the previous experiments it is clear that this poses a serious obstruction to obtaining accurate solutions to the corresponding unique continuation problem.
 
@@
                 %yticklabels={,,}, 
-                xlabel={$L$}, ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                xlabel={$L$}, 
+		%ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
                 ]
@@
     \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
-    %\label{fig:2DjumpCoefs}
+    \label{fig:2D-complicated-sol}
   \end{figure}
@@
 \section{More material}
+
+~\jp{Remove Fig.~\ref{fig:GCC-illustration} ?}
 
@@
 Could probably show that the GCC and the condition on $T$ are in fact equivalent in one dimension.}
+\label{fig:GCC-illustration}
 \end{figure}

### 2024-12-09 tex/main.tex
add abstract and some more keywords

@@
 
-\abstract{Todo...}
-
-\keywords{Data assimilation, wave equation, discontinuous coefficients}
+\abstract{In recent years several numerical methods for solving the unique continuation problem for the wave equation in a homogeneous medium with given data on the lateral boundary of the space-time cylinder have been proposed.
+Under these conditions the problem enjoys Lipschitz stability which allows to devise optimally convergent numerical methods.
+In this article we investigate whether these results carry over to the case in which the medium exhibits a jump discontinuity.
+Our numerical experiments suggest a positive answer provided that the geometric control condition is satisfied.
+However, we also observe that the presence of discontinuities in the medium renders the computations far more demanding than in the homogeneous case.
+}
+
+\keywords{Unique continuation, data assimilation, wave equation, discontinuous coefficients, geometric control condition}
 

### 2024-12-09 tex/main.tex
conclusion and reordering

@@
 
+\subsubsection{2nd one dimensional example}
+
+Let us consider a final one-dimensional example to illustrate the high computational demand 
+required to simulate wave propagation in heterogeneous media. 
+We consider the same geometrical setup as in Sec.
+\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
+With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
+\begin{equation}\label{eq:1D:complicatedSol}
+    u(x,t) = \begin{cases}
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
+      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
+    \end{cases}
+\end{equation}
+This solution describes a wave traveling towards the interface $\Gamma$.
+Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+In Fig.~\ref{fig:1D-complicated-sol} we consider the approximation of this function by the $L^2$-interpolation.
+The plot on the right shows that for $c_1 = 2.5$ the velocity is not captured well yet even for $k=3$ on the finest refinement level we considered.
+In terms of convergence rates, we merely observe $\mathcal{O}(h^2)$ for $k=2$.
+In view of the previous experiments it is clear that this poses a serious obstruction to obtaining accurate solutions to the corresponding unique continuation problem.
+
+\begin{comment}
+\begin{figure}[!htbp]
+    \begin{center}with 
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
+                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+                \legend{$k=2$,best,$k = 3$,best}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
+                legend pos=south west, %yticklabels={,,},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
+
+                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
+                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+                \legend{$k=2$,best,$k = 3$,best}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{...}
+    %\label{fig:2DjumpCoefs}
+  \end{figure}
+\end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
+                legend pos=south west, 
+                %yticklabels={,,}, 
+                xlabel={$L$}, 
+		%ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
+                ]
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
+
+                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
+
+                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
+                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
+
+                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
+                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
+
+                %L = 2
+                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
+                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
+                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
+                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
+
+                %L = 3
+                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
+                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
+                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
+                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
+                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
+                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
+                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
+
+                \legend{exact,$L=4$, $L=5$}
+            \end{groupplot}
+        \end{tikzpicture}
+    \end{center}
+    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
+    \label{fig:1D-complicated-sol}
+  \end{figure}
+
 \subsection{Example in two space dimensions}
-\noindent In this section, we present numerical examples in two space dimensions.
+\noindent In this section, we present a numerical examples in two space dimensions.
 We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
-
-\subsubsection{Simple example} 
 As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
@@
 
-\subsubsection{2nd one dimensional example}
-
-Let us consider a final two-dimensional example to illustrate the high computational demand 
-required to simulate wave propagation in heterogeneous media. 
-We consider the same geometrical setup as in Sec.
-\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
-With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
-\begin{equation}\label{eq:1D:complicatedSol}
-    u(x,t) = \begin{cases}
-      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
-      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
-    \end{cases}
-\end{equation}
-This solution describes a wave traveling towards the interface $\Gamma$.
-Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
-
-In Fig.~\ref{fig:2D-complicated-sol} we consider the approximation of this function by the $L^2$-interpolation.
-The plot on the right shows that for $c_1 = 2.5$ the velocity is not captured well yet even for $k=3$ on the finest refinement level we considered.
-In terms of convergence rates, we merely observe $\mathcal{O}(h^2)$ for $k=2$.
-In view of the previous experiments it is clear that this poses a serious obstruction to obtaining accurate solutions to the corresponding unique continuation problem.
-
-\begin{comment}
-\begin{figure}[!htbp]
-    \begin{center}with 
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,best,$k = 3$,best}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{...}
-    %\label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
-                legend pos=south west, 
-                %yticklabels={,,}, 
-                xlabel={$L$}, 
-		%ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
-
-                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-2) -- (0.25,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-2) -- (0.75,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-
-                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.53,0.125) {\color{gray} $\Gamma$};
-                \node [draw=none] at (axis description cs:0.175,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
-
-                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
-
-                %L = 2
-                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
-                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
-                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
-                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
-
-                %L = 3
-                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
-                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
-                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
-                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
-                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
-                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
-                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
-
-                \legend{exact,$L=4$, $L=5$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
-    \label{fig:2D-complicated-sol}
-  \end{figure}
-
  \section{Conclusion}
-Lalala
+
+In this article we have investigated a numerical method to solve the unique continuation problem 
+for the wave equation in the presence of a jump discontinuity in the wavespeed.
+The main conclusion from our numerical experiments is that obtaining accurate numerical solutions in the presence of material interface involving large contrasts is computationally demanding.
+Even though the problem appears to be Lipschitz stable if the geometric control condition is fulfilled, the resolution required to capture the complex behavior of the solution is a limiting factor in numerical simulations.
+Note here that unique continuation problems are globally coupled in space and time which poses an obstacle for their efficient numerical solution.
 

### 2024-12-10 tex/main.tex
minor fixes

@@
 \Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
- We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma$, but constant in time.
+ We consider a scalar wave speed
+\[
+ c(x) := \begin{cases}
+       c_1(x),  & x \in \Omega_1, \\
+        c_2(x), & x \in \Omega_2,
+    \end{cases}
+    \quad 
+    \text{ with } c_i \in C^\infty(\Omega_i), \; i = 1,2,
+\]
+ %$c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$,
+which may be discontinuous across the interface $\Gamma$, but constant in time.
 For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$.
@@
 where $\mathbf{n}_{\Gamma}$ is the normal vector on $\Gamma$ pointing into $\Omega_+$ 
-and the jump is defined\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}And anologously for vector-valued functions.} as $\jump{u}_{\Gamma} = u_{+}-u_{-}$ with $u_{\pm}$ being the traces
+and the jump across $\Gamma$ is defined\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}And anologously for vector-valued functions.} as $\jump{u}_{\Gamma} = u_{+}-u_{-}$ with $u_{\pm}$ being the traces
 of $u|_{\Omega_{\pm}}$ on $\Gamma$. \par 
@@
 While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} can be poor.
-It has been shown \cite[Thm.
-5.19]{Filippas22} under the assumption \eqref{eq:Tcondition} the following stability result holds:
+It has been shown in \cite[Thm.
+5.19]{Filippas22} that under the assumption \eqref{eq:Tcondition} the following stability result holds:
 \begin{thm}[Thm. 5.19 of \cite{Filippas22}]\label{thm:filippas}
@@
 
-That is, we would like to understand whether the Lipschitz stability property is preserved in presence of strong heterogeneity in the medium if the GCC holds.
+That is, we would like to understand whether the Lipschitz stability property is preserved in presence of strong heterogeneity in the medium provided that the GCC holds.
 This question is of high practical importance since discontinuous media appear in many applications, e.g.\ in seismology.
@@
 \section{Discretization (fully discrete \& dG in time)} 
-\noindent In this section, we introduce a fully discrete discontinuous in time finite element method to discretize the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} for the wave equation in heterogeneous media.
+\noindent In this section, we introduce a fully discrete discontinuous in time finite element method to discretize the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} for the wave equation in heterogeneous media.
 The discretization is based on the scheme introduced in \cite{BP24} for the homogeneous case.
@@
 We assume in what follows additionally that the triangulation $\mathcal{T}_h$ fits the interface $\Gamma$ and the data domain $\omega$.
-An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP23arxiv} but is certainly beyond the scope of this article.
+An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP23arxiv}, but is certainly beyond the scope of this article.
 
@@
 where $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ with $k, k^\ast, q \in \mathbb{N}$ and $q^\ast \in \mathbb{N}_0$. 
-To approximate solutions of \eqref{eq:waveEquation}-\eqref{eq:dataMatch}, we search for stationary points of the Lagrangian 
+To approximate solutions of \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch}, we search for stationary points of the Lagrangian 
 \begin{align*}
@@
 Indeed, it follows from the first conditon in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
-So stabbilizing the full gradient is not consistent, which becomes an issue in Cor.~\ref{cor:tnormConvRates}.
+So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.
 }
@@
 \section{Error analysis}
-\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:waveEquation}-\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
+\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
 In particular, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in suitable discrete norms defined below.
@@
 %\begin{proof}
-%    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, we conclude that  
+%    Since $B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnoas .. does not holdm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}$, we conclude that  
 %    \begin{align*}
@@
 \begin{thm}\label{thm:bestapprox}
-    Let $u$ be a sufficient regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be the solution to \eqref{eq:discreteProblem}.
+    Let $u$ be a sufficient regular solution of \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be the solution to \eqref{eq:discreteProblem}.
 Set $\mathbf{U} := (u,\partial_t u)$.
@@
 \ref{thm:Lipschitz}.
-Thus, we recover the result from \cite[Thm.
-4.4]{BP24}.
+Thus, we recover the result from \cite[Theorem 10]{BP24}.
 \end{rmk}

### 2024-12-11 tex/main.tex
fixes

@@
 \end{equation}
+~\jp{I am confused by this formula. What is the argument of the characteristic functions $\mathbbm{1}_{\Omega_1}$? Also, a metric is required to be symmetric, so $d_c(x,y) = d_c(y,x) $ 
+needs to be ensured?
+}
 Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.
@@
 leaving $c_2 = 1$ fixed (i.e.\ increasing the contrast value) is investigated.
-When $T$ is chosen such that the GCC is barely fulfilled we observe that the errors grow polynomially in the contrast, more precisely like $\mathcal{O}(c_1^3)$.
-This is an important observation, since an exponential growth in the contrast would have rendered the corresponding problems nearly impossible to resolve numerically.
+When $T$ is chosen such that the GCC is barely fulfilled we observe that the errors merely grow polynomially in the contrast, more precisely like $\mathcal{O}(c_1^3)$.
+This is an important observation since an exponential growth in the contrast would have rendered the corresponding problems nearly impossible to resolve numerically.
 Still, compared to the best approximation error which grows quadratically we 
@@
 For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
-$\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$.
-Then, we consider the following Ansatz for the exact solution:
+$\bar{\Omega} = \cup_{i = 1,2,3} \overline{\Omega}_i$.
+Then, we consider the following ansatz for the exact solution:
 \begin{equation}\label{eq:1D:exact:simpleMult}
@@
 
-Let us consider a final one-dimensional example to illustrate the high computational demand 
+Let us consider a final one-dimensional example to illustrate the high resolution 
 required to simulate wave propagation in heterogeneous media. 
@@
 \subsection{Example in two space dimensions}
-\noindent In this section, we present a numerical examples in two space dimensions.
-We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega^2 = (0.5,1.0)^2$.
+\noindent In this section, we present a numerical example in two space dimensions.
+We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega_2 = (0.5,1.0)^2$.
 As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
@@
 for the wave equation in the presence of a jump discontinuity in the wavespeed.
-The main conclusion from our numerical experiments is that obtaining accurate numerical solutions in the presence of material interface involving large contrasts is computationally demanding.
+The main conclusion from our numerical experiments is that obtaining accurate numerical solutions in the presence of material interfaces involving large contrasts is computationally demanding.
 Even though the problem appears to be Lipschitz stable if the geometric control condition is fulfilled, the resolution required to capture the complex behavior of the solution is a limiting factor in numerical simulations.

### 2024-12-13 tex/main.tex
minors

@@
 \abstract{In recent years several numerical methods for solving the unique continuation problem for the wave equation in a homogeneous medium with given data on the lateral boundary of the space-time cylinder have been proposed.
-Under these conditions the problem enjoys Lipschitz stability which allows to devise optimally convergent numerical methods.
+This problem enjoys Lipschitz stability if the geometric control condition is fulfilled, which allows to devise optimally convergent numerical methods.
 In this article we investigate whether these results carry over to the case in which the medium exhibits a jump discontinuity.
-Our numerical experiments suggest a positive answer provided that the geometric control condition is satisfied.
+Our numerical experiments suggest a positive answer.
 However, we also observe that the presence of discontinuities in the medium renders the computations far more demanding than in the homogeneous case.
@@
 where $\mathcal{P}^k(K)$ denotes the space of polynomials of degree at most $k \in \mathbb{N}$ on $K \in \mathcal{T}_h$.
-Furthermore, we partition the time axis into $N$ subinterals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$.
+Furthermore, we partition the time axis into $N$ subintervals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$.
 We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
-Then, we partition of $Q$ and $\Sigma$ into time-slabs
+Then, we partition $Q$ and $\Sigma$ into time-slabs
 \begin{equation}
@@
 ~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only.
-Indeed, it follows from the first conditon in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
+Indeed, it follows from the first condition in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
 So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.

### 2024-12-13 tex/main.tex
Updates from Overleaf

@@
 We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$.
-Then, we partition $Q$ and $\Sigma$ into time-slabs
+Then, we partition of $Q$ and $\Sigma$ into time-slabs
 \begin{equation}
@@
 ~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only.
-Indeed, it follows from the first condition in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
+Indeed, it follows from the first conditon in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
 So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.

### 2025-05-14 tex/main.tex
Reproduction update

--- 2024-12-13 tex/main.tex
@@
 \subsubsection{Simple Example}\label{sec:numex:1D:simple}
-\noindent We define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$.
-Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.
-As a first example, we consider the following exact solution \cite{MHI08}
+\noindent We define two subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ in $\Omega_2$.
+For variable $c_1 := c \vert_{\Omega_1}$, we consider the exact solution \cite{MHI08}
 \begin{equation}\label{eq:1D:exact:simple}
@@
 \end{equation}
-Note that in one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC.
-Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric.
-Then, we set
+In one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC. Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric. Then, we set
 \begin{equation}
@@
 
-\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$.
-In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally.
-
-In Fig.~\ref{fig:jumpCoefs:increasingcontrast} the dependence of the errors for increasing $c_1$ and 
+\noindent \Cref{fig:jumpCoefs:contrast:2.5} shows that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$ for $T$ large enough, but if $T$ is chosen too small, the order of convergence degrades.
+
+In \cref{fig:jumpCoefs:increasingcontrast} the dependence of the errors for increasing $c_1$ and 
 leaving $c_2 = 1$ fixed (i.e.\ increasing the contrast value) is investigated.
@@
 This is an important observation since an exponential growth in the contrast would have rendered the corresponding problems nearly impossible to resolve numerically.
-Still, compared to the best approximation error which grows quadratically we 
-loose a factor of $c_1$.
+Still, compared to the best approximation error which grows quadratically we loose a factor of $c_1$.
 This entails that a strong refinement of the discretization is required to maintain the accuracy of the numerical solution as the contrast increases.
@@
 
+%should come from: 1D-jump-convergence_Ex2.py
+\begin{comment}
 \begin{figure}[!htbp]
@@
             \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=2.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k2.csv};
 
@@
   \end{figure}
+\end{comment}
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 2,
+                horizontal sep=1.25cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named,
+            ]
+
+            %L-infty-L2-u (k = 2)
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=2.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k2.csv};
+
+            %L-infty-L2-u (k = 3)
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
+
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+
+            \addplot[gray, dotted, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {1.45*(1/2^(2))^(x-0.9)};
+            %\node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            %\node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
+            \legend{$k=2 $,, $k = 3$,,$\mathcal{O}(h^{2})$,$\mathcal{O}(h^{3})$}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+
+            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dotted, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
+            %\node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            %\legend{$k=2 $,, $k = 3$,}
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+
+            %L-infty-L2-u (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+
+            %L-infty-L2-u (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+
+            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4] {0.09*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray, dotted, domain=1:4] {0.05*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.009999968541169805
+                2 0.006666645694113204
+                3 0.004999984270584902
+                4 0.003999987416467922
+
+            };
+            %\node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            %\node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+
+            %\legend{$k=2 $,, $k = 3$,}
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            legend pos=south west, %yticklabels={,,},
+            ]
+            %L2-L2-u_t (k = 2)
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+
+            %L2-L2-u_t (k = 3)
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+
+            \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(2))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
+            \addplot[gray, dotted, domain=1:4] {0.2*(1/2^(3))^(x-0.9)};
+            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
+            \addplot[gray,dashed] table {
+                1 0.09999968541169805
+                2 0.06666645694113204
+                3 0.04999984270584902
+                4 0.03999987416467922
+
+            };
+            %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
+            %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+            %\legend{$k=2 $,, $k = 3$,}
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
+We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
+The gray dashed lines indicate the observed convergence rates.
+\textbf{adjust log lines..., shared legend...}}
+    \label{fig:jumpCoefs:contrast:2.5}
+  \end{figure}
 
@@
             %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
 
@@
             ]
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k3.csv};
-
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simpleExact_TAdapted_multipleContrasts_1D_jumpingCoefs_k3.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
+
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
 
@@
 
+%old figure
+  \begin{comment}
   \begin{figure}[!htbp]
@@
     \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
 The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
+    \label{fig:jumpCoefs:quality}
+  \end{figure}
+  \end{comment}
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = 1e-3, ymax = 0.5e1,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=5, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+                ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+
+                %\addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+
+                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=3pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{2},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{3},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \legend{exact,$L=1$, $L=2$, $L=3$, $L=4$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 5.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ymin = -2.25, ymax = 2.25,
+                ]
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
+                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
+                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
+                %\addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
+
+                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=3pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{2},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{3},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+
+                \draw[dashed,gray,very thick] (0.5,-3) -- (0.5,3);
+                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                %Colors
+                \definecolor{L1Color}{RGB}{55,126,184}
+                \definecolor{L2Color}{RGB}{77,175,74}
+                \definecolor{L3Color}{RGB}{152,78,163}
+                \definecolor{L4Color}{RGB}{255,127,0}
+
+                %L = 1
+                \draw[color=L1Color,thick] (0.75,-2) -- (1,-2);
+                \draw[color=L1Color,thick] (0.75,-2.05) -- (0.75,-1.95);
+                \draw[color=L1Color,thick] (1.0,-2.05) -- (1.0,-1.95);
+
+                %L = 2
+                \draw[color=L2Color,thick] (0.75,-1.75) -- (1,-1.75);
+                \draw[color=L2Color,thick] (0.75,-1.70) -- (0.75,-1.8);
+                \draw[color=L2Color,thick] (0.875,-1.70) -- (0.875,-1.8);
+                \draw[color=L2Color,thick] (1.0,-1.70) -- (1.0,-1.8);
+
+                %L = 3
+                \draw[color=L3Color,thick] (0.75,-1.5) -- (1,-1.5);
+                \draw[color=L3Color,thick] (0.75,-1.45) -- (0.75,-1.55);
+                \draw[color=L3Color,thick] (0.8125,-1.45) -- (0.8125,-1.55);
+                \draw[color=L3Color,thick] (0.875,-1.45) -- (0.875,-1.55);
+                \draw[color=L3Color,thick] (0.9375,-1.45) -- (0.9375,-1.55);
+                \draw[color=L3Color,thick] (1.0,-1.45) -- (1.0,-1.55);
+
+                %L = 4
+                \draw[color=L4Color,thick] (0.75,-1.25) -- (1,-1.25);
+                \draw[color=L4Color,thick] (0.75,-1.20) -- (0.75,-1.30);
+                \draw[color=L4Color,thick] (0.78125,-1.20) -- (0.78125,-1.30);
+                \draw[color=L4Color,thick] (0.8125,-1.20) -- (0.8125,-1.30);
+                \draw[color=L4Color,thick] (0.84375,-1.20) -- (0.84375,-1.30);
+                \draw[color=L4Color,thick] (0.875,-1.20) -- (0.875,-1.30);
+                \draw[color=L4Color,thick] (0.90625,-1.20) -- (0.90625,-1.30);
+                \draw[color=L4Color,thick] (0.9375,-1.20) -- (0.9375,-1.30);
+                \draw[color=L4Color,thick] (0.96875,-1.20) -- (0.96875,-1.30);
+                \draw[color=L4Color,thick] (1.0,-1.20) -- (1.0,-1.30);
+
+                %\legend{exact, $L=1$, $L=2$, $L=3$, $L=4$}
+
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.v \textbf{generate the data for the exact plots, at which time are we?}}
     \label{fig:jumpCoefs:quality}
@@
                 %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5_T0.5.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{7.5},line width=3.0pt,mark=None,color=yellow] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5.csv};
+
                 %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
@@
                 ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
+
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
+                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
                 %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
 
-                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3/2))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(2))^(x-0.9)};
+                \addplot[gray, dotted, domain=1:4] {0.0008*(1/2^(3))^(x-0.9)};
+                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(3/2))^(x-0.9)};
+                \addplot[gray, dotted, domain=1:4] {0.0008*(1/2^(5/2))^(x-0.9)};
 
@@
                 \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
                 %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                %\addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
 
@@
 
-                \legend{exact,$L=4$, $L=5$}
+                \legend{exact,$L=3$, $L=4$}
             \end{groupplot}
         \end{tikzpicture}
+        \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).
+\textbf{what is happening here now?
+before it was $\mathcal{O}(h^2)$ and $\mathcal{O}(h^{3/2})$..., right plot looks fine, also $c_1 = 2.0$ for the right plot...}}
     \end{center}
-    \caption{The $L^2$-bestapproximation error of \eqref{eq:1D:complicatedSol} with $k = 2$ for $c_2 = 1$ and $c_1 \in \{1.0,1.5,2.0\}$ (left) and the approximation of the time derivative of \eqref{eq:1D:complicatedSol} with $k = 3$ for $c_1 = 2.5$ for $L = 4,5$, $h = 1/2^{L+1} = \Delta t$ (right).}
     \label{fig:1D-complicated-sol}
@@
 For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$.
-Similar as already observed in the one-dimensional case the right plot in Fig.~\ref{fig:2DjumpCoefs} shows that these errors are more sensitive to inreasing $c_1$ than the corresponding best approximation errors.
-In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$ which renders it very demanding to maintain a resonable accuracy as the contrast increases.
+Similar as already observed in the one-dimensional case the right plot in Fig.~\ref{fig:2DjumpCoefs} shows that these errors are more sensitive to increasing $c_1$ than the corresponding best approximation errors.
+In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$ which renders it very demanding to maintain a reasonable accuracy as the contrast increases.
 

### 2025-05-14 codeNew/ApproxPlotsMultipleJumps.py

@@ -1,0 +1,385 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+from meshes import get_1Dmesh
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False #what does this do??
+
+GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,c3,pos,pos2):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    pre_upper_coords = x[0] > pos 
+    lower_coords = np.invert(pre_upper_coords)
+    upper_coords = x[0] > pos2
+    middle_coords = np.logical_and(x[0] >= pos, x[0] <= pos2)
+    values[upper_coords] = np.full(sum(upper_coords), c3**2)
+    values[middle_coords] = np.full(sum(middle_coords), c2**2)
[…]

### 2025-05-14 codeNew/GMREs.py

@@ -1,0 +1,414 @@
+import numpy as np
+from math import pi 
+
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from math import sqrt
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+import os
+from typing import Optional, Callable
+
+from math import log,sqrt
+
+if os.name == "nt":
+    _clear_line_command = ""
+else:
+    _clear_line_command = "\33[2K"
+
+sys.setrecursionlimit(10**6)
+
+class LinearSolver():
+    def __init__(self, mat : PETSc.Mat,
+                 pre = None,
+                 tol : float = None,
+                 maxiter : int = 100, 
+                 atol : float = None,
+                 callback : Optional[Callable[[int, float],None]] = None,
+                 callback_sol : Optional[Callable[[PETSc.Vec],None]] = None,
+                 printrates : bool = False,
+                 estimate_cond : bool = False 
+                 ):
+        if atol is None and tol is None:
+            tol = 1e-12
+        self.mat = mat
+        #assert (freedofs is None) != (pre is None)
+        self.pre = pre
+        self.tol = tol
+        self.atol = atol
+        self.maxiter = maxiter
+        self.callback = callback
+        self.callback_sol = callback_sol
+        self.printrates = printrates
+        self.residuals = []
+        self.iterations = 0
+        self.estimate_cond = estimate_cond
+        self.condest = None
+
+    def Solve(self, rhs: PETSc.Vec, sol: Optional[PETSc.Vec] = None,
+              initialize : bool = True) -> PETSc.Vec:
+        self.iterations = 0
+        self.residuals = []
+        if sol is None:
+            #sol = rhs.create(comm=MPI.COMM_WORLD)
+            sol,_ = self.mat.createVecs()
+            initialize = True
+        if initialize:
+            #print("ayyayayaya")
+            #help(sol)
+            #print("sol = ", sol)
+            #sol.copy(rhs)
+            sol.set(0)
+            #print(" lalala ")
+        self.sol = sol 
+        self._SolveImpl(rhs=rhs,sol=sol)
+        if self.estimate_cond:
+            return sol,self.residuals, self.condest, self.iterations
+        else: 
+            return sol,self.residuals
+
+    def CheckResiduals(self,residual):
[…]

### 2025-05-14 codeNew/MultContrast.py

@@ -1,0 +1,114 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+from Solve1D import *
+
+import sys
+args = ['fix','adap']
+
+if len(sys.argv) > 1 and sys.argv[1] in args:
+    TAdap = True if sys.argv[1] == 'adap' else False
+    print("Solving with TAdap = ", TAdap)
+else: 
+    raise ValueError('Please give either fix or adap as arguments')
+
+
+#Stabilization params
+def set_stabs(c1,c2=1.0): 
+    stabs = {#"data": 1e4,
+                "data": 1e4,
+                #"dual": 1.0,
+                "dual": 1e0,
+                #"primal": 1e-3,
+                "primal": 1e-2,
+                "primal-jump":1e-2, # for simple sol: 1e-2, 
+                #"primal-jump-vel":1.0,
+                "primal-jump-displ-grad":1e-2/max(c1**2,c2**2)**2 # for simple sol: 1e-2
+            } 
+    return stabs
+
+
+
+df = pd.DataFrame()
+
+
+## for multiple contrasts (well-posed=False, GCC = True)
+orders = [3]
+contrasts = [1.0,1.5,2.0,2.5,3.0,3.5,4.0,4.5]
+ref_lvls = lambda order, T : [3]
+
+#time
+#TAdap = True
+Tfunc = lambda contrast: 1/4*(1+1/contrast)*1.01 if TAdap else 0.5
+
+
+
+make_plots=True
+
+for order in orders:
+    for contrast in contrasts: 
+        T = Tfunc(contrast)
+        print("Solving with time T = ", T)
+        plot_df = pd.DataFrame()
+        for ref_lvl in ref_lvls(order,T):
+            print("Order = {}, ref_lvl = {}, contrast = {}".format(order,ref_lvl,contrast))
+            stabs = set_stabs(c1=contrast)
[…]

### 2025-05-14 codeNew/WeakDiscPlot.py

@@ -1,0 +1,334 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False
+
+GCC = True
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,pos):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    upper_coords = x[0] > pos 
+    lower_coords = np.invert(upper_coords)
+    values[upper_coords] = np.full(sum(upper_coords), c2**2)
+    values[lower_coords] = np.full(sum(lower_coords), c1**2)
+    return values
+
+
+
+
+#Exact solution for discontinuous wave numbers
+def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
+    if not dt:
+        #import pdb; pdb.set_trace()
+        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x[0]-c1*t)-p0(k-x[0]-c1*t)) for k in range(trunc)])
[…]

### 2025-05-14 codeNew/plot_exact.py

@@ -1,0 +1,49 @@
+import numpy as np
+import scipy.sparse as sp
+import matplotlib.pyplot as plt
+
+
+def conditional(x,eta,true,false):
+    if x <= eta: 
+        return true
+    else: 
+        return false
+
+def new_refsol(xu,t,c1,c2,w1,pos=0.5,dt=False):
+        w2 = c1*w1/c2
+        if not dt:
+            u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
+            u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
+            sol = conditional(xu,pos,u1,u2)
+        else: 
+            u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
+            u2 = -w2*c2*np.sin(w2*c2*t)*np.cos(w2*(xu-pos))
+            sol = conditional(xu,pos,u1,u2)
+        return sol
+    
+w1 = 3*np.pi
+c1 = 2.5
+c2 = 1
+pos= 0.5 
+
+
+def sol(t,xu):
+    return new_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=False)
+
+def dt_sol(t,xu):
+    return new_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=True)
+
+
+def plot(t):
+    x_pts = np.linspace(0.0,1.0,num=5000).tolist()
+
+
+    y_pts = np.zeros(len(x_pts))
+
+    for i in range(len(x_pts)):
+        y_pts[i] = sol(t,x_pts[i])
+
+    plt.plot(x_pts,y_pts)
+    plt.show()
+
+plot(0.5)

### 2025-05-14 codeNew/plot_exact_test.py

@@ -1,0 +1,83 @@
+import numpy as np
+import scipy.sparse as sp
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+from matplotlib.ticker import MaxNLocator, LinearLocator, FormatStrFormatter
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+
+#Testfile to check the implementation of the exact solution..., exchanged ufl.conditional with a function that should do the same, ufl.exp to np.exp and x[0] -> x as before...
+
+def conditional(x,eta,true,false):
+    if x <= eta: 
+        return true
+    else: 
+        return false
+
+def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
+    if not dt:
+        #import pdb; pdb.set_trace()
+        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x-c1*t)-p0(k-x-c1*t)) for k in range(trunc)])
+        u1_minus = ((1/pos*c1)/(c2+c1))*sum([((c2-c1)/(c2+c1))**k * p0(c1/c2*(x-pos)+k+pos-c1*t) for k in range(trunc)])
+    else:
+        u1_plus = sum([((c2-c1)/(c2+c1))**k * (800*c1*(k+x-c1*t-1/5)*p0(k+x-c1*t)-800*c1*(k-x-c1*t-1/5)*p0(k-x-c1*t)) for k in range(trunc)])
+        u1_minus = sum([((c2-c1)/(c2+c1))**k * 800*c1*(c1/c2*(x-pos)+k+pos-c1*t-1/5)*p0(c1/c2*(x-pos)+k+pos-c1*t) for k in range(trunc)])
+    sol = conditional(x,pos,u1_plus,u1_minus)
+    return sol
+
+p0 = lambda x : 1/100*np.exp(-(20*(x-1/5))**2)
+
+c1 = 1
+c2 = 0.1
+pos= 0.5
+t = 0.0
+trunc = 100
+
+def sol(t,xu):
+    return ref_sol(xu,t,p0,c1,c2,trunc,pos,dt=False)
+
+def dt_sol(t,xu):
+    return ref_sol(xu,t,p0,c1,c2,trunc,pos,dt=True)
+
+
+def plot(t):
+    x_pts = np.linspace(0.0,1.0,num=5000).tolist()
+
+
+    y_pts = np.zeros(len(x_pts))
+
+    for i in range(len(x_pts)):
[…]

### 2025-05-14 codeNew/reproduce.sh

@@ -1,0 +1,7 @@
+#Requirements: fenicsx, gmsh (!), pandas, numpy....
+#Reproduce experiments with a single contrast
+python3 SingleContrast.py 0.5
+python3 SingleContrast.py 0.1
+#Reproduce experiments for increasing contrast
+python3 MultContrast.py fix
+python3 MultContrast.py adap

### 2025-06-23 tex/main.tex
Reproduction (WIP)

@@
 \author[1]{\fnm{Erik} \sur{Burman}}\email{e.burman@ucl.ac.uk}
-\author[1]{\fnm{Janosch} \sur{Preuss}}\email{j.preuss@ucl.ac.uk}
-\author[2]{\fnm{Tim} \sur{van Beeck}}\email{t.beeck@math.uni-goettingen.de}
+\author[2]{\fnm{Janosch} \sur{Preuss}}\email{janosch.preuss@inria.fr}
+\author[3]{\fnm{Tim} \sur{van Beeck}}\email{t.beeck@math.uni-goettingen.de}
 
@@
 
-\affil[2]{\orgdiv{Institute for Numerical and Applied Mathematics}, \orgname{University of G\"{o}ttingen}, \orgaddress{\street{Lotzestr.
+\affil[2]{\orgdiv{MAKUTU}, \orgname{Inria}, \orgaddress{\street{...}, \city{...}, \postcode{...}, \country{France}}}
+
+\affil[3]{\orgdiv{Institute for Numerical and Applied Mathematics}, \orgname{University of G\"{o}ttingen}, \orgaddress{\street{Lotzestr.
 16-18}, \city{G\"{o}ttingen}, \postcode{37083}, \country{Germany}}}
@@
 \section{Introduction}
-\noindent In this article, we consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
+\todo[inline]{@JP: please update affiliation}
+\noindent We consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
 In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$.
@@
 We assume in what follows additionally that the triangulation $\mathcal{T}_h$ fits the interface $\Gamma$ and the data domain $\omega$.
-An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP23arxiv}, but is certainly beyond the scope of this article.
+An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP25}, but is certainly beyond the scope of this article.
 
@@
             \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            xtick={1,2,3,4}, 
             legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named,
@@
             \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            xtick={1,2,3,4},
             legend pos=south west, %yticklabels={,,},
@@
             \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+            xtick={1,2,3,4},
             legend pos=south west, %yticklabels={,,},
@@
             \addplot[gray, dotted, domain=1:4] {0.05*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.009999968541169805
-                2 0.006666645694113204
-                3 0.004999984270584902
-                4 0.003999987416467922
-
+            %\addplot[gray,dashed] table {
+            %    1 0.009999968541169805
+            %    2 0.006666645694113204
+            %    3 0.004999984270584902
+            %    4 0.003999987416467922
+            %};
+            \addplot[gray,dashdotted] table {
+                1 1.609999968541169805
+                2 1.606666645694113204
+                3 1.604999984270584902
+                4 1.603999987416467922
             };
@@
             %\node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+            \node [draw=none] at (axis description cs:0.7,0.94) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
 
@@
             \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            xtick={1,2,3,4},
             legend pos=south west, %yticklabels={,,},
@@
             %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.09999968541169805
-                2 0.06666645694113204
-                3 0.04999984270584902
-                4 0.03999987416467922
+            %\addplot[gray,dashed] table {
+            %    1 0.09999968541169805
+            %    2 0.06666645694113204
+            %    3 0.04999984270584902
+            %    4 0.03999987416467922
+            %};
+            \addplot[gray,dashdotted] table {
+                1 7.59999968541169805
+                2 7.56666645694113204
+                3 7.54999984270584902
+                4 7.53999987416467922
 
@@
             %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
+            \node [draw=none] at (axis description cs:0.7,0.94) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
             %\legend{$k=2 $,, $k = 3$,}
@@
     \end{center}
-    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
+    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-best approximation (dashed).
 We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
-The gray dashed lines indicate the observed convergence rates.
-\textbf{adjust log lines..., shared legend...}}
+The gray dashed lines indicate the observed convergence rates.}
     \label{fig:jumpCoefs:contrast:2.5}
@@
             legend style={legend columns=4, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+            xtick={1,1.5,2,2.5,3,3.5,4,4.5},
             %ymin=1e-7,ymax=1e1,
@@
             %ymin=1e-7,ymax=1e1,
+            xtick={1,1.5,2,2.5,3,3.5,4,4.5},
             ]
@@
 
-                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=3pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast2.5_time0.25.csv};
 
@@
                 %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-
-                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=3pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast5.5_time0.25.csv};
 
@@
     \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
-The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.v \textbf{generate the data for the exact plots, at which time are we?}}
+The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.v \textbf{generate the data for the exact plots, at which time are we?
+$t = 0.25$}}
     \label{fig:jumpCoefs:quality}
@@
 
-                \addplot+[discard if not={L}{1},discard if not={contrast}{7.5},line width=3.0pt,mark=None,color=yellow] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{3},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast7.5.csv};
+
+                \addplot+[discard if not={L}{4},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast7.5.csv};
 
                 %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
 
@@
 
-                \legend{exact, $L = 4$, $L = 3$}
+                \legend{exact, $L = 3$, $L = 4$}
                 \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
@@
 
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
+                %\addplot+[line width=3.0pt,mark=None,color=yellow] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
+                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast11.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{3},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast11.5.csv};
+
+                \addplot+[discard if not={L}{4},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast11.5.csv};
 
@@
     \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
 We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
@@
     \begin{center}
-        \begin{tikzpicture}[scale=0.72]
+        \begin{tikzpicture}[scale=0.76]
             \begin{groupplot}[%
@@
                 group size=2 by 1,
-                horizontal sep=1.5cm,
+                horizontal sep=1.25cm,
                 vertical sep=2cm,
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={L}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u errorreduced
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted,color=orange] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted,color=teal] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={refinement level $L$}, ylabel={}, title={Contrast $c_1 = 2.5$}, %cycle list name=paulcolors, 
+                %legend pos=north east, %yticklabels={,,},
+                xtick={1,2,3,4},
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},
+                legend to name=named,
+                ]
+                %
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
 
@@
                 \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={$c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={contrast $c_1$}, ylabel={}, title={}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
-                ]
-
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-
-                \addplot+[,discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                xtick={1.0,1.5,2.0,2.5},
+                ]
+
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma]  {../dataNew/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
 
                 %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsol_k3.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
 
@@
 
-                \legend{$k=2$,$k=3$}
+                %\legend{$k=2$,$k=3$}
 
@@
 
+\begin{comment}
 \section{More material}
@@
 \end{figure}
+\end{comment}
 

### 2025-06-23 codeNew/ApproxPlotsMultipleJumps.py

@@ -20,6 +20,15 @@ import cProfile
 import resource
 import pandas as pd 
 from meshes import get_1Dmesh
+import sys
+
+
+if len(sys.argv) > 2:
+    ref_lvl = int(sys.argv[1])
+    contrast = float(sys.argv[2])
+    print("Solving on level {} with contrast {}".format(ref_lvl,contrast))
+else: 
+    raise ValueError('Please provide ref level and contrast')
 
 #solver_type = "petsc-LU"  
 solver_type = "pypardiso" # 
@@ -132,7 +141,8 @@ def Solve(ref_lvl,order,contrast,stabs,plot_sol=False,plot_error=False,T=0.5):
 
     data_size = 0.3
     N = 32 
-    Nx = 64
+    Nxs = [4,8,16,32,64]
+    Nx = Nxs[ref_lvl]
 
     k = order
     q = order
@@ -155,7 +165,7 @@ def Solve(ref_lvl,order,contrast,stabs,plot_sol=False,plot_error=False,T=0.5):
     w2 = c1*w1/c2
 
     pos= 0.4
-    n_cos = 1
+    n_cos = 3 if contrast == 7.5 else 4
     pos2 = (2*np.pi*n_cos+w2*pos)/w2 
 
 
@@ -165,7 +175,7 @@ def Solve(ref_lvl,order,contrast,stabs,plot_sol=False,plot_error=False,T=0.5):
 
 
     # define quantities depending on space
-    msh_pts = gen_msh_pts_uniform(64,data_size,pos,pos2)
+    msh_pts = gen_msh_pts_uniform(Nx,data_size,pos,pos2)
     print(msh_pts)
 
 
@@ -340,46 +350,31 @@ def set_stabs(c1,c2=1.0):
 df = pd.DataFrame()
 
 
-#for single contrast, (for T = 0.5: well-posed=False, GCC = True)
-def ref_lvls(order,T):
-    if T == 0.5: 
-        lvls = [1,2,3,4]
-    else: 
-        lvls = [1,2,3,4] if order < 3 else [1,2,3]
-    lvls = [1]
-    return lvls    
-
-orders = [3]
-contrasts = [7.5,11.5]
-
-#time
-#T = 0.1
-
-T = 1.0
+order = 3
+T = 0.5
 
 make_plots=True
 
 plot_df = pd.DataFrame()
 
-for order in orders:
-    for contrast in contrasts: 
-        print("Solving with time T = ", T)
-        for ref_lvl in ref_lvls(order,T):
[…]

### 2025-06-23 codeNew/plot_exact.py

@@ -1,6 +1,18 @@
 import numpy as np
 import scipy.sparse as sp
 import matplotlib.pyplot as plt
+import sys 
+
+import pandas as pd
+
+rfs = ['SJ','MJ']
+
+if len(sys.argv) > 2 and sys.argv[1] in rfs: 
+    rf = sys.argv[1]
+    contrast = float(sys.argv[2])
+    print("Generating data for the reference solution = {} and contrast {}".format(rf,contrast))
+else: 
+    raise ValueError('Please provide one of the following options for the reference solution {} and a contrast'.format(rfs))
 
 
 def conditional(x,eta,true,false):
@@ -9,41 +21,83 @@ def conditional(x,eta,true,false):
     else: 
         return false
 
-def new_refsol(xu,t,c1,c2,w1,pos=0.5,dt=False):
-        w2 = c1*w1/c2
-        if not dt:
-            u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
-            u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
-            sol = conditional(xu,pos,u1,u2)
-        else: 
-            u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
-            u2 = -w2*c2*np.sin(w2*c2*t)*np.cos(w2*(xu-pos))
-            sol = conditional(xu,pos,u1,u2)
-        return sol
+def singleJump_refsol(xu,t,c1,c2,w1,pos=0.5,dt=False):
+    w2 = c1*w1/c2
+    if not dt:
+        u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
+        u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
+        sol = conditional(xu,pos,u1,u2)
+    else: 
+        u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
+        u2 = -w2*c2*np.sin(w2*c2*t)*np.cos(w2*(xu-pos))
+        sol = conditional(xu,pos,u1,u2)
+    return sol
+
+def multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3,dt=False):
+    w2 = c1*w1/c2
[…]

### 2025-06-23 codeNew/reproduce.sh

@@ -1,7 +1,23 @@
-#Requirements: fenicsx, gmsh (!), pandas, numpy....
+#Requirements: fenicsx, pip install: gmsh, pandas, numpy, sympy
 #Reproduce experiments with a single contrast
 python3 SingleContrast.py 0.5
 python3 SingleContrast.py 0.1
 #Reproduce experiments for increasing contrast
 python3 MultContrast.py fix
 python3 MultContrast.py adap
+
+#Generate data for exact solution 
+python3 plot_exact.py SJ 2.5
+python3 plot_exact.py SJ 5.5
+python3 plot_exact.py MJ 7.5
+python3 plot_exact.py MJ 11.5
+
+#For plots with single jump
+python3 ApproxPlots.py
+
+
+#For plots with multiple jumps
+python3 ApproxPlotsMultipleJumps.py 3 7.5
+python3 ApproxPlotsMultipleJumps.py 4 7.5
+python3 ApproxPlotsMultipleJumps.py 3 11.5
+python3 ApproxPlotsMultipleJumps.py 4 11.5

### 2025-06-23 codeNew/solve-2D-jump.py

@@ -1,0 +1,313 @@
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh#, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py.PETSc import ScalarType
+
+
+from petsc4py import PETSc
+
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+from meshes import get_2Dmesh_data_all_around
+import pypardiso
+import scipy.sparse as sp
+import time
+import cProfile
+import resource
+
+import pandas as pd 
+
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+
+well_posed = False
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    return solver
+
+# define alternative solvers here 
+#def GetSpMat(mat):
+#    ai, aj, av = mat.getValuesCSR()
+#    Asp = sp.csr_matrix((av, aj, ai))
+#    return Asp 
+
+
+#class PySolver:
+#    def __init__(self,Asp,psolver):
+#        self.Asp = Asp
+#        self.solver = psolver
+#    def solve(self,b_inp,x_out):
+#        x_py = self.solver.solve(self.Asp, b_inp.array )
+#        x_out.array[:] = x_py[:]
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+#Generates a sequence of meshes
[…]

### 2025-06-24 tex/main.tex
Some polishing

@@
 
-\abstract{In recent years several numerical methods for solving the unique continuation problem for the wave equation in a homogeneous medium with given data on the lateral boundary of the space-time cylinder have been proposed.
-This problem enjoys Lipschitz stability if the geometric control condition is fulfilled, which allows to devise optimally convergent numerical methods.
-In this article we investigate whether these results carry over to the case in which the medium exhibits a jump discontinuity.
+\abstract{In recent years, several numerical methods for solving the unique continuation problem for the wave equation in a homogeneous medium with given data on the lateral boundary of the space-time cylinder have been proposed.
+This problem enjoys Lipschitz stability if the geometric control condition is fulfilled, which allows devising optimally convergent numerical methods.
+In this article, we investigate whether these results carry over to the case in which the medium exhibits a jump discontinuity.
 Our numerical experiments suggest a positive answer.
@@
 \todo[inline]{@JP: please update affiliation}
-\noindent We consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
+\todo[inline]{@JP: Let's discuss the title again, I feel like we should include 'stability' somewhere, because it's our main objective...}
+We consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
 In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$.
-We assume that $\Omega$ is split by a smooth $(d-1)$-dimensional
-interface $\Gamma$ into two disjoint components, i.e.\ $\Omega \setminus \Gamma = \Omega_1 \cup 
+We assume that $\Omega$ is split by a smooth $(d-1)$-dimensional interface $\Gamma$ into two disjoint components such that $\Omega \setminus \Gamma = \Omega_1 \cup
 \Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
+
 We consider a scalar wave speed
@@
  %$c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$,
-which may be discontinuous across the interface $\Gamma$, but constant in time.
-For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$.
-For any nonempty subset $\omega \subset \Omega$, we set $\omega_T \coloneqq (0,T) \times \omega$.
-In the following, let $\wop$ be the wave operator with discontinuous wave-speed defined as
+which may be discontinuous across the interface $\Gamma$, but is constant in time.
+For a final time $T > 0$, we consider the space-time domain $Q = (0,T) \times \Omega$ with lateral boundary $\Sigma \coloneqq (0,T) \times \partial \Omega$, and for any nonempty subset $\omega \subset \Omega$, we set $\omega_T \coloneqq (0,T) \times \omega$.
+
+Let $\wop$ be the wave operator with discontinuous wave-speed defined as 
 \begin{equation*}
-    \wop u := \partial_t^2 - \div(c^2 \nabla u).
+    \wop u := \partial_t^2 u - \div(c^2 \nabla u).
 \end{equation*}
-In particular, we write $\square_1$ if $c_i = 1$, $i = 1,2$, i.e. if we are considering the case of homogeneous media. 
+In particular, we write $\square_1$ if $c_i = 1$ for $i = 1,2$, corresponding to the case of a homogeneous medium with unit wave speed.
+
 Then, we consider the problem: find $u : Q \rightarrow \mathbb{R}$ such that 
@@
 where $\mathbf{n}_{\Gamma}$ is the normal vector on $\Gamma$ pointing into $\Omega_+$ 
-and the jump across $\Gamma$ is defined\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}And anologously for vector-valued functions.} as $\jump{u}_{\Gamma} = u_{+}-u_{-}$ with $u_{\pm}$ being the traces
+and the jump across $\Gamma$ is defined\textsuperscript{1}\footnotemark \footnotetext{\textsuperscript{1}And analogously for vector-valued functions.} as $\jump{u}_{\Gamma} = u_{+}-u_{-}$ with $u_{\pm}$ being the traces
 of $u|_{\Omega_{\pm}}$ on $\Gamma$. \par 
-\noindent To ensure that the problem is well posed, one usually prescribes initial data
+To ensure that the problem is well posed, one usually prescribes initial data
 \begin{equation}\label{eq:initialData}
@@
 where $u_0 \in H^1(Q)$ and $u_1 \in L^2(Q)$ are given.
-For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:initialData} in heterogeneous media we refer to \cite{StolkPhD}.
-Here we consider a data assimilation problem instead, i.e.
-we assume that the initial data is unknown and that there are given measurements $u_{\omega} \in L^2(\omega_T)$ which are prescribed in a data domain $\omega_T$, $\omega \subset \Omega$, $\omega \not = \emptyset$:
+For a detailed analysis of the well-posedness of the problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:initialData} in heterogeneous media, we refer to \cite{StolkPhD}.
+
+In this work, we consider a \emph{data assimilation} problem instead, where the initial data is unknown, and we assume that there are given measurements $u_{\omega} \in L^2(\omega_T)$ prescribed in a data domain $\omega_T$, with $\omega \subset \Omega$, $\omega \not = \emptyset$:
 \begin{equation}\label{eq:dataMatch}
@@
 \end{equation}
-
-%\noindent In a homogeneous medium, where $c_i = 1$, $i = 1,2$,
-\noindent In a medium without an interface the problem \eqref{eq:waveEquation}+\eqref{eq:dataMatch} is well-studied, see e.g.~References \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
-In particular, it is known that if $c_i = 1$, $i = 1,2$, the boundary $\partial \Omega$ is strictly convex and the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR92}, then the problem is Lipschitz stable.
-Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{2}\footnotemark \footnotetext{\textsuperscript{2}with adapting the metric to the wave speed $c$.} in $\Omega$, taking into account possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
-For a precise definition, we refer to \cite{BLR92}.
+In a medium without an interface, the problem \eqref{eq:waveEquation}+\eqref{eq:dataMatch} is well-studied; see for example \cite{CM15,BFO20,BFMO21,MM21,DMS23,BDE24}.
+In particular, if the boundary $\partial \Omega$ is strictly convex, the problem is Lipschitz stable provided that the set $\omega_T \subset Q$ fulfills the geometric control condition (GCC) \cite{BLR92}.
+Roughly speaking, a set $\omega \subset \Omega$ and a final time $T$ fulfill the GCC if all geometric optic rays traveling with unit speed\textsuperscript{2}\footnotemark \footnotetext{\textsuperscript{2}We consider the metric to be adapted to the wave speed $c$.} in $\Omega$, accounting for possible reflections on the boundary $\partial \Omega$, intersect the set $(0,T) \times \omega$.
+For a more precise definition, we refer to \cite{BLR92}.
 Assuming that the GCC is satisfied, we have the following result.
@@
 \begin{thm}\label{thm:Lipschitz}
-    Assume that $c_i = 1$, $i = 1,2$, and that $\partial \Omega$ is stricly convex.
-If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$ we have the following estimates
+    Assume that $\partial \Omega$ is strictly convex and $c_i = 1$ for $i = 1,2$.
+If $\omega_T \subset Q$ fulfills the GCC, then there exists a constant $C > 0$ such that for any $\phi \in H^1(Q)$, we have the following estimates:
     \begin{align*}
@@
 
-\noindent For the heterogeneous case where $c_1 \not =  c_2$, the problem is less studied.
+In the heterogeneous case, where $c_1 \not =  c_2$, the problem is less studied.
 In the absence of the GCC, we have to assume that the final time $T$ is large enough to ensure that problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} is well-posed.
@@
 \end{equation}
-where $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$ with $d_c$ being the distance function defined as the length of the shortest continuous path in $\Omega$ connecting $x$ and $y$ with respect to the metric adapted to the discontinuous wave speed $c$.
+where $\operatorname{dist}_c(x,\omega_T) := \inf_{y \in \omega_T} d_c(x,y)$.
+Here, $d_c$ is the distance function defined as the length of the shortest continuous path in $\Omega$ connecting $x$ and $y$ with respect to the metric adapted to the discontinuous wave speed $c$.
 While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} can be poor.
-It has been shown in \cite[Thm.
-5.19]{Filippas22} that under the assumption \eqref{eq:Tcondition} the following stability result holds:
+However, as shown \cite[Thm.
+5.19]{Filippas22}, assumption \eqref{eq:Tcondition} grants the following stability result holds.
+
 \begin{thm}[Thm. 5.19 of \cite{Filippas22}]\label{thm:filippas}
-    Let $\omega_T \subset \Omega$ be nonempty and let $T$ be s.t.
+    Let $\omega_T \subset \Omega$ be nonempty and let $T > 0$ be s.t.
 \eqref{eq:Tcondition} holds.
@@
 
-\noindent In this article, we introduce a discontinuous in time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} in the heterogeneous case.
-In particular, we want to investigate numerically if the following assumption, motivated by Thm.
-\ref{thm:Lipschitz} for the homogeneous case, is justified.
+\todo[inline]{@JP: I made some minor changes to the introduction... Here, I felt that we should manage the reader's expectation a bit more and stress that we do not focus on a complete analysis. }
+
+In this article, we consider a discontinuous-in-time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} in the heterogeneous case.
+This method was originally introduced for the homogeneous case in \cite{BP24}.
+The focus of this article is not on the numerical analysis of the proposed discretization, but rather on investigating the numerically observed stability under the assumption of the GCC.
+Specifically, we want to investigate numerically whether the following assumption -- motivated by \cref{thm:Lipschitz} for the homogeneous case -- is justified.
 
@@
 
-That is, we would like to understand whether the Lipschitz stability property is preserved in presence of strong heterogeneity in the medium provided that the GCC holds.
-This question is of high practical importance since discontinuous media appear in many applications, e.g.\ in seismology.
-If the corresponding data assimilation problems were indeed subject to the poor logarithmic stability property ensured by \eqref{eq:FilippasEstimateLog}, this would pose an enormous challenge for the design of accurate and realiable numerical methods for their resolution.
-
-\section{Discretization (fully discrete \& dG in time)} 
-\noindent In this section, we introduce a fully discrete discontinuous in time finite element method to discretize the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} for the wave equation in heterogeneous media.
-The discretization is based on the scheme introduced in \cite{BP24} for the homogeneous case.
-Before introducing the method in Section \ref{sec:method}, we describe the geometric partition of the space-time domain $Q$ into time slabs in Section \ref{sec:spaceTimeDiscretization}.
+In summary, our goal is to understand whether the Lipschitz stability property is preserved in the presence of strong heterogeneity in the medium, provided that the GCC holds.
+This question is of high practical importance, as discontinuous media appear in many applications, for example, in seismology.
+If the corresponding data assimilation problems were indeed subject to the poor logarithmic stability property ensured by \eqref{eq:FilippasEstimateLog}, this would pose an enormous challenge for the design of accurate and reliable numerical methods.
+
+\vspace*{1cm}
+\noindent \textbf{Struture of the article.} In \cref{sec:discretization}, we introduce the method used to discretize \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch}.
+
+\section{Fully discrete discontinuous-in-time discretization}\label{sec:discretization} 
+In this section, we present a fully discrete discontinuous-in-time finite element method for discretizing the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch}, extending the method from \cite{BP24} to the heterogeneous case.
+\Cref{sec:spaceTimeDiscretization} describes the geometric partition of the space-time domain $Q$ into time slabs, followed by the full discretization in \cref{sec:method}.
 
@@
 \end{equation}
-We assume in what follows additionally that the triangulation $\mathcal{T}_h$ fits the interface $\Gamma$ and the data domain $\omega$.
-An extension to allow for unfitted interfaces could be possible utilizing techniques we introduced for a stationary problem in \cite{BP25}, but is certainly beyond the scope of this article.
-
-\noindent For $k \ge 1$, we define the $H^1$-conforming finite element space 
+We assume additionally that the triangulation $\mathcal{T}_h$ fits the interface $\Gamma$ and the data domain $\omega$.
+An extension to allow for unfitted interfaces could be possible by utilizing techniques introduced in \cite{BP25} for a stationary problem, but this is certainly beyond the scope of this article.
+
+For polynomial degree $k \ge 1$, we define the $H^1$-conforming finite element space 
 \begin{equation}
@@
 
-\subsection{A discontinuous in time FEM for the data assimilation problem}\label{sec:method}
-\noindent We define the discontinuous in time finite element spaces 
+\subsection{Full discretization}\label{sec:method}
+ We define the discontinuous in time finite element spaces 
 \begin{equation}
@@
 Indeed, it follows from the first condition in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
-So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.
+So stabbilizing the full gradient is not consistent, which becomes an issue in \cref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.
 }
@@
 
-\noindent With the definition of $\cL_h$, the first order optimality conditions take the form: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that 
+ With the definition of $\cL_h$, the first order optimality conditions take the form: Find $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ such that 
 \begin{alignat*}{2}
@@
 \section{Error analysis}
-\noindent In this section, we analyze the approximation of the continuous problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
-In particular, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in suitable discrete norms defined below.
-Then, we show that under Assumption \ref{assum:LipschitzStability}, we can recover convergence rates in a physically relevant norm.
-Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the semi-norms, respectively norms, induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
+This section outlines how the steps from \cite{BP24} can be adapted to the heterogeneous setting to analyze the approximation of \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} through \eqref{eq:discreteProblem}.
+In \cref{sec:analysis:infsup}, we establish inf-sup stability and continuity of the discrete problem with respect to suitable discrete norms.
+In \cref{sec:analysis:approx}, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in these norms.
+Finally, we argue that \cref{assum:LipschitzStability} allows recovering convergence rates in a physically relevant norm.
+
+\subsection{Inf-sup stability and continuity}\label{sec:analysis:infsup}
+Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the (semi-)norms induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
 \begin{equation}
@@
 \end{equation}
-\noindent Then, we define the discrete norm 
+Then, we define the discrete norm 
 \begin{equation}
@@
 It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$ and that the interface conditions \eqref{eq:IF-conditions} are fulfilled.
-Thus, by taking $\mu \rightarrow \infty$ in Thm.
-\ref{thm:filippas}, we conclude that $u_0 = u_1 = 0$.
+Thus, by taking $\mu \rightarrow \infty$ in \cref{thm:filippas}, we conclude that $u_0 = u_1 = 0$.
 As solutions to \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:initialData} depend continuously on the data \cite{StolkPhD}, it follows that $\Uh = 0$.
@@
 
-\noindent From this result and the identity
+ From this result and the identity
 \[
-B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)}
+B[(\Uh,\Zh),(\Uh,-\Zh)] = \tnorm{(\Uh,\Zh)}^2 = \tnorm{(\Uh,\Zh)}\tnorm{(\Uh,-\Zh)},
 \]
@@
 
-\begin{cor}
+\begin{cor}\label{cor:infsup}
     There exists a constant $C_B>0$ such that 
     \begin{equation}
-        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C_B \tnorm{(\Uh,\Zh)}.
-    \end{equation}
+        \sup_{(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}} \frac{B[(\Uh,\Zh),(\Wh,\Yh)]}{\tnorm{(\Wh,\Yh)}} \ge C_B \tnorm{(\Uh,\Zh)}
+    \end{equation}
+    for all $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$.
 \end{cor}
@@
 
-We report a continuity result for the bilinear form $A$ which follows from the Cauchy-Schwarz and the trace inequality \eqref{eq:traceInequality}. 
+The trace inequality \eqref{eq:traceInequality} and the Cauchy-Schwarz inequality immediately yield the continuity of the bilinear form $A$.
+
 \begin{lem}[Continuity of $A$]\label{lem:continuityA}
@@
 
-\noindent Using the inf-sup stability of $B$ and the continuity of $A$, we can show that the approximation error in the $\tnorm{(\cdot,\cdot)}$-norm is bounded by the best approximation error in the $\tnorm{(\cdot,\cdot)}_{\wop}$-norm.
+\subsection{Approximation results}\label{sec:analysis:approx}
+With \cref{cor:infsup} and \cref{lem:continuityA}, we can show that the approximation error in the $\tnorm{(\cdot,\cdot)}$-norm is bounded by the best approximation error in the $\tnorm{(\cdot,\cdot)}_{\wop}$-norm.
 
@@
     \end{align*} 
-    where we use the fact that $\mathbf{U}$ is sufficiently smooth and $u = u_{\omega}$ on $\omega_T$. Then, we can apply Lem. \ref{lem:continuityA} to obtain 
+    where we use the fact that $\mathbf{U}$ is sufficiently smooth and $u = u_{\omega}$ on $\omega_T$. Then, we can apply \cref{lem:continuityA} to obtain 
     \begin{align*}
@@
 \begin{cor}\label{cor:tnormConvRates}
-    Under the assumption of Thm. \ref{thm:bestapprox}, we have that
+    Under the assumption of \cref{thm:bestapprox}, we have that
     \begin{equation*}
@@
 
-\noindent In the following, we want to note that the assumption of Lipschitz stability, cf.
-Assumption \ref{assum:LipschitzStability} or Thm.
-\ref{thm:Lipschitz} in the homogeneous case, can be used to show convergence in a physically relevant norm.
-To utilize these results, we need to deal with the fact that the discrete solution is discontinuous in time.
-To this end, let $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ be a suitable lifting operator such that $L_{\Delta t} \ul_1 \in H^1(Q)$ as introduced in \cite[Sec.
+If the problem is Lipschitz stable, for instance in the homogeneous case (see \cref{thm:Lipschitz}), we can prove convergence in a physically relevant norm.
+To deal with the discontinuity in time of the discrete solution, a suitable lifting operator$L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ that ensures that $L_{\Delta t} \ul_1 \in H^1(Q)$ has been introduced in \cite[Sec.
 4]{BP24}.
-Then, we formulate the following result.
+Then, we state the following result.
 
 \begin{thm}\label{thm:convergence}
-    Let Assumption \ref{assum:LipschitzStability} be satisfied.
+    Let \cref{assum:LipschitzStability} be satisfied.
 For $u$ being a sufficiently regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ being the solution to \eqref{eq:discreteProblem}, there exists a constant $C>0$ such that
@@
 \begin{proof}
-    The proof follows from the same argumentation as the proof of \cite[Theorem 10]{BP24}.
+    The proof follows with the same arguments as the proof of \cite[Theorem 10]{BP24}.
 \end{proof}
@@
 \begin{rmk}[Homogenous media]\label{rem:homMedia}
-    In the homogenous case where $c_i = 1$, $i = 1,2$, we know that Assumption \ref{assum:LipschitzStability} is satisfied, cf.
-Thm.
-\ref{thm:Lipschitz}.
-Thus, we recover the result from \cite[Theorem 10]{BP24}.
+    If $c_i = 1$ for $i = 1,2$, \cref{assum:LipschitzStability} holds (see \cref{thm:Lipschitz}), and we recover the result from \cite[Theorem 10]{BP24}.
 \end{rmk}
 
-\begin{rmk}
-    Suppose that Assumption \ref{assum:LipschitzStability} is not satisfied, e.g.
-if the GCC is not fulfilled.
-If $T$ is large enough such that \eqref{eq:Tcondition} holds, we can still apply the results from Thm.
-\ref{thm:filippas}.
-To utilize this result similarly to Assumption \ref{assum:LipschitzStability}, we would have to deal with the following technicalities:
+\begin{rmk}[Logarithmic stability]
+    If \cref{assum:LipschitzStability} is not satisfied, we could still hope to utilize the results from \cref{thm:filippas}, provided that $T$ is large enough such that \eqref{eq:Tcondition} holds.
+To this end, we would have to deal with the following technicalities:
     \begin{enumerate}
-        \item The results from Thm.
-\ref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$.
-However, we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$.
-Thus, we would have to rewrite the estimates from Thm.
-\ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
+        \item The results from \cref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$, but we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$.
+Thus, we would have to rewrite the estimates from \cref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
 To this end, one might be able to shift the regularity suitably, cf.
@@
 A.1]{BFMO21}.
-        \item We have to ensure that the constants in the estimates from Thm.
-\ref{thm:filippas} remain bounded when we consider the residual $\tilde{e}_h$.
+        \item We have to ensure that the constants in the estimates from \cref{thm:filippas} remain bounded when we consider the residual $\tilde{e}_h$.
 In particular, we have to control $C_{0,1} := \Vert (\tilde{e}_h \vert_{t = 0}, \dt \tilde{e}_h \vert_{t = 0}) \Vert_{H^1 \times L^2}$.
@@
     Then, we can use the arguments of \cite[Theorem 10]{BP24} to show that 
-    \begin{equation}
+    \begin{equation*}
         \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1}. 
-    \end{equation}
+    \end{equation*}
 \end{rmk}
@@
 \section{Numerical experiments}
-\noindent In this section, we present numerical experiments carried out with the proposed method.
+ In this section, we present numerical experiments carried out with the proposed method.
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
@@
 \subsection{Examples in one space dimension}
-\noindent We consider the unit interval $\Omega \coloneqq (0,1) \subset \mathbb{R}$.
-For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$.
-The time step is chosen as $\Delta t = h$.
+ We consider the unit interval $\Omega \coloneqq (0,1) \subset \mathbb{R}$ partitioned into $2^{L+1}$, $L \in \mathbb{N}$, uniform elements of size $h = 1/2^{L+1}$.
+Unless specified otherwise, we choose the time step as $\Delta t = h$.
 
 \subsubsection{Simple Example}\label{sec:numex:1D:simple}
-\noindent We define two subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ in $\Omega_2$.
+ We define two subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ in $\Omega_2$.
 For variable $c_1 := c \vert_{\Omega_1}$, we consider the exact solution \cite{MHI08}
@@
 \end{equation}
+
 In one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC. Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric. Then, we set
@@
 
-\noindent \Cref{fig:jumpCoefs:contrast:2.5} shows that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$ for $T$ large enough, but if $T$ is chosen too small, the order of convergence degrades.
+\Cref{fig:jumpCoefs:contrast:2.5} shows that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$ for $T$ large enough, but if $T$ is chosen too small, the order of convergence degrades.
 
@@
 This entails that a strong refinement of the discretization is required to maintain the accuracy of the numerical solution as the contrast increases.
-We illustrate this problem in Fig.~\ref{fig:jumpCoefs:quality}.
+We illustrate this problem in \cref{fig:jumpCoefs:quality}.
 For $c_1 = 2.5$ the exact solution is already well-captured by the numerical solution on refinement level $L=2$.
@@
 
-%old figure
-  \begin{comment}
   \begin{figure}[!htbp]
@@
                 ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast2.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{2},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
 
@@
                 legend pos=north west, %yticklabels={,,},
-                ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={contrast}{5.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
+                ymin = -2.25, ymax = 2.25,
+                ]
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast5.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{2},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
 
@@
     \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+    \caption{At $t = 0.25$, we compare the exact solution \eqref{eq:1D:exact:simple} and approximations with polynomial degree $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
 The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
@@
   \end{figure}
-  \end{comment}
+
+\subsubsection{Multiple jumps}
+ The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
+For two points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
+$\bar{\Omega} = \cup_{i = 1,2,3} \overline{\Omega}_i$.
+Then, we consider the following ansatz for the exact solution:
+\begin{equation}\label{eq:1D:exact:simpleMult}
+    u(x,t) := \begin{cases}
+        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
+        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
+        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
+    \end{cases}
+\end{equation}
+To ensure the continuity of \eqref{eq:1D:exact:simpleMult}, we choose $p_2$ in dependence of $p_1$ and $w_2$. For $n \in \mathbb{Z}$, we set
+\begin{align*}
+    p_2 \coloneqq \frac{2 \pi n + w_2 p_1}{w_2} \quad \Longrightarrow \quad \cos(w_2(p_2-p_1)) = 1.
+\end{align*}
+
+In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
+As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
+For contrast $c_1 \in \{ 7.5,11.5 \}$, \cref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
+
+\begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            ymin = -0.6e0, ymax = 0.6e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1= 7.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.25.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast7.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast7.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.7,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
+
+                \legend{exact, $L = 3$, $L = 4$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
+
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast11.5_time0.25.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast11.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast11.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+        \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
+We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
+    \label{fig:jumpCoefs:multipleJumps}
+  \end{figure}
+
+ As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
+\begin{equation}
+    T > 2 \left[ (p_2 - p_1) + \frac{p_1 - 0.3 + 1 - p_2}{c_1} \right]. 
+\end{equation}
+\Cref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
+
+  \begin{figure}[!htbp]
+    \begin{center}
+        \begin{tikzpicture}[scale=0.72]
+            \begin{groupplot}[%
+                group style={%
+                group size=2 by 1,
+                horizontal sep=1.5cm,
+                vertical sep=2cm,
+                },
+            ymajorgrids=true,
+            grid style=dashed,
+            %ymin = -1.1e0, ymax = 1.1e0,
+            ]    
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
+                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+
+                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast2.5_time0.5.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
+
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+                \legend{exact,$T=1.0$,$T=0.5$}
+                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
+                legend pos=north west, %yticklabels={,,},
+                ]
+                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
+
+                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.5.csv};
+
+                \addplot+[line width=3.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast7.5Test.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast7.5.csv};
+
+                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
+                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
+                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
+                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
+                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
+
+            \end{groupplot}
+        \end{tikzpicture}
+         \pgfplotslegendfromname{named}
+    \end{center}
+    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
+We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
+    \label{fig:jumpCoefs:multipleJumps:noGCC}
+  \end{figure}
+
+\subsubsection{2nd one dimensional example}
+
+Let us consider a final one-dimensional example to illustrate the high resolution 
+required to simulate wave propagation in heterogeneous media. 
+We consider the same geometrical setup as in \cref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
+With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
+\begin{equation}\label{eq:1D:complicatedSol}
+    u(x,t) = \begin{cases}
+      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
+      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
+    \end{cases}
+\end{equation}
+This solution describes a wave traveling towards the interface $\Gamma$.
+Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+In \cref{fig:1D:complicatedSol} we consider the approximation of this function by the $L^2$-interpolation.
+The plot on the right shows that for $c_1 = 2.5$ the velocity is not captured well yet even for $k=3$ on the finest refinement level we considered.
+In terms of convergence rates, we merely observe $\mathcal{O}(h^2)$ for $k=2$.
+In view of the previous experiments it is clear that this poses a serious obstruction to obtaining accurate solutions to the corresponding unique continuation problem.
 
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=5, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
-                ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-
-                %\addplot+[discard if not={contrast}{2.5},line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_simple.csv};
-
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast2.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{1},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{2},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{3},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \legend{exact,$L=1$, $L=2$, $L=3$, $L=4$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={$x$}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 5.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ymin = -2.25, ymax = 2.25,
-                ]
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.25,-3) -- (0.25,3) -- (0,3) -- (0,-3) -- cycle;
-                %\draw[fill=gray!40,draw=none,opacity=0.5] (0.75,-3) -- (0.75,3) -- (1.0,3) -- (1.0,-3) -- cycle;
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast5.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{1},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{2},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{3},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.5,-3) -- (0.5,3);
-                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                %Colors
-                \definecolor{L1Color}{RGB}{55,126,184}
-                \definecolor{L2Color}{RGB}{77,175,74}
-                \definecolor{L3Color}{RGB}{152,78,163}
-                \definecolor{L4Color}{RGB}{255,127,0}
-
-                %L = 1
-                \draw[color=L1Color,thick] (0.75,-2) -- (1,-2);
-                \draw[color=L1Color,thick] (0.75,-2.05) -- (0.75,-1.95);
-                \draw[color=L1Color,thick] (1.0,-2.05) -- (1.0,-1.95);
-
-                %L = 2
-                \draw[color=L2Color,thick] (0.75,-1.75) -- (1,-1.75);
-                \draw[color=L2Color,thick] (0.75,-1.70) -- (0.75,-1.8);
-                \draw[color=L2Color,thick] (0.875,-1.70) -- (0.875,-1.8);
-                \draw[color=L2Color,thick] (1.0,-1.70) -- (1.0,-1.8);
-
-                %L = 3
-                \draw[color=L3Color,thick] (0.75,-1.5) -- (1,-1.5);
-                \draw[color=L3Color,thick] (0.75,-1.45) -- (0.75,-1.55);
-                \draw[color=L3Color,thick] (0.8125,-1.45) -- (0.8125,-1.55);
-                \draw[color=L3Color,thick] (0.875,-1.45) -- (0.875,-1.55);
-                \draw[color=L3Color,thick] (0.9375,-1.45) -- (0.9375,-1.55);
-                \draw[color=L3Color,thick] (1.0,-1.45) -- (1.0,-1.55);
-
-                %L = 4
-                \draw[color=L4Color,thick] (0.75,-1.25) -- (1,-1.25);
-                \draw[color=L4Color,thick] (0.75,-1.20) -- (0.75,-1.30);
-                \draw[color=L4Color,thick] (0.78125,-1.20) -- (0.78125,-1.30);
-                \draw[color=L4Color,thick] (0.8125,-1.20) -- (0.8125,-1.30);
-                \draw[color=L4Color,thick] (0.84375,-1.20) -- (0.84375,-1.30);
-                \draw[color=L4Color,thick] (0.875,-1.20) -- (0.875,-1.30);
-                \draw[color=L4Color,thick] (0.90625,-1.20) -- (0.90625,-1.30);
-                \draw[color=L4Color,thick] (0.9375,-1.20) -- (0.9375,-1.30);
-                \draw[color=L4Color,thick] (0.96875,-1.20) -- (0.96875,-1.30);
-                \draw[color=L4Color,thick] (1.0,-1.20) -- (1.0,-1.30);
-
-                %\legend{exact, $L=1$, $L=2$, $L=3$, $L=4$}
-
-            \end{groupplot}
-        \end{tikzpicture}
-        \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
-The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.v \textbf{generate the data for the exact plots, at which time are we?
-$t = 0.25$}}
-    \label{fig:jumpCoefs:quality}
-  \end{figure}
-
-  \begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=3 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1Test_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.5pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestnoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-                %\addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestNoGCC_1D_jumpingCoefs_k3_WPFalse_contrast3.5.csv};
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.0001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)}$}, %cycle list name=paulcolors, 
-                legend pos=south east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt] table [x=contrast, y=H1-u1-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/initialH1TestRestricted_NoGCC_1D_jumpingCoefs_k2_WPFalse_contrast3.5.csv};
-
-                \addplot+[line width=1.1pt,dashed] table [x=contrast, y expr=\thisrow{exp_Lambda}*0.00000001, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/1DsimpleSol_Filippas.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2 \quad L = 4$, $k = 3 \quad L = 4$, $e^\Lambda$ (rescaled)}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Filippas lambda...}
-  \end{figure}
-\end{comment}
-
-\subsubsection{Multiple jumps}
-\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
-For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
-$\bar{\Omega} = \cup_{i = 1,2,3} \overline{\Omega}_i$.
-Then, we consider the following ansatz for the exact solution:
-\begin{equation}\label{eq:1D:exact:simpleMult}
-    u(x,t) := \begin{cases}
-        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
-        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
-        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
-    \end{cases}
-\end{equation}
-To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
-\begin{equation*}
-    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
-\end{equation*}
-Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
-In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
-As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
-For contrast $c_1 \in \{ 7.5,11.5 \}$, Fig.
-\ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
-
-\begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            ymin = -0.6e0, ymax = 0.6e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1= 7.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                %\addplot+[line width=1.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps.csv};
-
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{3},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast7.5.csv};
-
-                \addplot+[discard if not={L}{4},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast7.5.csv};
-
-                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L4.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5_L3.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.7,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
-
-                 %L = 3
-                %\draw[color=orange,thick] (0.4,-0.5) -- (2/3,-0.5);
-                %\draw[color=orange,thick] (0.4,-0.48) -- (0.4,-0.52);
-                %\draw[color=orange,thick] (0.4375,-0.48) -- (0.4375,-0.52);
-                %\draw[color=orange,thick] (0.5,-0.48) -- (0.5,-0.52);
-                %\draw[color=orange,thick] (0.5625,-0.48) -- (0.5625,-0.52);
-                %\draw[color=orange,thick] (0.625,-0.48) -- (0.625,-0.52);
-                %\draw[color=orange,thick] (0.6666,-0.48) -- (0.6666,-0.52);
-
-                \legend{exact, $L = 3$, $L = 4$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($c_1 = 11.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform.csv};
-                %\addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_T0.5.csv};
-
-                %\addplot+[line width=3.0pt,mark=None,color=yellow] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L4.csv};
-                %\addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform_T0.5_L3.csv};
-
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast11.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{3},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast11.5.csv};
-
-                \addplot+[discard if not={L}{4},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast11.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.125) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-        \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
-We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
-    \label{fig:jumpCoefs:multipleJumps}
-  \end{figure}
-
-\noindent As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
-\begin{equation}
-    T > 2 \left[ (p_2 - p_1) + \frac{p_1 - 0.3 + 1 - p_2}{c_1} \right]. 
-\end{equation}
-Fig.~\ref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 2.5$)}, %cycle list name=paulcolors, 
-                legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast2.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \legend{exact,$T=1.0$,$T=0.5$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \addplot+[line width=3.0pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../data/exact_plot_data_1D_multipleJumps_contrast7.5.csv};
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast7.5_k3_dataLeft_T0.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.6666,-2) -- (0.6666,2);
-                \node [draw=none] at (axis description cs:0.38,0.125) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.125) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-         \pgfplotslegendfromname{named}
-    \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
-We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
-    \label{fig:jumpCoefs:multipleJumps:noGCC}
-  \end{figure}
-
-  \begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.5$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ - with bug in the code....}
-    \label{fig:jumpCoefs:multipleJumps2}
-  \end{figure}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = -1.1e0, ymax = 1.1e0,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data_1D_multipleJumps_contrast11.5.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                %\node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};
-
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
-                legend pos=north west, %yticklabels={,,},
-                ]
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.3,-2) -- (0.3,2) -- (0,2) -- (0,-2) -- cycle;
-                \draw[fill=gray!40,draw=none,opacity=0.5] (0.7,-2) -- (0.7,2) -- (1.0,2) -- (1.0,-2) -- cycle;
-                \addplot+[line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/multipleJumps_approx_plot_data_WPFalse_contrast11.5_k3_uniform.csv};
-
-                \draw[dashed,gray,very thick] (0.4,-2) -- (0.4,2);
-                \draw[dashed,gray,very thick] (0.63188,-2) -- (0.63188,2);
-                \node [draw=none] at (axis description cs:0.38,0.65) {\color{gray} $\Gamma_1$};
-                \node [draw=none] at (axis description cs:0.71,0.65) {\color{gray} $\Gamma_2$};
-                \node [draw=none] at (axis description cs:0.2,0.15) {\color{gray} $\omega$};
-                \node [draw=none] at (axis description cs:0.8,0.15) {\color{gray} $\omega$};
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Exact solution (left) and approximated solution with $k = 3$ (right) of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with $c_1 = c_3 = 11.5$ and $c_2 = 1.0$ (uniform mesh), computed with $64$ points in space, $32$ in time and $T = 0.5$.}
-    \label{fig:jumpCoefs:multipleJumps3}
-  \end{figure}
-\end{comment}
-
-\subsubsection{2nd one dimensional example}
-
-Let us consider a final one-dimensional example to illustrate the high resolution 
-required to simulate wave propagation in heterogeneous media. 
-We consider the same geometrical setup as in Sec.
-\ref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
-With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
-\begin{equation}\label{eq:1D:complicatedSol}
-    u(x,t) = \begin{cases}
-      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) - u_0(k-x-c_1 t)\right), &x \in \Omega_1, \\
-      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), & x \in \Omega_2.
-    \end{cases}
-\end{equation}
-This solution describes a wave traveling towards the interface $\Gamma$.
-Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
-
-In Fig.~\ref{fig:1D-complicated-sol} we consider the approximation of this function by the $L^2$-interpolation.
-The plot on the right shows that for $c_1 = 2.5$ the velocity is not captured well yet even for $k=3$ on the finest refinement level we considered.
-In terms of convergence rates, we merely observe $\mathcal{O}(h^2)$ for $k=2$.
-In view of the previous experiments it is clear that this poses a serious obstruction to obtaining accurate solutions to the corresponding unique continuation problem.
-
-\begin{comment}
-\begin{figure}[!htbp]
-    \begin{center}with 
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.0.csv};
-                %\addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,best,$k = 3$,best}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{1.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast1.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {1.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.0.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {5.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5, \Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors,
-                legend pos=south west, %yticklabels={,,},
-                ]
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k2_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/travelingWave_1D_jumpingCoefs_k3_WPFalse_contrast2.5.csv};
-
-                %\addplot[gray, dashed, domain=1:4] {22.5*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {12.5*(1/2^(3))^(x-0.9)};
-                %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,best,$k = 3$,best}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{...}
-    %\label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
-
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
                 \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
@@
 before it was $\mathcal{O}(h^2)$ and $\mathcal{O}(h^{3/2})$..., right plot looks fine, also $c_1 = 2.0$ for the right plot...}}
+        \label{fig:1D:complicatedSol}
     \end{center}
-    \label{fig:1D-complicated-sol}
   \end{figure}
@@
 \subsection{Example in two space dimensions}
-\noindent In this section, we present a numerical example in two space dimensions.
-We consider the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ partitioned into subdomains $\Omega_1 = (0.0,0.5)^2$ and $\Omega_2 = (0.5,1.0)^2$.
-As a simple test case, we can extend the one-dimensional exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) = u(x;t)$, i.e.
-we consider the original solution in the $x$-direction.
-We define the data domain $\omega = \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
+To conclude the numerical examples, we consider another example in two space dimensions.
+We partition the unit-square $\Omega \coloneqq [0,1]^2 \subset \mathbb{R}^2$ into subdomains $\Omega_1 = \{ (x,y) \in \Omega: x < 0.5 \}$ and $\Omega_2 = \{ (x,y) \in \Omega: x > 0.5 \}$, and
+extend the exact solution defined in \eqref{eq:1D:exact:simple} to the two-dimensional case by setting $u(x,y;t) \coloneqq u(x;t)$.
+
+We define the data domain $\omega \coloneqq \Omega \setminus [0.25,0.75]^2$ and note that $\omega$ fulfills the GCC.
 To ensure that the data domain and the interface $\Gamma$ are meshed exactly, we consider a quadrilateral mesh with $2^{L+1}$, $L \in \{1,2,3,4\}$, elements in each direction.
 We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
-As before, we fix $c_2 = 1$ and consider different values for $c_1$.
-The results of the experiment are presented in Fig.
-\ref{fig:2DjumpCoefs}.
+As before, we fix the wavespeed $c_2 = 1$ and consider different values for $c_1$ to control the contrast.
+
+The results of the experiment are presented in \cref{fig:2DjumpCoefs}. 
 For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$.
-Similar as already observed in the one-dimensional case the right plot in Fig.~\ref{fig:2DjumpCoefs} shows that these errors are more sensitive to increasing $c_1$ than the corresponding best approximation errors.
+Similar as already observed in the one-dimensional case the right plot in \cref{fig:2DjumpCoefs} shows that these errors are more sensitive to increasing $c_1$ than the corresponding best approximation errors.
 In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$ which renders it very demanding to maintain a reasonable accuracy as the contrast increases.
-
-\begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                %\addplot+[discard if not={contrast}{1.0},line width=1.1pt,dotted] table [x=L, y=bestapprox-L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.7*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-
-                \legend{$k=2$,$k=3$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 1.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.5.csv};
-
-                %\addplot+[discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{1.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {3*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.75*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.0$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.0.csv};
-
-                %\addplot+[discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.0},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {6.5*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {2*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.06*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-
-                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$c_1 = 2.5$}, %cycle list name=paulcolors, 
-                legend pos=north east, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c2.5.csv};
-
-                %\addplot+[discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L-infty-L2-error-ut, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_c1.0.csv};
-                \addplot+[discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_k3.csv};
-
-                \addplot[gray, dashed, domain=1:4] {11*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {6*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(3))^(x-0.9)};
-                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-                \legend{$k=2$,$k = 3$}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for polynomial degrees $k \in \{2,3\}$ and increasing values of $c_1 \in \{1.0,1.5,2.0,2.5\}$.}
-    \label{fig:2DjumpCoefs}
-  \end{figure}
-\end{comment}
 
@@
 
-\begin{comment}
-  \begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=1 by 1,
-                horizontal sep=1.5cm,
-                vertical sep=2cm,
-                },0m,domain=1:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert u_0 - u_h \vert_{t = 0} \Vert_{H^1(\Omega)} + \Vert \partial_t (u-L_{\Delta t} \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}$}, %cycle list name=paulcolors,
-                legend pos=south east, %ymax = 1e2, %yticklabels={,,},
-                ]
-                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt] table [x=contrast, y=H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/2D_errors_simpleRefsol_noGCC2_Restricted.csv};
-                \addplot+[discard if not={order}{2},discard if not={L}{3},line width=1.1pt,dashed] table [x=contrast, y=bestapprox-H1-dt-at-t-0, col sep=comma] {../../wave_data_assimilation/data/0
-
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-2))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {1*(1/2^(-1))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.003*(1/2^(-2))^(x-0.9)};
-
-                \legend{$k=2$, best, $e^\Lambda$ (rescaled)}
-
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{Filippas lambda... (2D), noGCC}
-  \end{figure}
-\end{comment}
-
 \section{Conclusion}
-
 In this article we have investigated a numerical method to solve the unique continuation problem 
@@
 
-\appendix
-
-\begin{comment}
-\section{More material}
-
-~\jp{Remove Fig.~\ref{fig:GCC-illustration} ?}
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=3]
-        \draw[-stealth] (-0.15,0) -- (1.15,0); 
-        \draw[-stealth] (0,-0.15) -- (0,1.15);
-        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
-        \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.5,0) -- (0.5,1) -- (0,1) -- cycle;
-        \draw[-stealth] (0.5,0) -- (1,0.5) -- (0.5,1);
-        \node at (-0.15,1) {\footnotesize $T$}; 
-        \node at (0.75,-0.15) {\footnotesize $\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
-        \node at (1.15,0.5) {\footnotesize $t_0$};
-        \draw (0.7,0) to[bend right=45] (0.65,0.15); 
-        \node at (0.6,0.05) {\footnotesize $\alpha$};
-        \node at (0.25,0.5) {\footnotesize $\omega_T$};
-        \begin{scope}[xshift=2cm]
-            \draw[-stealth] (-0.15,0) -- (1.15,0); 
-            \draw[-stealth] (0,-0.15) -- (0,1.15);
-            \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
-            \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.25,0) -- (0.25,1) -- (0,1) -- cycle;
-            \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,0) -- (1,0) -- (1,1) -- (0.75,1) -- cycle;
-            \draw[-stealth] (0.25,0) -- (0.75,0.5);
-            \node at (-0.15,1) {\footnotesize $T$}; 
-            \node at (0.5,-0.15) {\footnotesize $2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
-            \node at (0.67,0.5) {\footnotesize $t_0$};
-            \draw (0.45,0) to[bend right=45] (0.4,0.15); 
-            \node at (0.35,0.05) {\footnotesize $\alpha$};
-            \node at (0.125,0.5) {\footnotesize $\omega_T$};
-            \node at (0.875,0.5) {\footnotesize $\omega_T$};
-        \end{scope}
-    \end{tikzpicture}
-    \caption{(\textbf{Can be deleted lateron, only for our own understanding:}) Illustration of the GCC and condition \eqref{eq:Tcondition} in one space dimension.
-The geometrical setup where the data is given only in one half of the domain is the worst case, because the ray can be reflected at the boundary.
-We still calculate that $1 = \tan(\alpha) = t_0 / \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, i.e.
-$T > 2 t_0 = 2\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$ is required for the GCC.
-Note we can also assume that $c_1 = c_2 = 1$, because the metric is rescaled wrt to the wavespeed.
-Could probably show that the GCC and the condition on $T$ are in fact equivalent in one dimension.}
-\label{fig:GCC-illustration}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-\subsubsection{Snell's law... }
-\noindent Finally, we consider a more elaborate example. We consider the initial conditions 
-\begin{align*}
-    u_0 (x,y) &= \frac{1}{100} \exp(-(80(x+y-t-1/5))^2) \vert_{t=0}, \\
-    u_1(x,y) &= 128(x+y-t-1/5) \exp(-(80(x+y-t-1/5))^2) \vert_{t = 0}
-\end{align*}
-and compute a reference solution $u_{\text{ref}}$ numerically. We consider the data domain $\omega_T$ as described in Fig. \ref{fig:2d:SnellsLaw} and presribe $u = \Pi_h u_{\text{ref}}$ on $\omega_T$.
-
-\newcommand{\hpoint}{0.85}
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=4]
-        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
-        \draw[fill=gray!40,draw=none,opacity=0.5] (0,1) -- (0,\hpoint) -- (0.65,\hpoint) -- (0.65,1-\hpoint) -- (0,1-\hpoint) -- (0,0) -- (1,0) -- (1,1) -- cycle;
-        \node[draw=none] at (0.85,0.25) {\color{gray} $\omega$};
-        \draw[stealth-stealth] (0.7,1-\hpoint) -- (0.7,\hpoint); 
-        \node[draw=none] at (0.8,0.5) {\color{black} $h_\omega$};
-        \draw[dashed] (0.5,0.5) -- (0,0.5); 
-        \draw[-stealth,red,very thick] (0,0.2) -- (0.49,0.5) -- (0,0.8);
-        \draw[black,very thick] (0.5,0) -- (0.5,1); 
-        \node[draw=none] at (0.55,0.5) {\color{black} $\Gamma$};
-        \draw (0.25,0.5) to [bend right=45] (0.25,0.35);
-        \node[draw=none] at (0.28,0.44) {\color{black} $\theta_c$};
-        \node[draw=none] at (0.5,1.1) {GCC not fulfilled};
-        \begin{scope}[xshift=1.25cm]
-            \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
-            \draw[fill=gray!40,draw=none,opacity=0.5] (0,1) -- (0,0.85*\hpoint) -- (0.65,0.85*\hpoint) -- (0.65,1-0.85*\hpoint) -- (0,1-0.85*\hpoint) -- (0,0) -- (1,0) -- (1,1) -- cycle;
-            \draw[stealth-stealth] (0.7,1-0.85*\hpoint) -- (0.7,0.85*\hpoint); 
-            \node[draw=none] at (0.8,0.5) {\color{black} $h_\omega$};
-            \node[draw=none] at (0.85,0.25) {\color{gray} $\omega$};
-            \draw[dashed] (0.5,0.5) -- (0,0.5); 
-            \draw[-stealth,red,very thick] (0,0.2) -- (0.49,0.5) -- (0,0.8);
-            \draw[black,very thick] (0.5,0) -- (0.5,1); 
-            \node[draw=none] at (0.55,0.5) {\color{black} $\Gamma$};
-            \draw (0.25,0.5) to [bend right=45] (0.25,0.35);
-            \node[draw=none] at (0.28,0.44) {\color{black} $\theta_c$};
-            \node[draw=none] at (0.5,1.1) {GCC fulfilled};
-        \end{scope}
-    \end{tikzpicture}
-    \caption{According to Snell's law, rays hitting the interface with an angle greater than the critical angle $\theta_c := \arcsin(\frac{c_1}{c_2})$ are reflected back into the domain $\Omega_1$.
-To ensure that the GCC is fulfilled, the height $h_{\omega}$ has to chosen smaller than $\tan(\theta_c)$.}
-    \label{fig:2d:SnellsLaw}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-\section*{Outtakes}
-{\color{gray}
-\begin{lem}[Continuity of $A$]
-    \begin{enumerate}
-        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ and $\mathbf{Y} \in ...$ we have that 
-        \begin{equation}
-            A[(\Uh,\mathbf{Y})] \le C ... 
-        \end{equation}
-        \item For $\mathbf{U} \vert_{Q^n} \in ...$ for all $n = 0, \dots, N-1$ and $\Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ we have that
-        \begin{equation}
-            A[(\mathbf{U},\Yh)] \le C ...
-        \end{equation}
-    \end{enumerate}
-\end{lem}
-
-We recall the following interpolation result from \cite{BP24}:
-
-\begin{lem}[Lem. 2.4 of \cite{BP24}]\label{lem:interpolationOperator}
-    Assume that $\Delta t = Ch$ and set $(s,m) = (\min\{k,q\}, \max\{k,q\}+3)$.
-    Then, there exists an interpolation operator $\Pi_h$ into $\FullyDiscrSpace{k}{q}$ such that for $n = 0, \dots, N-1$ the following estimates hold
-    \begin{enumerate}
-        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert \nabla(u - \Pi_h u) \Vert_{L^2(Q^n)} \} \le C \Vert u \Vert_{H^1(Q)}$. 
-        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert u - \Pi_h u \Vert_{H^1(Q^n)} \} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}$.
-        \item $\left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert u - \Pi_h u \Vert^2_{H^2(K)} \ \dT \right)^{1/2} \le C h^{s} \Vert u \Vert_{H^{m}(Q)}$ for $u \in H^m(Q_n) \cap C^0(I_n,H^2(\Omega))$.
-    \end{enumerate}
-\end{lem}
-
-\begin{lem}[Similar to Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
-    In addition to the assumptions of Lem.
-\ref{lem:interpolationOperator}, let $u \in H^m(Q)$ solve \eqref{eq:waveEquation} and set $\mathbf{U} = (u,\partial_t u)$.
-Then, the following estimates hold true.
-    \begin{enumerate}
-        \item For $u \in H^m(Q) \cap C^0([0,2],H^2(\Omega))$ we have that 
-        \begin{equation}
-            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{S_h} = \vert \mathbf{\Pi}_h \mathbf{U} - \mathbf{U} \vert_{S_h} \le C h^{s} \Vert u \Vert_{H^m(Q)}.
-        \end{equation}
-        \item For $u \in H^m(Q)$ we have that
-        \begin{equation}
-            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{\uparrow \downarrow} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}.
-        \end{equation}
-        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ it holds that 
-        \begin{equation}
-            \Vert u - \ul_1 \Vert_{\Sigma} + \Vert u - \ul_1 \Vert_{\omega_T} \le C \left( h^{s+1/2} \Vert u \Vert_{H^m(Q)} + \tnorm{(\Uh - \mathbf{\Pi}_h \Uh,0)} \right).
-        \end{equation}
-        \item For $\mathbf{Y} = (y_1,y_2) \in [H^1(Q)]^2$, we have that
-        \begin{equation}
-            \Vert \mathbf{\Pi}^\ast_h \mathbf{Y} \Vert_{S_h^\ast} \le C \left( \Vert y_1 \Vert_{H^1(Q)} + \Vert y_2 \Vert_{H^2(Q)} \right). 
-        \end{equation}
-    \end{enumerate}
-\end{lem}
-
-\begin{proof}
-    has to be adapted to the current setting.
-\end{proof}}
-
-{\color{red} do we need this one? 
-\begin{lem}\label{eq:lemma:stability}
-    Let $u$ be a solution of \eqref{eq:waveEquation} and $\mathbf{U} = (u,\partial_t u)$. For any $(\Wh,\Yh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ it holds that
-    \begin{equation*}
-        (u - \Pi_h u, \wl_1)_{\omega_T} -  S_h(\mathbf{\Pi}_h \mathbf{U},\Wh) - A[\mathbf{\Pi}_h \mathbf{U},\Yh] - \Sud(\mathbf{\Pi}_h \mathbf{U}, \Wh) \le C h^s \Vert u \Vert_{H^m(Q)} \tnorm{(\Wh,\Yh)}.
-    \end{equation*}
-\end{lem}
-
-\begin{proof}
-    We follow the proof of \cite[Lem. 2.6]{BP24}. 
-\end{proof}}
-\end{comment}
-
-%\bibliographystyle{alpha}
 \bibliography{references}

### 2025-06-25 tex/main.tex
Reproduction + rewriting

@@
 
-\subsubsection{Simple Example}\label{sec:numex:1D:simple}
+\subsubsection{A first example}\label{sec:numex:1D:simple}
  We define two subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\bar{\Omega} = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ in $\Omega_2$.
@@
 
-In one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC. Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric. Then, we set
+In one space dimension, the requirement \eqref{eq:Tcondition} that $T > 2 \sup_{x \in \Omega} \operatorname{dist}_{c}(x,\omega_T)$ already implies the GCC.
+Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the standard Euclidean metric.
+As in \cite{Filippas22}, we define a metric scaled with the discontinuous wave speed through
 \begin{equation}
@@
 Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.
-
-\Cref{fig:jumpCoefs:contrast:2.5} shows that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$ for $T$ large enough, but if $T$ is chosen too small, the order of convergence degrades.
-
-In \cref{fig:jumpCoefs:increasingcontrast} the dependence of the errors for increasing $c_1$ and 
-leaving $c_2 = 1$ fixed (i.e.\ increasing the contrast value) is investigated.
-When $T$ is chosen such that the GCC is barely fulfilled we observe that the errors merely grow polynomially in the contrast, more precisely like $\mathcal{O}(c_1^3)$.
+First, we consider the contrast $c_1 = 2.5$, which means that the GCC is satisfied if $T > 0.35$.
+
+In \Cref{fig:jumpCoefs:contrast:2.5}, we observe that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with optimal order $\mathcal{O}(h^k)$ for $T = 0.5 > 0.35$.
+However, if $T = 0.1 < 0.35$, the order of convergence degrades, while the respective best approximation errors still converge with optimal order.
+This suggests that the GCC seems to imply Lipschitz stability even in the heterogeneous case, and therefore \cref{assum:LipschitzStability} is indeed justified.
+
+To investigate the dependence of the errors on the contrast, we fix the polynomial degree $k = 3$, refinement level $L = 3$, and $c_2 = 1$, and consider increasing values of $c_1 \in \{1.0,1.5,\dots,4.5\}$.
+In \cref{fig:jumpCoefs:increasingcontrast}, we observe that the approximation errors increase polynomially with $\mathcal{O}(c_1^3)$, while the $L^2$-best approximation errors grow quadratically with $\mathcal{O}(c_1^2)$.
 This is an important observation since an exponential growth in the contrast would have rendered the corresponding problems nearly impossible to resolve numerically.
-Still, compared to the best approximation error which grows quadratically we loose a factor of $c_1$.
-This entails that a strong refinement of the discretization is required to maintain the accuracy of the numerical solution as the contrast increases.
+
+However, this also entails that a strong refinement of the discretization is required to maintain the accuracy of the numerical solution as the contrast increases.
 We illustrate this problem in \cref{fig:jumpCoefs:quality}.
-For $c_1 = 2.5$ the exact solution is already well-captured by the numerical solution on refinement level $L=2$.
-However, for $c_1 = 5.5$ this refinement level is clearly insufficient.
+For $c_1 = 2.5$, the exact solution is already well-captured by the numerical solution on refinement level $L=2$.
+However, for higher contrast $c_1 = 5.5$ this refinement level is clearly insufficient.
 
@@
             ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={refinement level $L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             xtick={1,2,3,4}, 
@@
 
-            %L-infty-L2-u (k = 2)
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
             \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
             \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=2.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k2.csv};
-
-            %L-infty-L2-u (k = 3)
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
 
@@
             \addplot[gray, dashed, domain=1:4] {1.45*(1/2^(2))^(x-0.9)};
-            %\node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            %\node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
 
@@
 
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={refinement level $L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             xtick={1,2,3,4},
@@
             \addplot[gray, dotted, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
-            %\node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            %\legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
+
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={refinement level $L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             xtick={1,2,3,4},
@@
 
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
             \addplot[gray, dashed, domain=1:4] {0.09*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
             \addplot[gray, dotted, domain=1:4] {0.05*(1/2^(3))^(x-0.9)};
-            %\addplot[gray,dashed] table {
-            %    1 0.009999968541169805
-            %    2 0.006666645694113204
-            %    3 0.004999984270584902
-            %    4 0.003999987416467922
-            %};
             \addplot[gray,dashdotted] table {
@@
             };
-            %\node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            %\node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
+
             \node [draw=none] at (axis description cs:0.7,0.94) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
 
-            %\legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
+            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={refinement level $L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
             xtick={1,2,3,4},
@@
             \addplot[gray, dashed, domain=1:4] {0.5*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
             \addplot[gray, dotted, domain=1:4] {0.2*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            %\addplot[gray,dashed] table {
-            %    1 0.09999968541169805
-            %    2 0.06666645694113204
-            %    3 0.04999984270584902
-            %    4 0.03999987416467922
-            %};
             \addplot[gray,dashdotted] table {
@@
             };
-            %\node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            %\node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
             \node [draw=none] at (axis description cs:0.7,0.94) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
-            %\legend{$k=2 $,, $k = 3$,}
+
             \end{groupplot}
@@
     \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-best approximation (dashed).
-We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
-The gray dashed lines indicate the observed convergence rates.}
+For final time $T = 0.5 > 0.35$ (top), we observe optimal convergence rates, while for $T = 0.1 < 0.35$ (bottom) the order of convergence degrades.}
     \label{fig:jumpCoefs:contrast:2.5}
@@
 
-            \addplot[gray, dashed, domain=1:4.5] {0.00001*(1/2^(-2))^(x-0.9)};
+            \addplot[gray, dashed, domain=1:4.5] {0.00005*(1/2^(-2))^(x-0.9)};
             \addplot[gray, dashed, domain=1:4.5] {0.0003*(1/2^(-3))^(x-0.9)};
@@
     \end{center}
-    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
-We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
+    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) and the respective $L^2$-best approximation errors (dashed) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$.
+We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ adapted such that it barely fulfills $T > 0.25(1+c_1^{-1})$.}
     \label{fig:jumpCoefs:increasingcontrast}
@@
     \end{center}
-    \caption{At $t = 0.25$, we compare the exact solution \eqref{eq:1D:exact:simple} and approximations with polynomial degree $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
+    \caption{At time $t = 0.25$, we compare the exact solution \eqref{eq:1D:exact:simple} and approximations with polynomial degree $k = 3$ on refinement levels $L \in \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).
 The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
@@
 \subsubsection{Multiple jumps}
- The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$.
+To increase the complexityof the problem, we modify the exact solution \eqref{eq:1D:exact:simple} to allow for multiple jumps in the wave speed $c$.
 For two points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
@@
 \end{align*}
-
-In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
-As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$.
-For contrast $c_1 \in \{ 7.5,11.5 \}$, \cref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$.
+We fix $c_2 = 1.0$ and set $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$,$c_3 = c_1$, and $w_3 = w_1$.
+
+As a first example, we consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$ and choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$.
+Thus, the interval $(p_1,p_2)$ is not contained in the data domain.
+For contrast $c_1 = c_3 \in \{ 7.5,11.5 \}$, \cref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$ on the refinement levels $L \in \{3,4\}$.
+In the case of contrast $c_1 = 11.5$, the refinement level $L = 3$ does not seem to be sufficient to resolve the solution accurately, but for $L = 4$ the solution is captured reasonably well, even though we do not prescribe data in the interval $(p_1,p_2)$.
 
@@
     \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ of \eqref{eq:1D:exact:simpleMult} at $t = 0.25$ with contrast $c_1 = 7.5$ (left) and $c_1 = 11.5$ (right).
-We compare the approximations on the refinement levels $L = 3$ and $L = 4$, where we set $\Delta t = 1/32$ for both cases.}
+We compare the approximations on the refinement levels $L = 3$ and $L = 4$, and set $\Delta t = 1/32$ for both cases.}
     \label{fig:jumpCoefs:multipleJumps}
@@
 
- As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The GCC is fulfilled if 
+As a second example, we consider the case where the data is only given in one half of the interval, i.e. $\omega = [0,0.3]$. The requirement \eqref{eq:Tcondition} and thus the GCC is fulfilled if 
 \begin{equation}
@@
 \end{equation}
-\Cref{fig:jumpCoefs:multipleJumps:noGCC} shows once more that the approximate solution matches the exact solution well if the GCC is fulfilled, but fails to do so if the GCC is not fulfilled.
+We consider $c_1 \in \{ 2.5, 7.5\}$, for which the requirement $T > \{ 0.89,0.65 \}$ ensures the GCC.
+\Cref{fig:jumpCoefs:multipleJumps:noGCC} compares the results for polynomial degree $k = 3$ on the refinement level $L = 4$ with a fixed time step $\Delta t = 1/32$, for two final times $T = 0.5$ and $T = 1.0$.
+For both contrasts, the approximate solution matches the exact solution well if the GCC is fulfilled ($T = 1.0$), but shows significant deviations when it is not ($T = 0.5$).
+The deviation is more extreme for contrast $c_1 = 2.5$, where the gap between the considered time $T = 0.5$ and the threshold $T > 0.89$ is larger.
 
@@
                 legend style={legend columns=3, draw=none,nodes={scale=.8}},legend to name=named,, %yticklabels={,,},
+                ymin=-2,ymax=1,
                 ]
@@
 
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_uniform_noGCC.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/multipleJumps_approx_plot_data_WPFalse_contrast2.5_k3_dataLeft_T0.5.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast2.5.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast2.5.csv};
 
@@
                 \node [draw=none] at (axis description cs:0.2,0.125) {\color{gray} $\omega$};
-                \legend{exact,$T=1.0$,$T=0.5$}
+                \legend{exact,$T=0.5$,$T=1.0$}
                 \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs $u_h$ ($c_1 = 7.5$)}, %cycle list name=paulcolors, 
@@
 
-                \addplot+[line width=3.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast7.5Test.csv};
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast7.5Test.csv};
 
@@
     \end{center}
-    \caption{Exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution with $k = 3$ at $t = 0.5$ with $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right) and $c_2 = 1.0$.
-We compare the approximations on refinement level $L = 4$ with $T = 1.0$ and $T = 0.5$ while keeping the time step fixed at $\Delta t = 1/32$.}
+    \caption{For fixed time step $\Delta t = 1/32$, refinement level $L = 4$, and polynomial degree $k = 3$, we compare the exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution computed with $T = 1.0$ and $T = 0.5$ at time $t = 0.5$.
+We set $c_2 = 1.0$ and consider the cases $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right).}
     \label{fig:jumpCoefs:multipleJumps:noGCC}
@@
 
-\subsubsection{2nd one dimensional example}
-
+\subsubsection{A more complex example}
 Let us consider a final one-dimensional example to illustrate the high resolution 
 required to simulate wave propagation in heterogeneous media. 
-We consider the same geometrical setup as in \cref{sec:numex:1D:simple} with a more intricate reference solution considered in \cite{BDE22,MEMM19}.
+We consider the same geometrical setup as in \cref{sec:numex:1D:simple}, but choose a more intricate reference solution considered in \cite{BDE22,MEMM19}.
 With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, we consider the exact solution
@@
 Due to the jump in the wave speed, a part of the wave is reflected from the interface into the domain $\Omega_1$, while the other part passes through the interface into $\Omega_2$ and oscillates stronger.
+
+\todo[inline]{@JP: let's think about the interpretation of this example...}
 
@@
                 \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
+                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3, c_1 = 2.0$)}, %cycle list name=paulcolors, 
                 legend pos=north west, %yticklabels={,,},
@@
 We consider the final time $T = 0.75$  and set the time step size to $\Delta t = (1/2)^{L+1}$.
-As before, we fix the wavespeed $c_2 = 1$ and consider different values for $c_1$ to control the contrast.
+As before, we fix the wave speed $c_2 = 1$ and consider different values for $c_1$ to control the contrast.
 
 The results of the experiment are presented in \cref{fig:2DjumpCoefs}. 
-For $c_1 = 2.5$, $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ converge quasi-optimally with order $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$.
-Similar as already observed in the one-dimensional case the right plot in \cref{fig:2DjumpCoefs} shows that these errors are more sensitive to increasing $c_1$ than the corresponding best approximation errors.
-In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$ which renders it very demanding to maintain a reasonable accuracy as the contrast increases.
+With contrast $c_1 = 2.5$, we observe quasi-optimal convergence with order  $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ for the errors $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$.
+Similar as already observed in the one-dimensional case in \cref{fig:jumpCoefs:increasingcontrast}, we observe that these errors are more sensitive to increasing contrast $c_1$ than the corresponding best approximation errors.
+In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$, which renders it very demanding to maintain a reasonable accuracy as the contrast increases.
 
@@
     \end{center}
-    \caption{Left: Convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) for $c_1 = 2.5$.
-Right: Ratio between these errors and the $L^2$-bestapproximation error for increasing $c_1$.}
+    \caption{On the left: We observe quasi-optimal convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) with contrast $c_1 = 2.5$ and polynomial degrees $k \in \{2,3\}$.
+On the right: We consider the ratio between these errors and the $L^2$-bestapproximation error for increasing contrast $c_1$.}
     \label{fig:2DjumpCoefs}
@@
 \section{Conclusion}
-In this article we have investigated a numerical method to solve the unique continuation problem 
-for the wave equation in the presence of a jump discontinuity in the wavespeed.
-The main conclusion from our numerical experiments is that obtaining accurate numerical solutions in the presence of material interfaces involving large contrasts is computationally demanding.
-Even though the problem appears to be Lipschitz stable if the geometric control condition is fulfilled, the resolution required to capture the complex behavior of the solution is a limiting factor in numerical simulations.
-Note here that unique continuation problems are globally coupled in space and time which poses an obstacle for their efficient numerical solution.
+In this article, we investigated a numerical method for solving the variational data assimilation problem for the wave equation with discontinuous wave speed.
+Our numerical experiments lead to two main conclusions.
+First, obtaining accurate numerical solutions in the presence of material interfaces involving large contrasts is computationally demanding, and the resolution required to capture the complex behavior of the solution is a limiting factor in numerical simulations.
+This challenge is amplified by the fact that unique continuation problems are globally coupled in space and time.
+Second, even in the case of a discontinuous wave speed, the geometric control condition seems to ensure Lipschitz stability, allowing the design of accurate and reliable numerical methods.
 

### 2025-06-25 codeNew/ApproxPlotsMultipleJumpsMultT.py

@@ -1,0 +1,383 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+from meshes import get_1Dmesh
+import sys
+
+
+if len(sys.argv) > 2:
+    finalTime = float(sys.argv[1])
+    contrast = float(sys.argv[2])
+    print("Solving with final time T = {} and contrast {}".format(finalTime,contrast))
+else: 
+    raise ValueError('Please provide contrast')
+
+ref_lvl = 4
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False #what does this do??
+
+GCC = False #only controls wether data is set only on the lhs (False) or on both sides (True)
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,c3,pos,pos2):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    pre_upper_coords = x[0] > pos 
[…]

### 2025-06-25 codeNew/plot_exact.py

@@ -10,7 +10,8 @@ rfs = ['SJ','MJ']
 if len(sys.argv) > 2 and sys.argv[1] in rfs: 
     rf = sys.argv[1]
     contrast = float(sys.argv[2])
-    print("Generating data for the reference solution = {} and contrast {}".format(rf,contrast))
+    time =  float(sys.argv[3])
+    print("Generating data for the reference solution = {} and contrast {} at time {}".format(rf,contrast,time))
 else: 
     raise ValueError('Please provide one of the following options for the reference solution {} and a contrast'.format(rfs))
 
@@ -75,15 +76,15 @@ def get_params(rf,contrast):
 
 def sol(t,xu,contrast):
     w1,c1,c2,pos = get_params(rf,contrast)
-    return singleJump_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=False) if rf == 'SJ' else multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3 if contrast == 7.5 else 4,dt=False)
+    return singleJump_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=False) if rf == 'SJ' else multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3 if contrast == 7.5 else 1 if contrast == 2.5 else 4,dt=False)
 
 def dt_sol(t,xu,contrast):
     w1,c1,c2,pos = get_params(rf,contrast)
-    return singleJump_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=True) if rf == 'SJ' else multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3 if contrast == 7.5 else 4,dt=True)
+    return singleJump_refsol(xu=xu,t=t,c1=c1,c2=c2,w1=w1,pos=pos,dt=True) if rf == 'SJ' else multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3 if contrast == 7.5 else 1 if contrast == 2.5 else 4,dt=True)
 
 
 
-def plot(t,save_data=False):
+def plot(t,save_data=False,plot=False):
     w1,c1,c2,pos = get_params(rf,contrast)
     x_pts = np.linspace(0.0,1.0,num=500).tolist()
     y_pts = np.zeros(len(x_pts))
@@ -96,8 +97,8 @@ def plot(t,save_data=False):
[…]

### 2025-06-25 codeNew/reproduce.sh

@@ -7,9 +7,11 @@ python3 MultContrast.py fix
 python3 MultContrast.py adap
 
 #Generate data for exact solution 
-python3 plot_exact.py SJ 2.5
-python3 plot_exact.py SJ 5.5
-python3 plot_exact.py MJ 7.5
+python3 plot_exact.py SJ 2.5 0.25
+python3 plot_exact.py SJ 5.5 0.25
+python3 plot_exact.py MJ 2.5 0.5
+python3 plot_exact.py MJ 7.5 0.25
+python3 plot_exact.py MJ 7.5 0.5
 python3 plot_exact.py MJ 11.5
 
 #For plots with single jump
@@ -21,3 +23,7 @@ python3 ApproxPlotsMultipleJumps.py 3 7.5
 python3 ApproxPlotsMultipleJumps.py 4 7.5
 python3 ApproxPlotsMultipleJumps.py 3 11.5
 python3 ApproxPlotsMultipleJumps.py 4 11.5
+python3 ApproxPlotsMultipleJumpsMultT.py 0.5 2.5
+python3 ApproxPlotsMultipleJumpsMultT.py 1.0 2.5
+python3 ApproxPlotsMultipleJumpsMultT.py 0.5 7.5
+python3 ApproxPlotsMultipleJumpsMultT.py 1.0 7.5

### 2025-06-27 tex/main.tex
Minor

@@
 
+%\usetikzlibrary{external}
+%\tikzexternalize[prefix=figures/]
+
 %find colors at https://colorbrewer2.org/#type=qualitative&scheme=Set1&n=5
@@
 
-\title{A numerical study of variational data assimilation for the wave equation in heterogeneous media}
+\title{Variational data assimilation for the wave equation in heterogeneous media}
+\subtitle{Numerical investigation of stability}
 
@@
 \todo[inline]{@JP: please update affiliation}
-\todo[inline]{@JP: Let's discuss the title again, I feel like we should include 'stability' somewhere, because it's our main objective...}
+
 We consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
@@
 
-\todo[inline]{@JP: I made some minor changes to the introduction... Here, I felt that we should manage the reader's expectation a bit more and stress that we do not focus on a complete analysis. }
-
 In this article, we consider a discontinuous-in-time finite element method to solve the data assimilation problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} in the heterogeneous case.
@@
 If the corresponding data assimilation problems were indeed subject to the poor logarithmic stability property ensured by \eqref{eq:FilippasEstimateLog}, this would pose an enormous challenge for the design of accurate and reliable numerical methods.
-
-\vspace*{1cm}
-\noindent \textbf{Struture of the article.} In \cref{sec:discretization}, we introduce the method used to discretize \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch}.
 
@@
 \begin{align*}
-    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c^2 \nabla \ul_1}, \jump{c^2 \nabla \wl_1})_F \ \dT, \\
+    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c^2 \nabla \ul_1}  \cdot \mathbf{n}, \jump{c^2 \nabla \wl_1}  \cdot \mathbf{n})_F \ \dT, \\
     G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c^2 \nabla \ul_1),\dt \wl_2 -\div( c^2 \nabla \wl_1))_K \ \dT, \\
     I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \qquad 
-    R(\Uh,\Wh) := \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
+    R(\Uh,\Wh) := \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n},
 \end{align*}
-~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only.
-Indeed, it follows from the first condition in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$.
-So stabbilizing the full gradient is not consistent, which becomes an issue in \cref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.
-}
+where $\jump{c^2 \nabla \cdot} \cdot \mathbf{n}$  denotes the jump of the normal derivative over interior facets.
 $J(\cdot,\cdot)$ is a continuous interior penalty term in space, $G(\cdot,\cdot)$ is a Galerkin least squares term enforcing the PDE locally on each element, $I_0(\cdot,\cdot)$ enforces that $\ul_2 = \dt \ul_1$, and $R(\cdot,\cdot)$ ensures boundary stability.
@@
 If the problem is Lipschitz stable, for instance in the homogeneous case (see \cref{thm:Lipschitz}), we can prove convergence in a physically relevant norm.
-To deal with the discontinuity in time of the discrete solution, a suitable lifting operator$L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ that ensures that $L_{\Delta t} \ul_1 \in H^1(Q)$ has been introduced in \cite[Sec.
+To deal with the discontinuity in time of the discrete solution, a suitable lifting operator $L_{\Delta t} : \FullyDiscrSpace{k}{q} \rightarrow C^0(0,T;V_h^k)$ that ensures that $L_{\Delta t} \ul_1 \in H^1(Q)$ has been introduced in \cite[Sec.
 4]{BP24}.
@@
 \end{equation}
-~\jp{I am confused by this formula. What is the argument of the characteristic functions $\mathbbm{1}_{\Omega_1}$? Also, a metric is required to be symmetric, so $d_c(x,y) = d_c(y,x) $ 
-needs to be ensured?
-}
 Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.
@@
 \subsubsection{Multiple jumps}
-To increase the complexityof the problem, we modify the exact solution \eqref{eq:1D:exact:simple} to allow for multiple jumps in the wave speed $c$.
+To increase the complexity of the problem, we modify the exact solution \eqref{eq:1D:exact:simple} to allow for multiple jumps in the wave speed $c$.
 For two points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t.
@@
 Thus, the interval $(p_1,p_2)$ is not contained in the data domain.
+
 For contrast $c_1 = c_3 \in \{ 7.5,11.5 \}$, \cref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ for fixed time step $\Delta t = 1/32$ on the refinement levels $L \in \{3,4\}$.
@@
 
+\begin{comment}
 \subsubsection{A more complex example}
@@
                 group style={%
-                group size=2 by 1,
+                group size=1 by 1,
                 horizontal sep=1.5cm,
@@
             ]    
-                \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$L^2$-best approximation ($k = 2$)}, %cycle list name=paulcolors, 
-                legend pos=south west, 
-                %yticklabels={,,}, 
-                xlabel={$L$}, 
-		%ylabel={$\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$},
-                ]
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{1.5},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-                %\addplot+[discard if not={order}{2},discard if not={contrast}{2.0},line width=1.1pt,dashed] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/weakDisc_noRestrict_1D_jumpingCoefs_k2.csv};
-
-                \addplot[gray, dashed, domain=1:4] {0.0005*(1/2^(2))^(x-0.9)};
-                \addplot[gray, dotted, domain=1:4] {0.0008*(1/2^(3))^(x-0.9)};
-                \addplot[gray, dashed, domain=1:4] {0.0025*(1/2^(3/2))^(x-0.9)};
-                \addplot[gray, dotted, domain=1:4] {0.0008*(1/2^(5/2))^(x-0.9)};
-
-                \node [draw=none] at (axis description cs:0.50,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-                \node [draw=none] at (axis description cs:0.90,0.60) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3/2})$};
-
-                \legend{$c_1 = 1.0$,$c_1 = 1.5$,$c_1 = 2.0$}
                 \nextgroupplot[width=9cm,height=7cm,domain=0:4,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$\dt u$ vs. $\dt u_h$ ($k = 3, c_1 = 2.0$)}, %cycle list name=paulcolors, 
@@
                 \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
-                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                %\addplot+[discard if not={L}{3},line width=1.1pt,mark=none,dotted] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-                %\addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/weakDisc_higherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
 
@@
                 \node [draw=none] at (axis description cs:0.83,0.125) {\color{gray} $\omega$};
-
-                %\addplot[gray, dashed, domain=1:4] {0.01*(1/2^(2))^(x-0.9)};
-                %\addplot[gray, dashed, domain=1:4] {0.025*(1/2^(3/2))^(x-0.9)};
-
-                %L = 2
-                %\draw[color=black,thick] (0.75,-0.7) -- (1,-0.7);
-                %\draw[color=black,thick] (0.75,-0.68) -- (0.75,-0.72);
-                %\draw[color=black,thick] (0.875,-0.68) -- (0.875,-0.72);
-                %\draw[color=black,thick] (1.0,-0.68) -- (1.0,-0.72);
-
-                %L = 3
-                %\draw[color=black,thick] (0.75,-0.6) -- (1,-0.6);
-                %\draw[color=black,thick] (0.75,-0.58) -- (0.75,-0.62);
-                %\draw[color=black,thick] (0.8125,-0.58) -- (0.8125,-0.62);
-                %\draw[color=black,thick] (0.875,-0.58) -- (0.875,-0.62);
-                %\draw[color=black,thick] (0.9375,-0.58) -- (0.9375,-0.62);
-                %\draw[color=black,thick] (1.0,-0.58) -- (1.0,-0.62);
-                %\node[draw=none] at (0.67,-0.6) {\color{black} \footnotesize $L = 3$};
 
@@
   \end{figure}
+
+\end{comment}
 

### 2025-06-27 tex/main.tex
update refs to homogeneous paper and minors

@@
 
-\affil[2]{\orgdiv{MAKUTU}, \orgname{Inria}, \orgaddress{\street{...}, \city{...}, \postcode{...}, \country{France}}}
+ \affil[2]{\orgdiv{Inria Project-Team Makutu}, \orgname{Université de Pau et des Pays de l’Adour}, \orgaddress{\street{Avenue de l'Université - BP 1155}, \city{Pau}, \postcode{64013}, \country{France}}}
 
@@
 \section{Introduction}
-\todo[inline]{@JP: please update affiliation}
 
@@
 Furthermore, by definition of the stabilization terms $S_h$ and $S_h^{\ast}$, we have that $\Zh = 0$, $\ul_1 \vert_{\Sigma} = 0$, $\ul_1 \vert_{\omega_T} = 0$ and $\dt \ul_1 = \ul_2$.
-Similar to \cite[Lem.
-2.1]{BP24}, partial integration yields
+Similar to \cite[Lemma 2]{BP24}, partial integration yields
     \begin{align*}
@@
 \begin{proof}
-    The proof follows with the same arguments as the proof of \cite[Theorem 10]{BP24}.
+    The proof follows with the same arguments as the proof of \cite[Theorem 14]{BP24}.
 \end{proof}
@@
 \begin{rmk}[Homogenous media]\label{rem:homMedia}
-    If $c_i = 1$ for $i = 1,2$, \cref{assum:LipschitzStability} holds (see \cref{thm:Lipschitz}), and we recover the result from \cite[Theorem 10]{BP24}.
+    If $c_i = 1$ for $i = 1,2$, \cref{assum:LipschitzStability} holds (see \cref{thm:Lipschitz}), and we recover the result from \cite[Theorem 14]{BP24}.
 \end{rmk}
@@
     \end{enumerate}
-    Then, we can use the arguments of \cite[Theorem 10]{BP24} to show that 
+    Then, we can use the arguments of \cite[Theorem 14]{BP24} to show that 
     \begin{equation*}

### 2025-06-28 tex/main.tex
minor fixes

@@
 While the condition \eqref{eq:Tcondition} guarantees unique solvability, the stability of problem \eqref{eq:waveEquation}-\eqref{eq:IF-conditions}+\eqref{eq:dataMatch} can be poor.
-However, as shown \cite[Thm.
+However, as shown in \cite[Thm.
 5.19]{Filippas22}, assumption \eqref{eq:Tcondition} grants the following stability result holds.
@@
 \end{align*}
-where $\jump{c^2 \nabla \cdot} \cdot \mathbf{n}$  denotes the jump of the normal derivative over interior facets.
+where $\jump{c^2 \nabla \cdot} \cdot \mathbf{n}$  denotes the jump of the normal derivative over interior facets $\mathcal{F}_i$.
 $J(\cdot,\cdot)$ is a continuous interior penalty term in space, $G(\cdot,\cdot)$ is a Galerkin least squares term enforcing the PDE locally on each element, $I_0(\cdot,\cdot)$ enforces that $\ul_2 = \dt \ul_1$, and $R(\cdot,\cdot)$ ensures boundary stability.
@@
 \begin{align*}
-    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c^2 \jump{\nabla \ul_1^n},c^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
-    \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
+    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 1}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c^2 \jump{\nabla \ul_1^n},c^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
+    \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 1}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
 \end{align*}
@@
 In \cref{sec:analysis:approx}, we show that the error between the first component $\ul_1$ of the discrete solution and the continuous solution $u$ is bounded by the best approximation error in these norms.
-Finally, we argue that \cref{assum:LipschitzStability} allows recovering convergence rates in a physically relevant norm.
+Finally, we argue that \cref{assum:LipschitzStability} allows to recover convergence rates in a physically relevant norm.
 
@@
     \end{align*}
-where $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$  denotes the jump of the normal derivative over interior facets.
 It follows by definition of the stabilizers and $\tnorm{(\Uh,\Zh)} = 0$ that $\Vert \wop \ul_1 \Vert_{H^{-1}(Q)} = 0$ and that the interface conditions \eqref{eq:IF-conditions} are fulfilled.
@@
 
-\begin{cor}\label{cor:tnormConvRates}
-    Under the assumption of \cref{thm:bestapprox}, we have that
+\begin{cor}\label{cor:tnormConvRates }
+    Under the assumption of \cref{thm:bestapprox} and assuming additionally that $\Delta t = C' h$ for some $C'>0$ we have that
     \begin{equation*}
-        \tnorm{(\mathbf{U} - \Uh,\Zh)} \le C h^s \Vert u \Vert_{H^m(Q)},
+	    \tnorm{(\mathbf{U} - \Uh,\Zh)} \le C h^s \Vert u \Vert_{H^{s+2}(Q)},
     \end{equation*}
-    where $(s,m) := (\min\{ k,q \}, \max\{k,q\}+3)$. 
+    where $s := \min\{ k,q \}$.
 \end{cor}
@@
 where $\tnorm{(\cdot, \cdot)}_{\square_1}$ is defined by \eqref{eq:tnormwop} with $c_i = 1$, $i = 1,2$.
-Thus, we can apply the interpolation results derived in \cite[Lemma 5]{BP24} to obtain the claim.
+Thus, we can apply the interpolation results derived in \cite[Lemma 5 \& 11]{BP24} to obtain the claim.
 \end{proof}
@@
 \begin{thm}\label{thm:convergence}
-    Let \cref{assum:LipschitzStability} be satisfied.
+    Let \cref{assum:LipschitzStability} be satisfied and assume that $\Delta t = C' h$.
 For $u$ being a sufficiently regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ being the solution to \eqref{eq:discreteProblem}, there exists a constant $C>0$ such that
     \begin{equation}
-        \Vert u - L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt (u - L_{\Delta t} \ul_1) \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C h^s \Vert u \Vert_{H^m(Q)}. 
-    \end{equation}
-    In particular, we have that 
-    \begin{equation}
-        \Vert u_0 - \ul_1 \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert u_1 - (\dt \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C h^s \Vert u \Vert_{H^m(Q)}.
+	    \Vert u - L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))} + \Vert \dt (u - L_{\Delta t} \ul_1) \Vert_{L^2(0,T;H^{-1}(\Omega))} \le C h^s \Vert u \Vert_{H^{s+2}(Q)}, 
+    \end{equation}
+    where $s := \min\{ k,q \}$. In particular, we have that 
+    \begin{equation}
+	    \Vert u_0 - \ul_1 \vert_{t = 0} \Vert_{L^2(\Omega)} + \Vert u_1 - (\dt \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C h^s \Vert u \Vert_{H^{s+2}(Q)}.
     \end{equation}
@@
     \begin{equation*}
-        \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1}. 
+	    \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^{s+2}(Q)}^{-1})^{-1}. 
     \end{equation*}

### 2025-06-30 tex/main.tex
minor comment
renaming

@@
 \Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
+~\jp{We should specify the range of $d$. Is there any restriction in Filippas?}
 
@@
 
-%should come from: 1D-jump-convergence_Ex2.py
-\begin{comment}
-\begin{figure}[!htbp]
-    \begin{center}
-        \begin{tikzpicture}[scale=0.72]
-            \begin{groupplot}[%
-                group style={%
-                group size=2 by 2,
-                horizontal sep=1.25cm,
-                vertical sep=2cm,
-                },
-            ymajorgrids=true,
-            grid style=dashed,
-            %ymin = 1e-3, ymax = 0.5e1,
-            ]    
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L-infty-L2-u (k = 2)
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            %\addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=2.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simpleExact_T0.5_multipleContrasts_1D_jumpingCoefs_k2.csv};
-
-            %L-infty-L2-u (k = 3)
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-            %\addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
-
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.3*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.03*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.80,0.55) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \legend{$k=2 $,, $k = 3$,}
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u-L_{\Delta t} \ul_1) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-
-            %L-infty-L2-u (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %L-infty-L2-u (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %\addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.005*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.001*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.009999968541169805
-                2 0.006666645694113204
-                3 0.004999984270584902
-                4 0.003999987416467922
-
-            };
-            \node [draw=none] at (axis description cs:0.75,0.45) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.45,0.35) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
-            \legend{$k=2 $,, $k = 3$,}
-
-            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=,
-            legend pos=south west, %yticklabels={,,},
-            ]
-            %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
-
-            \addplot[gray, dashed, domain=1:4] {0.1*(1/2^(2))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
-            \addplot[gray, dashed, domain=1:4] {0.02*(1/2^(3))^(x-0.9)};
-            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
-            \addplot[gray,dashed] table {
-                1 0.09999968541169805
-                2 0.06666645694113204
-                3 0.04999984270584902
-                4 0.03999987416467922
-
-            };
-            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
-            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
-            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
-            \legend{$k=2 $,, $k = 3$,}
-            \end{groupplot}
-        \end{tikzpicture}
-    \end{center}
-    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed).
-We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom).
-The gray dashed lines indicate the observed convergence rates.}
-    \label{fig:jumpCoefs:contrast:2.5}
-  \end{figure}
-\end{comment}
-
 \begin{figure}[!htbp]
@@
 
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
+
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.5.csv};
 
@@
             %L-infty-L2-u (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
 
             %L-infty-L2-u (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L-infty-L2-error-u, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
 
@@
             %L2-L2-u_t (k = 2)
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
-            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
 
             %L2-L2-u_t (k = 3)
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
-            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../dataNew/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,color=cyan!60!black,mark=diamond*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
+            \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=cyan!60!black,mark=diamond*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simplexExact_singleContrast_T0.1.csv};
 
@@
             ]
-            %\addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simpleExact_1D_jumpingCoefs_k3.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
+
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L2-L2-error-u_t, col sep=comma]{../data/simplexExact_MultContrast_TAdap.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L2-L2-error-u_t, col sep=comma]{../data/simplexExact_MultContrast_TAdap.csv};
 
@@
             ]
-            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
-            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_T0.5.csv};
-
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
-            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../dataNew/simplexExact_MultContrast_TAdap.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simplexExact_MultContrast_T0.5.csv};
+            \addplot+[line width=1.1pt,color=teal,mark=*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simplexExact_MultContrast_T0.5.csv};
+
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*] table [x=contrast, y=L-infty-L2-error-u, col sep=comma]{../data/simplexExact_MultContrast_TAdap.csv};
+            \addplot+[line width=1.1pt,color=orange,mark=diamond*,dashed] table [x=contrast, y=bestapprox-L-infty-L2-error-u, col sep=comma]{../data/simplexExact_MultContrast_TAdap.csv};
 
@@
 
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast2.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{1},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{2},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{3},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotSJ_contrast2.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{2},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{2.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
 
@@
 
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotSJ_contrast5.5_time0.25.csv};
-
-                \addplot+[discard if not={L}{1},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{2},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{3},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
-                %
-                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/simpleExact_ApproxPlot_T0.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotSJ_contrast5.5_time0.25.csv};
+
+                \addplot+[discard if not={L}{1},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{2},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{5.5},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/simpleExact_ApproxPlot_T0.5.csv};
 
@@
 
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.25.csv};
-                %
-                \addplot+[discard if not={L}{3},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast7.5.csv};
-                %
-                \addplot+[discard if not={L}{4},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast7.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotMJ_contrast7.5_time0.25.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast7.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{7.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast7.5.csv};
 
@@
 
-                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast11.5_time0.25.csv};
-                %
-                \addplot+[discard if not={L}{3},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast11.5.csv};
-                %
-                \addplot+[discard if not={L}{4},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast11.5.csv};
+                \addplot[black,line width=3pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotMJ_contrast11.5_time0.25.csv};
+                %
+                \addplot+[discard if not={L}{3},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_T0.5_L3_contrast11.5.csv};
+                %
+                \addplot+[discard if not={L}{4},discard if not={contrast}{11.5},line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_T0.5_L4_contrast11.5.csv};
 
@@
 
-                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast2.5_time0.5.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast2.5.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast2.5.csv};
+                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotMJ_contrast2.5_time0.5.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast2.5.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast2.5.csv};
 
@@
 
-                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../dataNew/plots/exact_plotMJ_contrast7.5_time0.5.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast7.5Test.csv};
-
-                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast7.5.csv};
+                \addplot[black,line width=3.0pt,mark=None] table [x=x, y=y, col sep=comma] {../data/plots/exact_plotMJ_contrast7.5_time0.5.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=blue!75!white] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_CompareT0.5_contrast7.5Test.csv};
+
+                \addplot+[line width=1.0pt,mark=None,color=orange] table [x=x, y=y, col sep=comma] {../data/plots/MultipleJumpsExact_ApproxPlot_CompareT1.0_contrast7.5.csv};
 
@@
 
-                \addplot+[discard if not={contrast}{2.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y_dt, col sep=comma] {../data/exact_plot_data_1D_complexSol.csv};
-
-                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
-
-                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+                \addplot+[discard if not={L}{3},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
+
+                \addplot+[discard if not={L}{4},line width=1.1pt,mark=none] table [x=x, y=y_dt, col sep=comma] {../data/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WPFalse_contrast2.0_k3.csv};
 
@@
                 %
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
-                %
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
-                %
-                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
-                %
-                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,color=orange] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,color=teal] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{2},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={contrast}{2.5},line width=1.1pt,dashed,color=teal] table [x=L, y=L-infty-L2-error-u, col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
 
@@
 
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma]  {../dataNew/2D_errors_simpleRefsolFull.csv};
-                %
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,color=orange] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma]  {../data/2D_errors_simpleRefsolFull.csv};
+                %
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,color=teal] table [x=contrast, y expr= abs(\thisrow{L2-L2-error-u_t}/\thisrow{bestapprox-L2-L2-error-u_t}), col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
 
                 %L-infty-L2-u error
-                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
-                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../dataNew/2D_errors_simpleRefsolFull.csv};
+                \addplot+[discard if not={order}{2},discard if not={L}{4},line width=1.1pt,dashed,color=orange] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
+                \addplot+[discard if not={order}{3},discard if not={L}{4},line width=1.1pt,dashed,color=teal] table [x=contrast, y expr= abs(\thisrow{L-infty-L2-error-u}/\thisrow{bestapprox-L-infty-L2-error-u}), col sep=comma] {../data/2D_errors_simpleRefsolFull.csv};
 

### 2025-06-30 code/ApproxPlots.py

@@ -1,0 +1,350 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False #what does this do??
+
+GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,pos):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    upper_coords = x[0] > pos 
+    lower_coords = np.invert(upper_coords)
+    values[upper_coords] = np.full(sum(upper_coords), c2**2)
+    values[lower_coords] = np.full(sum(lower_coords), c1**2)
+    return values
+
+
+
+
+#Exact solution for discontinuous wave numbers
+def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
+    if not dt:
[…]

### 2025-06-30 code/ApproxPlotsMultipleJumps.py

@@ -1,0 +1,380 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+from meshes import get_1Dmesh
+import sys
+
+
+if len(sys.argv) > 2:
+    ref_lvl = int(sys.argv[1])
+    contrast = float(sys.argv[2])
+    print("Solving on level {} with contrast {}".format(ref_lvl,contrast))
+else: 
+    raise ValueError('Please provide ref level and contrast')
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False #what does this do??
+
+GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,c3,pos,pos2):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    pre_upper_coords = x[0] > pos 
[…]

### 2025-06-30 code/SingleContrast.py

@@ -1,0 +1,114 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+from Solve1D import *
+
+import sys
+
+if len(sys.argv) > 1: 
+    T = float(sys.argv[1])
+    print("Solving with final time T = ", T)
+else: 
+    raise ValueError('Please provide final time T')
+
+
+#Stabilization params
+def set_stabs(c1,c2=1.0): 
+    stabs = {#"data": 1e4,
+                "data": 1e4,
+                #"dual": 1.0,
+                "dual": 1e0,
+                #"primal": 1e-3,
+                "primal": 1e-2,
+                "primal-jump":1e-2, # for simple sol: 1e-2, 
+                #"primal-jump-vel":1.0,
+                "primal-jump-displ-grad":1e-2/max(c1**2,c2**2)**2 # for simple sol: 1e-2
+            } 
+    return stabs
+
+
+
+df = pd.DataFrame()
+
+
+#for single contrast, (for T = 0.5: well-posed=False, GCC = True)
+def ref_lvls(order,T):
+    if T == 0.5: 
+        lvls = [1,2,3,4]
+    else: 
+        lvls = [1,2,3,4] if order < 3 else [1,2,3]
+    return lvls    
+
+orders = [2,3]
+contrasts = [2.5]
+
+#time
+#T = 0.1
+
+make_plots=True
+
+for order in orders:
+    for contrast in contrasts: 
+        print("Solving with time T = ", T)
+        plot_df = pd.DataFrame()
+        for ref_lvl in ref_lvls(order,T):
+            print("Order = {}, ref_lvl = {}, contrast = {}".format(order,ref_lvl,contrast))
+            stabs = set_stabs(c1=contrast)
[…]

### 2025-06-30 code/Solve1D.py

@@ -1,0 +1,288 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False #what does this do??
+
+GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,pos):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    upper_coords = x[0] > pos 
+    lower_coords = np.invert(upper_coords)
+    values[upper_coords] = np.full(sum(upper_coords), c2**2)
+    values[lower_coords] = np.full(sum(lower_coords), c1**2)
+    return values
+
+
+
+
+#Exact solution for discontinuous wave numbers
+def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
+    if not dt:
[…]

### 2025-06-30 code/WeakDiscConv.py

@@ -1,0 +1,332 @@
+## IMPORTS ##
+import numpy as np
+from math import pi,sqrt  
+import ufl
+from dolfinx import fem, io, mesh, plot
+from ufl import ds, dx, grad, inner, dS,jump,div
+from mpi4py import MPI
+from petsc4py import PETSc
+from petsc4py.PETSc import ScalarType
+from dolfinx.mesh import create_unit_interval
+from dolfinx.io import XDMFFile
+import sys
+sys.setrecursionlimit(10**6)
+from GMREs import GMRes
+from space_time import * 
+from precomp_time_int import theta_ref, d_theta_ref 
+import pypardiso
+import time
+import cProfile
+import resource
+import pandas as pd 
+
+#solver_type = "petsc-LU"  
+solver_type = "pypardiso" # 
+#solver_type = "direct" # 
+well_posed = False
+
+GCC = True
+
+## Helping Functions ##
+
+def GetLuSolver(msh,mat):
+    solver = PETSc.KSP().create(msh.comm) 
+    solver.setOperators(mat)
+    solver.setType(PETSc.KSP.Type.PREONLY)
+    solver.getPC().setType(PETSc.PC.Type.LU)
+    #solver.getPC().setFactorSolverType("mumps")
+    return solver
+
+class PySolver:
+    def __init__(self,Asp,psolver):
+        self.Asp = Asp
+        self.solver = psolver
+    def solve(self,b_inp,x_out): 
+        self.solver._check_A(self.Asp)
+        b = self.solver._check_b(self.Asp, b_inp.array)
+        self.solver.set_phase(33)
+        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
+
+
+def csq_preInd(x,c1,c2,pos):
+    values = np.zeros(x.shape[1],dtype=ScalarType)
+    upper_coords = x[0] > pos 
+    lower_coords = np.invert(upper_coords)
+    values[upper_coords] = np.full(sum(upper_coords), c2**2)
+    values[lower_coords] = np.full(sum(lower_coords), c1**2)
+    return values
+
+
+
+
+#Exact solution for discontinuous wave numbers
+def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
+    if not dt:
+        #import pdb; pdb.set_trace()
+        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x[0]-c1*t)-p0(k-x[0]-c1*t)) for k in range(trunc)])
[…]

### 2025-06-30 code/plot_exact.py

@@ -1,0 +1,104 @@
+import numpy as np
+import scipy.sparse as sp
+import matplotlib.pyplot as plt
+import sys 
+
+import pandas as pd
+
+rfs = ['SJ','MJ']
+
+if len(sys.argv) > 2 and sys.argv[1] in rfs: 
+    rf = sys.argv[1]
+    contrast = float(sys.argv[2])
+    time =  float(sys.argv[3])
+    print("Generating data for the reference solution = {} and contrast {} at time {}".format(rf,contrast,time))
+else: 
+    raise ValueError('Please provide one of the following options for the reference solution {} and a contrast'.format(rfs))
+
+
+def conditional(x,eta,true,false):
+    if x <= eta: 
+        return true
+    else: 
+        return false
+
+def singleJump_refsol(xu,t,c1,c2,w1,pos=0.5,dt=False):
+    w2 = c1*w1/c2
+    if not dt:
+        u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
+        u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
+        sol = conditional(xu,pos,u1,u2)
+    else: 
+        u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
+        u2 = -w2*c2*np.sin(w2*c2*t)*np.cos(w2*(xu-pos))
+        sol = conditional(xu,pos,u1,u2)
+    return sol
+
+def multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3,dt=False):
+    w2 = c1*w1/c2
+    pos2 = (2*np.pi*n + w2*pos)/w2
+    w3 = w1
+    c3 = c1
+    if not dt:
+        u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
+        u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
+        u3 = np.cos(w3*c3*t)*np.cos(w3*(xu-pos2))
+        sol = conditional(xu,pos2,conditional(xu,pos,u1,u2),u3)
+        #sol = ufl.conditional(ufl.le(xu-pos2,0.0),ufl.conditional(ufl.le(xu-pos,0.0),u1,u2),u3)
+    else: 
+        u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
[…]

### 2025-06-30 code/reproduce.sh

@@ -1,0 +1,29 @@
+#Requirements: fenicsx, pip install: gmsh, pandas, numpy, sympy
+#Reproduce experiments with a single contrast
+python3 SingleContrast.py 0.5
+python3 SingleContrast.py 0.1
+#Reproduce experiments for increasing contrast
+python3 MultContrast.py fix
+python3 MultContrast.py adap
+
+#Generate data for exact solution 
+python3 plot_exact.py SJ 2.5 0.25
+python3 plot_exact.py SJ 5.5 0.25
+python3 plot_exact.py MJ 2.5 0.5
+python3 plot_exact.py MJ 7.5 0.25
+python3 plot_exact.py MJ 7.5 0.5
+python3 plot_exact.py MJ 11.5
+
+#For plots with single jump
+python3 ApproxPlots.py
+
+
+#For plots with multiple jumps
+python3 ApproxPlotsMultipleJumps.py 3 7.5
+python3 ApproxPlotsMultipleJumps.py 4 7.5
+python3 ApproxPlotsMultipleJumps.py 3 11.5
+python3 ApproxPlotsMultipleJumps.py 4 11.5
+python3 ApproxPlotsMultipleJumpsMultT.py 0.5 2.5
+python3 ApproxPlotsMultipleJumpsMultT.py 1.0 2.5
+python3 ApproxPlotsMultipleJumpsMultT.py 0.5 7.5
+python3 ApproxPlotsMultipleJumpsMultT.py 1.0 7.5

### 2025-06-30 code/space_time.py

@@ -1,0 +1,2494 @@
+import numpy as np
+from math import pi,sqrt 
+import ufl
+from ufl import ds, dx, grad, inner, dS,jump,div
+from dolfinx import fem, io, mesh, plot,geometry
+from mpi4py import MPI
+from petsc4py import PETSc
+from precomp_time_int import get_elmat_time, quad_rule, basis_in_time,theta_ref,d_theta_ref 
+import scipy.sparse as sp
+from dolfinx.fem.petsc import assemble_matrix
+from numpy.typing import ArrayLike, NDArray
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+from matplotlib.ticker import MaxNLocator, LinearLocator, FormatStrFormatter, NullFormatter
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+#import sparse_dot_mkl
+
+
+def GetSpMat(mat):
+    ai, aj, av = mat.getValuesCSR()
+    Asp = sp.csr_matrix((av, aj, ai))
+    return Asp
+
+# copied this here from https://github.com/UCL/dxh for experimental purposes 
+def evaluate_function_at_points(
+    function: fem.Function,
+    points: NDArray[np.float64],) -> ArrayLike:
+    """
+    Evaluate a finite element function at one or more points.
+
+    Args:
+        function: Finite element function to evaluate.
+        points: One or more points in domain of function to evaluate at. Should be
+            either a one-dimensional array corresponding to a single point (with size
+            equal to the geometric dimension or 3) or a two-dimensional array
+            corresponding to one point per row (with size of last axis equal to the
+            geometric dimension or 3).
+
+    Returns:
+        Value(s) of function evaluated at point(s).
+    """
+    mesh = function.function_space.mesh
+    if points.ndim not in (1, 2):
+        msg = "points argument should be one or two-dimensional array"
+        raise ValueError(msg)
+    if points.shape[-1] not in (3, mesh.geometry.dim):
+        msg = "Last axis of points argument should be of size 3 or spatial dimension"
+        raise ValueError(msg)
+    if points.ndim == 1:
+        points = points[None]
+    if points.shape[-1] != 3:
+        padded_points = np.zeros(points.shape[:-1] + (3,))
[…]

### 2025-06-30 codeNew/ApproxPlots.py
Cleanup

@@ -1,350 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False #what does this do??
-
-GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,pos):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    upper_coords = x[0] > pos 
-    lower_coords = np.invert(upper_coords)
-    values[upper_coords] = np.full(sum(upper_coords), c2**2)
-    values[lower_coords] = np.full(sum(lower_coords), c1**2)
-    return values
-
-
-
-
-#Exact solution for discontinuous wave numbers
-def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
-    if not dt:
[…]

### 2025-06-30 codeNew/ApproxPlotsMultipleJumps.py

@@ -1,380 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-from meshes import get_1Dmesh
-import sys
-
-
-if len(sys.argv) > 2:
-    ref_lvl = int(sys.argv[1])
-    contrast = float(sys.argv[2])
-    print("Solving on level {} with contrast {}".format(ref_lvl,contrast))
-else: 
-    raise ValueError('Please provide ref level and contrast')
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False #what does this do??
-
-GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,c3,pos,pos2):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    pre_upper_coords = x[0] > pos 
[…]

### 2025-06-30 codeNew/ApproxPlotsMultipleJumpsMultT.py

@@ -1,383 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-from meshes import get_1Dmesh
-import sys
-
-
-if len(sys.argv) > 2:
-    finalTime = float(sys.argv[1])
-    contrast = float(sys.argv[2])
-    print("Solving with final time T = {} and contrast {}".format(finalTime,contrast))
-else: 
-    raise ValueError('Please provide contrast')
-
-ref_lvl = 4
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False #what does this do??
-
-GCC = False #only controls wether data is set only on the lhs (False) or on both sides (True)
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,c3,pos,pos2):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    pre_upper_coords = x[0] > pos 
[…]

### 2025-06-30 codeNew/GMREs.py

@@ -1,414 +1,0 @@
-import numpy as np
-from math import pi 
-
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from math import sqrt
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-import os
-from typing import Optional, Callable
-
-from math import log,sqrt
-
-if os.name == "nt":
-    _clear_line_command = ""
-else:
-    _clear_line_command = "\33[2K"
-
-sys.setrecursionlimit(10**6)
-
-class LinearSolver():
-    def __init__(self, mat : PETSc.Mat,
-                 pre = None,
-                 tol : float = None,
-                 maxiter : int = 100, 
-                 atol : float = None,
-                 callback : Optional[Callable[[int, float],None]] = None,
-                 callback_sol : Optional[Callable[[PETSc.Vec],None]] = None,
-                 printrates : bool = False,
-                 estimate_cond : bool = False 
-                 ):
-        if atol is None and tol is None:
-            tol = 1e-12
-        self.mat = mat
-        #assert (freedofs is None) != (pre is None)
-        self.pre = pre
-        self.tol = tol
-        self.atol = atol
-        self.maxiter = maxiter
-        self.callback = callback
-        self.callback_sol = callback_sol
-        self.printrates = printrates
-        self.residuals = []
-        self.iterations = 0
-        self.estimate_cond = estimate_cond
-        self.condest = None
-
-    def Solve(self, rhs: PETSc.Vec, sol: Optional[PETSc.Vec] = None,
-              initialize : bool = True) -> PETSc.Vec:
-        self.iterations = 0
-        self.residuals = []
-        if sol is None:
-            #sol = rhs.create(comm=MPI.COMM_WORLD)
-            sol,_ = self.mat.createVecs()
-            initialize = True
-        if initialize:
-            #print("ayyayayaya")
-            #help(sol)
-            #print("sol = ", sol)
-            #sol.copy(rhs)
-            sol.set(0)
-            #print(" lalala ")
-        self.sol = sol 
-        self._SolveImpl(rhs=rhs,sol=sol)
-        if self.estimate_cond:
-            return sol,self.residuals, self.condest, self.iterations
-        else: 
-            return sol,self.residuals
-
-    def CheckResiduals(self,residual):
[…]

### 2025-06-30 codeNew/MultContrast.py

@@ -1,114 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-from Solve1D import *
-
-import sys
-args = ['fix','adap']
-
-if len(sys.argv) > 1 and sys.argv[1] in args:
-    TAdap = True if sys.argv[1] == 'adap' else False
-    print("Solving with TAdap = ", TAdap)
-else: 
-    raise ValueError('Please give either fix or adap as arguments')
-
-
-#Stabilization params
-def set_stabs(c1,c2=1.0): 
-    stabs = {#"data": 1e4,
-                "data": 1e4,
-                #"dual": 1.0,
-                "dual": 1e0,
-                #"primal": 1e-3,
-                "primal": 1e-2,
-                "primal-jump":1e-2, # for simple sol: 1e-2, 
-                #"primal-jump-vel":1.0,
-                "primal-jump-displ-grad":1e-2/max(c1**2,c2**2)**2 # for simple sol: 1e-2
-            } 
-    return stabs
-
-
-
-df = pd.DataFrame()
-
-
-## for multiple contrasts (well-posed=False, GCC = True)
-orders = [3]
-contrasts = [1.0,1.5,2.0,2.5,3.0,3.5,4.0,4.5]
-ref_lvls = lambda order, T : [3]
-
-#time
-#TAdap = True
-Tfunc = lambda contrast: 1/4*(1+1/contrast)*1.01 if TAdap else 0.5
-
-
-
-make_plots=True
-
-for order in orders:
-    for contrast in contrasts: 
-        T = Tfunc(contrast)
-        print("Solving with time T = ", T)
-        plot_df = pd.DataFrame()
-        for ref_lvl in ref_lvls(order,T):
-            print("Order = {}, ref_lvl = {}, contrast = {}".format(order,ref_lvl,contrast))
-            stabs = set_stabs(c1=contrast)
[…]

### 2025-06-30 codeNew/SingleContrast.py

@@ -1,114 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-from Solve1D import *
-
-import sys
-
-if len(sys.argv) > 1: 
-    T = float(sys.argv[1])
-    print("Solving with final time T = ", T)
-else: 
-    raise ValueError('Please provide final time T')
-
-
-#Stabilization params
-def set_stabs(c1,c2=1.0): 
-    stabs = {#"data": 1e4,
-                "data": 1e4,
-                #"dual": 1.0,
-                "dual": 1e0,
-                #"primal": 1e-3,
-                "primal": 1e-2,
-                "primal-jump":1e-2, # for simple sol: 1e-2, 
-                #"primal-jump-vel":1.0,
-                "primal-jump-displ-grad":1e-2/max(c1**2,c2**2)**2 # for simple sol: 1e-2
-            } 
-    return stabs
-
-
-
-df = pd.DataFrame()
-
-
-#for single contrast, (for T = 0.5: well-posed=False, GCC = True)
-def ref_lvls(order,T):
-    if T == 0.5: 
-        lvls = [1,2,3,4]
-    else: 
-        lvls = [1,2,3,4] if order < 3 else [1,2,3]
-    return lvls    
-
-orders = [2,3]
-contrasts = [2.5]
-
-#time
-#T = 0.1
-
-make_plots=True
-
-for order in orders:
-    for contrast in contrasts: 
-        print("Solving with time T = ", T)
-        plot_df = pd.DataFrame()
-        for ref_lvl in ref_lvls(order,T):
-            print("Order = {}, ref_lvl = {}, contrast = {}".format(order,ref_lvl,contrast))
-            stabs = set_stabs(c1=contrast)
[…]

### 2025-06-30 codeNew/Solve1D.py

@@ -1,288 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False #what does this do??
-
-GCC = True #only controls wether data is set only on the lhs (False) or on both sides (True)
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,pos):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    upper_coords = x[0] > pos 
-    lower_coords = np.invert(upper_coords)
-    values[upper_coords] = np.full(sum(upper_coords), c2**2)
-    values[lower_coords] = np.full(sum(lower_coords), c1**2)
-    return values
-
-
-
-
-#Exact solution for discontinuous wave numbers
-def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
-    if not dt:
[…]

### 2025-06-30 codeNew/WeakDiscConv.py

@@ -1,332 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False
-
-GCC = True
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,pos):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    upper_coords = x[0] > pos 
-    lower_coords = np.invert(upper_coords)
-    values[upper_coords] = np.full(sum(upper_coords), c2**2)
-    values[lower_coords] = np.full(sum(lower_coords), c1**2)
-    return values
-
-
-
-
-#Exact solution for discontinuous wave numbers
-def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
-    if not dt:
-        #import pdb; pdb.set_trace()
-        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x[0]-c1*t)-p0(k-x[0]-c1*t)) for k in range(trunc)])
[…]

### 2025-06-30 codeNew/WeakDiscPlot.py

@@ -1,334 +1,0 @@
-## IMPORTS ##
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-from petsc4py.PETSc import ScalarType
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-import pypardiso
-import time
-import cProfile
-import resource
-import pandas as pd 
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-well_posed = False
-
-GCC = True
-
-## Helping Functions ##
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-
-def csq_preInd(x,c1,c2,pos):
-    values = np.zeros(x.shape[1],dtype=ScalarType)
-    upper_coords = x[0] > pos 
-    lower_coords = np.invert(upper_coords)
-    values[upper_coords] = np.full(sum(upper_coords), c2**2)
-    values[lower_coords] = np.full(sum(lower_coords), c1**2)
-    return values
-
-
-
-
-#Exact solution for discontinuous wave numbers
-def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
-    if not dt:
-        #import pdb; pdb.set_trace()
-        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x[0]-c1*t)-p0(k-x[0]-c1*t)) for k in range(trunc)])
[…]

### 2025-06-30 codeNew/meshes.py

@@ -1,265 +1,0 @@
-import gmsh
-import numpy as np
-
-from dolfinx.fem import (Constant, dirichletbc, Function, FunctionSpace, assemble_scalar,
-                         form, locate_dofs_geometrical, locate_dofs_topological)
-from dolfinx.fem.petsc import LinearProblem
-from dolfinx.io import XDMFFile
-from dolfinx.mesh import create_unit_square, locate_entities, refine, compute_incident_entities, GhostMode
-#from dolfinx.plot import create_vtk_mesh
-
-from ufl import (SpatialCoordinate, TestFunction, TrialFunction,
-                 dx, grad, inner,And,Not,conditional)
-
-from mpi4py import MPI
-from petsc4py.PETSc import ScalarType
-from math import pi
-from dolfinx.io import XDMFFile,gmshio
-from dolfinx.cpp.io import perm_gmsh
-from dolfinx.mesh import CellType, create_mesh
-from dolfinx.cpp import mesh as cmesh
-#help(CellType)
-import itertools
-GM = GhostMode.shared_facet
-
-
-def get_1Dmesh(xcoord = [0.0,0.25,0.5,0.75,1.0]): 
-
-
-    # points to connect
-    points = [(xc, 0, 0) for xc in xcoord]
-
-    # assign node numbers
-    nodes = [x for x in range(1, len(points)+1)]
-    # get a flat list of coordinates
-    coords = list(itertools.chain.from_iterable(points))
-
-    gmsh.initialize()
-    # add a dummy line to add nodes to
-    dummy_line = 1
-    gmsh.model.addDiscreteEntity(1, dummy_line)
-
-    # add nodes
-    gmsh.model.mesh.addNodes(1, dummy_line, nodes, coords)
-
-    # add line elements between each node
-    line_elt = 1
-    for i in range(len(nodes) - 1):
-        gmsh.model.mesh.addElementsByType(
-            dummy_line, line_elt, [], [nodes[i], nodes[i+1]])
-
-    gdim = 1  # 1D mesh 
-    proc = MPI.COMM_WORLD.rank 
-
-    its = 1 
[…]

### 2025-06-30 codeNew/plot_exact.py

@@ -1,104 +1,0 @@
-import numpy as np
-import scipy.sparse as sp
-import matplotlib.pyplot as plt
-import sys 
-
-import pandas as pd
-
-rfs = ['SJ','MJ']
-
-if len(sys.argv) > 2 and sys.argv[1] in rfs: 
-    rf = sys.argv[1]
-    contrast = float(sys.argv[2])
-    time =  float(sys.argv[3])
-    print("Generating data for the reference solution = {} and contrast {} at time {}".format(rf,contrast,time))
-else: 
-    raise ValueError('Please provide one of the following options for the reference solution {} and a contrast'.format(rfs))
-
-
-def conditional(x,eta,true,false):
-    if x <= eta: 
-        return true
-    else: 
-        return false
-
-def singleJump_refsol(xu,t,c1,c2,w1,pos=0.5,dt=False):
-    w2 = c1*w1/c2
-    if not dt:
-        u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
-        u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
-        sol = conditional(xu,pos,u1,u2)
-    else: 
-        u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
-        u2 = -w2*c2*np.sin(w2*c2*t)*np.cos(w2*(xu-pos))
-        sol = conditional(xu,pos,u1,u2)
-    return sol
-
-def multipleJump_refsol(t,xu,c1,c2,w1,pos,n=3,dt=False):
-    w2 = c1*w1/c2
-    pos2 = (2*np.pi*n + w2*pos)/w2
-    w3 = w1
-    c3 = c1
-    if not dt:
-        u1 = np.cos(w1*c1*t) *np.cos(w1*(xu-pos))
-        u2 = np.cos(w2*c2*t)*np.cos(w2*(xu-pos))
-        u3 = np.cos(w3*c3*t)*np.cos(w3*(xu-pos2))
-        sol = conditional(xu,pos2,conditional(xu,pos,u1,u2),u3)
-        #sol = ufl.conditional(ufl.le(xu-pos2,0.0),ufl.conditional(ufl.le(xu-pos,0.0),u1,u2),u3)
-    else: 
-        u1 = -w1*c1*np.sin(w1*c1*t) *np.cos(w1*(xu-pos))
[…]

### 2025-06-30 codeNew/plot_exact_test.py

@@ -1,83 +1,0 @@
-import numpy as np
-import scipy.sparse as sp
-import matplotlib.pyplot as plt
-import matplotlib.colors as colors
-from matplotlib.ticker import MaxNLocator, LinearLocator, FormatStrFormatter
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-
-#Testfile to check the implementation of the exact solution..., exchanged ufl.conditional with a function that should do the same, ufl.exp to np.exp and x[0] -> x as before...
-
-def conditional(x,eta,true,false):
-    if x <= eta: 
-        return true
-    else: 
-        return false
-
-def ref_sol(x,t,p0,c1,c2,trunc,pos,dt=False):
-    if not dt:
-        #import pdb; pdb.set_trace()
-        u1_plus = sum([((c2-c1)/(c2+c1))**k * (p0(k+x-c1*t)-p0(k-x-c1*t)) for k in range(trunc)])
-        u1_minus = ((1/pos*c1)/(c2+c1))*sum([((c2-c1)/(c2+c1))**k * p0(c1/c2*(x-pos)+k+pos-c1*t) for k in range(trunc)])
-    else:
-        u1_plus = sum([((c2-c1)/(c2+c1))**k * (800*c1*(k+x-c1*t-1/5)*p0(k+x-c1*t)-800*c1*(k-x-c1*t-1/5)*p0(k-x-c1*t)) for k in range(trunc)])
-        u1_minus = sum([((c2-c1)/(c2+c1))**k * 800*c1*(c1/c2*(x-pos)+k+pos-c1*t-1/5)*p0(c1/c2*(x-pos)+k+pos-c1*t) for k in range(trunc)])
-    sol = conditional(x,pos,u1_plus,u1_minus)
-    return sol
-
-p0 = lambda x : 1/100*np.exp(-(20*(x-1/5))**2)
-
-c1 = 1
-c2 = 0.1
-pos= 0.5
-t = 0.0
-trunc = 100
-
-def sol(t,xu):
-    return ref_sol(xu,t,p0,c1,c2,trunc,pos,dt=False)
-
-def dt_sol(t,xu):
-    return ref_sol(xu,t,p0,c1,c2,trunc,pos,dt=True)
-
-
-def plot(t):
-    x_pts = np.linspace(0.0,1.0,num=5000).tolist()
-
-
-    y_pts = np.zeros(len(x_pts))
-
-    for i in range(len(x_pts)):
[…]

### 2025-06-30 codeNew/precomp_time_int.py

@@ -1,171 +1,0 @@
-from sympy import * 
-import numpy as np
-
-def get_elmat_time(q,qstar):
-
-    elmat_time = { } 
-
-    x, y = symbols('x y') 
-
-    basis_in_time = { 0: [1],
-                      1: [1-x, x],
-                      2: [2*(1-x)*(1/2-x), 4*x*(1-x), 2*x*(x-1/2)],
-                      3: [(-9/2)*(x-1)*(x-2/3)*(x-1/3),(27/2)*x*(x-1)*(x-2/3), -(27/2)*x*(x-1)*(x-1/3), (9/2)*x*(x-1/3)*(x-2/3)] 
-                    }
-
-    phis = basis_in_time[q]
-    chis = basis_in_time[qstar]
-
-    M_time_q_qstar = np.zeros((qstar+1,q+1))
-    for i in range(qstar+1):
-        for j in range(q+1):
-            M_time_q_qstar[i,j] = integrate(phis[j]*chis[i], (x,0,1))
-    elmat_time["M_time_q_qstar"] = M_time_q_qstar 
-
-    M_time_q_q = np.zeros((q+1,q+1))
-    for i in range(q+1):
-        for j in range(q+1):
-            M_time_q_q[i,j] = integrate(phis[j]*phis[i], (x,0,1))
-    elmat_time["M_time_q_q"] = M_time_q_q
-
-    M_time_qstar_qstar = np.zeros((qstar+1,qstar+1))
-    for i in range(qstar+1):
-        for j in range(qstar+1):
-            M_time_qstar_qstar[i,j] = integrate(chis[j]*chis[i], (x,0,1))
-    elmat_time["M_time_qstar_qstar"] = M_time_qstar_qstar 
-
-
-    DM_time_q_qstar = np.zeros((qstar+1,q+1))
-    for i in range(qstar+1):
-        for j in range(q+1):
-            DM_time_q_qstar[i,j] = integrate(diff(phis[j],x)*chis[i], (x,0,1))
-    elmat_time["DM_time_q_qstar"] = DM_time_q_qstar 
-
-
-    DMT_time_q_qstar = np.zeros((qstar+1,q+1))
-    for i in range(qstar+1):
-        for j in range(q+1):
-            DMT_time_q_qstar[i,j] = integrate( phis[j] * diff(chis[i],x) , (x,0,1))
-    elmat_time["DMT_time_q_qstar"] = DMT_time_q_qstar 
-
-    DM_time_q_q = np.zeros((q+1,q+1))
[…]

### 2025-06-30 codeNew/reproduce.sh

@@ -1,29 +1,0 @@
-#Requirements: fenicsx, pip install: gmsh, pandas, numpy, sympy
-#Reproduce experiments with a single contrast
-python3 SingleContrast.py 0.5
-python3 SingleContrast.py 0.1
-#Reproduce experiments for increasing contrast
-python3 MultContrast.py fix
-python3 MultContrast.py adap
-
-#Generate data for exact solution 
-python3 plot_exact.py SJ 2.5 0.25
-python3 plot_exact.py SJ 5.5 0.25
-python3 plot_exact.py MJ 2.5 0.5
-python3 plot_exact.py MJ 7.5 0.25
-python3 plot_exact.py MJ 7.5 0.5
-python3 plot_exact.py MJ 11.5
-
-#For plots with single jump
-python3 ApproxPlots.py
-
-
-#For plots with multiple jumps
-python3 ApproxPlotsMultipleJumps.py 3 7.5
-python3 ApproxPlotsMultipleJumps.py 4 7.5
-python3 ApproxPlotsMultipleJumps.py 3 11.5
-python3 ApproxPlotsMultipleJumps.py 4 11.5
-python3 ApproxPlotsMultipleJumpsMultT.py 0.5 2.5
-python3 ApproxPlotsMultipleJumpsMultT.py 1.0 2.5
-python3 ApproxPlotsMultipleJumpsMultT.py 0.5 7.5
-python3 ApproxPlotsMultipleJumpsMultT.py 1.0 7.5

### 2025-06-30 codeNew/solve-2D-jump.py

@@ -1,313 +1,0 @@
-import numpy as np
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh#, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py.PETSc import ScalarType
-
-
-from petsc4py import PETSc
-
-from dolfinx.mesh import create_unit_interval
-from dolfinx.io import XDMFFile
-import sys
-sys.setrecursionlimit(10**6)
-from GMREs import GMRes
-from space_time import * 
-from precomp_time_int import theta_ref, d_theta_ref 
-from meshes import get_2Dmesh_data_all_around
-import pypardiso
-import scipy.sparse as sp
-import time
-import cProfile
-import resource
-
-import pandas as pd 
-
-
-#solver_type = "petsc-LU"  
-solver_type = "pypardiso" # 
-#solver_type = "direct" # 
-
-well_posed = False
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    return solver
-
-# define alternative solvers here 
-#def GetSpMat(mat):
-#    ai, aj, av = mat.getValuesCSR()
-#    Asp = sp.csr_matrix((av, aj, ai))
-#    return Asp 
-
-
-#class PySolver:
-#    def __init__(self,Asp,psolver):
-#        self.Asp = Asp
-#        self.solver = psolver
-#    def solve(self,b_inp,x_out):
-#        x_py = self.solver.solve(self.Asp, b_inp.array )
-#        x_out.array[:] = x_py[:]
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-#Generates a sequence of meshes
[…]

### 2025-06-30 codeNew/solver_tools.py

@@ -1,38 +1,0 @@
-import numpy as np
-import scipy.sparse as sp
-from math import pi,sqrt  
-import ufl
-from dolfinx import fem, io, mesh, plot
-from ufl import ds, dx, grad, inner, dS,jump,div
-from mpi4py import MPI
-from petsc4py import PETSc
-import pypardiso
-
-def GetSpMat(mat):
-    ai, aj, av = mat.getValuesCSR()
-    Asp = sp.csr_matrix((av, aj, ai))
-    return Asp
-
-def GetLuSolver(msh,mat):
-    solver = PETSc.KSP().create(msh.comm) 
-    solver.setOperators(mat)
-    solver.setType(PETSc.KSP.Type.PREONLY)
-    solver.getPC().setType(PETSc.PC.Type.LU)
-    #solver.getPC().setFactorSolverType("mumps")
-    return solver
-
-class PySolver:
-    def __init__(self,Asp,psolver):
-        self.Asp = Asp
-        self.solver = psolver
-    def solve(self,b_inp,x_out): 
-        self.solver._check_A(self.Asp)
-        b = self.solver._check_b(self.Asp, b_inp.array)
-        self.solver.set_phase(33)
-        x_out.array[:] = self.solver._call_pardiso(self.Asp , b )[:]
-
-def GetPyPardisoSolver(mat):
-    solver_instance = pypardiso.PyPardisoSolver()
-    matrix_A  = GetSpMat(mat)
-    solver_instance.factorize(matrix_A)
-    return PySolver( matrix_A, solver_instance)

### 2025-06-30 codeNew/space_time.py

@@ -1,2494 +1,0 @@
-import numpy as np
-from math import pi,sqrt 
-import ufl
-from ufl import ds, dx, grad, inner, dS,jump,div
-from dolfinx import fem, io, mesh, plot,geometry
-from mpi4py import MPI
-from petsc4py import PETSc
-from precomp_time_int import get_elmat_time, quad_rule, basis_in_time,theta_ref,d_theta_ref 
-import scipy.sparse as sp
-from dolfinx.fem.petsc import assemble_matrix
-from numpy.typing import ArrayLike, NDArray
-import matplotlib.pyplot as plt
-import matplotlib.colors as colors
-from matplotlib.ticker import MaxNLocator, LinearLocator, FormatStrFormatter, NullFormatter
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-#import sparse_dot_mkl
-
-
-def GetSpMat(mat):
-    ai, aj, av = mat.getValuesCSR()
-    Asp = sp.csr_matrix((av, aj, ai))
-    return Asp
-
-# copied this here from https://github.com/UCL/dxh for experimental purposes 
-def evaluate_function_at_points(
-    function: fem.Function,
-    points: NDArray[np.float64],) -> ArrayLike:
-    """
-    Evaluate a finite element function at one or more points.
-
-    Args:
-        function: Finite element function to evaluate.
-        points: One or more points in domain of function to evaluate at. Should be
-            either a one-dimensional array corresponding to a single point (with size
-            equal to the geometric dimension or 3) or a two-dimensional array
-            corresponding to one point per row (with size of last axis equal to the
-            geometric dimension or 3).
-
-    Returns:
-        Value(s) of function evaluated at point(s).
-    """
-    mesh = function.function_space.mesh
-    if points.ndim not in (1, 2):
-        msg = "points argument should be one or two-dimensional array"
-        raise ValueError(msg)
-    if points.shape[-1] not in (3, mesh.geometry.dim):
-        msg = "Last axis of points argument should be of size 3 or spatial dimension"
-        raise ValueError(msg)
-    if points.ndim == 1:
-        points = points[None]
-    if points.shape[-1] != 3:
-        padded_points = np.zeros(points.shape[:-1] + (3,))
[…]

### 2025-06-30 code/ApproxPlots.py
Code cleanup

@@ -341,7 +341,7 @@ for order in orders:
             dt_y_pts = np.array(plot_data_sol[3][ int(len(ts)/2) ,: ])
             new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts)),'contrast':np.repeat(contrast,len(x_pts))}
             plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-            plot_df.to_csv('../dataNew/plots/simpleExact_ApproxPlot_T{0}.csv'.format(T),index=False)
+            plot_df.to_csv('../data/plots/simpleExact_ApproxPlot_T{0}.csv'.format(T),index=False)
 
          
         

### 2025-06-30 code/ApproxPlotsMultipleJumps.py

@@ -371,7 +371,7 @@ fun_y_pts = np.array(plot_data_sol[2][ int(len(ts)/2) ,: ])
 dt_y_pts = np.array(plot_data_sol[3][ int(len(ts)/2) ,: ])
 new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts)),'contrast':np.repeat(contrast,len(x_pts))}
 plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-plot_df.to_csv('../dataNew/plots/MultipleJumpsExact_ApproxPlot_T{}_L{}_contrast{}.csv'.format(T,ref_lvl,contrast),index=False)
+plot_df.to_csv('../data/plots/MultipleJumpsExact_ApproxPlot_T{}_L{}_contrast{}.csv'.format(T,ref_lvl,contrast),index=False)
 
             
             

### 2025-06-30 code/ApproxPlotsMultipleJumpsMultT.py

@@ -374,7 +374,7 @@ else:
     dt_y_pts = np.array(plot_data_sol[3][ int(len(ts)/2) ,: ])
 new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts)),'contrast':np.repeat(contrast,len(x_pts))}
 plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-plot_df.to_csv('../dataNew/plots/MultipleJumpsExact_ApproxPlot_CompareT{}_contrast{}.csv'.format(T,contrast),index=False)
+plot_df.to_csv('../data/plots/MultipleJumpsExact_ApproxPlot_CompareT{}_contrast{}.csv'.format(T,contrast),index=False)
 
             
             

### 2025-06-30 code/MultContrast.py

@@ -90,8 +90,8 @@ for order in orders:
             new_data = {'L':ref_lvl,'order':order,'contrast':contrast,'condest':condest} | errors | ba_errors
             df = pd.concat([df,pd.DataFrame(new_data,index=[0])],ignore_index=True)
             T = 'Adap' if TAdap else T 
-            df.to_csv('../dataNew/simplexExact_MultContrast_T{}.csv'.format(T),index=False)
-            #df.to_csv('../dataNew/test_differentstabs.csv'.format(order,well_posed),index=False)
+            df.to_csv('../data/simplexExact_MultContrast_T{}.csv'.format(T),index=False)
+            #df.to_csv('../data/test_differentstabs.csv'.format(order,well_posed),index=False)
 
             #Generate Data for plots (approximate solution)
             x_pts = np.array(plot_data_sol[0])
@@ -101,13 +101,13 @@ for order in orders:
             new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts))}
             #import pdb; pdb.set_trace()
             plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-            plot_df.to_csv('../dataNew/plots/simpleExact_T{0}_multipleContrasts_approx_plot_data_WP{1}_contrast{2}_k{3}.csv'.format(T,well_posed,contrast,order),index=False)
+            plot_df.to_csv('../data/plots/simpleExact_T{0}_multipleContrasts_approx_plot_data_WP{1}_contrast{2}_k{3}.csv'.format(T,well_posed,contrast,order),index=False)
 
             #Save data for error plots (use np.genfromtxt("... .csv", delimiter=",")
-            np.savetxt('../dataNew/plots/simpleExact_T{0}_multipleContrasts_error_plot_xpts_WP{1}_k{2}_contrast{3}_ref{4}.csv'.format(T,well_posed,order,contrast,ref_lvl),plot_data_errors[0],delimiter=',')
[…]

### 2025-06-30 code/SingleContrast.py

@@ -90,8 +90,8 @@ for order in orders:
             ba_errors = {'bestapprox-'+k:v for k,v in ba_errors.items()}
             new_data = {'L':ref_lvl,'order':order,'contrast':contrast,'condest':condest} | errors | ba_errors
             df = pd.concat([df,pd.DataFrame(new_data,index=[0])],ignore_index=True)
-            df.to_csv('../dataNew/simplexExact_singleContrast_T{}.csv'.format(T),index=False)
-            #df.to_csv('../dataNew/test_differentstabs.csv'.format(order,well_posed),index=False)
+            df.to_csv('../data/simplexExact_singleContrast_T{}.csv'.format(T),index=False)
+            #df.to_csv('../data/test_differentstabs.csv'.format(order,well_posed),index=False)
 
             #Generate Data for plots (approximate solution)
             x_pts = np.array(plot_data_sol[0])
@@ -101,13 +101,13 @@ for order in orders:
             new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts))}
             #import pdb; pdb.set_trace()
             plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-            plot_df.to_csv('../dataNew/plots/simpleExact_T{0}_multipleContrasts_approx_plot_data_WP{1}_contrast{2}_k{3}.csv'.format(T,well_posed,contrast,order),index=False)
+            plot_df.to_csv('../data/plots/simpleExact_T{0}_multipleContrasts_approx_plot_data_WP{1}_contrast{2}_k{3}.csv'.format(T,well_posed,contrast,order),index=False)
 
             #Save data for error plots (use np.genfromtxt("... .csv", delimiter=",")
-            np.savetxt('../dataNew/plots/simpleExact_T{0}_multipleContrasts_error_plot_xpts_WP{1}_k{2}_contrast{3}_ref{4}.csv'.format(T,well_posed,order,contrast,ref_lvl),plot_data_errors[0],delimiter=',')
[…]

### 2025-06-30 code/WeakDiscConv.py

@@ -308,7 +308,7 @@ for order in orders:
             ba_errors = {'bestapprox-'+k:v for k,v in ba_errors.items()}
             new_data = {'L':ref_lvl,'order':order,'contrast':contrast,'condest':condest} | errors | ba_errors
             df = pd.concat([df,pd.DataFrame(new_data,index=[0])],ignore_index=True)
-            df.to_csv('../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k{0}.csv'.format(order,well_posed,contrast),index=False)
+            df.to_csv('../data/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k{0}.csv'.format(order,well_posed,contrast),index=False)
             #df.to_csv('../data/jumpCoefs/test_differentstabs.csv'.format(order,well_posed),index=False)
 
             #Generate Data for plots (approximate solution)
@@ -319,13 +319,13 @@ for order in orders:
             new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts))}
             #import pdb; pdb.set_trace()
             plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-            #plot_df.to_csv('../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WP{0}_contrast{1}_k{2}.csv'.format(well_posed,contrast,order),index=False)
+            #plot_df.to_csv('../data/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WP{0}_contrast{1}_k{2}.csv'.format(well_posed,contrast,order),index=False)
 
             #Save data for error plots (use np.genfromtxt("... .csv", delimiter=",")
-            #np.savetxt('../dataNew/plots/weakDisc_evenhigherDt_noRestrict_error_plot_xpts_WP{0}_k{1}_contrast{2}_ref{3}.csv'.format(well_posed,order,contrast,ref_lvl),plot_data_errors[0],delimiter=',')
[…]

### 2025-06-30 code/WeakDiscPlot.py

@@ -310,7 +310,7 @@ for order in orders:
             ba_errors = {'bestapprox-'+k:v for k,v in ba_errors.items()}
             new_data = {'L':ref_lvl,'order':order,'contrast':contrast,'condest':condest} | errors | ba_errors
             df = pd.concat([df,pd.DataFrame(new_data,index=[0])],ignore_index=True)
-            #df.to_csv('../dataNew/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k{0}.csv'.format(order,well_posed,contrast),index=False)
+            #df.to_csv('../data/weakDisc_evenhigherDt_noRestrict_1D_jumpingCoefs_k{0}.csv'.format(order,well_posed,contrast),index=False)
             #df.to_csv('../data/jumpCoefs/test_differentstabs.csv'.format(order,well_posed),index=False)
 
             #Generate Data for plots (approximate solution)
@@ -321,13 +321,13 @@ for order in orders:
             new_plot_data = {'x':x_pts,'y':fun_y_pts,'y_dt':dt_y_pts,'L':np.repeat(ref_lvl,len(x_pts)),'k':np.repeat(order,len(x_pts))}
             #import pdb; pdb.set_trace()
             plot_df = pd.concat([plot_df,pd.DataFrame.from_dict(new_plot_data)],ignore_index=True)
-            plot_df.to_csv('../dataNew/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WP{0}_contrast{1}_k{2}.csv'.format(well_posed,contrast,order),index=False)
+            plot_df.to_csv('../data/plots/weakDisc_evenhigherDt_noRestrict_approx_plot_data_WP{0}_contrast{1}_k{2}.csv'.format(well_posed,contrast,order),index=False)
 
             #Save data for error plots (use np.genfromtxt("... .csv", delimiter=",")
-            #np.savetxt('../dataNew/plots/weakDisc_evenhigherDt_noRestrict_error_plot_xpts_WP{0}_k{1}_contrast{2}_ref{3}.csv'.format(well_posed,order,contrast,ref_lvl),plot_data_errors[0],delimiter=',')
[…]

### 2025-06-30 code/plot_exact.py

@@ -95,7 +95,7 @@ def plot(t,save_data=False,plot=False):
     if save_data: 
         data = {'x':x_pts,'y':y_pts}
         df = pd.DataFrame(data)
-        df.to_csv('../dataNew/plots/exact_plot{}_contrast{}_time{}.csv'.format(rf,c1,t),index=False)
+        df.to_csv('../data/plots/exact_plot{}_contrast{}_time{}.csv'.format(rf,c1,t),index=False)
         
     if plot: 
         plt.plot(x_pts,y_pts)

### 2025-06-30 code/solve-2D-jump.py

@@ -310,4 +310,4 @@ for order in orders:
             ba_errors = {'bestapprox-'+k:v for k,v in ba_errors.items()}
             new_data = {'L':ref_lvl,'order':order,'contrast':contrast} | errors | ba_errors
             df = pd.concat([df,pd.DataFrame(new_data,index=[0])],ignore_index=True)
-            df.to_csv('../dataNew/2D_errors_simpleRefsol_contrast{}.csv'.format(contrast),index=False)
+            df.to_csv('../data/2D_errors_simpleRefsol_contrast{}.csv'.format(contrast),index=False)

### 2025-06-30 tex/main.tex
Minor

@@
 We consider the discretization of a data assimilation problem for the wave equation in heterogeneous media.
-In the following, let $\Omega \subset \mathbb{R}^d$ be a bounded domain with smooth boundary $\partial \Omega$.
+In the following, let $\Omega \subset \mathbb{R}^d$, $d \in \{1,2,3\}$, be a bounded domain with smooth boundary $\partial \Omega$.
 We assume that $\Omega$ is split by a smooth $(d-1)$-dimensional interface $\Gamma$ into two disjoint components such that $\Omega \setminus \Gamma = \Omega_1 \cup
 \Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
-~\jp{We should specify the range of $d$. Is there any restriction in Filippas?}
+~\jp{We should specify the range of $d$. Is there any restriction in Filippas? TvB: does not seem, I included 1,2,3?}
 

### 2025-06-30 code/reproduce.sh
Reproduction instructions

@@ -1,4 +1,7 @@
 #Requirements: fenicsx, pip install: gmsh, pandas, numpy, sympy
+
+#1D-examples
+#
 #Reproduce experiments with a single contrast
 python3 SingleContrast.py 0.5
 python3 SingleContrast.py 0.1
@@ -17,7 +20,6 @@ python3 plot_exact.py MJ 11.5
 #For plots with single jump
 python3 ApproxPlots.py
 
-
 #For plots with multiple jumps
 python3 ApproxPlotsMultipleJumps.py 3 7.5
 python3 ApproxPlotsMultipleJumps.py 4 7.5
@@ -27,3 +29,6 @@ python3 ApproxPlotsMultipleJumpsMultT.py 0.5 2.5
 python3 ApproxPlotsMultipleJumpsMultT.py 1.0 2.5
 python3 ApproxPlotsMultipleJumpsMultT.py 0.5 7.5
 python3 ApproxPlotsMultipleJumpsMultT.py 1.0 7.5
+
+#2D-examples
+python3 solve-2D-jump.py

### 2025-06-30 code/solve-2D-jump.py
Minor & URL

@@ -292,12 +292,8 @@ def set_stabs(c1,c2=1.0):
 df = pd.DataFrame()
 
 
-ref_lvls = [1,2,3,4]
-orders = [2,3]
-contrasts = [1.0,1.5,2.0,2.5]
 
-#for testing 
-ref_lvls = lambda order: [1,2,3] if order < 3 else [1,2] 
+ref_lvls = lambda order: [1,2,3,4] if order < 3 else [1,2,3,4] 
 orders = [2,3]
 contrasts = [1.0,1.5,2.0,2.5]
 

### 2025-09-16 tex/main.tex
Minor & URL
Minor

@@
 \Omega_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$.
-~\jp{We should specify the range of $d$. Is there any restriction in Filippas? TvB: does not seem, I included 1,2,3?}
 
@@
 \begin{alignat*}{2}
-    (\ul_1,\wl_1)_{\omega_T} \! + \! A[\Wh,\Zh] + S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \ &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q} \\
-    A[\Uh,\Yh] -  S_h^\ast(\Yh,\Zh) &= 0 \ &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast} 
+    (\ul_1,\wl_1)_{\omega_T} \! + \! A[\Wh,\Zh] + S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \ &&\forall \Wh \in \ProdFullyDiscrSpace{k}{q}, \\
+    A[\Uh,\Yh] -  S_h^\ast(\Yh,\Zh) &= 0 \ &&\forall \Yh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}.
 \end{alignat*}
@@
     \begin{enumerate}
-        \item The results from \cref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$, but we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$.
+        \item The results from \cref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$, but we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$ to the right order.
 Thus, we would have to rewrite the estimates from \cref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$.
@@
 The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}.
-~\jp{We need to prepare some reproduction material ...}
+Reproduction material is available at \url{https://github.com/TimvanBeeck/waveUC_discCoefs}.
+
 \subsection{Examples in one space dimension}

### 2025-11-19 review/response/letter.tex
Review

\documentclass[11pt,a4paper,twoside,onecolumn]{article}
\usepackage[left=20mm,right=20mm,top=25mm,bottom=20mm]{geometry}

%------------------------------------------------------------------------------------------------
% Additional packages
%------------------------------------------------------------------------------------------------

\usepackage[colorlinks=true]{hyperref}
\usepackage[hyperref,dvipsnames]{xcolor}

\usepackage[T1]{fontenc} 							
\usepackage[english]{babel} 					
\usepackage{amssymb,amsmath,amsthm,amsbsy}		
\usepackage{array} 						
\usepackage{pdfpages}								
\usepackage{graphicx} 						
\usepackage{caption}[2004/07/16]					
\usepackage{subfigure}							
\usepackage{mathrsfs} 	
\usepackage{empheq}								
\usepackage{nicefrac}								
\usepackage{stmaryrd}								
\usepackage{fixltx2e} 							
\usepackage{fix-cm}								
\usepackage{bm}
\usepackage{booktabs}
\usepackage{here}								
\usepackage{url}
\usepackage{enumitem}
\usepackage{thmbox}
\usepackage{shadethm}		
\usepackage{siunitx}
\usepackage{todonotes}	
\usepackage{bm}

\newcommand{\revcommentA}[1]{\textbf{\textcolor{blue}{#1}}~}
\newcommand{\revcommentB}[1]{\textbf{\textcolor{blue}{#1}}~}
\newcommand{\revcommentC}[1]{\textit{\textcolor{blue}{#1}}~}
\newcommand{\reply}[1]{~\\[0.25cm] \textcolor{green!40!black}{#1}~}
\newcommand{\todiscuss}[1]{\textcolor{red!60!orange}{\underline{To discuss:} #1}~}
\newcommand{\tocheck}{\textcolor{red!60!black}{\underline{ToCheck}}~}
\newcommand{\fixed}{\textcolor{green!50!black}{\underline{fixed}}~}

\renewcommand{\baselinestretch}{1,3}
\setlength{\parindent}{0pt}

%--------------------------------------------------ENVIRONMENTS---------------------------------------
\newtheorem[style=S,underline=true,bodystyle=\normalfont\noindent]{thmDef}{Definition}[section]
\newtheorem[style=S,cut=false]{thmCor}[thmDef]{Corollary}
\newtheorem[style=S,cut=false,headstyle=\normalsize\bfseries\boldmath####1~####2]{thmLem}[thmDef]{Lemma}
\newtheorem[style=S]{thmCor}[thmDef]{Corollary}
\newshadetheorem{thm}[thmDef]{Theorem}
\newenvironment{thmThe}[1][]{%
 	\definecolor{shadethmcolor}{gray}{0.9}%
  	\definecolor{shaderulecolor}{rgb}{0.0,0.0,0.0}%
  	\setlength{\shadeboxrule}{0.0pt}%
  	\begin{thm}[#1]%
}{\end{thm}}

\newenvironment{thmProof}
                [0]
                { \begin{example}[Proof] \normalsize}
                { $\hfill\blacksquare$ \end{example} }

\newenvironment{thmRem}
                [0]
                { \begin{example}[Remark] \normalsize}
                { $\hfill\blacktriangle$ \end{example} }							
%-----------------------------------------------------------------------------------------------------

\makeatletter % Mit \vhrulefill{x.xpt} lassen sich horizontale Striche mit variabler Dicke machen
  \def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

\usepackage{fancyhdr}
\fancyhf{}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}

\usepackage{csquotes}

\begin{document}

%\pagestyle{empty}
\setlength{\footskip}{20pt}

%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\section*{Response to Reviewers \\
Communications on Applied Mathematics and Computation
}	
%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\vspace{-5mm}
\vhrulefill{1pt}

\begin{flushright}
  Erik Burman, Janosch Preuss, Tim van Beeck\\[0.2cm]
  Department of Mathematics, \\
  University College London, United Kingdom \\[0.2cm]
  Inria Project-Team Makutu, \\
  Université de Pau et des Pays de l’Adour, France \\[0.2cm]
  Institute for Numerical and Applied Mathematics, \\
  Georg-August-Universit\"{a}t G{\"o}ttingen, Germany \\
\end{flushright}

\vspace{5mm}

Professor Chi-Wang Shu \\
Editor-in-Chief \\
Communications on Applied Mathematics and Computation

\vspace{5mm}
\hfill \today
\vspace{5mm}

Dear Professor Shu, \\

First of all, thank you for considering our article "Variational data assimilation for the wave equation in heterogeneous media: Numerical investigation of stability" for publication in \textit{Communications on Applied Mathematics and Computation}. We also thank the reviewers for their valuable comments and suggestions for improvement. Below, we address their points one after another. \\

%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\subsection*{Referee 1}	
%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------

\begin{enumerate}
  \item The Geometric Control Condition (GCC) was originally introduced in [8]. However, the
  manuscript does not clarify how GCC satisfaction is verified in the specific numerical
  simulations. For completeness, I recommend including a precise definition of the GCC.
  \item On page 7, could the authors clarify whether $\bm{Z}_h$ belongs to the space $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$?
  \item In the numerical experiments, what values are chosen for the parameters $k, q, k^{\ast}$ and
  $q^{\ast}$? The current description appears to only specify the value of $k$.
  \item How is the “best approximation” determined in the numerical experiments? Please
  explain the criteria or method used to obtain it.
  \item On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
  or at time 1? It seems to depict the solution at $T = 1.0$, where the approximation
  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be
  shown.
  \item In the two-dimensional case, only a square data domain is considered. A more inter-
  esting scenario would involve a curved interface, such as a circular interface. Could the
  authors provide related numerical results for such a case?
\end{enumerate}

\subsection*{Referee {2}}	
%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\begin{enumerate}
  \item How did you numerically verify Assumption 1? Specifically, how were the two
  inequalities in Assumption 1 verified?
  \item What is the relationship between the GCC and condition (1.3)? In the numerical
  tests in Section 4.1, you use condition (1.3) to imply the GCC. It appears that
  you have verified stability under a much stronger condition. I am wondering
  what would happen if you directly let the data satisfy the GCC, as you did in
  Section 4.2. Moreover, could you please explain why $T = 0.75$ was chosen in
  Section 4.2? Would a smaller $T$ work?
  \item Could you please explain why you adopted the discontinuous-in-time FEM
  method? What are the advantages of this method for the problem under consideration?
  \item Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.
  \item Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
  (1.3)?
  \item The authors are encouraged to provide a detailed proof of Lemma 3.3.
  \item What would happen if $c_1$ becomes larger?
  \item Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.
  \item Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.
\end{enumerate}

% \vspace{1cm}
Yours sincerely,\\
Erik Burman, Janosch Preuss, and Tim van Beeck

\end{document}

### 2025-11-26 tex/main.tex
Minor on revision

@@
 \end{lem}
-\begin{comment}
+
 \begin{proof}
-    First, note that $\tnorm{(0,\Yh)} = \Vert \Yh \Vert_{S_h^\ast}$. Using the Cauchy-Schwarz inequality, we obtain
+    \todo[inline]{TvB: Check if notation, etc., is still up-to-date}
+    First, note that $\tnorm{(0,\Yh)} = \Vert \Yh \Vert_{S_h^\ast}$. With the Cauchy-Schwarz inequality, we obtain
     \begin{equation*}
@@
     \end{align*}
-    Putting all estimates together, the claim follows. 
+    The claim follows from putting all estimates together.
 \end{proof}
-\end{comment}
 
@@
     \caption{On the left: We observe quasi-optimal convergence of $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ (solid) and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ (dashed) with contrast $c_1 = 2.5$ and polynomial degrees $k \in \{2,3\}$.
-On the right: We consider the ratio between these errors and the $L^2$-bestapproximation error for increasing contrast $c_1$.}
+On the right: We consider the ratio between these errors and the $L^2$-best approximation error for increasing contrast $c_1$.}
     \label{fig:2DjumpCoefs}

### 2025-11-26 review/response/letter.tex
Minor on revision
Notes on Review

@@
   simulations. For completeness, I recommend including a precise definition of the GCC.
+  \reply{\textbf{add a bit of detail, lightlike..., precise definition to technical...} @Janosch}
   \item On page 7, could the authors clarify whether $\bm{Z}_h$ belongs to the space $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$?
+  \reply{Indeed, it does belong to $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$. We have added this after the definition of the Lagrangian $\mathcal{L}$.}
   \item In the numerical experiments, what values are chosen for the parameters $k, q, k^{\ast}$ and
   $q^{\ast}$? The current description appears to only specify the value of $k$.
-  \item How is the “best approximation” determined in the numerical experiments? Please
-  explain the criteria or method used to obtain it.
+  \reply{\textbf{check scripts, @Tim}}
+  \item How is the “best approximation” determined in the numerical experiments? Please explain the criteria or method used to obtain it.
+  \reply{Clarify that we calculate the $L^2$-orthogonal projection onto the subspaces... @Tim}
   \item On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
   or at time 1? It seems to depict the solution at $T = 1.0$, where the approximation
-  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be
-  shown.
-  \item In the two-dimensional case, only a square data domain is considered. A more inter-
-  esting scenario would involve a curved interface, such as a circular interface. Could the
+  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be shown.
+  \reply{missunderstanding...}
+  \item In the two-dimensional case, only a square data domain is considered. A more interesting scenario would involve a curved interface, such as a circular interface. Could the
   authors provide related numerical results for such a case?
@@
   inequalities in Assumption 1 verified?
-  \item What is the relationship between the GCC and condition (1.3)? In the numerical
-  tests in Section 4.1, you use condition (1.3) to imply the GCC. It appears that
-  you have verified stability under a much stronger condition. I am wondering
-  what would happen if you directly let the data satisfy the GCC, as you did in
-  Section 4.2. Moreover, could you please explain why $T = 0.75$ was chosen in
+  \reply{We proved that the assumptions gives us convergence rates and check the convergence rates numerically..., refer to Remark 2, numerical method gives stability of the continuous problem}
+  \item What is the relationship between the GCC and condition (1.3)?
+In the numerical tests in Section 4.1, you use condition (1.3) to imply the GCC.
+It appears that you have verified stability under a much stronger condition.
+I am wondering what would happen if you directly let the data satisfy the GCC, as you did in Section 4.2.
+Moreover, could you please explain why $T = 0.75$ was chosen in
   Section 4.2? Would a smaller $T$ work?
+  \reply{In 1D: (1.3) is equivalent to the GCC... \textbf{2D not sure, think about this after modifications from Ref 1}}
   \item Could you please explain why you adopted the discontinuous-in-time FEM
   method? What are the advantages of this method for the problem under consideration?
+  \reply{@ Janosch}
   \item Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.
+  \reply{See above.}
   \item Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
   (1.3)?
+  \reply{it requires (1.3), we have added it in the beginning of Sec. 3.1}
   \item The authors are encouraged to provide a detailed proof of Lemma 3.3.
+  \reply{We added a proof of Lemma 3.3.} 
   \item What would happen if $c_1$ becomes larger?
+  \reply{becomes harder to solve, see conclusion and discussion in 4.2...}
   \item Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.
+  \reply{See above: Clarify that we calculate the $L^2$-orthogonal projection onto the subspaces... @Tim}
   \item Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.
+  \reply{We thank the review for spotting this typo. We have corrected it.}
 \end{enumerate}

### 2025-11-26 tex/main.tex
Notes on Review

@@
 
+\newcommand{\changed}[1]{{\color{blue!70!black} #1}}
+
 %%% TvB: Added for plots, some might be redundant ##
@@
 \end{align*}
-where $S_h$, $S_h^\ast$, and $\Sud$ are stabilization terms yet to be defined.
+\changed{for $\Uh \in \ProdFullyDiscrSpace{k}{q}, \Zh \in \ProdFullyDiscrSpace{k^\ast}{q^\ast}$}, where $S_h$, $S_h^\ast$, and $\Sud$ are stabilization terms yet to be defined.
 Note that the first and the second terms of $\cL_h$ incorporate the data and the PDE constraints, respectively.
@@
 \subsection{Inf-sup stability and continuity}\label{sec:analysis:infsup}
+\changed{In the following, we assume that \eqref{eq:Tcondition} is satisfied.}
 Let $\vert \cdot \vert_{S_h}, \vert \cdot \vert_{\uparrow \downarrow}$, and $\Vert \cdot \Vert_{S_h^{\ast}}$ be the (semi-)norms induced by the stabilizers $S_h$, $\Sud$, and $S_h^{\ast}$:
@@
     \todo[inline]{TvB: Check if notation, etc., is still up-to-date}
+    \changed{
     First, note that $\tnorm{(0,\Yh)} = \Vert \Yh \Vert_{S_h^\ast}$. With the Cauchy-Schwarz inequality, we obtain
@@
     \end{align*}
-    The claim follows from putting all estimates together.
+    The claim follows from putting all estimates together.}
 \end{proof}

### 2025-12-02 code/ngsolve/space_time.py
start with whispering gallery mode exmaple

@@ -1,0 +1,456 @@
+from ngsolve import *
+from xfem import *
+from xfem.lset_spacetime import *
+from ngsolve.comp import GlobalSpace
+solver = "pardiso"
+#solver = "umfpack"
+
+class quad_rule:
+
+    def __init__(self,name,npoints):
+        self.name = name
+        self.npoints = npoints
+
+        # available quadrature rules
+        gauss_lobatto = {
+            3: ( [ -1, 0, 1 ],
+                 [ 1/3, 4/3, 1/3 ] ),
+            4: ( [ -1, -sqrt(1/5), sqrt(1/5), 1],
+                 [ 1/6, 5/6, 5/6, 1/6 ] ),
+            5: ( [ -1, -(1/7)*sqrt(21),0.0, (1/7)*sqrt(21), 1.0 ],
+                 [ 1/10,49/90,32/45, 49/90, 1/10  ] ),
+            6: ( [ -1, -sqrt((1/21)*(7+2*sqrt(7))), -sqrt((1/21)*(7-2*sqrt(7))), sqrt((1/21)*(7-2*sqrt(7))), sqrt((1/21)*(7+2*sqrt(7))), 1.0 ],
+                 [ 1/15, (1/30)*(14-sqrt(7)), (1/30)*(14+sqrt(7)), (1/30)*(14+sqrt(7)), (1/30)*(14-sqrt(7)),  1/15 ] ),
+        }
+
+        if name == "Gauss-Lobatto":
+            self.points = gauss_lobatto[npoints][0]
+            self.weights = gauss_lobatto[npoints][1]
+
+    def current_pts(self,a,b):
+        if self.name == "Gauss-Lobatto":
+            return [0.5*(b-a) * pt + 0.5*(b+a)  for pt in self.points]
+    
+    def t_weights(self,delta_t):
+        if self.name == "Gauss-Lobatto":
+            return [0.5*delta_t*w for w in self.weights]
+
+def GetSpaceTimeFESpace(mesh,order_space,order_time,bc=".*",return_base=False):
+    V_space = H1(mesh, order=order_space, dirichlet=bc,dgjumps=True)
+    if return_base:
+        return V_space
+    tfe = ScalarTimeFE(order_time)
+    st_fes = tfe * V_space
+    return st_fes
+
+def LaplacianProxy(u,d):
+    return sum([ u.Operator("hesse")[i,i] for i in range(d)])
+
+
+class SpaceTimeMat(BaseMatrix):
+    
[…]

### 2025-12-02 code/ngsolve/whispering-gallery.py

@@ -1,0 +1,399 @@
+from netgen.meshing import *
+from netgen.csg import *
+from netgen.meshing import Mesh as netmesh
+from netgen.geom2d import SplineGeometry
+from ngsolve.TensorProductTools import MeshingParameters
+from ngsolve import *
+from ngsolve.solvers import GMRes
+from xfem import *
+from xfem.lset_spacetime import *
+import numpy as np
+from ngsolve import Mesh as NGSMesh
+from scipy.sparse import csr_matrix
+import scipy.sparse.linalg
+import matplotlib.pyplot as plt
+from math import pi 
+import sys
+sys.path.append("/home/janosch/projects/waveUC_discCoefs/code/ngsolve")
+from space_time import space_time, SpaceTimeMat
+
+
+
+tol = 1e-7 #GMRes
+R0 = 0.25
+R1 = 1.0 
+R2 = sqrt(2)  
+#R1_neg = 0.8
+R1_neg = 0.8
+R1_pos = 1.1*R1 
+Rmid = R1 + 0.5*(R2-R1) 
+n_mode = 50
+#n_mode = 40
+order_ODE = 1
+#order_ODE = 4
+
+c_minus = 1 
+c_pos = 2.5 
+maxh = 0.05
+bonus_intorder = 8
+order = 1 
+
+
+def get_order(order_global):
+    
+    k = order_global
+    kstar = 1
+    q = order_global
+    if order_global == 1:
+        qstar = 1
+    else:
+        qstar = 0
+
+    return q,k,qstar,kstar
+
+
+
+def Make1DMesh_givenpts(mesh_r_pts):
+
+    mesh_1D = netmesh(dim=1)
+    pids = []
+    for r_coord in mesh_r_pts:
+        pids.append (mesh_1D.Add (MeshPoint(Pnt(r_coord, 0, 0))))
+    n_mesh = len(pids)-1
+    for i in range(n_mesh):
+        mesh_1D.Add(Element1D([pids[i],pids[i+1]],index=1))
+    mesh_1D.Add (Element0D( pids[0], index=1))
+    mesh_1D.Add (Element0D( pids[n_mesh], index=2))
+    mesh_1D.SetBCName(0,"left")
+    mesh_1D.SetBCName(1,"right")
+    mesh_1D = NGSMesh(mesh_1D)
+    return mesh_1D
+
[…]

### 2025-12-03 code/ngsolve/space_time.py
add well-posed option

@@ -68,7 +68,8 @@ class SpaceTimeMat(BaseMatrix):
 
 
 class space_time:
-    def __init__(self,q,qstar,k,kstar,N,T,delta_t,mesh,stabs,t_slice,u_exact_slice,ut_exact_slice,tstart=None,told=None,perturbations=None, bonus_intorder_error = 5, shift=None):
+    def __init__(self,q,qstar,k,kstar,N,T,delta_t,mesh,stabs,t_slice,u_exact_slice,ut_exact_slice,tstart=None,told=None,perturbations=None, bonus_intorder_error = 5, shift=None, 
+            well_posed=False ):
         self.q = q 
         self.qstar = qstar
         self.k = k 
@@ -77,6 +78,7 @@ class space_time:
         self.time_order = 2*max(q,qstar)
         self.tstart = tstart
         self.tend = T 
+        self.well_posed = well_posed
         #if not tstart:
         #    self.tstart = -self.tend 
         self.mesh = mesh
@@ -190,16 +192,16 @@ class space_time:
         a += self.stabs["primal"] * self.h**2 * InnerProduct(  self.dt(u2) - LaplacianProxy(u1,self.mesh.dim) , self.dt(w2) - LaplacianProxy(w1,self.mesh.dim) ) * self.dxt
         a += self.stabs["primal"] * InnerProduct( u2 - self.dt(u1) , w2 - self.dt(w1) ) * self.dxt
         a += self.stabs["Tikh"] * self.h**(2*min(self.q,self.k)) *  u1 *  w1 * self.dxt
-
+        # boundary term
         a +=  (40/self.h) * u1 * w1 * self.dst
-
 
         # A[U_h,Y_h]
         a += self.dt(u2) * y1 * self.dxt  
         a += grad(u1) * grad(y1) * self.dxt
         a += (self.dt(u1) - u2) * y2 * self.dxt
         a += (-1) * grad(u1) * self.nF * y1 * self.dst_outer
-        a +=  grad(u1) * self.nF * y1 * self.dst_inner
+        a +=  grad(u1) * self.nF * y1 * self.dst_inner 
+           
 
         # S*(Y_h,Z_h)
         a += self.stabs["dual"] *  (-1)* y1 * z1 * self.dxt  
@@ -262,6 +264,11 @@ class space_time:
         for n in range(self.N):
             f +=  self.stabs["data"] * self.u_exact_slice[n] * w1[n] * self.dxt_omega
[…]

### 2025-12-03 code/ngsolve/whispering-gallery.py

@@ -34,10 +34,11 @@ order_ODE = 1
 
 c_minus = 1 
 c_pos = 2.5 
-maxh = 0.05
+maxh = 0.0625
+print("maxh = ", maxh) 
 bonus_intorder = 8
 order = 1 
-
+well_posed = True 
 
 def get_order(order_global):
     
@@ -221,7 +222,8 @@ rho_cleanB = BSpline(spline_order,rs, c_clean )(r)
 #eval_c[-1] = cBB(rS[::-1][-1]-1e-11)
 #eval_rho = [rhoBB(pp) for pp in rS[::-1]]
 
-mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=True ) 
+#mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=True ) 
+mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=False ) 
 Draw(mesh)
 Draw(rho_cleanB, mesh, 'cr')  
 
@@ -296,7 +298,7 @@ def SolveProblem( order_global, lami, wp_mode_space ):
     q,k,qstar,kstar = get_order(order_global)
     time_order = 2*max(q,qstar)
 
-    N = 15
+    N = 32
     tstart = 0.0
     tend = 2.0
     delta_t = tend / N
@@ -317,7 +319,8 @@ def SolveProblem( order_global, lami, wp_mode_space ):
     
 
     st = space_time(q=q,qstar=qstar,k=k,kstar=kstar,N=N,T=tend,delta_t=delta_t,mesh=mesh,stabs=stabs,
-                    t_slice=t_slice, u_exact_slice=u_exact_slice, ut_exact_slice=ut_exact_slice, tstart=tstart, told=told) 
+                    t_slice=t_slice, u_exact_slice=u_exact_slice, ut_exact_slice=ut_exact_slice, tstart=tstart, 
+                    told=told, well_posed = well_posed ) 
 
     st.SetupSpaceTimeFEs()
     st.SetupRightHandSide()
@@ -396,4 +399,11 @@ if True:
  
         result = SolveProblem(order_global, lami, wp_mode_space )
         
+
+# smooth sol as data, no jump
+# N = [8,16,32, 64 ] 
+# maxh = [0.25,0.125, 0.0625, 0.03125  ]
+# l2_errors = [0.4750260066626608, 0.09060563861975547, 0.014688240968942253 ] 
+# with well_posed = True 
[…]

### 2025-12-03 code/ngsolve/space_time.py
add the jumping soundspeed into the class

@@ -69,7 +69,7 @@ class SpaceTimeMat(BaseMatrix):
 
 class space_time:
     def __init__(self,q,qstar,k,kstar,N,T,delta_t,mesh,stabs,t_slice,u_exact_slice,ut_exact_slice,tstart=None,told=None,perturbations=None, bonus_intorder_error = 5, shift=None, 
-            well_posed=False ):
+            well_posed=False, c_squared =  1.0 ):
         self.q = q 
         self.qstar = qstar
         self.k = k 
@@ -79,6 +79,7 @@ class space_time:
         self.tstart = tstart
         self.tend = T 
         self.well_posed = well_posed
+        self.c_squared = c_squared 
         #if not tstart:
         #    self.tstart = -self.tend 
         self.mesh = mesh
@@ -178,18 +179,20 @@ class space_time:
         w1,w2,y1,y2 = self.X_slab.TestFunction()
     
         a += self.dt(w2) * z1 * self.dxt  
-        a += grad(w1) * grad(z1) * self.dxt
+        a += self.c_squared * grad(w1) * grad(z1) * self.dxt
         a += (self.dt(w1) - w2) * z2 * self.dxt
-        a += (-1) * grad(w1) * self.nF * z1 * self.dst_outer
-        a +=  grad(w1) * self.nF * z1 * self.dst_inner
-
+        a += (-1) * self.c_squared *  grad(w1) * self.nF * z1 * self.dst_outer
+        a += self.c_squared * grad(w1) * self.nF * z1 * self.dst_inner
+        
 
         # (u_1,w_1)_omega
         a += self.stabs["data"] * u1 * w1 * self.dxt_omega 
 
         # S(U_h,W_h) 
-        a += self.stabs["primal"] * self.h * InnerProduct( ( grad(u1) - grad(u1).Other()) * self.nF , ( grad(w1) - grad(w1).Other()) * self.nF ) * self.dxtF
-        a += self.stabs["primal"] * self.h**2 * InnerProduct(  self.dt(u2) - LaplacianProxy(u1,self.mesh.dim) , self.dt(w2) - LaplacianProxy(w1,self.mesh.dim) ) * self.dxt
+        a += self.stabs["primal"] * self.h * InnerProduct( ( self.c_squared * grad(u1) -  self.c_squared.Other() * grad(u1).Other()) * self.nF ,
[…]

### 2025-12-03 code/ngsolve/whispering-gallery.py

@@ -249,8 +249,14 @@ Draw(wp_mode_space , mesh, 'wp-mode')
 
 domain_values = {'B': c_minus,  'IF-inner': c_minus,  'IF-outer': c_pos, 'void' : c_pos,  'omega-outer' : c_pos  }
 #domain_values = {'inner': 3.7,  'outer': 1}
+
+
 c_disc = mesh.MaterialCF(domain_values)
+#help(c_disc)
 Draw(c_disc, mesh, 'cdisk')
+
+domain_values_2 = { 'B': 1.0,  'IF-inner': 1.0,  'IF-outer': 1.0, 'void' : 1.0,  'omega-outer' : 1.0 }
+c_squared = mesh.MaterialCF(domain_values_2)
 
 
 def CheckSpatial(c_disc,lami, wp_mode_space,mesh): 
@@ -290,7 +296,7 @@ stabs = {"data": 1e4,
          "primal": 1e-4,
          "primal-jump":1e1,
          "primal-jump-displ-grad":1e1,
-         "Tikh": 1e-5
+         "Tikh": 1e-18
         }
 
 def SolveProblem( order_global, lami, wp_mode_space ):
@@ -320,7 +326,7 @@ def SolveProblem( order_global, lami, wp_mode_space ):
 
     st = space_time(q=q,qstar=qstar,k=k,kstar=kstar,N=N,T=tend,delta_t=delta_t,mesh=mesh,stabs=stabs,
                     t_slice=t_slice, u_exact_slice=u_exact_slice, ut_exact_slice=ut_exact_slice, tstart=tstart, 
-                    told=told, well_posed = well_posed ) 
+                    told=told, well_posed = well_posed, c_squared = c_squared) 
 
     st.SetupSpaceTimeFEs()
     st.SetupRightHandSide()

### 2025-12-04 review/response/letter.tex
Minors for the review

@@
   $q^{\ast}$? The current description appears to only specify the value of $k$.
-  \reply{\textbf{check scripts, @Tim}}
+  \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments. \textbf{@ Janosch, why do we choose them that way?}}
   \item How is the “best approximation” determined in the numerical experiments? Please explain the criteria or method used to obtain it.
-  \reply{Clarify that we calculate the $L^2$-orthogonal projection onto the subspaces... @Tim}
+  \reply{In the numerical experiments, we compare the approximation error of our method with the $L^2$-best approximation error, i.e.
+we calculate the $L^2$-orthogonal projection of the exact solution onto the discrete space.
+We have added a footnote.}
   \item On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
@@
   matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be shown.
-  \reply{missunderstanding...}
+  \reply{We compute the approximation twice, once with final time $T = 0.5$ and once with final time $T = 1.0$, but compare it for both cases at $t = 0.5$.
+The figure illustrates that the approximation is not reliable if the final time is not large enough to satisfy the GCC.
+We have slightly adjusted the text and the figure to avoid any misunderstandings.}
   \item In the two-dimensional case, only a square data domain is considered. A more interesting scenario would involve a curved interface, such as a circular interface. Could the
@@
   \item Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.
-  \reply{See above.}
+  \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments.}
   \item Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
   (1.3)?
-  \reply{it requires (1.3), we have added it in the beginning of Sec. 3.1}
+  \reply{It requires (1.3), which is required for unique solvability anyway. We have added a short sentence in the beginning of Sec. 3.1 that we assume (1.3) to be satisfied.}
   \item The authors are encouraged to provide a detailed proof of Lemma 3.3.
@@
   \item Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.
-  \reply{See above: Clarify that we calculate the $L^2$-orthogonal projection onto the subspaces... @Tim}
+  \reply{We have added a footnote (see above, point 4.).}
   \item Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.

### 2025-12-07 code/ngsolve/space_time.py
fix Nitsche terms

@@ -108,7 +108,9 @@ class space_time:
         
         self.dmesh = dmesh(self.mesh)
         #self.dst = self.delta_t * dxtref(self.mesh, time_order=self.time_order,skeleton=True, vb=BND)
+        #self.dst_outer  = self.dst 
         self.dst = self.delta_t * dxtref(self.mesh, time_order=self.time_order,skeleton=True, definedon=mesh.Boundaries("R0|R2"))
+        #self.dst = self.delta_t * dxtref(self.mesh, time_order=self.time_order,skeleton=True, definedon=mesh.Boundaries("R2"))
         self.dst_inner = self.delta_t * dxtref(self.mesh, time_order=self.time_order,skeleton=True, definedon=mesh.Boundaries("R0"))
         self.dst_outer = self.delta_t * dxtref(self.mesh, time_order=self.time_order,skeleton=True, definedon=mesh.Boundaries("R2"))
 
@@ -182,7 +184,10 @@ class space_time:
         a += self.c_squared * grad(w1) * grad(z1) * self.dxt
         a += (self.dt(w1) - w2) * z2 * self.dxt
         a += (-1) * self.c_squared *  grad(w1) * self.nF * z1 * self.dst_outer
-        a += self.c_squared * grad(w1) * self.nF * z1 * self.dst_inner
+        a +=  self.c_squared * grad(w1) * self.nF * z1 * self.dst_inner
+
+        a += (40/self.h) * w1 * z1 * self.dst
+    
         
 
         # (u_1,w_1)_omega
@@ -203,8 +208,10 @@ class space_time:
         a += self.c_squared * grad(u1) * grad(y1) * self.dxt
         a += (self.dt(u1) - u2) * y2 * self.dxt
         a += (-1) * self.c_squared * grad(u1) * self.nF * y1 * self.dst_outer
-        a += self.c_squared *  grad(u1) * self.nF * y1 * self.dst_inner 
-           
+        a +=  self.c_squared *  grad(u1) * self.nF * y1 * self.dst_inner 
+
+        a += (40/self.h) * u1 * y1 * self.dst
+
 
         # S*(Y_h,Z_h)
         a += self.stabs["dual"] *  (-1)* y1 * z1 * self.dxt  
@@ -267,11 +274,14 @@ class space_time:
         f = LinearForm(self.X)
         for n in range(self.N):
             f +=  self.stabs["data"] * self.u_exact_slice[n] * w1[n] * self.dxt_omega
[…]

### 2025-12-07 code/ngsolve/whispering-gallery.py

@@ -34,7 +34,7 @@ order_ODE = 1
 
 c_minus = 1 
 c_pos = 2.5 
-maxh = 0.0625
+maxh = 0.25 
 print("maxh = ", maxh) 
 bonus_intorder = 8
 order = 1 
@@ -99,6 +99,29 @@ def CreateAnnulusMesh(maxh=0.4,order_geom=5,domain_maxh=0.03,extra_refinement=Fa
     mesh = NGSMesh(geo.GenerateMesh (maxh=maxh,quad_dominated=False))
     mesh.Curve(order_geom)
     return mesh
+
+
+
+def CreateAnnulusMesh2(maxh=0.4,order_geom=1,domain_maxh=0.03,extra_refinement=False):
+    
+    geo = SplineGeometry()
+    geo.AddCircle( (0,0), R0, leftdomain=0, rightdomain=1,bc="R0")
+
+    #geo.AddCircle( (0,0), 1.0, leftdomain=1, rightdomain=2,bc="R1")
+    
+    #geo.AddCircle( (0,0), R2, leftdomain=2, rightdomain=0,bc="R2")
+
+    #geo.SetMaterial(1, "B")
+    #geo.SetMaterial(2, "IF-inner")
+    #geo.SetMaterial(3, "omega-outer")
+  
+    geo.AddCircle( (0,0), R2, leftdomain=1, rightdomain=0,bc="R2")
+   
+    mesh = NGSMesh(geo.GenerateMesh (maxh=maxh,quad_dominated=False))
+    mesh.Curve(order_geom)
+    return mesh
+
+
 
 
 
@@ -223,7 +246,8 @@ rho_cleanB = BSpline(spline_order,rs, c_clean )(r)
 #eval_rho = [rhoBB(pp) for pp in rS[::-1]]
 
 #mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=True ) 
-mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=False ) 
+mesh = CreateAnnulusMesh(maxh=maxh, extra_refinement=True ) 
+
 Draw(mesh)
 Draw(rho_cleanB, mesh, 'cr')  
 
@@ -291,7 +315,8 @@ def CheckSpatial(c_disc,lami, wp_mode_space,mesh):
 
 #l2_errors = [ 0.23088207463877092, 0.06298057321067921]
 
-stabs = {"data": 1e4,
+stabs = {#"data": 1e4,
[…]

### 2025-12-07 tex/main.tex

@@
 Unless specified otherwise, we choose the time step as $\Delta t = h$.
+\changed{Further, we set $q = k$ and choose $k^{\ast} = 1$, $q^{\ast} = 1$ if $k = 1$ and $q^{\ast} = 0$ if $k > 1$.}
 
@@
 In \Cref{fig:jumpCoefs:contrast:2.5}, we observe that the errors $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with optimal order $\mathcal{O}(h^k)$ for $T = 0.5 > 0.35$.
-However, if $T = 0.1 < 0.35$, the order of convergence degrades, while the respective best approximation errors still converge with optimal order.
+However, if $T = 0.1 < 0.35$, the order of convergence degrades, while the respective $L^2$-best approximation\textsuperscript{3}\footnotemark \footnotetext{\textsuperscript{3}\changed{We compare with the $L^2$-best approximation error, where we solve for the $L^2$-orthogonal projection of the exact solution onto the discrete space, as a measure of the approximation quality of the discrete space.}} errors still converge with optimal order.
 This suggests that the GCC seems to imply Lipschitz stability even in the heterogeneous case, and therefore \cref{assum:LipschitzStability} is indeed justified.
@@
 \Cref{fig:jumpCoefs:multipleJumps:noGCC} compares the results for polynomial degree $k = 3$ on the refinement level $L = 4$ with a fixed time step $\Delta t = 1/32$, for two final times $T = 0.5$ and $T = 1.0$.
+\changed{We compare the approximation of the exact solution for both final times at time $t = 0.5$}.
 For both contrasts, the approximate solution matches the exact solution well if the GCC is fulfilled ($T = 1.0$), but shows significant deviations when it is not ($T = 0.5$). 
@@
     \end{center}
-    \caption{For fixed time step $\Delta t = 1/32$, refinement level $L = 4$, and polynomial degree $k = 3$, we compare the exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution computed with $T = 1.0$ and $T = 0.5$ at time $t = 0.5$.
+    \caption{For fixed time step $\Delta t = 1/32$, refinement level $L = 4$, and polynomial degree $k = 3$, we compare the exact solution \eqref{eq:1D:exact:simpleMult} and approximated solution computed with \changed{final time} $T = 1.0$ and $T = 0.5$ at time $t = 0.5$.
 We set $c_2 = 1.0$ and consider the cases $c_1 = c_3 = 2.5$, $n = 1$ (left) and $c_1 = c_3 = 7.5$, $n = 3$ (right).}
@@
 As before, we fix the wave speed $c_2 = 1$ and consider different values for $c_1$ to control the contrast.
+\changed{Further, we choose the parameters $q = k^{\ast} = q^{\ast} = k$.}
 
@@
 With contrast $c_1 = 2.5$, we observe quasi-optimal convergence with order  $\mathcal{O}(h^k)$ for polynomial degrees $k \in \{2,3\}$ for the errors $\Vert \dt(u-L_{\Delta t} \ul_1) \Vert_{L^2(0,T;L^2(\Omega))}$ and $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$.
-Similar as already observed in the one-dimensional case in \cref{fig:jumpCoefs:increasingcontrast}, we observe that these errors are more sensitive to increasing contrast $c_1$ than the corresponding best approximation errors.
+Similar as already observed in the one-dimensional case in \cref{fig:jumpCoefs:increasingcontrast}, we observe that these errors are more sensitive to increasing contrast $c_1$ than the corresponding $L^2$-best approximation errors.
 In particular, the ratio for $\Vert u-L_{\Delta t} \ul_1 \Vert_{L^\infty(0,T;L^2(\Omega))}$ with $k=2$ appears to grow as $\mathcal{O}(c_1^{3/2})$, which renders it very demanding to maintain a reasonable accuracy as the contrast increases.

### 2025-12-07 code/ngsolve/space_time.py
save scaling with c in jump term

@@ -185,9 +185,7 @@ class space_time:
         a += (self.dt(w1) - w2) * z2 * self.dxt
         a += (-1) * self.c_squared *  grad(w1) * self.nF * z1 * self.dst_outer
         a +=  self.c_squared * grad(w1) * self.nF * z1 * self.dst_inner
-
         a += (40/self.h) * w1 * z1 * self.dst
-    
         
 
         # (u_1,w_1)_omega
@@ -209,7 +207,6 @@ class space_time:
         a += (self.dt(u1) - u2) * y2 * self.dxt
         a += (-1) * self.c_squared * grad(u1) * self.nF * y1 * self.dst_outer
         a +=  self.c_squared *  grad(u1) * self.nF * y1 * self.dst_inner 
-
         a += (40/self.h) * u1 * y1 * self.dst
 
 
@@ -259,6 +256,8 @@ class space_time:
         m += self.stabs["primal-jump"] * (1/self.delta_t) * InnerProduct( u2[1] - u2[0], w2[1] - w2[0]) * self.dmesh
         m += self.stabs["primal-jump-displ-grad"] * self.delta_t * InnerProduct( self.c_squared * (grad(u1[1]) - grad(u1[0]) )
                 ,  self.c_squared * ( grad(w1[1]) - grad(w1[0]) ) ) * self.dmesh
+
+
 
     def SetupScaledMassMatrixBetweenSlices(self,m): 
         u1,u2 = self.V_space2.TrialFunction() 
@@ -370,7 +369,7 @@ class space_time:
         u1s,u2s,z1s,z2s = self.X_slab.TrialFunction()
         w1s,w2s,y1s,y2s = self.X_slab.TestFunction()
         a_general_slab += self.stabs["primal-jump"] * (1/self.delta_t)  * u1s * w1s * dmesh(self.mesh, tref=0)  
-        a_general_slab += self.stabs["primal-jump-displ-grad"] * self.delta_t * self.c_squared * grad(u1s) * grad(w1s) * dmesh(self.mesh, tref=0)  
+        a_general_slab += self.stabs["primal-jump-displ-grad"] * self.delta_t * self.c_squared * grad(u1s) * self.c_squared * grad(w1s) * dmesh(self.mesh, tref=0)  
         a_general_slab += self.stabs["primal-jump"] * (1/self.delta_t)  * u2s * w2s * dmesh(self.mesh, tref=0)  
         a_general_slab.Assemble() 
         self.a_general_slab = a_general_slab

### 2025-12-08 review/response/letter.tex
Minor on review

@@
 \begin{enumerate}
-  \item The Geometric Control Condition (GCC) was originally introduced in [8]. However, the
+  \item \emph{The Geometric Control Condition (GCC) was originally introduced in [8]. However, the
   manuscript does not clarify how GCC satisfaction is verified in the specific numerical
-  simulations. For completeness, I recommend including a precise definition of the GCC.
+  simulations. For completeness, I recommend including a precise definition of the GCC.}
   \reply{\textbf{add a bit of detail, lightlike..., precise definition to technical...} @Janosch}
-  \item On page 7, could the authors clarify whether $\bm{Z}_h$ belongs to the space $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$?
+  \item \emph{On page 7, could the authors clarify whether $\bm{Z}_h$ belongs to the space $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$?}
   \reply{Indeed, it does belong to $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$. We have added this after the definition of the Lagrangian $\mathcal{L}$.}
-  \item In the numerical experiments, what values are chosen for the parameters $k, q, k^{\ast}$ and
-  $q^{\ast}$? The current description appears to only specify the value of $k$.
+  \item \emph{In the numerical experiments, what values are chosen for the parameters $k, q, k^{\ast}$ and
+  $q^{\ast}$? The current description appears to only specify the value of $k$.}
   \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments. \textbf{@ Janosch, why do we choose them that way?}}
-  \item How is the “best approximation” determined in the numerical experiments? Please explain the criteria or method used to obtain it.
+  \item \emph{How is the “best approximation” determined in the numerical experiments? Please explain the criteria or method used to obtain it.}
   \reply{In the numerical experiments, we compare the approximation error of our method with the $L^2$-best approximation error, i.e.
@@
 We have added a footnote.}
-  \item On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
+  \item \emph{On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
   or at time 1? It seems to depict the solution at $T = 1.0$, where the approximation
-  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be shown.
+  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be shown.}
   \reply{We compute the approximation twice, once with final time $T = 0.5$ and once with final time $T = 1.0$, but compare it for both cases at $t = 0.5$.
@@
 We have slightly adjusted the text and the figure to avoid any misunderstandings.}
-  \item In the two-dimensional case, only a square data domain is considered. A more interesting scenario would involve a curved interface, such as a circular interface. Could the
-  authors provide related numerical results for such a case?
+  \item \emph{In the two-dimensional case, only a square data domain is considered. A more interesting scenario would involve a curved interface, such as a circular interface. Could the
+  authors provide related numerical results for such a case?}
 \end{enumerate}
@@
 \begin{enumerate}
-  \item How did you numerically verify Assumption 1? Specifically, how were the two
-  inequalities in Assumption 1 verified?
-  \reply{We proved that the assumptions gives us convergence rates and check the convergence rates numerically..., refer to Remark 2, numerical method gives stability of the continuous problem}
-  \item What is the relationship between the GCC and condition (1.3)?
+  \item \emph{How did you numerically verify Assumption 1? Specifically, how were the two
+  inequalities in Assumption 1 verified?}
+  \reply{We do not verify Assumption 1 numerically.
+The takeaway from the analysis presented in the article is that we expect our numerical method to exhibit the same stability as the continuous problem.
+Therefore, we check whether the assumption of the GCC grants good convergence rates.
+We refer to the last paragraphs of the introduction and also Remark 2.}
+  \item \emph{What is the relationship between the GCC and condition (1.3)?
 In the numerical tests in Section 4.1, you use condition (1.3) to imply the GCC.
@@
 Moreover, could you please explain why $T = 0.75$ was chosen in
-  Section 4.2? Would a smaller $T$ work?
-  \reply{In 1D: (1.3) is equivalent to the GCC... \textbf{2D not sure, think about this after modifications from Ref 1}}
-  \item Could you please explain why you adopted the discontinuous-in-time FEM
-  method? What are the advantages of this method for the problem under consideration?
+  Section 4.2? Would a smaller $T$ work?}
+  \reply{In general, the GCC is a stronger assumption than (1.3), because (1.3) only grants unique solvability, but stability can be (very) poor.
+The GCC ensures better stability.
+In the 1D case, however, both conditions are equivalent ((1.3) implies the GCC in 1D) and thus, we can focus on (1.3) for the 1D experiments.
+We have added a sentence in the article to point that out.}
+  \reply{\textbf{2D not sure, think about this after modifications from Ref 1}}
+  \item \emph{Could you please explain why you adopted the discontinuous-in-time FEM
+  method? What are the advantages of this method for the problem under consideration?}
   \reply{@ Janosch}
-  \item Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.
+  \item \emph{Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.}
   \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments.}
-  \item Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
-  (1.3)?
+  \item \emph{Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
+  (1.3)?}
   \reply{It requires (1.3), which is required for unique solvability anyway. We have added a short sentence in the beginning of Sec. 3.1 that we assume (1.3) to be satisfied.}
-  \item The authors are encouraged to provide a detailed proof of Lemma 3.3.
+  \item \emph{The authors are encouraged to provide a detailed proof of Lemma 3.3.}
   \reply{We added a proof of Lemma 3.3.} 
-  \item What would happen if $c_1$ becomes larger?
-  \reply{becomes harder to solve, see conclusion and discussion in 4.2...}
-  \item Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.
+  \item \emph{What would happen if $c_1$ becomes larger?}
+  \reply{We observe that the larger the contrast, the harder the problem is to resolve numerically.
+We point that out in the conclusion and the discussion in Section 4.2.
+The conclusion that the GCC seems to imply Lipschitz stability does not change for higher contrasts.}
+  \item \emph{Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.}
   \reply{We have added a footnote (see above, point 4.).}
-  \item Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.
+  \item \emph{Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.}
   \reply{We thank the review for spotting this typo. We have corrected it.}
